### 2021-10-14 ABCD_Prelim_Analyses.Rmd
Preliminary ABCD Analyses
These are the very preliminary analyses done *PRIOR* to harmonizing inclusion/exclusion criteria with the UMinn team.

---
title: "ABCD_Prelim_Analyses"
output: html_document
---

# Load data
```{r cars}
var_exp <- read.csv("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/variance_exp_by_subj.csv")
nihtb<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/NihTB/abcd_tbss01.txt",header=TRUE)
nihtb.baseline<-nihtb[nihtb$eventname=="baseline_year_1_arm_1",]
merged.data1 <- merge(var_exp,nihtb.baseline,by="subjectkey")
lmt<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/Thomp/lmtp201.txt",header=TRUE)
lmt.baseline<-lmt[lmt$eventname=="baseline_year_1_arm_1",]
merged.data2 <- merge(merged.data1,lmt.baseline[, c("subjectkey", setdiff(colnames(lmt.baseline),colnames(merged.data1)))],by="subjectkey")
ravlt<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/Thomp/abcd_ps01.txt",header=TRUE)
ravlt.baseline<-ravlt[ravlt$eventname=="baseline_year_1_arm_1",]
merged.data3 <- merge(merged.data2,ravlt.baseline[, c("subjectkey", setdiff(colnames(ravlt.baseline),colnames(merged.data2)))],by="subjectkey")
trauma<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/Strife/abcd_ptsd01.txt",header=TRUE)
trauma.baseline<-trauma[trauma$eventname=="baseline_year_1_arm_1",]
combined.data <- merge(merged.data3,trauma.baseline[, c("subjectkey", setdiff(colnames(trauma.baseline),colnames(merged.data3)))],by="subjectkey")
```

# Coerce data types
```{r}
combined.data$nihtbx_flanker_uncorrected <- as.numeric(combined.data$nihtbx_flanker_uncorrected)
combined.data$nihtbx_picvocab_uncorrected <- as.numeric(combined.data$nihtbx_picvocab_uncorrected)
combined.data$nihtbx_list_uncorrected <- as.numeric(combined.data$nihtbx_list_uncorrected)
combined.data$nihtbx_pattern_uncorrected <- as.numeric(combined.data$nihtbx_pattern_uncorrected)
combined.data$nihtbx_cardsort_uncorrected <- as.numeric(combined.data$nihtbx_cardsort_uncorrected)
combined.data$nihtbx_picture_uncorrected <- as.numeric(combined.data$nihtbx_picture_uncorrected)
combined.data$nihtbx_reading_uncorrected <- as.numeric(combined.data$nihtbx_reading_uncorrected)
combined.data$lmt_scr_perc_correct <- as.numeric(combined.data$lmt_scr_perc_correct)
combined.data$pea_ravlt_sd_trial_i_tc <- as.numeric(combined.data$pea_ravlt_sd_trial_i_tc)
combined.data$pea_ravlt_sd_trial_ii_tc <- as.numeric(combined.data$pea_ravlt_sd_trial_ii_tc)
combined.data$pea_ravlt_sd_trial_iii_tc <- as.numeric(combined.data$pea_ravlt_sd_trial_iii_tc)
combined.data$pea_ravlt_sd_trial_iv_tc <- as.numeric(combined.data$pea_ravlt_sd_trial_iv_tc)
combined.data$pea_ravlt_sd_trial_v_tc <- as.numeric(combined.data$pea_ravlt_sd_trial_v_tc)
combined.data$interview_age <- as.numeric(combined.data$interview_age)

ind_pea_ravlt = c(which(names(combined.data)=="pea_ravlt_sd_trial_i_tc"),which(names(combined.data)=="pea_ravlt_sd_trial_ii_tc"),
	which(names(combined.data)=="pea_ravlt_sd_trial_iii_tc"),which(names(combined.data)=="pea_ravlt_sd_trial_iv_tc"),
	which(names(combined.data)=="pea_ravlt_sd_trial_v_tc")); names(combined.data)[ind_pea_ravlt]; summary(combined.data[,ind_pea_ravlt])
combined.data$pea_ravlt_ld = apply(combined.data[,ind_pea_ravlt],1,sum)

combined.data$pea_ravlt_ld <- as.numeric(combined.data$pea_ravlt_ld)

# Rename according to Thompson 2018 code
names(combined.data)[which(names(combined.data)=="nihtbx_picvocab_uncorrected")] = "PicVocab"
names(combined.data)[which(names(combined.data)=="nihtbx_flanker_uncorrected")] = "Flanker"
names(combined.data)[which(names(combined.data)=="nihtbx_list_uncorrected")] = "List"
names(combined.data)[which(names(combined.data)=="nihtbx_cardsort_uncorrected")] = "CardSort"
names(combined.data)[which(names(combined.data)=="nihtbx_pattern_uncorrected")] = "Pattern"
names(combined.data)[which(names(combined.data)=="nihtbx_picture_uncorrected")] = "Picture"
names(combined.data)[which(names(combined.data)=="nihtbx_reading_uncorrected")] = "Reading"
names(combined.data)[which(names(combined.data)=="pea_ravlt_ld")] = "RAVLT"
names(combined.data)[which(names(combined.data)=="lmt_scr_perc_correct")] = "LMT"
```

# Calculate Thompson factor scores
```{r}
combined.data$thompson_PC1 <- (0.754*combined.data$PicVocab)+(0.213*combined.data$Flanker)+(0.471*combined.data$List)+(0.205*combined.data$CardSort)+(0.015*combined.data$Pattern)+(0.012*combined.data$Picture)+(0.82*combined.data$Reading)+(0.306*combined.data$RAVLT)+(0.5*combined.data$LMT)

combined.data$thompson_PC2 <- (0.065*combined.data$PicVocab)+(0.712*combined.data$Flanker)+(0.148*combined.data$List)+(0.71*combined.data$CardSort)+(0.813*combined.data$Pattern)+(0.135*combined.data$Picture)+(0.12*combined.data$Reading)+(0.125*combined.data$RAVLT)+(0.299*combined.data$LMT)

combined.data$thompson_PC3 <- (0.19*combined.data$PicVocab)+(0.067*combined.data$Flanker)+(0.493*combined.data$List)+(0.232*combined.data$CardSort)+(0.085*combined.data$Pattern)+(0.863*combined.data$Picture)+(0.122*combined.data$Reading)+(0.712*combined.data$RAVLT)+(0.068*combined.data$LMT)
```

# Compare variance explained to Thompson factor scores
```{r}
summary(lm(varexp~interview_age+sex+thompson_PC1+thompson_PC2+thompson_PC3,data=combined.data))
model1<-lm(thompson_PC2~interview_age+sex,data=combined.data)
model2<-lm(thompson_PC2~interview_age+sex+varexp,data=combined.data)
anova(model1,model2,test = "Chisq")
```

# Compare variance explained to Trauma types
```{r}
combined.data[,225:241]<-as.numeric(unlist(combined.data[,225:241]))
combined.data$ACEsTotal <- rowSums(combined.data[,c("ksads_ptsd_raw_754_p","ksads_ptsd_raw_755_p","ksads_ptsd_raw_756_p","ksads_ptsd_raw_757_p","ksads_ptsd_raw_758_p","ksads_ptsd_raw_759_p","ksads_ptsd_raw_760_p","ksads_ptsd_raw_761_p","ksads_ptsd_raw_762_p","ksads_ptsd_raw_763_p","ksads_ptsd_raw_764_p","ksads_ptsd_raw_765_p","ksads_ptsd_raw_766_p","ksads_ptsd_raw_767_p","ksads_ptsd_raw_768_p","ksads_ptsd_raw_769_p","ksads_ptsd_raw_770_p")])

summary(lm(varexp~interview_age+sex+ksads_ptsd_raw_754_p+ksads_ptsd_raw_755_p+ksads_ptsd_raw_756_p+ksads_ptsd_raw_757_p+ksads_ptsd_raw_758_p+ksads_ptsd_raw_759_p+ksads_ptsd_raw_760_p+ksads_ptsd_raw_761_p+ksads_ptsd_raw_762_p+ksads_ptsd_raw_763_p+ksads_ptsd_raw_764_p+ksads_ptsd_raw_765_p+ksads_ptsd_raw_766_p+ksads_ptsd_raw_767_p+ksads_ptsd_raw_768_p+ksads_ptsd_raw_769_p+ksads_ptsd_raw_770_p,data=combined.data))

# Trauma endorsements are sparse (yay) so will use lasso
library(glmnet)
set.seed(1)
combined.data<-combined.data[complete.cases(combined.data$ACEsTotal),]
combined.data<-combined.data[complete.cases(combined.data$thompson_PC2),]
train=sample(seq(length(combined.data$subjectkey)),round((2/3)*length(combined.data$subjectkey)),replace=FALSE)
lasso.tr=glmnet(as.matrix(combined.data[train,c("ksads_ptsd_raw_754_p","ksads_ptsd_raw_755_p","ksads_ptsd_raw_756_p","ksads_ptsd_raw_757_p","ksads_ptsd_raw_758_p","ksads_ptsd_raw_759_p","ksads_ptsd_raw_760_p","ksads_ptsd_raw_761_p","ksads_ptsd_raw_762_p","ksads_ptsd_raw_763_p","ksads_ptsd_raw_764_p","ksads_ptsd_raw_765_p","ksads_ptsd_raw_766_p","ksads_ptsd_raw_767_p","ksads_ptsd_raw_768_p","ksads_ptsd_raw_769_p","ksads_ptsd_raw_770_p")]),combined.data[train,"varexp"],family="gaussian")
#lasso.tr
pred=predict(lasso.tr,as.matrix(combined.data[-train,c("ksads_ptsd_raw_754_p","ksads_ptsd_raw_755_p","ksads_ptsd_raw_756_p","ksads_ptsd_raw_757_p","ksads_ptsd_raw_758_p","ksads_ptsd_raw_759_p","ksads_ptsd_raw_760_p","ksads_ptsd_raw_761_p","ksads_ptsd_raw_762_p","ksads_ptsd_raw_763_p","ksads_ptsd_raw_764_p","ksads_ptsd_raw_765_p","ksads_ptsd_raw_766_p","ksads_ptsd_raw_767_p","ksads_ptsd_raw_768_p","ksads_ptsd_raw_769_p","ksads_ptsd_raw_770_p")]))
dim(pred)
rmse=sqrt(apply((combined.data[-train,"varexp"]-pred)^2,2,mean))
plot(log(lasso.tr$lambda),rmse,type="b",xlab="Log(lambda")
lam.best=lasso.tr$lambda[order(rmse)[1]] # extracting the best lambda
lam.best
coef(lasso.tr,s=lam.best)

summary(lm(varexp~interview_age+sex+ksads_ptsd_raw_755_p+ksads_ptsd_raw_756_p+ksads_ptsd_raw_757_p+ksads_ptsd_raw_758_p+ksads_ptsd_raw_762_p+ksads_ptsd_raw_763_p+ksads_ptsd_raw_764_p+ksads_ptsd_raw_766_p,data=combined.data))

model1<-lm(varexp~interview_age+sex,data=combined.data)
model2<-lm(varexp~interview_age+sex+ksads_ptsd_raw_755_p+ksads_ptsd_raw_756_p+ksads_ptsd_raw_757_p+ksads_ptsd_raw_758_p+ksads_ptsd_raw_762_p+ksads_ptsd_raw_763_p+ksads_ptsd_raw_764_p+ksads_ptsd_raw_766_p,data=combined.data)
anova(model1,model2,test = "Chisq")

```

```{r}

model1<-lm(varexp~interview_age+sex,data=combined.data)
model2<-lm(varexp~interview_age+sex+thompson_PC2,data=combined.data)
model3<-lm(varexp~interview_age+sex+thompson_PC2+interview_age*thompson_PC2,data=combined.data)
anova(model1,model2,test = "Chisq")
anova(model2,model3,test = "Chisq")

model1<-lm(thompson_PC2~interview_age+sex,data=combined.data)
model2<-lm(thompson_PC2~interview_age+sex+varexp,data=combined.data)
model3<-lm(thompson_PC2~interview_age+sex+varexp+interview_age*varexp,data=combined.data)
anova(model1,model2,test = "Chisq")
anova(model2,model3,test = "Chisq")

summary(lm(thompson_PC2~interview_age*sex*varexp,data=combined.data))
```

## Check for outliers (>3sd) on Thompson factor scores
```{r}
mean_PC1 <- mean(combined.data$thompson_PC1)
mean_PC2 <- mean(combined.data$thompson_PC2)
mean_PC3 <- mean(combined.data$thompson_PC3)
sd3_PC1 <- sd(combined.data$thompson_PC1)*3
sd3_PC2 <- sd(combined.data$thompson_PC2)*3
sd3_PC3 <- sd(combined.data$thompson_PC3)*3

sum(combined.data$thompson_PC1 > mean_PC1+sd3_PC1) # 3 outliers
sum(combined.data$thompson_PC2 > mean_PC2+sd3_PC2) # 0 outliers
sum(combined.data$thompson_PC3 > mean_PC3+sd3_PC3) # 2 outliers

combined.data.noOutliers <- combined.data[(combined.data$thompson_PC1>(mean_PC1-sd3_PC1) & combined.data$thompson_PC1<(mean_PC1+sd3_PC1) & combined.data$thompson_PC2>(mean_PC2-sd3_PC2) & combined.data$thompson_PC2<(mean_PC2+sd3_PC2) & combined.data$thompson_PC3>(mean_PC3-sd3_PC3) & combined.data$thompson_PC3<(mean_PC3+sd3_PC3)),]

summary(lm(thompson_PC2~interview_age*sex*varexp,data=combined.data.noOutliers))

```

### 2021-10-14 BHRC_Prelim_Analyses.Rmd
Preliminary BHRC Analyses
Nothing super convincing so far :/

---
title: "BHRC Preliminary Analyses"
output: html_notebook
---

## For these analyses, I'll look at how early life trauma (Threat and Deprivation factors) affects three metrics of performance on the Attention Network Task (ANT): Alerting, Orienting, and Conflict.

### Load and organize data:
```{r}
sle_factors<-readRDS("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/BHRC/thdp_20212904.rds")
ant_scores<-read.csv("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/BHRC/ANT SCORES 100-1700ms RT cutoffs.csv")
demo_data<-read.csv("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/BHRC/BHRCS_w0_Arielle.csv")
proposal.data<-readRDS("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/BHRC/PhD_117BHRC_2021_10_02.rds")

colnames(sle_factors)[2]<-"SUBJECTID"
colnames(demo_data)[2]<-"SUBJECTID"
combined.data1<-merge(demo_data,ant_scores,by="SUBJECTID")

proposal.data.w0<-proposal.data[proposal.data$redcap_event_name=="wave0_arm_1",c("ident", setdiff(colnames(proposal.data),colnames(combined.data1)))]

combined.data2<-merge(proposal.data.w0,sle_factors,by="ident")
all.data<-merge(combined.data1,combined.data2,by="SUBJECTID")
```

### Remove test set:
```{r}
set.seed(2021)
test=sample(seq(1015),200,replace=FALSE)
test.data<-all.data[test,]
all.data<-all.data[-test,]
```

### View raw data
```{r}
ggplot(data=all.data,aes(threat,ALERT))+geom_point()
ggplot(data=all.data,aes(threat,ORIENT))+geom_point()
ggplot(data=all.data,aes(threat,CONFLICT))+geom_point()

ggplot(data=all.data,aes(depriv,ALERT))+geom_point()
ggplot(data=all.data,aes(depriv,ORIENT))+geom_point()
ggplot(data=all.data,aes(depriv,CONFLICT))+geom_point()
```

### Remove outliers (>3sd) on Alerting, Orienting, and Conflict scores
```{r}
ALERT.3sd <- sd(all.data[!is.na(all.data$ALERT),]$ALERT)*3
ORIENT.3sd <- sd(all.data[!is.na(all.data$ORIENT),]$ORIENT)*3
CONFLICT.3sd <- sd(all.data[!is.na(all.data$CONFLICT),]$CONFLICT)*3

ALERT.mean <- mean(all.data[!is.na(all.data$ALERT),]$ALERT)
ORIENT.mean <- mean(all.data[!is.na(all.data$ORIENT),]$ORIENT)
CONFLICT.mean <- mean(all.data[!is.na(all.data$CONFLICT),]$CONFLICT)

# These will be separate data structures retaining as many subjects as possible for each of the 3 performance metrics
all.data.ALERT <- all.data[(all.data$ALERT>(ALERT.mean-ALERT.3sd) & all.data$ALERT<(ALERT.mean+ALERT.3sd)),]
all.data.ORIENT <- all.data[(all.data$ORIENT>(ORIENT.mean-ORIENT.3sd) & all.data$ORIENT<(ORIENT.mean+ORIENT.3sd)),]
all.data.CONFLICT <- all.data[(all.data$CONFLICT>(CONFLICT.mean-CONFLICT.3sd) & all.data$CONFLICT<(CONFLICT.mean+CONFLICT.3sd)),]

all.data.complete.set <- all.data[(all.data$ALERT>(ALERT.mean-ALERT.3sd) & all.data$ALERT<(ALERT.mean+ALERT.3sd)) & (all.data$ORIENT>(ORIENT.mean-ORIENT.3sd) & all.data$ORIENT<(ORIENT.mean+ORIENT.3sd)) & (all.data$CONFLICT>(CONFLICT.mean-CONFLICT.3sd) & all.data$CONFLICT<(CONFLICT.mean+CONFLICT.3sd)),]
```

### Run linear models using Threat and Deprivation scores to predict ANT performance metrics
```{r}
summary(lm(ALERT~age+gender+threat+depriv,data=all.data.ALERT))
summary(lm(ORIENT~age+gender+threat+depriv,data=all.data.ORIENT))
summary(lm(CONFLICT~age+gender+threat+depriv,data=all.data.CONFLICT))

summary(lm(ALERT~age+gender+threat+depriv+age*threat+age*depriv+gender*threat+gender*depriv,data=all.data.ALERT)) # sig gender x threat
summary(lm(ORIENT~age+gender+threat+depriv+age*threat+age*depriv+gender*threat+gender*depriv,data=all.data.ORIENT))
summary(lm(CONFLICT~age+gender+threat+depriv+age*threat+age*depriv+gender*threat+gender*depriv,data=all.data.CONFLICT)) # close age x threat

summary(lm(ALERT~age+gender+threat+depriv+age*threat+age*depriv+gender*threat+gender*depriv+age*gender*threat+age*gender*depriv,data=all.data.ALERT))
summary(lm(ORIENT~age+gender+threat+depriv+age*threat+age*depriv+gender*threat+gender*depriv+age*gender*threat+age*gender*depriv,data=all.data.ORIENT)) 
summary(lm(CONFLICT~age+gender+threat+depriv+age*threat+age*depriv+gender*threat+gender*depriv+age*gender*threat+age*gender*depriv,data=all.data.CONFLICT))

summary(lm(ALERT~age+gender+depriv+depriv*age+depriv*gender,data=all.data.ALERT)) 
summary(lm(ORIENT~age+gender+depriv+depriv*age+depriv*gender,data=all.data.ORIENT))
summary(lm(CONFLICT~age+gender+depriv+depriv*age+depriv*gender,data=all.data.CONFLICT))

summary(lm(ALERT~age+gender+threat+threat*age+threat*gender,data=all.data.ALERT)) # Close on gender x threat
summary(lm(ORIENT~age+gender+threat+threat*age+threat*gender,data=all.data.ORIENT))
summary(lm(CONFLICT~age+gender+threat+threat*age+threat*gender,data=all.data.CONFLICT))
```

### Plotting
```{r}

ggplot(data=all.data.ALERT[!is.na(all.data.ALERT$gender),],aes(depriv,ALERT))+geom_point(size=1,colour=all.data.ALERT[!is.na(all.data.ALERT$gender),]$age)+geom_smooth(method=lm)+ facet_wrap(~ factor(gender,labels=c("Gender 1","Gender 2")))

ggplot(data=all.data.ALERT[!is.na(all.data.ALERT$gender),],aes(depriv,ALERT))+geom_point(size=1,colour=all.data.ALERT[!is.na(all.data.ALERT$gender),]$gender)+geom_smooth(method=lm)+ facet_grid(factor(all.data.ALERT[!is.na(all.data.ALERT$gender),]$gender,labels=c("Gender 1","Gender 2"))~factor(round(all.data.ALERT[!is.na(all.data.ALERT$gender),]$age)))

ggplot(data=all.data.ALERT[!is.na(all.data.ALERT$gender),],aes(threat,ALERT))+geom_point(size=1,colour=all.data.ALERT[!is.na(all.data.ALERT$gender),]$age)+geom_smooth(method=lm)+ facet_wrap(~ factor(gender,labels=c("Gender 1","Gender 2")))

ggplot(data=all.data.ALERT[!is.na(all.data.ALERT$gender),],aes(threat,ALERT))+geom_point(size=1,colour=all.data.ALERT[!is.na(all.data.ALERT$gender),]$gender)+geom_smooth(method=lm)+ facet_grid(factor(gender,labels=c("Gender 1","Gender 2"))~factor(round(age)))

```

### Stepwise linear regression
```{r}
model1<-lm(ALERT~age+gender,data=all.data.ALERT)
model2<-lm(ALERT~age+gender+depriv,data=all.data.ALERT)
model3<-lm(ALERT~age+gender+depriv+depriv*age+depriv*gender,data=all.data.ALERT)
model4<-lm(ALERT~age+gender+depriv+depriv*age+depriv*gender+age*gender*depriv,data=all.data.ALERT)
anova(model1,model2,test = "Chisq")
anova(model2,model3,test = "Chisq")
anova(model3,model4,test = "Chisq")

model1<-lm(ALERT~age+gender,data=all.data.ALERT)
model2<-lm(ALERT~age+gender+threat,data=all.data.ALERT)
model3<-lm(ALERT~age+gender+threat+threat*age+threat*gender,data=all.data.ALERT)
model4<-lm(ALERT~age+gender+threat+threat*age+threat*gender+age*gender*threat,data=all.data.ALERT)
model5<-lm(ALERT~age+gender+threat+threat*gender,data=all.data.ALERT)
anova(model1,model2,test = "Chisq")
anova(model2,model3,test = "Chisq")
anova(model3,model4,test = "Chisq")
anova(model2,model5,test = "Chisq") # close 0.057
```

### What if we split by symptoms?

### Sandbox
```{r}

summary(lm(threat~age+ALERT+ORIENT+CONFLICT,data=all.data.complete.set[all.data.complete.set$gender==1,]))
summary(lm(depriv~age+ALERT+ORIENT+CONFLICT,data=all.data.complete.set[all.data.complete.set$gender==1,]))

summary(lm(threat~age+ALERT+ORIENT+CONFLICT,data=all.data.complete.set[all.data.complete.set$gender==2,]))
summary(lm(depriv~age+ALERT+ORIENT+CONFLICT,data=all.data.complete.set[all.data.complete.set$gender==2,]))

summary(lm(threat~age+gender+ALERT+ORIENT+CONFLICT,data=all.data.complete.set))
summary(lm(depriv~age+gender+ALERT+ORIENT+CONFLICT,data=all.data.complete.set))

```

### 2021-10-26 BHRC_Prelim_Analyses.Rmd
Added visualizations

@@
 title: "BHRC Preliminary Analyses"
-output: html_notebook
+output:
+  html_document:
+    df_print: paged
+  html_notebook: default
+  pdf_document: default
 ---
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+options(width=250)
+library(tidyr)
+library(dplyr)
+library(ggplot2)
+library(lsr)
+```
 
@@
 all.data<-merge(combined.data1,combined.data2,by="SUBJECTID")
+all.data$gender<-as.factor(all.data$gender)
 ```
@@
 test=sample(seq(1015),200,replace=FALSE)
-test.data<-all.data[test,]
-all.data<-all.data[-test,]
+test.data<-all.data[test,] # Test set (n=200)
+all.data<-all.data[-test,] # Training set (n=815)
 ```
@@
 
+# This is a complete set with subjects who have all 3 measures within the bounds of 3SD
 all.data.complete.set <- all.data[(all.data$ALERT>(ALERT.mean-ALERT.3sd) & all.data$ALERT<(ALERT.mean+ALERT.3sd)) & (all.data$ORIENT>(ORIENT.mean-ORIENT.3sd) & all.data$ORIENT<(ORIENT.mean+ORIENT.3sd)) & (all.data$CONFLICT>(CONFLICT.mean-CONFLICT.3sd) & all.data$CONFLICT<(CONFLICT.mean+CONFLICT.3sd)),]
@@
 
+### Threat and deprivation scores are correlated, so we'll test them in separate models
+```{r}
+cor.test(all.data.complete.set$threat,all.data.complete.set$depriv)
+```
+
 ### Run linear models using Threat and Deprivation scores to predict ANT performance metrics
+# Note: Gender 1 = Male, Gender 2 = Female
 ```{r}
-summary(lm(ALERT~age+gender+threat+depriv,data=all.data.ALERT))
-summary(lm(ORIENT~age+gender+threat+depriv,data=all.data.ORIENT))
-summary(lm(CONFLICT~age+gender+threat+depriv,data=all.data.CONFLICT))
+# Without interactions
+summary(lm(ALERT~age+gender+threat,data=all.data.ALERT))
+summary(lm(ORIENT~age+gender+threat,data=all.data.ORIENT))
+summary(lm(CONFLICT~age+gender+threat,data=all.data.CONFLICT))
 
-summary(lm(ALERT~age+gender+threat+depriv+age*threat+age*depriv+gender*threat+gender*depriv,data=all.data.ALERT)) # sig gender x threat
-summary(lm(ORIENT~age+gender+threat+depriv+age*threat+age*depriv+gender*threat+gender*depriv,data=all.data.ORIENT))
-summary(lm(CONFLICT~age+gender+threat+depriv+age*threat+age*depriv+gender*threat+gender*depriv,data=all.data.CONFLICT)) # close age x threat
+summary(lm(ALERT~age+gender+depriv,data=all.data.ALERT))
+summary(lm(ORIENT~age+gender+depriv,data=all.data.ORIENT))
+summary(lm(CONFLICT~age+gender+depriv,data=all.data.CONFLICT))
 
-summary(lm(ALERT~age+gender+threat+depriv+age*threat+age*depriv+gender*threat+gender*depriv+age*gender*threat+age*gender*depriv,data=all.data.ALERT))
-summary(lm(ORIENT~age+gender+threat+depriv+age*threat+age*depriv+gender*threat+gender*depriv+age*gender*threat+age*gender*depriv,data=all.data.ORIENT)) 
-summary(lm(CONFLICT~age+gender+threat+depriv+age*threat+age*depriv+gender*threat+gender*depriv+age*gender*threat+age*gender*depriv,data=all.data.CONFLICT))
-
+# With interactions
 summary(lm(ALERT~age+gender+depriv+depriv*age+depriv*gender,data=all.data.ALERT)) 
@@
 summary(lm(CONFLICT~age+gender+threat+threat*age+threat*gender,data=all.data.CONFLICT))
+
+summary(lm(ALERT~age+threat,data=all.data.ALERT[all.data.ALERT$gender==1,]))
+summary(lm(ALERT~age+threat,data=all.data.ALERT[all.data.ALERT$gender==2,])) # significant just in girls
+
+# Including threat and deprivation together in the same model (just to see?)
+summary(lm(ALERT~age+gender+threat+depriv+age*threat+age*depriv+gender*threat+gender*depriv,data=all.data.ALERT)) # sig gender x threat
+summary(lm(ORIENT~age+gender+threat+depriv+age*threat+age*depriv+gender*threat+gender*depriv,data=all.data.ORIENT))
+summary(lm(CONFLICT~age+gender+threat+depriv+age*threat+age*depriv+gender*threat+gender*depriv,data=all.data.CONFLICT))
+
 ```
@@
 
-ggplot(data=all.data.ALERT[!is.na(all.data.ALERT$gender),],aes(depriv,ALERT))+geom_point(size=1,colour=all.data.ALERT[!is.na(all.data.ALERT$gender),]$age)+geom_smooth(method=lm)+ facet_wrap(~ factor(gender,labels=c("Gender 1","Gender 2")))
+ggplot(data=all.data.ALERT[!is.na(all.data.ALERT$gender),],aes(depriv,ALERT))+geom_point(size=1,colour=all.data.ALERT[!is.na(all.data.ALERT$gender),]$age)+geom_smooth(method=lm)+ facet_wrap(~ factor(gender,labels=c("Male","Female")))
 
-ggplot(data=all.data.ALERT[!is.na(all.data.ALERT$gender),],aes(depriv,ALERT))+geom_point(size=1,colour=all.data.ALERT[!is.na(all.data.ALERT$gender),]$gender)+geom_smooth(method=lm)+ facet_grid(factor(all.data.ALERT[!is.na(all.data.ALERT$gender),]$gender,labels=c("Gender 1","Gender 2"))~factor(round(all.data.ALERT[!is.na(all.data.ALERT$gender),]$age)))
+ggplot(data=all.data.ALERT[!is.na(all.data.ALERT$gender),],aes(depriv,ALERT))+geom_point(size=1,colour=all.data.ALERT[!is.na(all.data.ALERT$gender),]$gender)+geom_smooth(method=lm)+ facet_grid(factor(all.data.ALERT[!is.na(all.data.ALERT$gender),]$gender,labels=c("Male","Female"))~factor(round(all.data.ALERT[!is.na(all.data.ALERT$gender),]$age)))
 
-ggplot(data=all.data.ALERT[!is.na(all.data.ALERT$gender),],aes(threat,ALERT))+geom_point(size=1,colour=all.data.ALERT[!is.na(all.data.ALERT$gender),]$age)+geom_smooth(method=lm)+ facet_wrap(~ factor(gender,labels=c("Gender 1","Gender 2")))
+ggplot(data=all.data.ALERT[!is.na(all.data.ALERT$gender),],aes(threat,ALERT))+geom_point(size=1,colour=all.data.ALERT[!is.na(all.data.ALERT$gender),]$age)+geom_smooth(method=lm)+ facet_wrap(~ factor(gender,labels=c("Male","Female")))
 
-ggplot(data=all.data.ALERT[!is.na(all.data.ALERT$gender),],aes(threat,ALERT))+geom_point(size=1,colour=all.data.ALERT[!is.na(all.data.ALERT$gender),]$gender)+geom_smooth(method=lm)+ facet_grid(factor(gender,labels=c("Gender 1","Gender 2"))~factor(round(age)))
+ggplot(data=all.data.ALERT[!is.na(all.data.ALERT$gender),],aes(threat,ALERT))+geom_point(size=1,colour=all.data.ALERT[!is.na(all.data.ALERT$gender),]$gender)+geom_smooth(method=lm)+ facet_grid(factor(gender,labels=c("Male","Female"))~factor(round(age)))
 
@@
 anova(model2,model5,test = "Chisq") # close 0.057
+
 ```
 
-### What if we split by symptoms?
+### Next steps: What if we split by symptoms?
 
@@
 ```{r}
-
-summary(lm(threat~age+ALERT+ORIENT+CONFLICT,data=all.data.complete.set[all.data.complete.set$gender==1,]))
-summary(lm(depriv~age+ALERT+ORIENT+CONFLICT,data=all.data.complete.set[all.data.complete.set$gender==1,]))
-
-summary(lm(threat~age+ALERT+ORIENT+CONFLICT,data=all.data.complete.set[all.data.complete.set$gender==2,]))
-summary(lm(depriv~age+ALERT+ORIENT+CONFLICT,data=all.data.complete.set[all.data.complete.set$gender==2,]))
 

### 2021-10-26 ABCD_Prelim_Analyses.Rmd
Inclusion/Exclusion
Added inclusion and exclusion criteria to match with UMinn and Adam's analyses

@@
 names(combined.data)[which(names(combined.data)=="lmt_scr_perc_correct")] = "LMT"
+```
+
+# Inclusion/Exclusion
+```{r}
+# First, to harmonize our criteria with UMinn, retain participants with at least 8min of clean data instead of 12min. TR = 0.8s so 8min = 480s = 600TRs
+num_TRs <- read.csv("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/num_TRs_by_subj_redo.csv")
+data<-merge(combined.data,num_TRs,by="subjectkey")
+data.clean<-data[data$numTRs>=600,]
+
+# Second, remove participants based on booleans from ABCD
+abcd_imgincl01 <- read.csv("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/abcd_imgincl01.csv")
+abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$eventnam=="baseline_year_1_arm_1",]
+abcd_imgincl01 <- abcd_imgincl01[!abcd_imgincl01$visit=="",]
+abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_t1w_include==1,]
+abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_rsfmri_include==1,]
+abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_mid_include==1,]
+abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_nback_include==1,]
+abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_sst_include==1,]
+
+combined.data <- merge(data.clean,abcd_imgincl01[, c("subjectkey",'imgincl_t1w_include')],by="subjectkey")
 ```

### 2021-10-28 ABCD_Prelim_Analyses.Rmd
Added preliminary PFN analysis

@@
 ```
+
+## PFNs analysis (CLEAR BEFORE RUNNING)
+# First load in the spatial extent of each PFN (they're in order, 1-17)
+# Then merge with the same datasets as above (NIH toolbox, trauma, etc.)
+```{r}
+pfn_sizes <- read.csv("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/All_PFN_sizes.csv")
+nihtb<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/NihTB/abcd_tbss01.txt",header=TRUE)
+nihtb.baseline<-nihtb[nihtb$eventname=="baseline_year_1_arm_1",]
+merged.data1 <- merge(pfn_sizes,nihtb.baseline,by="subjectkey")
+lmt<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/Thomp/lmtp201.txt",header=TRUE)
+lmt.baseline<-lmt[lmt$eventname=="baseline_year_1_arm_1",]
+merged.data2 <- merge(merged.data1,lmt.baseline[, c("subjectkey", setdiff(colnames(lmt.baseline),colnames(merged.data1)))],by="subjectkey")
+ravlt<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/Thomp/abcd_ps01.txt",header=TRUE)
+ravlt.baseline<-ravlt[ravlt$eventname=="baseline_year_1_arm_1",]
+merged.data3 <- merge(merged.data2,ravlt.baseline[, c("subjectkey", setdiff(colnames(ravlt.baseline),colnames(merged.data2)))],by="subjectkey")
+trauma<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/Strife/abcd_ptsd01.txt",header=TRUE)
+trauma.baseline<-trauma[trauma$eventname=="baseline_year_1_arm_1",]
+combined.data <- merge(merged.data3,trauma.baseline[, c("subjectkey", setdiff(colnames(trauma.baseline),colnames(merged.data3)))],by="subjectkey")
+
+# Coerce data types
+combined.data$nihtbx_flanker_uncorrected <- as.numeric(combined.data$nihtbx_flanker_uncorrected)
+combined.data$nihtbx_picvocab_uncorrected <- as.numeric(combined.data$nihtbx_picvocab_uncorrected)
+combined.data$nihtbx_list_uncorrected <- as.numeric(combined.data$nihtbx_list_uncorrected)
+combined.data$nihtbx_pattern_uncorrected <- as.numeric(combined.data$nihtbx_pattern_uncorrected)
+combined.data$nihtbx_cardsort_uncorrected <- as.numeric(combined.data$nihtbx_cardsort_uncorrected)
+combined.data$nihtbx_picture_uncorrected <- as.numeric(combined.data$nihtbx_picture_uncorrected)
+combined.data$nihtbx_reading_uncorrected <- as.numeric(combined.data$nihtbx_reading_uncorrected)
+combined.data$lmt_scr_perc_correct <- as.numeric(combined.data$lmt_scr_perc_correct)
+combined.data$pea_ravlt_sd_trial_i_tc <- as.numeric(combined.data$pea_ravlt_sd_trial_i_tc)
+combined.data$pea_ravlt_sd_trial_ii_tc <- as.numeric(combined.data$pea_ravlt_sd_trial_ii_tc)
+combined.data$pea_ravlt_sd_trial_iii_tc <- as.numeric(combined.data$pea_ravlt_sd_trial_iii_tc)
+combined.data$pea_ravlt_sd_trial_iv_tc <- as.numeric(combined.data$pea_ravlt_sd_trial_iv_tc)
+combined.data$pea_ravlt_sd_trial_v_tc <- as.numeric(combined.data$pea_ravlt_sd_trial_v_tc)
+combined.data$interview_age <- as.numeric(combined.data$interview_age)
+
+ind_pea_ravlt = c(which(names(combined.data)=="pea_ravlt_sd_trial_i_tc"),which(names(combined.data)=="pea_ravlt_sd_trial_ii_tc"),
+	which(names(combined.data)=="pea_ravlt_sd_trial_iii_tc"),which(names(combined.data)=="pea_ravlt_sd_trial_iv_tc"),
+	which(names(combined.data)=="pea_ravlt_sd_trial_v_tc")); names(combined.data)[ind_pea_ravlt]; summary(combined.data[,ind_pea_ravlt])
+combined.data$pea_ravlt_ld = apply(combined.data[,ind_pea_ravlt],1,sum)
+
+combined.data$pea_ravlt_ld <- as.numeric(combined.data$pea_ravlt_ld)
+
+# Rename according to Thompson 2018 code
+names(combined.data)[which(names(combined.data)=="nihtbx_picvocab_uncorrected")] = "PicVocab"
+names(combined.data)[which(names(combined.data)=="nihtbx_flanker_uncorrected")] = "Flanker"
+names(combined.data)[which(names(combined.data)=="nihtbx_list_uncorrected")] = "List"
+names(combined.data)[which(names(combined.data)=="nihtbx_cardsort_uncorrected")] = "CardSort"
+names(combined.data)[which(names(combined.data)=="nihtbx_pattern_uncorrected")] = "Pattern"
+names(combined.data)[which(names(combined.data)=="nihtbx_picture_uncorrected")] = "Picture"
+names(combined.data)[which(names(combined.data)=="nihtbx_reading_uncorrected")] = "Reading"
+names(combined.data)[which(names(combined.data)=="pea_ravlt_ld")] = "RAVLT"
+names(combined.data)[which(names(combined.data)=="lmt_scr_perc_correct")] = "LMT"
+
+num_TRs <- read.csv("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/num_TRs_by_subj_redo.csv")
+data<-merge(combined.data,num_TRs,by="subjectkey")
+data.clean<-data[data$numTRs>=600,] # we go from 9,132 to 8,293 at this step
+
+# Remove participants based on booleans from ABCD
+abcd_imgincl01 <- read.csv("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/abcd_imgincl01.csv")
+abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$eventnam=="baseline_year_1_arm_1",]
+abcd_imgincl01 <- abcd_imgincl01[!abcd_imgincl01$visit=="",] # start here with 11,663 (8,287 of the 9,132 set)
+abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_t1w_include==1,] # down to 11,124 (8,045 of the 9,132 set)
+abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_rsfmri_include==1,] # down to 9,388 (7,475 of the 9,132 set)
+abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_mid_include==1,] # down to 7,847 (6,344 of the 9,132 set)
+abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_nback_include==1,] # down to 6,348 (5,161 of the 9,132 set)
+abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_sst_include==1,] # down to 5,606 (4,164 of the 9,132 set)
+
+combined.data <- merge(data.clean,abcd_imgincl01[, c("subjectkey",'imgincl_t1w_include')],by="subjectkey")
+
+# Calculate Thompson factor scores
+combined.data$thompson_PC1 <- (0.754*combined.data$PicVocab)+(0.213*combined.data$Flanker)+(0.471*combined.data$List)+(0.205*combined.data$CardSort)+(0.015*combined.data$Pattern)+(0.012*combined.data$Picture)+(0.82*combined.data$Reading)+(0.306*combined.data$RAVLT)+(0.5*combined.data$LMT)
+
+combined.data$thompson_PC2 <- (0.065*combined.data$PicVocab)+(0.712*combined.data$Flanker)+(0.148*combined.data$List)+(0.71*combined.data$CardSort)+(0.813*combined.data$Pattern)+(0.135*combined.data$Picture)+(0.12*combined.data$Reading)+(0.125*combined.data$RAVLT)+(0.299*combined.data$LMT)
+
+combined.data$thompson_PC3 <- (0.19*combined.data$PicVocab)+(0.067*combined.data$Flanker)+(0.493*combined.data$List)+(0.232*combined.data$CardSort)+(0.085*combined.data$Pattern)+(0.863*combined.data$Picture)+(0.122*combined.data$Reading)+(0.712*combined.data$RAVLT)+(0.068*combined.data$LMT)
+
+# Compute a ksads "abuse" variable" and a total score
+# These are the items that will go into this score (they're the physical and sexual abuse variables)
+# 761, 762, 763, 767, 768, 769
+combined.data$abuse <- rowSums(data.frame(as.numeric(combined.data$ksads_ptsd_raw_761_p),as.numeric(combined.data$ksads_ptsd_raw_762_p),as.numeric(combined.data$ksads_ptsd_raw_763_p),as.numeric(combined.data$ksads_ptsd_raw_767_p),as.numeric(combined.data$ksads_ptsd_raw_768_p),as.numeric(combined.data$ksads_ptsd_raw_769_p)),na.rm=TRUE)
+
+combined.data$totalACEs <- rowSums(data.frame(as.numeric(combined.data$ksads_ptsd_raw_754_p),as.numeric(combined.data$ksads_ptsd_raw_755_p),as.numeric(combined.data$ksads_ptsd_raw_756_p),as.numeric(combined.data$ksads_ptsd_raw_757_p),as.numeric(combined.data$ksads_ptsd_raw_758_p),as.numeric(combined.data$ksads_ptsd_raw_759_p),as.numeric(combined.data$ksads_ptsd_raw_760_p),as.numeric(combined.data$ksads_ptsd_raw_761_p),as.numeric(combined.data$ksads_ptsd_raw_762_p),as.numeric(combined.data$ksads_ptsd_raw_763_p),as.numeric(combined.data$ksads_ptsd_raw_764_p),as.numeric(combined.data$ksads_ptsd_raw_765_p),as.numeric(combined.data$ksads_ptsd_raw_766_p),as.numeric(combined.data$ksads_ptsd_raw_767_p),as.numeric(combined.data$ksads_ptsd_raw_768_p),as.numeric(combined.data$ksads_ptsd_raw_769_p),as.numeric(combined.data$ksads_ptsd_raw_770_p)),na.rm=TRUE)
+
+# Remove outliers
+mean_PC1 <- mean(combined.data$thompson_PC1,na.rm=TRUE)
+mean_PC2 <- mean(combined.data$thompson_PC2,na.rm=TRUE)
+mean_PC3 <- mean(combined.data$thompson_PC3,na.rm=TRUE)
+sd3_PC1 <- sd(combined.data$thompson_PC1,na.rm=TRUE)*3
+sd3_PC2 <- sd(combined.data$thompson_PC2,na.rm=TRUE)*3
+sd3_PC3 <- sd(combined.data$thompson_PC3,na.rm=TRUE)*3
+sum(combined.data$thompson_PC1 > mean_PC1+sd3_PC1,na.rm=TRUE) # 8 outliers
+sum(combined.data$thompson_PC2 > mean_PC2+sd3_PC2,na.rm=TRUE) # 2 outliers
+sum(combined.data$thompson_PC3 > mean_PC3+sd3_PC3,na.rm=TRUE) # 0 outliers
+combined.data.noOutliers <- combined.data[(combined.data$thompson_PC1>(mean_PC1-sd3_PC1) & combined.data$thompson_PC1<(mean_PC1+sd3_PC1) & combined.data$thompson_PC2>(mean_PC2-sd3_PC2) & combined.data$thompson_PC2<(mean_PC2+sd3_PC2) & combined.data$thompson_PC3>(mean_PC3-sd3_PC3) & combined.data$thompson_PC3<(mean_PC3+sd3_PC3) & combined.data$totalACEs<16 & combined.data$df18>3000),]
+
+# calculate a total FPN score
+combined.data.noOutliers$totalFPN <- rowSums(data.frame(as.numeric(combined.data.noOutliers$df4),as.numeric(combined.data.noOutliers$df16),as.numeric(combined.data.noOutliers$df18)))
+```
+
+## PFN ANALYSES
+# Remember that networks 1-17 are in variables df2-18
+```{r}
+
+# Replicate findings from Cui et al., 2020
+summary(lm(thompson_PC2~interview_age+sex+df18,data=combined.data.noOutliers)) #0.06
+summary(lm(df18~interview_age,data=combined.data.noOutliers)) # **
+summary(lm(thompson_PC2~interview_age+sex+df16,data=combined.data.noOutliers))
+summary(lm(df16~interview_age,data=combined.data.noOutliers)) # **
+summary(lm(thompson_PC2~interview_age+sex+df4,data=combined.data.noOutliers))
+summary(lm(df4~interview_age,data=combined.data.noOutliers)) # **
+
+# See which networks are associated with which cognitive factor scores
+summary(lm(thompson_PC1~interview_age+sex+df2+df3+df4+df5+df6+df7+df8+df9+df10+df11+df12+df13+df14+df15+df16+df17+df18,data=combined.data.noOutliers))
+summary(lm(thompson_PC2~interview_age+sex+df2+df3+df4+df5+df6+df7+df8+df9+df10+df11+df12+df13+df14+df15+df16+df17+df18,data=combined.data.noOutliers))
+summary(lm(thompson_PC3~interview_age+sex+df2+df3+df4+df5+df6+df7+df8+df9+df10+df11+df12+df13+df14+df15+df16+df17+df18,data=combined.data.noOutliers))
+
+summary(lm(df4~interview_age+sex+abuse,data=combined.data.noOutliers))
+summary(lm(df4~interview_age+sex+totalACEs,data=combined.data.noOutliers))
+
+summary(lm(df16~interview_age+sex+abuse,data=combined.data.noOutliers))
+summary(lm(df16~interview_age+sex+totalACEs,data=combined.data.noOutliers))
+
+summary(lm(df18~interview_age+sex+abuse,data=combined.data.noOutliers))
+summary(lm(df18~interview_age+sex+totalACEs,data=combined.data.noOutliers))
+
+summary(lm(thompson_PC1~interview_age+sex+totalACEs,data=combined.data.noOutliers)) # ***
+summary(lm(thompson_PC2~interview_age+sex+totalACEs,data=combined.data.noOutliers)) # *
+summary(lm(thompson_PC3~interview_age+sex+totalACEs,data=combined.data.noOutliers)) # ***
+summary(lm(thompson_PC1~interview_age+sex+abuse,data=combined.data.noOutliers)) # *
+summary(lm(thompson_PC2~interview_age+sex+abuse,data=combined.data.noOutliers)) #ns
+summary(lm(thompson_PC3~interview_age+sex+abuse,data=combined.data.noOutliers)) # *
+
+summary(lm(thompson_PC1~interview_age+sex+df18,data=combined.data.noOutliers)) # ***
+summary(lm(thompson_PC1~interview_age+sex+df16,data=combined.data.noOutliers)) # ***
+summary(lm(thompson_PC1~interview_age+sex+df4,data=combined.data.noOutliers)) # ns
+
+# total FPN:
+summary(lm(thompson_PC1~interview_age+sex+totalFPN,data=combined.data.noOutliers)) # ***
+summary(lm(thompson_PC2~interview_age+sex+totalFPN,data=combined.data.noOutliers)) # .
+summary(lm(thompson_PC3~interview_age+sex+totalFPN,data=combined.data.noOutliers)) # .
+
+summary(lm(thompson_PC1~interview_age+sex+totalFPN,data=combined.data.noOutliers[combined.data.noOutliers$totalACEs==0,]))
+summary(lm(thompson_PC1~interview_age+sex+totalFPN,data=combined.data.noOutliers[combined.data.noOutliers$totalACEs>0,]))
+
+ggplot(data=combined.data.noOutliers,aes(totalFPN,thompson_PC1))+geom_point()+geom_smooth(method="lm")
+ggplot(data=combined.data.noOutliers,aes(totalFPN,thompson_PC2))+geom_point()+geom_smooth(method="lm")
+ggplot(data=combined.data.noOutliers,aes(totalFPN,thompson_PC3))+geom_point()+geom_smooth(method="lm")
+
+combined.data.noOutliers$ACEsFactor <- factor(combined.data.noOutliers$totalACEs==0,labels = c("ACEs","No ACEs"))
+ggplot(data=combined.data.noOutliers,aes(totalFPN,thompson_PC1,color=ACEsFactor))+geom_point(size=1)+geom_smooth(method="lm")
+
+summary(lm(thompson_PC1~interview_age+sex+totalFPN+ACEsFactor,data=combined.data.noOutliers))
+summary(lm(df18~interview_age+sex+ACEsFactor+ACEsFactor*interview_age+ACEsFactor*sex,data=combined.data.noOutliers))
+
+ggplot(data=combined.data.noOutliers,aes(interview_age,df18,color=ACEsFactor))+geom_point(size=1)+geom_smooth(method="lm")
+
+ggplot(data=combined.data.noOutliers,aes(interview_age,totalFPN,color=ACEsFactor))+geom_point(size=1)+geom_smooth(method="lm")
+```

### 2021-11-15 ABCD_Prelim_Analyses.Rmd
Updated files

@@
 combined.data.noOutliers$totalFPN <- rowSums(data.frame(as.numeric(combined.data.noOutliers$df4),as.numeric(combined.data.noOutliers$df16),as.numeric(combined.data.noOutliers$df18)))
+
+# separate train and test sets
+trainIDs <- read.csv("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/train.csv")
+train.data <- merge(combined.data.noOutliers,trainIDs,by="subjectkey") # n=2,143
+test.data <- combined.data.noOutliers[!is.element(combined.data.noOutliers$subjectkey,trainIDs$subjectkey),] #n=2,424
 ```
@@
 
-# Replicate findings from Cui et al., 2020
-summary(lm(thompson_PC2~interview_age+sex+df18,data=combined.data.noOutliers)) #0.06
-summary(lm(df18~interview_age,data=combined.data.noOutliers)) # **
-summary(lm(thompson_PC2~interview_age+sex+df16,data=combined.data.noOutliers))
-summary(lm(df16~interview_age,data=combined.data.noOutliers)) # **
-summary(lm(thompson_PC2~interview_age+sex+df4,data=combined.data.noOutliers))
-summary(lm(df4~interview_age,data=combined.data.noOutliers)) # **
+# Try to replicate findings from Cui et al., 2020
+summary(lm(thompson_PC2~interview_age+sex+df18,data=train.data))
+summary(lm(df18~interview_age,data=train.data)) # **
+summary(lm(thompson_PC2~interview_age+sex+df16,data=train.data))
+summary(lm(df16~interview_age,data=train.data)) # **
+summary(lm(thompson_PC2~interview_age+sex+df4,data=train.data))
+summary(lm(df4~interview_age,data=train.data)) # **
 
 # See which networks are associated with which cognitive factor scores
-summary(lm(thompson_PC1~interview_age+sex+df2+df3+df4+df5+df6+df7+df8+df9+df10+df11+df12+df13+df14+df15+df16+df17+df18,data=combined.data.noOutliers))
-summary(lm(thompson_PC2~interview_age+sex+df2+df3+df4+df5+df6+df7+df8+df9+df10+df11+df12+df13+df14+df15+df16+df17+df18,data=combined.data.noOutliers))
-summary(lm(thompson_PC3~interview_age+sex+df2+df3+df4+df5+df6+df7+df8+df9+df10+df11+df12+df13+df14+df15+df16+df17+df18,data=combined.data.noOutliers))
+summary(lm(thompson_PC1~interview_age+sex+df2+df3+df4+df5+df6+df7+df8+df9+df10+df11+df12+df13+df14+df15+df16+df17+df18,data=train.data))
+summary(lm(thompson_PC2~interview_age+sex+df2+df3+df4+df5+df6+df7+df8+df9+df10+df11+df12+df13+df14+df15+df16+df17+df18,data=train.data))
+summary(lm(thompson_PC3~interview_age+sex+df2+df3+df4+df5+df6+df7+df8+df9+df10+df11+df12+df13+df14+df15+df16+df17+df18,data=train.data))
 
-summary(lm(df4~interview_age+sex+abuse,data=combined.data.noOutliers))
-summary(lm(df4~interview_age+sex+totalACEs,data=combined.data.noOutliers))
+summary(lm(df4~interview_age+sex+abuse,data=train.data))
+summary(lm(df4~interview_age+sex+totalACEs,data=train.data))
 
-summary(lm(df16~interview_age+sex+abuse,data=combined.data.noOutliers))
-summary(lm(df16~interview_age+sex+totalACEs,data=combined.data.noOutliers))
+summary(lm(df16~interview_age+sex+abuse,data=train.data))
+summary(lm(df16~interview_age+sex+totalACEs,data=train.data))
 
-summary(lm(df18~interview_age+sex+abuse,data=combined.data.noOutliers))
-summary(lm(df18~interview_age+sex+totalACEs,data=combined.data.noOutliers))
+summary(lm(df18~interview_age+sex+abuse,data=train.data))
+summary(lm(df18~interview_age+sex+totalACEs,data=train.data))
 
-summary(lm(thompson_PC1~interview_age+sex+totalACEs,data=combined.data.noOutliers)) # ***
-summary(lm(thompson_PC2~interview_age+sex+totalACEs,data=combined.data.noOutliers)) # *
-summary(lm(thompson_PC3~interview_age+sex+totalACEs,data=combined.data.noOutliers)) # ***
-summary(lm(thompson_PC1~interview_age+sex+abuse,data=combined.data.noOutliers)) # *
-summary(lm(thompson_PC2~interview_age+sex+abuse,data=combined.data.noOutliers)) #ns
-summary(lm(thompson_PC3~interview_age+sex+abuse,data=combined.data.noOutliers)) # *
+summary(lm(thompson_PC1~interview_age+sex+totalACEs,data=train.data)) # ***
+summary(lm(thompson_PC2~interview_age+sex+totalACEs,data=train.data)) # .
+summary(lm(thompson_PC3~interview_age+sex+totalACEs,data=train.data)) # ***
+summary(lm(thompson_PC1~interview_age+sex+abuse,data=train.data)) #ns
+summary(lm(thompson_PC2~interview_age+sex+abuse,data=train.data)) #ns
+summary(lm(thompson_PC3~interview_age+sex+abuse,data=train.data)) #ns
 
-summary(lm(thompson_PC1~interview_age+sex+df18,data=combined.data.noOutliers)) # ***
-summary(lm(thompson_PC1~interview_age+sex+df16,data=combined.data.noOutliers)) # ***
-summary(lm(thompson_PC1~interview_age+sex+df4,data=combined.data.noOutliers)) # ns
+summary(lm(thompson_PC1~interview_age+sex+df18,data=train.data)) # ***
+summary(lm(thompson_PC1~interview_age+sex+df16,data=train.data)) # ***
+summary(lm(thompson_PC1~interview_age+sex+df4,data=train.data)) # ns
 
 # total FPN:
-summary(lm(thompson_PC1~interview_age+sex+totalFPN,data=combined.data.noOutliers)) # ***
-summary(lm(thompson_PC2~interview_age+sex+totalFPN,data=combined.data.noOutliers)) # .
-summary(lm(thompson_PC3~interview_age+sex+totalFPN,data=combined.data.noOutliers)) # .
+summary(lm(thompson_PC1~interview_age+sex+totalFPN,data=train.data)) # **
+summary(lm(thompson_PC2~interview_age+sex+totalFPN,data=train.data)) # 
+summary(lm(thompson_PC3~interview_age+sex+totalFPN,data=train.data)) #
 
-summary(lm(thompson_PC1~interview_age+sex+totalFPN,data=combined.data.noOutliers[combined.data.noOutliers$totalACEs==0,]))
-summary(lm(thompson_PC1~interview_age+sex+totalFPN,data=combined.data.noOutliers[combined.data.noOutliers$totalACEs>0,]))
+summary(lm(thompson_PC1~interview_age+sex+totalFPN,data=train.data[train.data$totalACEs==0,]))
+summary(lm(thompson_PC1~interview_age+sex+totalFPN,data=train.data[train.data$totalACEs>0,]))
 
-ggplot(data=combined.data.noOutliers,aes(totalFPN,thompson_PC1))+geom_point()+geom_smooth(method="lm")
-ggplot(data=combined.data.noOutliers,aes(totalFPN,thompson_PC2))+geom_point()+geom_smooth(method="lm")
-ggplot(data=combined.data.noOutliers,aes(totalFPN,thompson_PC3))+geom_point()+geom_smooth(method="lm")
+ggplot(data=train.data,aes(totalFPN,thompson_PC1))+geom_point()+geom_smooth(method="lm")
+ggplot(data=train.data,aes(totalFPN,thompson_PC2))+geom_point()+geom_smooth(method="lm")
+ggplot(data=train.data,aes(totalFPN,thompson_PC3))+geom_point()+geom_smooth(method="lm")
 
-combined.data.noOutliers$ACEsFactor <- factor(combined.data.noOutliers$totalACEs==0,labels = c("ACEs","No ACEs"))
-ggplot(data=combined.data.noOutliers,aes(totalFPN,thompson_PC1,color=ACEsFactor))+geom_point(size=1)+geom_smooth(method="lm")
+train.data$ACEsFactor <- factor(train.data$totalACEs==0,labels = c("ACEs","No ACEs"))
+test.data$ACEsFactor <- factor(test.data$totalACEs==0,labels = c("ACEs","No ACEs"))
+
+ggplot(data=train.data,aes(totalFPN,thompson_PC1,color=ACEsFactor))+geom_point(size=1)+geom_smooth(method="lm")
 
@@
 
-ggplot(data=combined.data.noOutliers,aes(interview_age,df18,color=ACEsFactor))+geom_point(size=1)+geom_smooth(method="lm")
+ggplot(data=train.data,aes(interview_age,df18,color=ACEsFactor))+geom_point(size=1)+geom_smooth(method="lm")
 
-ggplot(data=combined.data.noOutliers,aes(interview_age,totalFPN,color=ACEsFactor))+geom_point(size=1)+geom_smooth(method="lm")
+ggplot(data=train.data,aes(interview_age,totalFPN,color=ACEsFactor))+geom_point(size=1)+geom_smooth(method="lm")
+
+summary(lm(thompson_PC1~interview_age+sex+totalFPN,data=combined.data.noOutliers)) # path B ***
+summary(lm(thompson_PC1~interview_age+sex+ACEsFactor,data=combined.data.noOutliers)) # path C ***
+summary(lm(totalFPN~interview_age+sex+ACEsFactor,data=combined.data.noOutliers)) # path A ns
+summary(lm(thompson_PC1~interview_age+sex+totalFPN+ACEsFactor,data=combined.data.noOutliers)) # path C' *** ***
+
+summary(lm(thompson_PC1~interview_age+sex+df18,data=combined.data.noOutliers)) # path B ***
+summary(lm(thompson_PC1~interview_age+sex+ACEsFactor,data=combined.data.noOutliers)) # path C ***
+summary(lm(df18~interview_age+sex+ACEsFactor,data=combined.data.noOutliers)) # path A ns
+summary(lm(thompson_PC1~interview_age+sex+df18+ACEsFactor,data=combined.data.noOutliers)) # path C' *** ***
+
+summary(lm(thompson_PC1~interview_age+sex+df16,data=combined.data.noOutliers)) # path B ***
+summary(lm(thompson_PC1~interview_age+sex+ACEsFactor,data=combined.data.noOutliers)) # path C ***
+summary(lm(df16~interview_age+sex+ACEsFactor,data=combined.data.noOutliers)) # path A ns
+summary(lm(thompson_PC1~interview_age+sex+df16+ACEsFactor,data=combined.data.noOutliers)) # path C' *** ***
+
+summary(lm(thompson_PC1~interview_age+sex+totalFPN*ACEsFactor*sex,data=combined.data.noOutliers))
+
+ggplot(data=train.data[train.data$sex=="M",],aes(ACEsFactor,totalFPN))+geom_col()
+ggplot(data=train.data[train.data$sex=="F",],aes(ACEsFactor,totalFPN))+geom_bar()
 ```
+
+#Plotting
+```{r}
+
+df.summary <- train.data %>%
+     group_by(ACEsFactor,sex) %>%
+     summarise(
+         se = sd(totalFPN, na.rm = TRUE)/sqrt(length(totalFPN)),
+         totalFPN = mean(totalFPN))
+ggplot(data=df.summary, aes(x=sex,y=totalFPN,fill=as.factor(interaction(ACEsFactor,sex)))) +
+  geom_bar(stat="identity",position="dodge") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+panel.background = element_blank(), axis.line = element_line(colour = "black")) +xlab("Biological Sex") + ylab("Total FPN (3, 15, 17) Topography") + geom_errorbar(aes(ymin=totalFPN-se, ymax=totalFPN+se), width=.2,position=position_dodge(.9))+coord_cartesian(ylim=c(11500,12000))
+
+df.summary <- train.data %>%
+     group_by(ACEsFactor,sex) %>%
+     summarise(
+         se = sd(thompson_PC1, na.rm = TRUE)/sqrt(length(thompson_PC1)),
+         thompson_PC1 = mean(thompson_PC1))
+ggplot(data=df.summary, aes(x=sex,y=thompson_PC1,fill=as.factor(interaction(ACEsFactor,sex)))) +
+  geom_bar(stat="identity",position="dodge") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+panel.background = element_blank(), axis.line = element_line(colour = "black")) +xlab("Biological Sex") + ylab("Thompson PC1") + geom_errorbar(aes(ymin=thompson_PC1-se, ymax=thompson_PC1+se), width=.2,position=position_dodge(.9))+coord_cartesian(ylim=c(220,250))
+
+df.summary <- train.data %>%
+     group_by(ACEsFactor,sex) %>%
+     summarise(
+         se = sd(df16, na.rm = TRUE)/sqrt(length(df16)),
+         df16 = mean(df16))
+ggplot(data=df.summary, aes(x=sex,y=df16,fill=as.factor(interaction(ACEsFactor,sex)))) +
+  geom_bar(stat="identity",position="dodge") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+panel.background = element_blank(), axis.line = element_line(colour = "black")) +xlab("Biological Sex") + ylab("Net 15 Topography") + geom_errorbar(aes(ymin=df16-se, ymax=df16+se), width=.2,position=position_dodge(.9))+coord_cartesian(ylim=c(1000,1500))
+
+df.summary <- train.data %>%
+     group_by(ACEsFactor,sex) %>%
+     summarise(
+         se = sd(df4, na.rm = TRUE)/sqrt(length(df4)),
+         df4 = mean(df4))
+ggplot(data=df.summary, aes(x=sex,y=df4,fill=as.factor(interaction(ACEsFactor,sex)))) +
+  geom_bar(stat="identity",position="dodge") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+panel.background = element_blank(), axis.line = element_line(colour = "black")) +xlab("Biological Sex") + ylab("Net 3 Topography") + geom_errorbar(aes(ymin=df4-se, ymax=df4+se), width=.2,position=position_dodge(.9))+coord_cartesian(ylim=c(6000,6500))
+
+df.summary <- train.data %>%
+     group_by(ACEsFactor,sex) %>%
+     summarise(
+         se = sd(thompson_PC3, na.rm = TRUE)/sqrt(length(thompson_PC3)),
+         thompson_PC3 = mean(thompson_PC3))
+ggplot(data=df.summary, aes(x=sex,y=thompson_PC3,fill=as.factor(interaction(ACEsFactor,sex)))) +
+  geom_bar(stat="identity",position="dodge") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+panel.background = element_blank(), axis.line = element_line(colour = "black")) +xlab("Biological Sex") + ylab("Thompson PC3") + geom_errorbar(aes(ymin=thompson_PC3-se, ymax=thompson_PC3+se), width=.2,position=position_dodge(.9))+coord_cartesian(ylim=c(220,250))
+
+```

### 2021-11-15 SOBP_Analyses_BHRC_ABCD_ACEsCog.Rmd
Script for behavioral results in ABCD and BHRC

---
title: "SOBP_Analyses_BHRC_ABCD_ACEsCog"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(width=250)
library(tidyr)
library(dplyr)
library(ggplot2)
library(lsr)
library(lme4)
library(lmerTest)
```

## The goal of these analyses will be to compare ACEs (particularly Threat experiences) to cognition in two samples, the Brazilian High-Risk Cohort (BHRC) and the Adolescent Brain and Cognitive Development (ABCD) study. Here I will collect and organize results with the intention of submitting for SOBP.

## ~~~~~~~~ BHRC ~~~~~~~~

### Load and organize data:
```{r}
# Load and combine dataframes
sle_factors<-readRDS("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/BHRC/thdp_20212904.rds")
ant_scores<-read.csv("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/BHRC/ANT SCORES 100-1700ms RT cutoffs.csv")
demo_data<-read.csv("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/BHRC/BHRCS_w0_Arielle.csv")
proposal.data<-readRDS("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/BHRC/PhD_117BHRC_2021_10_02.rds") 
colnames(sle_factors)[2]<-"SUBJECTID"
colnames(demo_data)[2]<-"SUBJECTID"
combined.data1<-merge(demo_data,ant_scores,by="SUBJECTID")
proposal.data.w0<-proposal.data[proposal.data$redcap_event_name=="wave0_arm_1",c("ident", setdiff(colnames(proposal.data),colnames(combined.data1)))]
combined.data2<-merge(proposal.data.w0,sle_factors,by="ident")
all.data<-merge(combined.data1,combined.data2,by="SUBJECTID")
all.data$gender<-as.factor(all.data$gender)
all.data<-all.data[!is.na(all.data$gender),] #make sure gender variable is available for all participants

# Remove outliers (>3sd) on Alerting, Orienting, and Conflict scores
ALERT.3sd <- sd(all.data[!is.na(all.data$ALERT),]$ALERT)*3
ORIENT.3sd <- sd(all.data[!is.na(all.data$ORIENT),]$ORIENT)*3
CONFLICT.3sd <- sd(all.data[!is.na(all.data$CONFLICT),]$CONFLICT)*3
ALERT.mean <- mean(all.data[!is.na(all.data$ALERT),]$ALERT)
ORIENT.mean <- mean(all.data[!is.na(all.data$ORIENT),]$ORIENT)
CONFLICT.mean <- mean(all.data[!is.na(all.data$CONFLICT),]$CONFLICT)

# These will be separate data structures retaining as many subjects as possible for each of the 3 performance metrics
all.data.ALERT <- all.data[(all.data$ALERT>(ALERT.mean-ALERT.3sd) & all.data$ALERT<(ALERT.mean+ALERT.3sd)),]
all.data.ORIENT <- all.data[(all.data$ORIENT>(ORIENT.mean-ORIENT.3sd) & all.data$ORIENT<(ORIENT.mean+ORIENT.3sd)),]
all.data.CONFLICT <- all.data[(all.data$CONFLICT>(CONFLICT.mean-CONFLICT.3sd) & all.data$CONFLICT<(CONFLICT.mean+CONFLICT.3sd)),]

# This is a complete set with subjects who have all 3 measures within the bounds of 3SD
all.data.complete.set <- all.data[(all.data$ALERT>(ALERT.mean-ALERT.3sd) & all.data$ALERT<(ALERT.mean+ALERT.3sd)) & (all.data$ORIENT>(ORIENT.mean-ORIENT.3sd) & all.data$ORIENT<(ORIENT.mean+ORIENT.3sd)) & (all.data$CONFLICT>(CONFLICT.mean-CONFLICT.3sd) & all.data$CONFLICT<(CONFLICT.mean+CONFLICT.3sd)),]

```

### Threat and deprivation scores are correlated at r=0.39
```{r}
cor.test(all.data.complete.set$threat,all.data.complete.set$depriv)
```

### Run linear models using Threat and Deprivation scores to predict ANT performance metrics
# Note: Gender 1 = Male, Gender 2 = Female
# Key observation: females with greater experiences of Threat have worse Alerting scores
```{r}
summary(lm(ALERT~age+gender+threat+depriv+gender*threat+gender*depriv,data=all.data.ALERT)) #Threat x Gender 0.048*
summary(lm(ORIENT~age+gender+threat+depriv+gender*threat+gender*depriv,data=all.data.complete.set)) #ns
summary(lm(CONFLICT~age+gender+threat+depriv+gender*threat+gender*depriv,data=all.data.complete.set)) #ns

ggplot(data=all.data.ALERT[!is.na(all.data.ALERT$gender),],aes(threat,ALERT))+geom_point(size=1,colour=all.data.ALERT[!is.na(all.data.ALERT$gender),]$age)+geom_smooth(method=lm)+ facet_wrap(~ factor(gender,labels=c("Male","Female")))

all.data.ALERT$threat.binary <- factor(all.data.ALERT$threat>0,labels = c("More Threat","Less Threat"))

df.summary <- all.data.ALERT %>%
     group_by(threat.binary,gender) %>%
     summarise(
         se = sd(ALERT, na.rm = TRUE)/sqrt(length(ALERT)),
         ALERT = mean(ALERT))
ggplot(data=df.summary, aes(x=gender,y=ALERT,fill=as.factor(interaction(threat.binary,gender)))) +
  geom_bar(stat="identity",position="dodge") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +xlab("Gender") + ylab("ALERT") + geom_errorbar(aes(ymin=ALERT-se, ymax=ALERT+se), width=.2,position=position_dodge(.9))+coord_cartesian(ylim=c(0,100))

```

## ~~~~~~~~ ABCD ~~~~~~~~

### Load and organize data:
```{r}
nihtb<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/NihTB/abcd_tbss01.txt",header=TRUE)
nihtb.baseline<-nihtb[nihtb$eventname=="baseline_year_1_arm_1",]
lmt<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/Thomp/lmtp201.txt",header=TRUE)
lmt.baseline<-lmt[lmt$eventname=="baseline_year_1_arm_1",]
merged.data2 <- merge(nihtb.baseline,lmt.baseline[, c("subjectkey", setdiff(colnames(lmt.baseline),colnames(nihtb.baseline)))],by="subjectkey")
ravlt<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/Thomp/abcd_ps01.txt",header=TRUE)
ravlt.baseline<-ravlt[ravlt$eventname=="baseline_year_1_arm_1",]
merged.data3 <- merge(merged.data2,ravlt.baseline[, c("subjectkey", setdiff(colnames(ravlt.baseline),colnames(merged.data2)))],by="subjectkey")
trauma<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/Strife/abcd_ptsd01.txt",header=TRUE)
trauma.baseline<-trauma[trauma$eventname=="baseline_year_1_arm_1",]
combined.data <- merge(merged.data3,trauma.baseline[, c("subjectkey", setdiff(colnames(trauma.baseline),colnames(merged.data3)))],by="subjectkey")
combined.data$nihtbx_flanker_uncorrected <- as.numeric(combined.data$nihtbx_flanker_uncorrected)
combined.data$nihtbx_picvocab_uncorrected <- as.numeric(combined.data$nihtbx_picvocab_uncorrected)
combined.data$nihtbx_list_uncorrected <- as.numeric(combined.data$nihtbx_list_uncorrected)
combined.data$nihtbx_pattern_uncorrected <- as.numeric(combined.data$nihtbx_pattern_uncorrected)
combined.data$nihtbx_cardsort_uncorrected <- as.numeric(combined.data$nihtbx_cardsort_uncorrected)
combined.data$nihtbx_picture_uncorrected <- as.numeric(combined.data$nihtbx_picture_uncorrected)
combined.data$nihtbx_reading_uncorrected <- as.numeric(combined.data$nihtbx_reading_uncorrected)
combined.data$lmt_scr_perc_correct <- as.numeric(combined.data$lmt_scr_perc_correct)
combined.data$pea_ravlt_sd_trial_i_tc <- as.numeric(combined.data$pea_ravlt_sd_trial_i_tc)
combined.data$pea_ravlt_sd_trial_ii_tc <- as.numeric(combined.data$pea_ravlt_sd_trial_ii_tc)
combined.data$pea_ravlt_sd_trial_iii_tc <- as.numeric(combined.data$pea_ravlt_sd_trial_iii_tc)
combined.data$pea_ravlt_sd_trial_iv_tc <- as.numeric(combined.data$pea_ravlt_sd_trial_iv_tc)
combined.data$pea_ravlt_sd_trial_v_tc <- as.numeric(combined.data$pea_ravlt_sd_trial_v_tc)
combined.data$interview_age <- as.numeric(combined.data$interview_age)

ind_pea_ravlt = c(which(names(combined.data)=="pea_ravlt_sd_trial_i_tc"),which(names(combined.data)=="pea_ravlt_sd_trial_ii_tc"),
	which(names(combined.data)=="pea_ravlt_sd_trial_iii_tc"),which(names(combined.data)=="pea_ravlt_sd_trial_iv_tc"),
	which(names(combined.data)=="pea_ravlt_sd_trial_v_tc")); names(combined.data)[ind_pea_ravlt]; summary(combined.data[,ind_pea_ravlt])
combined.data$pea_ravlt_ld = apply(combined.data[,ind_pea_ravlt],1,sum)

combined.data$pea_ravlt_ld <- as.numeric(combined.data$pea_ravlt_ld)

# Rename according to Thompson 2018 code
names(combined.data)[which(names(combined.data)=="nihtbx_picvocab_uncorrected")] = "PicVocab"
names(combined.data)[which(names(combined.data)=="nihtbx_flanker_uncorrected")] = "Flanker"
names(combined.data)[which(names(combined.data)=="nihtbx_list_uncorrected")] = "List"
names(combined.data)[which(names(combined.data)=="nihtbx_cardsort_uncorrected")] = "CardSort"
names(combined.data)[which(names(combined.data)=="nihtbx_pattern_uncorrected")] = "Pattern"
names(combined.data)[which(names(combined.data)=="nihtbx_picture_uncorrected")] = "Picture"
names(combined.data)[which(names(combined.data)=="nihtbx_reading_uncorrected")] = "Reading"
names(combined.data)[which(names(combined.data)=="pea_ravlt_ld")] = "RAVLT"
names(combined.data)[which(names(combined.data)=="lmt_scr_perc_correct")] = "LMT"
```

# Calculate Thompson factor scores, remove outliers, calculate total ACEs
```{r}
combined.data$thompson_PC1 <- (0.754*combined.data$PicVocab)+(0.213*combined.data$Flanker)+(0.471*combined.data$List)+(0.205*combined.data$CardSort)+(0.015*combined.data$Pattern)+(0.012*combined.data$Picture)+(0.82*combined.data$Reading)+(0.306*combined.data$RAVLT)+(0.5*combined.data$LMT)

combined.data$thompson_PC2 <- (0.065*combined.data$PicVocab)+(0.712*combined.data$Flanker)+(0.148*combined.data$List)+(0.71*combined.data$CardSort)+(0.813*combined.data$Pattern)+(0.135*combined.data$Picture)+(0.12*combined.data$Reading)+(0.125*combined.data$RAVLT)+(0.299*combined.data$LMT)

combined.data$thompson_PC3 <- (0.19*combined.data$PicVocab)+(0.067*combined.data$Flanker)+(0.493*combined.data$List)+(0.232*combined.data$CardSort)+(0.085*combined.data$Pattern)+(0.863*combined.data$Picture)+(0.122*combined.data$Reading)+(0.712*combined.data$RAVLT)+(0.068*combined.data$LMT)

mean_PC1 <- mean(combined.data$thompson_PC1,na.rm=TRUE)
mean_PC2 <- mean(combined.data$thompson_PC2,na.rm=TRUE)
mean_PC3 <- mean(combined.data$thompson_PC3,na.rm=TRUE)
sd3_PC1 <- sd(combined.data$thompson_PC1,na.rm=TRUE)*3
sd3_PC2 <- sd(combined.data$thompson_PC2,na.rm=TRUE)*3
sd3_PC3 <- sd(combined.data$thompson_PC3,na.rm=TRUE)*3
sum(combined.data$thompson_PC1 > mean_PC1+sd3_PC1,na.rm=TRUE) # 10 outliers
sum(combined.data$thompson_PC2 > mean_PC2+sd3_PC2,na.rm=TRUE) # 3 outliers
sum(combined.data$thompson_PC3 > mean_PC3+sd3_PC3,na.rm=TRUE) # 2 outliers

combined.data.noOutliers <- combined.data[(combined.data$thompson_PC1>(mean_PC1-sd3_PC1) & combined.data$thompson_PC1<(mean_PC1+sd3_PC1) & combined.data$thompson_PC2>(mean_PC2-sd3_PC2) & combined.data$thompson_PC2<(mean_PC2+sd3_PC2) & combined.data$thompson_PC3>(mean_PC3-sd3_PC3) & combined.data$thompson_PC3<(mean_PC3+sd3_PC3)),]

combined.data.noOutliers[,224:240]<-as.numeric(unlist(combined.data.noOutliers[,224:240]))

combined.data.noOutliers$abuse <- rowSums(data.frame(as.numeric(combined.data.noOutliers$ksads_ptsd_raw_761_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_762_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_763_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_767_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_768_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_769_p)),na.rm=TRUE)
combined.data.noOutliers$totalACEs <- rowSums(data.frame(as.numeric(combined.data.noOutliers$ksads_ptsd_raw_754_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_755_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_756_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_757_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_758_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_759_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_760_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_761_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_762_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_763_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_764_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_765_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_766_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_767_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_768_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_769_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_770_p)),na.rm=TRUE)

family <-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/ses/acspsw03.txt",header=TRUE)
family.baseline<-family[family$eventname=="baseline_year_1_arm_1",]
abcd.data <- merge(combined.data.noOutliers,family.baseline[, c("subjectkey", setdiff(colnames(family.baseline),colnames(combined.data.noOutliers)))],by="subjectkey")
```

```{r}
summary(lmer(thompson_PC1~interview_age+sex+race_ethnicity+(1|rel_family_id)+totalACEs+totalACEs*sex,data=abcd.data))
summary(lmer(thompson_PC2~interview_age+sex+race_ethnicity+(1|rel_family_id)+totalACEs+totalACEs*sex,data=abcd.data))
summary(lmer(thompson_PC3~interview_age+sex+race_ethnicity+(1|rel_family_id)+totalACEs+totalACEs*sex,data=abcd.data))

summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+abuse+abuse*sex,data=abcd.data))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+abuse+abuse*sex,data=abcd.data))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+abuse+abuse*sex,data=abcd.data))
```

### 2021-11-16 SOBP_Analyses_BHRC_ABCD_ACEsCog.Rmd
added ABCD deprivation components

@@
 abcd.data <- merge(combined.data.noOutliers,family.baseline[, c("subjectkey", setdiff(colnames(family.baseline),colnames(combined.data.noOutliers)))],by="subjectkey")
+
+emo.neglect <-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/neglect/crpbi01.txt",header=TRUE)
+emo.neglect.baseline<-emo.neglect[emo.neglect$eventname=="baseline_year_1_arm_1",]
+phy.neglect <-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/neglect/pmq01.txt",header=TRUE)
+phy.neglect.baseline<-phy.neglect[phy.neglect$eventname=="baseline_year_1_arm_1",]
+neglect.data <- merge(emo.neglect.baseline,phy.neglect.baseline[, c("subjectkey", setdiff(colnames(phy.neglect.baseline),colnames(emo.neglect.baseline)))],by="subjectkey")
+
+abcd.data<-merge(abcd.data,neglect.data[,c("subjectkey", setdiff(colnames(neglect.data),colnames(abcd.data)))],by="subjectkey")
+
+# https://www.sciencedirect.com/science/article/pii/S2352289518300821
+abcd.data$acceptance <- rowSums(data.frame(as.numeric(abcd.data$crpbi_parent1_y),as.numeric(abcd.data$crpbi_parent2_y),as.numeric(abcd.data$crpbi_parent3_y),as.numeric(abcd.data$crpbi_parent4_y),as.numeric(abcd.data$crpbi_parent5_y)))
+
+abcd.data$monitoring <- rowSums(data.frame(as.numeric(abcd.data$parent_monitor_q1_y),as.numeric(abcd.data$parent_monitor_q2_y),as.numeric(abcd.data$parent_monitor_q3_y),as.numeric(abcd.data$parent_monitor_q4_y),as.numeric(abcd.data$parent_monitor_q5_y)))
+
 ```
@@
 ```{r}
-summary(lmer(thompson_PC1~interview_age+sex+race_ethnicity+(1|rel_family_id)+totalACEs+totalACEs*sex,data=abcd.data))
-summary(lmer(thompson_PC2~interview_age+sex+race_ethnicity+(1|rel_family_id)+totalACEs+totalACEs*sex,data=abcd.data))
-summary(lmer(thompson_PC3~interview_age+sex+race_ethnicity+(1|rel_family_id)+totalACEs+totalACEs*sex,data=abcd.data))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+totalACEs+totalACEs*sex,data=abcd.data))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+totalACEs+totalACEs*sex,data=abcd.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+totalACEs+totalACEs*sex,data=abcd.data))
 
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+abuse+abuse*sex,data=abcd.data))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+abuse+abuse*sex,data=abcd.data))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+abuse+abuse*sex,data=abcd.data))
+abcd.data$ACEs.binary <- factor(abcd.data$totalACEs>0,labels = c("More Threat","Less Threat"))
+abcd.data$ACEs.binary.numeric <- as.numeric(abcd.data$ACEs.binary)
+
+summary(lmer(ACEs.binary.numeric~interview_age+sex+(1|rel_family_id)+thompson_PC1+thompson_PC2+thompson_PC3,data=abcd.data))
+
+summary(lmer(acceptance~interview_age+sex+(1|rel_family_id)+thompson_PC1+thompson_PC2+thompson_PC3,data=abcd.data))
+summary(lmer(monitoring~interview_age+sex+(1|rel_family_id)+thompson_PC1+thompson_PC2+thompson_PC3,data=abcd.data))
+
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+ACEs.binary.numeric+acceptance+monitoring,data=abcd.data))
+
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+ACEs.binary.numeric+acceptance+monitoring,data=abcd.data))
+
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+ACEs.binary.numeric+acceptance+monitoring,data=abcd.data))
+
+ggplot(data=abcd.data,aes(totalACEs,thompson_PC1))+geom_point(size=1,colour=abcd.data$interview_age)+geom_smooth(method=lm)+ facet_wrap(~ factor(sex,labels=c("Male","Female")))
 ```
+
+# sandbox
+```{r}
+
+ggplot(data=abcd.data,aes(totalACEs,thompson_PC2))+geom_point(size=1,colour=abcd.data$interview_age)+geom_smooth(method=lm)+ facet_wrap(~ factor(sex,labels=c("Male","Female")))
+
+df.summary <- abcd.data %>%
+     group_by(ACEs.binary,sex) %>%
+     summarise(
+         se = sd(thompson_PC2, na.rm = TRUE)/sqrt(length(thompson_PC2)),
+         thompson_PC2 = mean(thompson_PC2))
+ggplot(data=df.summary, aes(x=sex,y=thompson_PC2,fill=as.factor(interaction(ACEs.binary,sex)))) +
+  geom_bar(stat="identity",position="dodge") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+panel.background = element_blank(), axis.line = element_line(colour = "black")) +xlab("Sex") + ylab("thompson_PC2") + geom_errorbar(aes(ymin=thompson_PC2-se, ymax=thompson_PC2+se), width=.2,position=position_dodge(.9))+coord_cartesian(ylim=c(240,265))
+
+df.summary <- abcd.data %>%
+     group_by(ACEs.binary,sex) %>%
+     summarise(
+         se = sd(thompson_PC1, na.rm = TRUE)/sqrt(length(thompson_PC1)),
+         thompson_PC1 = mean(thompson_PC1))
+ggplot(data=df.summary, aes(x=sex,y=thompson_PC1,fill=as.factor(interaction(ACEs.binary,sex)))) +
+  geom_bar(stat="identity",position="dodge") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+panel.background = element_blank(), axis.line = element_line(colour = "black")) +xlab("Sex") + ylab("thompson_PC1") + geom_errorbar(aes(ymin=thompson_PC1-se, ymax=thompson_PC1+se), width=.2,position=position_dodge(.9))+coord_cartesian(ylim=c(220,245))
+
+df.summary <- abcd.data %>%
+     group_by(ACEs.binary,sex) %>%
+     summarise(
+         se = sd(thompson_PC3, na.rm = TRUE)/sqrt(length(thompson_PC3)),
+         thompson_PC3 = mean(thompson_PC3))
+ggplot(data=df.summary, aes(x=sex,y=thompson_PC3,fill=as.factor(interaction(ACEs.binary,sex)))) +
+  geom_bar(stat="identity",position="dodge") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+panel.background = element_blank(), axis.line = element_line(colour = "black")) +xlab("Sex") + ylab("thompson_PC3") + geom_errorbar(aes(ymin=thompson_PC3-se, ymax=thompson_PC3+se), width=.2,position=position_dodge(.9))+coord_cartesian(ylim=c(220,245))
+
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+ACEs.binary+ACEs.binary*interview_age,data=abcd.data))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+ACEs.binary+ACEs.binary*interview_age,data=abcd.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+ACEs.binary+ACEs.binary*interview_age,data=abcd.data))
+
+abcd.data$agesRounded <- round(abcd.data$interview_age)
+df.summary <- abcd.data %>%
+     group_by(ACEs.binary,sex,agesRounded) %>%
+     summarise(
+         se = sd(thompson_PC1, na.rm = TRUE)/sqrt(length(thompson_PC1)),
+         thompson_PC1 = mean(thompson_PC1))
+ggplot(data=df.summary, aes(x=sex,y=thompson_PC1,fill=as.factor(interaction(ACEs.binary,sex)))) +
+  geom_bar(stat="identity",position="dodge") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+panel.background = element_blank(), axis.line = element_line(colour = "black")) +xlab("Sex") + ylab("thompson_PC1") + geom_errorbar(aes(ymin=thompson_PC1-se, ymax=thompson_PC1+se), width=.2,position=position_dodge(.9))+ facet_wrap(~ factor(round(agesRounded)))
+
+df.summary <- abcd.data %>%
+     group_by(ACEs.binary,agesRounded) %>%
+     summarise(
+         se = sd(thompson_PC1, na.rm = TRUE)/sqrt(length(thompson_PC1)),
+         thompson_PC1 = mean(thompson_PC1))
+ggplot(data=df.summary, aes(x=ACEs.binary,y=thompson_PC1)) +
+  geom_bar(stat="identity",position="dodge") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+panel.background = element_blank(), axis.line = element_line(colour = "black")) +xlab("ACEs") + ylab("thompson_PC1") + geom_errorbar(aes(ymin=thompson_PC1-se, ymax=thompson_PC1+se), width=.2,position=position_dodge(.9))+ facet_wrap(~ factor(round(agesRounded)))+coord_cartesian(ylim=c(210,255))
+```

### 2021-11-17 SOBP_Analyses_BHRC_ABCD_ACEsCog.Rmd
final analyses for abstract
this includes each of the analyses for the SOBP abstract

@@
 
-# Calculate Thompson factor scores, remove outliers, calculate total ACEs
+# Calculate Thompson factor scores and remove outliers
 ```{r}
@@
 combined.data.noOutliers <- combined.data[(combined.data$thompson_PC1>(mean_PC1-sd3_PC1) & combined.data$thompson_PC1<(mean_PC1+sd3_PC1) & combined.data$thompson_PC2>(mean_PC2-sd3_PC2) & combined.data$thompson_PC2<(mean_PC2+sd3_PC2) & combined.data$thompson_PC3>(mean_PC3-sd3_PC3) & combined.data$thompson_PC3<(mean_PC3+sd3_PC3)),]
+```
 
+## Calculate types of ACEs
+```{r}
 combined.data.noOutliers[,224:240]<-as.numeric(unlist(combined.data.noOutliers[,224:240]))
 
+# Calculation of subscore with items related to physical and sexual abuse
 combined.data.noOutliers$abuse <- rowSums(data.frame(as.numeric(combined.data.noOutliers$ksads_ptsd_raw_761_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_762_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_763_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_767_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_768_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_769_p)),na.rm=TRUE)
+
+# Calculation of subscore with items related to trauma (car accidents, natural disasters, loss, etc.)
+combined.data.noOutliers$trauma <- rowSums(data.frame(as.numeric(combined.data.noOutliers$ksads_ptsd_raw_754_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_755_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_756_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_757_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_758_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_759_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_760_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_766_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_770_p)),na.rm=TRUE)
+
+# Calculation of total score from the KSADS items
 combined.data.noOutliers$totalACEs <- rowSums(data.frame(as.numeric(combined.data.noOutliers$ksads_ptsd_raw_754_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_755_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_756_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_757_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_758_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_759_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_760_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_761_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_762_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_763_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_764_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_765_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_766_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_767_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_768_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_769_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_770_p)),na.rm=TRUE)
 
+# Remember to add in this variable about family structure so we can use it as a covariate
 family <-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/ses/acspsw03.txt",header=TRUE)
@@
 
-# https://www.sciencedirect.com/science/article/pii/S2352289518300821
+# Calculate subscales of deprivation (emotional and physical neglect) - see this ref for motivation https://www.sciencedirect.com/science/article/pii/S2352289518300821
 abcd.data$acceptance <- rowSums(data.frame(as.numeric(abcd.data$crpbi_parent1_y),as.numeric(abcd.data$crpbi_parent2_y),as.numeric(abcd.data$crpbi_parent3_y),as.numeric(abcd.data$crpbi_parent4_y),as.numeric(abcd.data$crpbi_parent5_y)))
@@
 abcd.data$monitoring <- rowSums(data.frame(as.numeric(abcd.data$parent_monitor_q1_y),as.numeric(abcd.data$parent_monitor_q2_y),as.numeric(abcd.data$parent_monitor_q3_y),as.numeric(abcd.data$parent_monitor_q4_y),as.numeric(abcd.data$parent_monitor_q5_y)))
+```
+
+## Binarize the four ACEs subtypes (2 "Threat" types: Abuse and Trauma; 2 "Deprivation" types: Emotional Neglect and Physical Neglect)
+
+```{r}
+abcd.data$abuse.binary <- factor(abcd.data$abuse>=1,labels = c("No Abuse","Abuse"))
+abcd.data$abuse.binary.numeric <- as.numeric(abcd.data$abuse.binary)
+abcd.data$trauma.binary <- factor(abcd.data$trauma>=1,labels = c("No Trauma","Trauma"))
+abcd.data$trauma.binary.numeric <- as.numeric(abcd.data$trauma.binary)
+
+median.monitoring = median(na.omit(abcd.data$monitoring))
+median.acceptance = median(na.omit(abcd.data$acceptance))
+abcd.data$monitoring.binary <- factor(abcd.data$monitoring<20,labels = c("Low Physical Neglect","High Physical Neglect"))
+abcd.data$monitoring.binary.numeric <- as.numeric(abcd.data$monitoring.binary)
+abcd.data$acceptance.binary <- factor(abcd.data$acceptance<7.5,labels = c("Low Emotional Neglect","High Emotional Neglect"))
+abcd.data$acceptance.binary.numeric <- as.numeric(abcd.data$acceptance.binary)
+```
+
+## Plot everything
+```{r}
+
+data.long <- gather(abcd.data, CogType, CogScore, thompson_PC1,thompson_PC2,thompson_PC3, factor_key=TRUE)
+abcd.long <- gather(data.long, ACEsType, ACEsScore, acceptance.binary.numeric,monitoring.binary.numeric,abuse.binary.numeric,trauma.binary.numeric, factor_key=TRUE)
+
+abcd.long.complete <- abcd.long[complete.cases(abcd.long[,c("CogType","CogScore","ACEsType","ACEsScore")]),c("CogType","CogScore","ACEsType","ACEsScore")]
+
+ggplot(data=abcd.long.complete, aes(x=ACEsScore,y=CogScore,fill=interaction(ACEsType,CogType))) +
+  geom_bar(stat="identity",position="dodge") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+panel.background = element_blank(), axis.line = element_line(colour = "black")) +xlab("ACEs") + ylab("Cognition") +coord_cartesian(ylim=c(250,325)) + facet_grid(abcd.long.complete$ACEsType~abcd.long.complete$CogType)
 
@@
 
+## Run linear mixed effects models!
 ```{r}
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+totalACEs+totalACEs*sex,data=abcd.data))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+totalACEs+totalACEs*sex,data=abcd.data))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+totalACEs+totalACEs*sex,data=abcd.data))
 
-abcd.data$ACEs.binary <- factor(abcd.data$totalACEs>0,labels = c("More Threat","Less Threat"))
-abcd.data$ACEs.binary.numeric <- as.numeric(abcd.data$ACEs.binary)
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+acceptance.binary+monitoring.binary+abuse.binary+trauma.binary,data=abcd.data))
 
-summary(lmer(ACEs.binary.numeric~interview_age+sex+(1|rel_family_id)+thompson_PC1+thompson_PC2+thompson_PC3,data=abcd.data))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+acceptance.binary+monitoring.binary+abuse.binary+trauma.binary,data=abcd.data))
 
-summary(lmer(acceptance~interview_age+sex+(1|rel_family_id)+thompson_PC1+thompson_PC2+thompson_PC3,data=abcd.data))
-summary(lmer(monitoring~interview_age+sex+(1|rel_family_id)+thompson_PC1+thompson_PC2+thompson_PC3,data=abcd.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+acceptance.binary+monitoring.binary+abuse.binary+trauma.binary,data=abcd.data))
 
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+ACEs.binary.numeric+acceptance+monitoring,data=abcd.data))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+acceptance.binary,data=abcd.data))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=abcd.data))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+abuse.binary,data=abcd.data))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary,data=abcd.data))
 
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+ACEs.binary.numeric+acceptance+monitoring,data=abcd.data))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+acceptance.binary,data=abcd.data))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=abcd.data))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+abuse.binary,data=abcd.data))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+trauma.binary,data=abcd.data))
 
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+ACEs.binary.numeric+acceptance+monitoring,data=abcd.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+acceptance.binary,data=abcd.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=abcd.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+abuse.binary,data=abcd.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+trauma.binary,data=abcd.data))
 
-ggplot(data=abcd.data,aes(totalACEs,thompson_PC1))+geom_point(size=1,colour=abcd.data$interview_age)+geom_smooth(method=lm)+ facet_wrap(~ factor(sex,labels=c("Male","Female")))
 ```
@@
 panel.background = element_blank(), axis.line = element_line(colour = "black")) +xlab("ACEs") + ylab("thompson_PC1") + geom_errorbar(aes(ymin=thompson_PC1-se, ymax=thompson_PC1+se), width=.2,position=position_dodge(.9))+ facet_wrap(~ factor(round(agesRounded)))+coord_cartesian(ylim=c(210,255))
+
+df.summary <- abcd.long %>%
+     group_by(ACEsType,ACEsScore,CogType) %>%
+     summarise(
+         se = sd(CogScore, na.rm = TRUE)/sqrt(length(CogScore)),
+         CogScore = mean(na.omit(CogScore)))
+ggplot(data=df.summary, aes(x=ACEsScore,y=CogScore,fill=interaction(ACEsType,CogType))) + geom_bar(stat="identity",position="dodge") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +xlab("ACEs") + ylab("Cognition") +coord_cartesian(ylim=c(220,265)) + geom_errorbar(aes(ymin=CogScore-se, ymax=CogScore+se), width=.2,position=position_dodge(.9)) +  facet_grid(df.summary$ACEsType~df.summary$CogType)
 ```

### 2021-11-18 SOBP_Analyses_BHRC_ABCD_ACEsCog.Rmd
bonferroni correction and moderation effects
Updated bonferroni correction to include adjusted p-values, and added analysis of moderation effects with sex in ABCD dataset.

@@
 
-abcd.long.complete <- abcd.long[complete.cases(abcd.long[,c("CogType","CogScore","ACEsType","ACEsScore")]),c("CogType","CogScore","ACEsType","ACEsScore")]
+abcd.long.complete <- abcd.long[complete.cases(abcd.long[,c("CogType","CogScore","ACEsType","ACEsScore")]),c("CogType","CogScore","ACEsType","ACEsScore","interview_age","sex","rel_family_id")]
 
@@
 summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+acceptance.binary+monitoring.binary+abuse.binary+trauma.binary,data=abcd.data))
+p.adjust(c(0.615, 2e-16,0.035,6.96e-11),method="bonferroni")
 
 summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+acceptance.binary+monitoring.binary+abuse.binary+trauma.binary,data=abcd.data))
+p.adjust(c(0.389, 7.47e-15,0.0096,4.39e-7),method="bonferroni")
 
 summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+acceptance.binary+monitoring.binary+abuse.binary+trauma.binary,data=abcd.data))
+p.adjust(c(0.034, 2e-16,0.014,6.18e-8),method="bonferroni")
+
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary+monitoring.binary*sex,data=abcd.data))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+monitoring.binary+monitoring.binary*sex,data=abcd.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary+monitoring.binary*sex,data=abcd.data))
+
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+abuse.binary+abuse.binary*sex,data=abcd.data))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+abuse.binary+abuse.binary*sex,data=abcd.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+abuse.binary+abuse.binary*sex,data=abcd.data))
+
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary+trauma.binary*sex,data=abcd.data))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+trauma.binary+trauma.binary*sex,data=abcd.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+trauma.binary+trauma.binary*sex,data=abcd.data))
+
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+acceptance.binary+acceptance.binary*sex,data=abcd.data))
+
+summary(lmer(CogScore~interview_age+sex+(1|rel_family_id)+acceptance.binary+CogType+CogType*acceptance.binary,data=data.long))
+summary(lmer(CogScore~interview_age+sex+(1|rel_family_id)+monitoring.binary+CogType+CogType*monitoring.binary,data=data.long))
+summary(lmer(CogScore~interview_age+sex+(1|rel_family_id)+abuse.binary+CogType+CogType*abuse.binary,data=data.long))
+summary(lmer(CogScore~interview_age+sex+(1|rel_family_id)+trauma.binary+CogType+CogType*trauma.binary,data=data.long))
 

### 2021-11-19 ABCD_OHBM_PFN_Analyses.Rmd
Analyses of PFNs in ABCD for OHBM abstract

---
title: "ABCD_OHBM_PFN_Analyses"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(width=250)
library(tidyr)
library(dplyr)
library(ggplot2)
library(lsr)
library(lme4)
library(lmerTest)
```

# First load in the spatial extent of each PFN (they're in order, 1-17)
# Then merge with the same datasets as above (NIH toolbox, trauma, etc.)
```{r}
pfn_sizes <- read.csv("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/All_PFN_sizes.csv")
nihtb<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/NihTB/abcd_tbss01.txt",header=TRUE)
nihtb.baseline<-nihtb[nihtb$eventname=="baseline_year_1_arm_1",]
merged.data1 <- merge(pfn_sizes,nihtb.baseline,by="subjectkey")
lmt<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/Thomp/lmtp201.txt",header=TRUE)
lmt.baseline<-lmt[lmt$eventname=="baseline_year_1_arm_1",]
merged.data2 <- merge(merged.data1,lmt.baseline[, c("subjectkey", setdiff(colnames(lmt.baseline),colnames(merged.data1)))],by="subjectkey")
ravlt<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/Thomp/abcd_ps01.txt",header=TRUE)
ravlt.baseline<-ravlt[ravlt$eventname=="baseline_year_1_arm_1",]
merged.data3 <- merge(merged.data2,ravlt.baseline[, c("subjectkey", setdiff(colnames(ravlt.baseline),colnames(merged.data2)))],by="subjectkey")
trauma<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/Strife/abcd_ptsd01.txt",header=TRUE)
trauma.baseline<-trauma[trauma$eventname=="baseline_year_1_arm_1",]
combined.data <- merge(merged.data3,trauma.baseline[, c("subjectkey", setdiff(colnames(trauma.baseline),colnames(merged.data3)))],by="subjectkey")
```

# Organize behavioral data
```{r}
# Coerce data types
combined.data$nihtbx_flanker_uncorrected <- as.numeric(combined.data$nihtbx_flanker_uncorrected)
combined.data$nihtbx_picvocab_uncorrected <- as.numeric(combined.data$nihtbx_picvocab_uncorrected)
combined.data$nihtbx_list_uncorrected <- as.numeric(combined.data$nihtbx_list_uncorrected)
combined.data$nihtbx_pattern_uncorrected <- as.numeric(combined.data$nihtbx_pattern_uncorrected)
combined.data$nihtbx_cardsort_uncorrected <- as.numeric(combined.data$nihtbx_cardsort_uncorrected)
combined.data$nihtbx_picture_uncorrected <- as.numeric(combined.data$nihtbx_picture_uncorrected)
combined.data$nihtbx_reading_uncorrected <- as.numeric(combined.data$nihtbx_reading_uncorrected)
combined.data$lmt_scr_perc_correct <- as.numeric(combined.data$lmt_scr_perc_correct)
combined.data$pea_ravlt_sd_trial_i_tc <- as.numeric(combined.data$pea_ravlt_sd_trial_i_tc)
combined.data$pea_ravlt_sd_trial_ii_tc <- as.numeric(combined.data$pea_ravlt_sd_trial_ii_tc)
combined.data$pea_ravlt_sd_trial_iii_tc <- as.numeric(combined.data$pea_ravlt_sd_trial_iii_tc)
combined.data$pea_ravlt_sd_trial_iv_tc <- as.numeric(combined.data$pea_ravlt_sd_trial_iv_tc)
combined.data$pea_ravlt_sd_trial_v_tc <- as.numeric(combined.data$pea_ravlt_sd_trial_v_tc)
combined.data$interview_age <- as.numeric(combined.data$interview_age)

ind_pea_ravlt = c(which(names(combined.data)=="pea_ravlt_sd_trial_i_tc"),which(names(combined.data)=="pea_ravlt_sd_trial_ii_tc"),
	which(names(combined.data)=="pea_ravlt_sd_trial_iii_tc"),which(names(combined.data)=="pea_ravlt_sd_trial_iv_tc"),
	which(names(combined.data)=="pea_ravlt_sd_trial_v_tc")); names(combined.data)[ind_pea_ravlt]; summary(combined.data[,ind_pea_ravlt])
combined.data$pea_ravlt_ld = apply(combined.data[,ind_pea_ravlt],1,sum)

combined.data$pea_ravlt_ld <- as.numeric(combined.data$pea_ravlt_ld)

# Rename according to Thompson 2018 code
names(combined.data)[which(names(combined.data)=="nihtbx_picvocab_uncorrected")] = "PicVocab"
names(combined.data)[which(names(combined.data)=="nihtbx_flanker_uncorrected")] = "Flanker"
names(combined.data)[which(names(combined.data)=="nihtbx_list_uncorrected")] = "List"
names(combined.data)[which(names(combined.data)=="nihtbx_cardsort_uncorrected")] = "CardSort"
names(combined.data)[which(names(combined.data)=="nihtbx_pattern_uncorrected")] = "Pattern"
names(combined.data)[which(names(combined.data)=="nihtbx_picture_uncorrected")] = "Picture"
names(combined.data)[which(names(combined.data)=="nihtbx_reading_uncorrected")] = "Reading"
names(combined.data)[which(names(combined.data)=="pea_ravlt_ld")] = "RAVLT"
names(combined.data)[which(names(combined.data)=="lmt_scr_perc_correct")] = "LMT"
```

# Remove subjects based on the following criteria:
## 1) 8min of retained TRs (600 TRs)
## 2) ABCD Booleans for rest and task
```{r}
num_TRs <- read.csv("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/num_TRs_by_subj_redo.csv")
data<-merge(combined.data,num_TRs,by="subjectkey")
data.clean<-data[data$numTRs>=600,] # we go from 9,132 to 8,293 at this step

# Remove participants based on booleans from ABCD
abcd_imgincl01 <- read.csv("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/abcd_imgincl01.csv")
abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$eventnam=="baseline_year_1_arm_1",]
abcd_imgincl01 <- abcd_imgincl01[!abcd_imgincl01$visit=="",] # start here with 11,663 (8,287 of the 9,132 set)
abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_t1w_include==1,] # down to 11,124 (8,045 of the 9,132 set)
abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_rsfmri_include==1,] # down to 9,388 (7,475 of the 9,132 set)
abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_mid_include==1,] # down to 7,847 (6,344 of the 9,132 set)
abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_nback_include==1,] # down to 6,348 (5,161 of the 9,132 set)
abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_sst_include==1,] # down to 5,606 (4,164 of the 9,132 set)

combined.data <- merge(data.clean,abcd_imgincl01[, c("subjectkey",'imgincl_t1w_include')],by="subjectkey")
```

# Calculate Thompson factor scores
```{r}
combined.data$thompson_PC1 <- (0.754*combined.data$PicVocab)+(0.213*combined.data$Flanker)+(0.471*combined.data$List)+(0.205*combined.data$CardSort)+(0.015*combined.data$Pattern)+(0.012*combined.data$Picture)+(0.82*combined.data$Reading)+(0.306*combined.data$RAVLT)+(0.5*combined.data$LMT)

combined.data$thompson_PC2 <- (0.065*combined.data$PicVocab)+(0.712*combined.data$Flanker)+(0.148*combined.data$List)+(0.71*combined.data$CardSort)+(0.813*combined.data$Pattern)+(0.135*combined.data$Picture)+(0.12*combined.data$Reading)+(0.125*combined.data$RAVLT)+(0.299*combined.data$LMT)

combined.data$thompson_PC3 <- (0.19*combined.data$PicVocab)+(0.067*combined.data$Flanker)+(0.493*combined.data$List)+(0.232*combined.data$CardSort)+(0.085*combined.data$Pattern)+(0.863*combined.data$Picture)+(0.122*combined.data$Reading)+(0.712*combined.data$RAVLT)+(0.068*combined.data$LMT)

# Remove outliers
mean_PC1 <- mean(combined.data$thompson_PC1,na.rm=TRUE)
mean_PC2 <- mean(combined.data$thompson_PC2,na.rm=TRUE)
mean_PC3 <- mean(combined.data$thompson_PC3,na.rm=TRUE)
sd3_PC1 <- sd(combined.data$thompson_PC1,na.rm=TRUE)*3
sd3_PC2 <- sd(combined.data$thompson_PC2,na.rm=TRUE)*3
sd3_PC3 <- sd(combined.data$thompson_PC3,na.rm=TRUE)*3
sum(combined.data$thompson_PC1 > mean_PC1+sd3_PC1,na.rm=TRUE) # 8 outliers
sum(combined.data$thompson_PC2 > mean_PC2+sd3_PC2,na.rm=TRUE) # 2 outliers
sum(combined.data$thompson_PC3 > mean_PC3+sd3_PC3,na.rm=TRUE) # 0 outliers
combined.data.noOutliers <- combined.data[combined.data$thompson_PC1>(mean_PC1-sd3_PC1) & combined.data$thompson_PC1<(mean_PC1+sd3_PC1) & combined.data$thompson_PC2>(mean_PC2-sd3_PC2) & combined.data$thompson_PC2<(mean_PC2+sd3_PC2) & combined.data$thompson_PC3>(mean_PC3-sd3_PC3) & combined.data$thompson_PC3<(mean_PC3+sd3_PC3),]
```

# Calculate ACEs variables
```{r}

combined.data.noOutliers[,224:240]<-as.numeric(unlist(combined.data.noOutliers[,224:240]))

# Calculation of subscore with items related to physical and sexual abuse
combined.data.noOutliers$abuse <- rowSums(data.frame(as.numeric(combined.data.noOutliers$ksads_ptsd_raw_761_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_762_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_763_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_767_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_768_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_769_p)),na.rm=TRUE)

# Calculation of subscore with items related to trauma (car accidents, natural disasters, loss, etc.)
combined.data.noOutliers$trauma <- rowSums(data.frame(as.numeric(combined.data.noOutliers$ksads_ptsd_raw_754_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_755_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_756_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_757_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_758_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_759_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_760_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_766_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_770_p)),na.rm=TRUE)

# Remember to add in this variable about family structure so we can use it as a covariate
family <-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/ses/acspsw03.txt",header=TRUE)
family.baseline<-family[family$eventname=="baseline_year_1_arm_1",]
abcd.data <- merge(combined.data.noOutliers,family.baseline[, c("subjectkey", setdiff(colnames(family.baseline),colnames(combined.data.noOutliers)))],by="subjectkey")

emo.neglect <-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/neglect/crpbi01.txt",header=TRUE)
emo.neglect.baseline<-emo.neglect[emo.neglect$eventname=="baseline_year_1_arm_1",]
phy.neglect <-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/neglect/pmq01.txt",header=TRUE)
phy.neglect.baseline<-phy.neglect[phy.neglect$eventname=="baseline_year_1_arm_1",]
neglect.data <- merge(emo.neglect.baseline,phy.neglect.baseline[, c("subjectkey", setdiff(colnames(phy.neglect.baseline),colnames(emo.neglect.baseline)))],by="subjectkey")

abcd.data<-merge(abcd.data,neglect.data[,c("subjectkey", setdiff(colnames(neglect.data),colnames(abcd.data)))],by="subjectkey")

# Calculate subscales of deprivation (emotional and physical neglect) - see this ref for motivation https://www.sciencedirect.com/science/article/pii/S2352289518300821
abcd.data$acceptance <- rowSums(data.frame(as.numeric(abcd.data$crpbi_parent1_y),as.numeric(abcd.data$crpbi_parent2_y),as.numeric(abcd.data$crpbi_parent3_y),as.numeric(abcd.data$crpbi_parent4_y),as.numeric(abcd.data$crpbi_parent5_y)))

abcd.data$monitoring <- rowSums(data.frame(as.numeric(abcd.data$parent_monitor_q1_y),as.numeric(abcd.data$parent_monitor_q2_y),as.numeric(abcd.data$parent_monitor_q3_y),as.numeric(abcd.data$parent_monitor_q4_y),as.numeric(abcd.data$parent_monitor_q5_y)))

abcd.data$abuse.binary <- factor(abcd.data$abuse>=1,labels = c("No Abuse","Abuse"))
abcd.data$abuse.binary.numeric <- as.numeric(abcd.data$abuse.binary)
abcd.data$trauma.binary <- factor(abcd.data$trauma>=1,labels = c("No Trauma","Trauma"))
abcd.data$trauma.binary.numeric <- as.numeric(abcd.data$trauma.binary)

median.monitoring = median(na.omit(abcd.data$monitoring))
median.acceptance = median(na.omit(abcd.data$acceptance))
abcd.data$monitoring.binary <- factor(abcd.data$monitoring<20,labels = c("Low Physical Neglect","High Physical Neglect"))
abcd.data$monitoring.binary.numeric <- as.numeric(abcd.data$monitoring.binary)
abcd.data$acceptance.binary <- factor(abcd.data$acceptance<7.5,labels = c("Low Emotional Neglect","High Emotional Neglect"))
abcd.data$acceptance.binary.numeric <- as.numeric(abcd.data$acceptance.binary)

# calculate a total FPN score
combined.data.noOutliers$totalFPN <- rowSums(data.frame(as.numeric(combined.data.noOutliers$df4),as.numeric(combined.data.noOutliers$df16),as.numeric(combined.data.noOutliers$df18)))

# separate train and test sets
trainIDs <- read.csv("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/train.csv")
train.data <- merge(combined.data.noOutliers,trainIDs,by="subjectkey") # n=2,149
test.data <- combined.data.noOutliers[!is.element(combined.data.noOutliers$subjectkey,trainIDs$subjectkey),] #n=2,424
```

# Run some models!
```{r}

```

### 2021-11-24 ABCD_OHBM_PFN_Analyses.Rmd
Added correlation matrix

@@
 library(lmerTest)
+library(mediation)
+library(ggcorrplot)
+library(corrplot)
+library(RColorBrewer)
 ```
@@
 # calculate a total FPN score
-combined.data.noOutliers$totalFPN <- rowSums(data.frame(as.numeric(combined.data.noOutliers$df4),as.numeric(combined.data.noOutliers$df16),as.numeric(combined.data.noOutliers$df18)))
+abcd.data$totalFPN <- rowSums(data.frame(as.numeric(abcd.data$df4),as.numeric(abcd.data$df16),as.numeric(abcd.data$df18)))
 
@@
 trainIDs <- read.csv("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/train.csv")
-train.data <- merge(combined.data.noOutliers,trainIDs,by="subjectkey") # n=2,149
-test.data <- combined.data.noOutliers[!is.element(combined.data.noOutliers$subjectkey,trainIDs$subjectkey),] #n=2,424
+train.data <- merge(abcd.data,trainIDs,by="subjectkey") # n=2,148
+test.data <- abcd.data[!is.element(abcd.data$subjectkey,trainIDs$subjectkey),] #n=2,151
 ```
@@
 ```{r}
+# Network 17 is specifically associated with PC1 and not PC2 or PC3
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+df18,data=train.data)) #***
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+df18,data=train.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+df18,data=train.data))
+
+# Network 15 is specifically associated with PC1 and PC3 but not PC2
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+df16,data=train.data)) #**
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+df16,data=train.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+df16,data=train.data)) #**
+
+# Network 3 is not associated with any of the PCs
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+df4,data=train.data)) 
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+df4,data=train.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+df4,data=train.data))
+
+# We already know that trauma and physical neglect are associated with impairment in PC1
+# Physical neglect is also associated with impairment in PC3
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary,data=train.data)) #**
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=train.data)) #***
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=train.data)) #***
+
+# Are any subtypes of ACEs associated with PFN topography?
+summary(lmer(totalFPN~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=train.data)) # ns
+summary(lmer(totalFPN~interview_age+sex+(1|rel_family_id)+acceptance.binary,data=train.data)) # ns
+summary(lmer(totalFPN~interview_age+sex+(1|rel_family_id)+abuse.binary,data=train.data)) # ns
+summary(lmer(totalFPN~interview_age+sex+(1|rel_family_id)+trauma.binary,data=train.data)) # ns
+
+summary(lmer(df18~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=train.data)) # ns
+summary(lmer(df18~interview_age+sex+(1|rel_family_id)+acceptance.binary,data=train.data)) # ns
+summary(lmer(df18~interview_age+sex+(1|rel_family_id)+abuse.binary,data=train.data)) # ns
+summary(lmer(df18~interview_age+sex+(1|rel_family_id)+trauma.binary,data=train.data)) # ns
+
+summary(lmer(df16~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=train.data)) # ns (0.056)
+summary(lmer(df16~interview_age+sex+(1|rel_family_id)+acceptance.binary,data=train.data)) # ns
+summary(lmer(df16~interview_age+sex+(1|rel_family_id)+abuse.binary,data=train.data)) # ns
+summary(lmer(df16~interview_age+sex+(1|rel_family_id)+trauma.binary,data=train.data)) # ns
+
+summary(lmer(df4~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=train.data)) # ns
+summary(lmer(df4~interview_age+sex+(1|rel_family_id)+acceptance.binary,data=train.data)) # ns
+summary(lmer(df4~interview_age+sex+(1|rel_family_id)+abuse.binary,data=train.data)) # ns
+summary(lmer(df4~interview_age+sex+(1|rel_family_id)+trauma.binary,data=train.data)) # ns
 
 ```
+
+# Mediation analyses -- these are significant!
+```{r}
+# Mediation: trauma --> Network 17 --> PC1 (path C does decrease) *
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary,data=train.data))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary+df18,data=train.data))
+
+bs_indir = c()
+for (i in 1:1000){
+  thisSample <- sample(c(1:length(train.data$subjectkey)),length(train.data$subjectkey),replace=TRUE)
+  pathc<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary,data=train.data[thisSample,])
+  pathcp<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary+df18,data=train.data[thisSample,])
+  indir<-fixef(pathc)[4]-fixef(pathcp)[5]
+  bs_indir <- c(bs_indir,indir)
+}
+t.test(bs_indir,conf.level=0.95)
+
+# Mediation: trauma --> Network 15 --> PC1 (path C does not decrease)
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary,data=train.data))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary+df16,data=train.data))
+
+# Mediation: physical neglect --> Network 17 --> PC1 (path C does decrease) *
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=train.data))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary+df18,data=train.data))
+
+bs_indir = c()
+for (i in 1:1000){
+  thisSample <- sample(c(1:length(train.data$subjectkey)),length(train.data$subjectkey),replace=TRUE)
+  pathc<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=train.data[thisSample,])
+  pathcp<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary+df18,data=train.data[thisSample,])
+  indir<-fixef(pathc)[4]-fixef(pathcp)[5]
+  bs_indir <- c(bs_indir,indir)
+}
+t.test(bs_indir,conf.level=0.95)
+
+# Mediation: physical neglect --> Network 15 --> PC1 (path C does not decrease)
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=train.data))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary+df16,data=train.data))
+
+# Mediation: physical neglect --> Network 17 --> PC3 (path C does decrease) *
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=train.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary+df18,data=train.data))
+
+bs_indir = c()
+for (i in 1:1000){
+  thisSample <- sample(c(1:length(train.data$subjectkey)),length(train.data$subjectkey),replace=TRUE)
+  pathc<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=train.data[thisSample,])
+  pathcp<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary+df18,data=train.data[thisSample,])
+  indir<-fixef(pathc)[4]-fixef(pathcp)[5]
+  bs_indir <- c(bs_indir,indir)
+}
+t.test(bs_indir,conf.level=0.95)
+
+# Mediation: physical neglect --> Network 15 --> PC3 (path C does not decrease)
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=train.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary+df16,data=train.data))
+
+```
+
+# No moderations were significant
+```{r}
+# Moderation: trauma * Network 17 --> PC1
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary*df18,data=train.data))
+
+# Moderation: trauma * Network 15 --> PC1
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary*df16,data=train.data))
+
+# Moderation: physical neglect * Network 17 --> PC1
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary*df18,data=train.data))
+
+# Moderation: physical neglect * Network 15 --> PC1
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary*df16,data=train.data))
+
+# Moderation: physical neglect * Network 17 --> PC3
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary*df18,data=train.data))
+
+# Moderation: physical neglect * Network 15 --> PC3 
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary*df16,data=train.data))
+
+# Moderation: sex * trauma * Network 17 --> PC1
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary*df18*sex,data=train.data))
+
+# Moderation: sex * trauma * Network 15 --> PC1
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary*df16*sex,data=train.data))
+
+# Moderation: sex * physical neglect * Network 17 --> PC1
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary*df18*sex,data=train.data))
+
+# Moderation: sex * physical neglect * Network 15 --> PC1
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary*df16*sex,data=train.data))
+
+# Moderation: sex * physical neglect * Network 17 --> PC3
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary*df18*sex,data=train.data))
+
+# Moderation: sex * physical neglect * Network 15 --> PC3 
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary*df16*sex,data=train.data))
+```
+
+# Analyses of total FPN
+```{r}
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+totalFPN,data=train.data)) #**
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+totalFPN,data=train.data)) #ns
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+totalFPN,data=train.data)) #ns
+
+summary(lmer(totalFPN~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=train.data)) #ns
+summary(lmer(totalFPN~interview_age+sex+(1|rel_family_id)+acceptance.binary,data=train.data)) #ns
+summary(lmer(totalFPN~interview_age+sex+(1|rel_family_id)+abuse.binary,data=train.data)) #ns
+summary(lmer(totalFPN~interview_age+sex+(1|rel_family_id)+trauma.binary,data=train.data)) #ns
+
+summary(lmer(totalFPN~interview_age+sex+(1|rel_family_id)+monitoring.binary*sex,data=train.data)) #ns
+summary(lmer(totalFPN~interview_age+sex+(1|rel_family_id)+acceptance.binary*sex,data=train.data)) #ns
+summary(lmer(totalFPN~interview_age+sex+(1|rel_family_id)+abuse.binary*sex,data=train.data)) #ns
+summary(lmer(totalFPN~interview_age+sex+(1|rel_family_id)+trauma.binary*sex,data=train.data)) #ns
+
+```
+
+# Port data over to matlab (womp) so I can run the Canlab multilevel mediation toolbox 
+```{r}
+write.csv(train.data,file="trainData_forMatlab.csv")
+write.csv(test.data,file="testData_forMatlab.csv")
+```
+
+# Create a correlation matrix of all the important variables
+```{r}
+important.variables <- train.data[,c("interview_age","monitoring","acceptance","abuse","trauma","df2","df3","df4","df5","df6","df7","df8","df9","df10","df11","df12","df13","df14","df15","df16","df17","df18","thompson_PC1","thompson_PC2","thompson_PC3")]
+
+colnames(important.variables)<-c("Age","Phys Neglect","Emo Neglect","Abuse","Trauma","PFN 1","PFN 2","PFN 3","PFN 4","PFN 5","PFN 6","PFN 7","PFN 8","PFN 9","PFN 10","PFN 11","PFN 12","PFN 13","PFN 14","PFN 15","PFN 16","PFN 17","General Cog (PC1)","Exec Fxn (PC2)","Learn/Mem (PC3)")
+
+png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/ABCD_PFNs_ACES_Cog_CorrMatrix.png",
+    width = 8000, 
+    height = 4000,
+    res=300)
+corrplot(cor(important.variables,use="complete.obs"),method=c("number"), tl.col = "black", col=brewer.pal(n=8, name="Spectral"))
+dev.off() 
+```

### 2021-12-14 PaperOutline_ACEsCog.Rmd
Paper outline

--- 2021-11-18 SOBP_Analyses_BHRC_ABCD_ACEsCog.Rmd
@@
+---
+title: "PaperOutline_ACEsCog"
+author: "Arielle Keller"
+date: "12/14/2021"
+output: html_document
+---
+
 ---
@@
 library(lmerTest)
+library(RColorBrewer)
 ```
@@
 ## The goal of these analyses will be to compare ACEs (particularly Threat experiences) to cognition in two samples, the Brazilian High-Risk Cohort (BHRC) and the Adolescent Brain and Cognitive Development (ABCD) study.
-Here I will collect and organize results with the intention of submitting for SOBP.
 
@@
 
+# Add new data for BHRC
+new_cog_data<-readRDS("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/BHRC/BHRCS_Cog_IQ_TDE_w0.rds")
+colnames(new_cog_data)[1]<-"SUBJECTID"
+all.data.new<-merge(all.data.complete.set,new_cog_data[,c("SUBJECTID", setdiff(colnames(new_cog_data),colnames(all.data.complete.set)))],by="SUBJECTID")
+
 ```
 
-### Threat and deprivation scores are correlated at r=0.39
+### Run linear models using Threat and Deprivation scores to predict cognition
+# Note: Gender 1 = Male, Gender 2 = Female
+# Covariates for age, gender, and random effects for school and state
+
+# Significant:
 ```{r}
-cor.test(all.data.complete.set$threat,all.data.complete.set$depriv)
+summary(lmer(EF~age+gender+(1|state)+(1|schoolID)+threat,data=all.data.new)) # ***
+summary(lmer(EF~age+gender+(1|state)+(1|schoolID)+depriv,data=all.data.new)) # ***
+
+summary(lmer(WM~age+gender+(1|state)+(1|schoolID)+threat,data=all.data.new)) # * (does not pass correction)
+summary(lmer(WM~age+gender+(1|state)+(1|schoolID)+depriv,data=all.data.new)) # ***
+
+summary(lmer(TP~age+gender+(1|state)+(1|schoolID)+threat,data=all.data.new)) # ***
+summary(lmer(TP~age+gender+(1|state)+(1|schoolID)+depriv,data=all.data.new)) # ***
+
+p.adjust(c(0.000463,9.78e-07,0.0184,1.16e-07,0.000233,5.03e-06),method="bonferroni")
+
 ```
 
-### Run linear models using Threat and Deprivation scores to predict ANT performance metrics
-# Note: Gender 1 = Male, Gender 2 = Female
-# Key observation: females with greater experiences of Threat have worse Alerting scores
+# Plots:
 ```{r}
-summary(lm(ALERT~age+gender+threat+depriv+gender*threat+gender*depriv,data=all.data.ALERT)) #Threat x Gender 0.048*
-summary(lm(ORIENT~age+gender+threat+depriv+gender*threat+gender*depriv,data=all.data.complete.set)) #ns
-summary(lm(CONFLICT~age+gender+threat+depriv+gender*threat+gender*depriv,data=all.data.complete.set)) #ns
+correlation <- cor.test(all.data.new$threat,all.data.new$WM)
+ggplot(data=all.data.new,aes(threat,WM))+geom_point(size=1,colour='#70677D')+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Working Memory') + xlab('Threat') + ggtitle(paste("r=",as.character(round(correlation$estimate,3)),", p=",as.character(round(correlation$p.value,3))))
 
-ggplot(data=all.data.ALERT[!is.na(all.data.ALERT$gender),],aes(threat,ALERT))+geom_point(size=1,colour=all.data.ALERT[!is.na(all.data.ALERT$gender),]$age)+geom_smooth(method=lm)+ facet_wrap(~ factor(gender,labels=c("Male","Female")))
+correlation <- cor.test(all.data.new$depriv,all.data.new$WM)
+ggplot(data=all.data.new,aes(depriv,WM))+geom_point(size=1,colour='#7393C4')+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Working Memory') + xlab('Deprivation') + ggtitle(paste("r=",as.character(round(correlation$estimate,3)),", p=",as.character(round(correlation$p.value,3))))
+```
 
-all.data.ALERT$threat.binary <- factor(all.data.ALERT$threat>0,labels = c("More Threat","Less Threat"))
+# Non-significant:
+```{r}
+summary(lmer(ALERT~age+gender+(1|state)+(1|schoolID)+threat,data=all.data.new)) #ns
+summary(lmer(ORIENT~age+gender+(1|state)+(1|schoolID)+threat,data=all.data.new)) #ns
+summary(lmer(CONFLICT~age+gender+(1|state)+(1|schoolID)+threat,data=all.data.new)) #ns
 
-df.summary <- all.data.ALERT %>%
-     group_by(threat.binary,gender) %>%
-     summarise(
-         se = sd(ALERT, na.rm = TRUE)/sqrt(length(ALERT)),
-         ALERT = mean(ALERT))
-ggplot(data=df.summary, aes(x=gender,y=ALERT,fill=as.factor(interaction(threat.binary,gender)))) +
-  geom_bar(stat="identity",position="dodge") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
-panel.background = element_blank(), axis.line = element_line(colour = "black")) +xlab("Gender") + ylab("ALERT") + geom_errorbar(aes(ymin=ALERT-se, ymax=ALERT+se), width=.2,position=position_dodge(.9))+coord_cartesian(ylim=c(0,100))
+summary(lmer(ALERT~age+gender+(1|state)+(1|schoolID)+depriv,data=all.data.new)) #ns
+summary(lmer(ORIENT~age+gender+(1|state)+(1|schoolID)+depriv,data=all.data.new)) #ns
+summary(lmer(CONFLICT~age+gender+(1|state)+(1|schoolID)+depriv,data=all.data.new)) #ns
 
+summary(lmer(ALERT~age+gender+(1|state)+(1|schoolID)+threat+depriv+threat*gender+depriv*gender,data=all.data.new)) # 0.055
+
+summary(lmer(IC~age+gender+(1|state)+(1|schoolID)+threat,data=all.data.new)) # ns
+summary(lmer(IC~age+gender+(1|state)+(1|schoolID)+depriv,data=all.data.new)) # ns
 ```
@@
 names(combined.data)[which(names(combined.data)=="lmt_scr_perc_correct")] = "LMT"
-```
 
 # Calculate Thompson factor scores and remove outliers
-```{r}
 combined.data$thompson_PC1 <- (0.754*combined.data$PicVocab)+(0.213*combined.data$Flanker)+(0.471*combined.data$List)+(0.205*combined.data$CardSort)+(0.015*combined.data$Pattern)+(0.012*combined.data$Picture)+(0.82*combined.data$Reading)+(0.306*combined.data$RAVLT)+(0.5*combined.data$LMT)
@@
 combined.data.noOutliers <- combined.data[(combined.data$thompson_PC1>(mean_PC1-sd3_PC1) & combined.data$thompson_PC1<(mean_PC1+sd3_PC1) & combined.data$thompson_PC2>(mean_PC2-sd3_PC2) & combined.data$thompson_PC2<(mean_PC2+sd3_PC2) & combined.data$thompson_PC3>(mean_PC3-sd3_PC3) & combined.data$thompson_PC3<(mean_PC3+sd3_PC3)),]
-```
 
-## Calculate types of ACEs
-```{r}
+# Calculate types of ACEs
 combined.data.noOutliers[,224:240]<-as.numeric(unlist(combined.data.noOutliers[,224:240]))
@@
 abcd.data$monitoring <- rowSums(data.frame(as.numeric(abcd.data$parent_monitor_q1_y),as.numeric(abcd.data$parent_monitor_q2_y),as.numeric(abcd.data$parent_monitor_q3_y),as.numeric(abcd.data$parent_monitor_q4_y),as.numeric(abcd.data$parent_monitor_q5_y)))
-```
 
-## Binarize the four ACEs subtypes (2 "Threat" types: Abuse and Trauma; 2 "Deprivation" types: Emotional Neglect and Physical Neglect)
-
-```{r}
+# Binarize the four ACEs subtypes (2 "Threat" types: Abuse and Trauma; 2 "Deprivation" types: Emotional Neglect and Physical Neglect)
 abcd.data$abuse.binary <- factor(abcd.data$abuse>=1,labels = c("No Abuse","Abuse"))
@@
 ```
-
-# sandbox
-```{r}
-
-ggplot(data=abcd.data,aes(totalACEs,thompson_PC2))+geom_point(size=1,colour=abcd.data$interview_age)+geom_smooth(method=lm)+ facet_wrap(~ factor(sex,labels=c("Male","Female")))
-
-df.summary <- abcd.data %>%
-     group_by(ACEs.binary,sex) %>%
-     summarise(
-         se = sd(thompson_PC2, na.rm = TRUE)/sqrt(length(thompson_PC2)),
-         thompson_PC2 = mean(thompson_PC2))
-ggplot(data=df.summary, aes(x=sex,y=thompson_PC2,fill=as.factor(interaction(ACEs.binary,sex)))) +
-  geom_bar(stat="identity",position="dodge") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
-panel.background = element_blank(), axis.line = element_line(colour = "black")) +xlab("Sex") + ylab("thompson_PC2") + geom_errorbar(aes(ymin=thompson_PC2-se, ymax=thompson_PC2+se), width=.2,position=position_dodge(.9))+coord_cartesian(ylim=c(240,265))
-
-df.summary <- abcd.data %>%
-     group_by(ACEs.binary,sex) %>%
-     summarise(
-         se = sd(thompson_PC1, na.rm = TRUE)/sqrt(length(thompson_PC1)),
-         thompson_PC1 = mean(thompson_PC1))
-ggplot(data=df.summary, aes(x=sex,y=thompson_PC1,fill=as.factor(interaction(ACEs.binary,sex)))) +
-  geom_bar(stat="identity",position="dodge") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
-panel.background = element_blank(), axis.line = element_line(colour = "black")) +xlab("Sex") + ylab("thompson_PC1") + geom_errorbar(aes(ymin=thompson_PC1-se, ymax=thompson_PC1+se), width=.2,position=position_dodge(.9))+coord_cartesian(ylim=c(220,245))
-
-df.summary <- abcd.data %>%
-     group_by(ACEs.binary,sex) %>%
-     summarise(
-         se = sd(thompson_PC3, na.rm = TRUE)/sqrt(length(thompson_PC3)),
-         thompson_PC3 = mean(thompson_PC3))
-ggplot(data=df.summary, aes(x=sex,y=thompson_PC3,fill=as.factor(interaction(ACEs.binary,sex)))) +
-  geom_bar(stat="identity",position="dodge") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
-panel.background = element_blank(), axis.line = element_line(colour = "black")) +xlab("Sex") + ylab("thompson_PC3") + geom_errorbar(aes(ymin=thompson_PC3-se, ymax=thompson_PC3+se), width=.2,position=position_dodge(.9))+coord_cartesian(ylim=c(220,245))
-
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+ACEs.binary+ACEs.binary*interview_age,data=abcd.data))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+ACEs.binary+ACEs.binary*interview_age,data=abcd.data))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+ACEs.binary+ACEs.binary*interview_age,data=abcd.data))
-
-abcd.data$agesRounded <- round(abcd.data$interview_age)
-df.summary <- abcd.data %>%
-     group_by(ACEs.binary,sex,agesRounded) %>%
-     summarise(
-         se = sd(thompson_PC1, na.rm = TRUE)/sqrt(length(thompson_PC1)),
-         thompson_PC1 = mean(thompson_PC1))
-ggplot(data=df.summary, aes(x=sex,y=thompson_PC1,fill=as.factor(interaction(ACEs.binary,sex)))) +
-  geom_bar(stat="identity",position="dodge") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
-panel.background = element_blank(), axis.line = element_line(colour = "black")) +xlab("Sex") + ylab("thompson_PC1") + geom_errorbar(aes(ymin=thompson_PC1-se, ymax=thompson_PC1+se), width=.2,position=position_dodge(.9))+ facet_wrap(~ factor(round(agesRounded)))
-
-df.summary <- abcd.data %>%
-     group_by(ACEs.binary,agesRounded) %>%
-     summarise(
-         se = sd(thompson_PC1, na.rm = TRUE)/sqrt(length(thompson_PC1)),
-         thompson_PC1 = mean(thompson_PC1))
-ggplot(data=df.summary, aes(x=ACEs.binary,y=thompson_PC1)) +
-  geom_bar(stat="identity",position="dodge") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
-panel.background = element_blank(), axis.line = element_line(colour = "black")) +xlab("ACEs") + ylab("thompson_PC1") + geom_errorbar(aes(ymin=thompson_PC1-se, ymax=thompson_PC1+se), width=.2,position=position_dodge(.9))+ facet_wrap(~ factor(round(agesRounded)))+coord_cartesian(ylim=c(210,255))
-
-df.summary <- abcd.long %>%
-     group_by(ACEsType,ACEsScore,CogType) %>%
-     summarise(
-         se = sd(CogScore, na.rm = TRUE)/sqrt(length(CogScore)),
-         CogScore = mean(na.omit(CogScore)))
-ggplot(data=df.summary, aes(x=ACEsScore,y=CogScore,fill=interaction(ACEsType,CogType))) + geom_bar(stat="identity",position="dodge") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +xlab("ACEs") + ylab("Cognition") +coord_cartesian(ylim=c(220,265)) + geom_errorbar(aes(ymin=CogScore-se, ymax=CogScore+se), width=.2,position=position_dodge(.9)) +  facet_grid(df.summary$ACEsType~df.summary$CogType)
-```

### 2022-01-26 PaperOutline_ACEsCog.Rmd
physical vs. emotional neglect
focused on analyses of physical vs emotional neglect instead of threat vs. deprviation

@@
 
----
-title: "SOBP_Analyses_BHRC_ABCD_ACEsCog"
-output: html_document
----
 ```{r setup, include=FALSE}
@@
 library(lmerTest)
+library(ggcorrplot)
+library(corrplot)
 library(RColorBrewer)
@@
 
-## The goal of these analyses will be to compare ACEs (particularly Threat experiences) to cognition in two samples, the Brazilian High-Risk Cohort (BHRC) and the Adolescent Brain and Cognitive Development (ABCD) study.
+# The goal of these analyses will be to compare ACEs (particularly Threat experiences) to cognition in two samples, the Brazilian High-Risk Cohort (BHRC) and the Adolescent Brain and Cognitive Development (ABCD) study.
 
@@
 sle_factors<-readRDS("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/BHRC/thdp_20212904.rds")
-ant_scores<-read.csv("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/BHRC/ANT SCORES 100-1700ms RT cutoffs.csv")
+#ant_scores<-read.csv("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/BHRC/ANT SCORES 100-1700ms RT cutoffs.csv")
 demo_data<-read.csv("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/BHRC/BHRCS_w0_Arielle.csv")
 proposal.data<-readRDS("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/BHRC/PhD_117BHRC_2021_10_02.rds") 
-colnames(sle_factors)[2]<-"SUBJECTID"
+data_depriv_emoneg<-readRDS("/Users/ariellekeller/Downloads/Arielle_BHRC_2021_12_26_2.rds")
+sle_and_depriv <- merge(sle_factors[,c(1,2,4,5)],data_depriv_emoneg,by="ident") #don't duplicate redcap event name
+colnames(sle_and_depriv)[2]<-"SUBJECTID"
 colnames(demo_data)[2]<-"SUBJECTID"
-combined.data1<-merge(demo_data,ant_scores,by="SUBJECTID")
-proposal.data.w0<-proposal.data[proposal.data$redcap_event_name=="wave0_arm_1",c("ident", setdiff(colnames(proposal.data),colnames(combined.data1)))]
-combined.data2<-merge(proposal.data.w0,sle_factors,by="ident")
-all.data<-merge(combined.data1,combined.data2,by="SUBJECTID")
+#combined.data1<-merge(demo_data,ant_scores,by="SUBJECTID")
+proposal.data.w0<-proposal.data[proposal.data$redcap_event_name=="wave0_arm_1",c("ident", setdiff(colnames(proposal.data),colnames(demo_data)))]
+combined.data2<-merge(proposal.data.w0,sle_and_depriv[,c("ident", setdiff(colnames(sle_and_depriv),colnames(proposal.data.w0)))],by="ident")
+all.data<-merge(demo_data,combined.data2[,c("SUBJECTID", setdiff(colnames(combined.data2),colnames(demo_data)))],by="SUBJECTID")
 all.data$gender<-as.factor(all.data$gender)
 all.data<-all.data[!is.na(all.data$gender),] #make sure gender variable is available for all participants
-
-# Remove outliers (>3sd) on Alerting, Orienting, and Conflict scores
-ALERT.3sd <- sd(all.data[!is.na(all.data$ALERT),]$ALERT)*3
-ORIENT.3sd <- sd(all.data[!is.na(all.data$ORIENT),]$ORIENT)*3
-CONFLICT.3sd <- sd(all.data[!is.na(all.data$CONFLICT),]$CONFLICT)*3
-ALERT.mean <- mean(all.data[!is.na(all.data$ALERT),]$ALERT)
-ORIENT.mean <- mean(all.data[!is.na(all.data$ORIENT),]$ORIENT)
-CONFLICT.mean <- mean(all.data[!is.na(all.data$CONFLICT),]$CONFLICT)
-
-# These will be separate data structures retaining as many subjects as possible for each of the 3 performance metrics
-all.data.ALERT <- all.data[(all.data$ALERT>(ALERT.mean-ALERT.3sd) & all.data$ALERT<(ALERT.mean+ALERT.3sd)),]
-all.data.ORIENT <- all.data[(all.data$ORIENT>(ORIENT.mean-ORIENT.3sd) & all.data$ORIENT<(ORIENT.mean+ORIENT.3sd)),]
-all.data.CONFLICT <- all.data[(all.data$CONFLICT>(CONFLICT.mean-CONFLICT.3sd) & all.data$CONFLICT<(CONFLICT.mean+CONFLICT.3sd)),]
-
-# This is a complete set with subjects who have all 3 measures within the bounds of 3SD
-all.data.complete.set <- all.data[(all.data$ALERT>(ALERT.mean-ALERT.3sd) & all.data$ALERT<(ALERT.mean+ALERT.3sd)) & (all.data$ORIENT>(ORIENT.mean-ORIENT.3sd) & all.data$ORIENT<(ORIENT.mean+ORIENT.3sd)) & (all.data$CONFLICT>(CONFLICT.mean-CONFLICT.3sd) & all.data$CONFLICT<(CONFLICT.mean+CONFLICT.3sd)),]
+# 
+# # Remove outliers (>3sd) on Alerting, Orienting, and Conflict scores
+# ALERT.3sd <- sd(all.data[!is.na(all.data$ALERT),]$ALERT)*3
+# ORIENT.3sd <- sd(all.data[!is.na(all.data$ORIENT),]$ORIENT)*3
+# CONFLICT.3sd <- sd(all.data[!is.na(all.data$CONFLICT),]$CONFLICT)*3
+# ALERT.mean <- mean(all.data[!is.na(all.data$ALERT),]$ALERT)
+# ORIENT.mean <- mean(all.data[!is.na(all.data$ORIENT),]$ORIENT)
+# CONFLICT.mean <- mean(all.data[!is.na(all.data$CONFLICT),]$CONFLICT)
+# 
+# # These will be separate data structures retaining as many subjects as possible for each of the 3 performance metrics
+# all.data.ALERT <- all.data[(all.data$ALERT>(ALERT.mean-ALERT.3sd) & all.data$ALERT<(ALERT.mean+ALERT.3sd)),]
+# all.data.ORIENT <- all.data[(all.data$ORIENT>(ORIENT.mean-ORIENT.3sd) & all.data$ORIENT<(ORIENT.mean+ORIENT.3sd)),]
+# all.data.CONFLICT <- all.data[(all.data$CONFLICT>(CONFLICT.mean-CONFLICT.3sd) & all.data$CONFLICT<(CONFLICT.mean+CONFLICT.3sd)),]
+# 
+# # This is a complete set with subjects who have all 3 measures within the bounds of 3SD
+# all.data.complete.set <- all.data[(all.data$ALERT>(ALERT.mean-ALERT.3sd) & all.data$ALERT<(ALERT.mean+ALERT.3sd)) & (all.data$ORIENT>(ORIENT.mean-ORIENT.3sd) & all.data$ORIENT<(ORIENT.mean+ORIENT.3sd)) & (all.data$CONFLICT>(CONFLICT.mean-CONFLICT.3sd) & all.data$CONFLICT<(CONFLICT.mean+CONFLICT.3sd)),]
 
@@
 colnames(new_cog_data)[1]<-"SUBJECTID"
-all.data.new<-merge(all.data.complete.set,new_cog_data[,c("SUBJECTID", setdiff(colnames(new_cog_data),colnames(all.data.complete.set)))],by="SUBJECTID")
+all.data.new<-merge(all.data,new_cog_data[,c("SUBJECTID", setdiff(colnames(new_cog_data),colnames(all.data)))],by="SUBJECTID")
 
@@
 
-### Run linear models using Threat and Deprivation scores to predict cognition
-# Note: Gender 1 = Male, Gender 2 = Female
-# Covariates for age, gender, and random effects for school and state
+```{r}
+# Remove outliers (>3sd)
+EF.3sd <- sd(all.data.new[!is.na(all.data.new$EF),]$EF)*3
+WM.3sd <- sd(all.data.new[!is.na(all.data.new$WM),]$WM)*3
+TP.3sd <- sd(all.data.new[!is.na(all.data.new$TP),]$TP)*3
+IC.3sd <- sd(all.data.new[!is.na(all.data.new$IC),]$IC)*3
+EF.mean <- mean(all.data.new[!is.na(all.data.new$EF),]$EF)
+WM.mean <- mean(all.data.new[!is.na(all.data.new$WM),]$WM)
+TP.mean <- mean(all.data.new[!is.na(all.data.new$TP),]$TP)
+IC.mean <- mean(all.data.new[!is.na(all.data.new$IC),]$IC)
 
-# Significant:
-```{r}
-summary(lmer(EF~age+gender+(1|state)+(1|schoolID)+threat,data=all.data.new)) # ***
-summary(lmer(EF~age+gender+(1|state)+(1|schoolID)+depriv,data=all.data.new)) # ***
-
-summary(lmer(WM~age+gender+(1|state)+(1|schoolID)+threat,data=all.data.new)) # * (does not pass correction)
-summary(lmer(WM~age+gender+(1|state)+(1|schoolID)+depriv,data=all.data.new)) # ***
-
-summary(lmer(TP~age+gender+(1|state)+(1|schoolID)+threat,data=all.data.new)) # ***
-summary(lmer(TP~age+gender+(1|state)+(1|schoolID)+depriv,data=all.data.new)) # ***
-
-p.adjust(c(0.000463,9.78e-07,0.0184,1.16e-07,0.000233,5.03e-06),method="bonferroni")
+# This is a complete set with subjects who have all 4 cog measures within the bounds of 3SD
+all.data.complete <- all.data.new[(all.data.new$EF>(EF.mean-EF.3sd) & all.data.new$EF<(EF.mean+EF.3sd)) & (all.data.new$WM>(WM.mean-WM.3sd) & all.data.new$WM<(WM.mean+WM.3sd)) & (all.data.new$IC>(IC.mean-IC.3sd) & all.data.new$IC<(IC.mean+IC.3sd)) & (all.data.new$TP>(TP.mean-TP.3sd) & all.data.new$TP<(TP.mean+TP.3sd)),]
 
@@
 
-# Plots:
+## Run linear models using Threat and Deprivation scores to predict cognition
+### Note: Gender 1 = Male, Gender 2 = Female
+### Covariates for age, gender, and random effects for school and state
+
+### Significant:
 ```{r}
-correlation <- cor.test(all.data.new$threat,all.data.new$WM)
-ggplot(data=all.data.new,aes(threat,WM))+geom_point(size=1,colour='#70677D')+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
-panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Working Memory') + xlab('Threat') + ggtitle(paste("r=",as.character(round(correlation$estimate,3)),", p=",as.character(round(correlation$p.value,3))))
+# summary(lmer(EF~age+gender+(1|state)+(1|schoolID)+threat,data=all.data.new)) # ***
+# summary(lmer(EF~age+gender+(1|state)+(1|schoolID)+depriv,data=all.data.new)) # ***
+# 
+# summary(lmer(WM~age+gender+(1|state)+(1|schoolID)+threat,data=all.data.new)) # * (does not pass correction)
+# summary(lmer(WM~age+gender+(1|state)+(1|schoolID)+depriv,data=all.data.new)) # ***
+# 
+# summary(lmer(TP~age+gender+(1|state)+(1|schoolID)+threat,data=all.data.new)) # ***
+# summary(lmer(TP~age+gender+(1|state)+(1|schoolID)+depriv,data=all.data.new)) # ***
+# 
+# p.adjust(c(0.000463,9.78e-07,0.0184,1.16e-07,0.000233,5.03e-06),method="bonferroni")
 
-correlation <- cor.test(all.data.new$depriv,all.data.new$WM)
-ggplot(data=all.data.new,aes(depriv,WM))+geom_point(size=1,colour='#7393C4')+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
-panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Working Memory') + xlab('Deprivation') + ggtitle(paste("r=",as.character(round(correlation$estimate,3)),", p=",as.character(round(correlation$p.value,3))))
 ```
 
-# Non-significant:
+### Plots:
 ```{r}
-summary(lmer(ALERT~age+gender+(1|state)+(1|schoolID)+threat,data=all.data.new)) #ns
-summary(lmer(ORIENT~age+gender+(1|state)+(1|schoolID)+threat,data=all.data.new)) #ns
-summary(lmer(CONFLICT~age+gender+(1|state)+(1|schoolID)+threat,data=all.data.new)) #ns
+# correlation <- cor.test(all.data.new$threat,all.data.new$WM)
+# ggplot(data=all.data.new,aes(threat,WM))+geom_point(size=1,colour='#70677D')+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+# panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Working Memory') + xlab('Threat') + ggtitle(paste("r=",as.character(round(correlation$estimate,3)),", p=",as.character(round(correlation$p.value,3))))
+# 
+# correlation <- cor.test(all.data.new$depriv,all.data.new$WM)
+# ggplot(data=all.data.new,aes(depriv,WM))+geom_point(size=1,colour='#7393C4')+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+# panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Working Memory') + xlab('Deprivation') + ggtitle(paste("r=",as.character(round(correlation$estimate,3)),", p=",as.character(round(correlation$p.value,3))))
+```
 
-summary(lmer(ALERT~age+gender+(1|state)+(1|schoolID)+depriv,data=all.data.new)) #ns
-summary(lmer(ORIENT~age+gender+(1|state)+(1|schoolID)+depriv,data=all.data.new)) #ns
-summary(lmer(CONFLICT~age+gender+(1|state)+(1|schoolID)+depriv,data=all.data.new)) #ns
+### For the effects where there was also a significant effect of gender, look for an interaction (there are none)
+```{r}
+# summary(lmer(EF~age+gender+(1|state)+(1|schoolID)+threat+threat*gender,data=all.data.new)) # ns
+# summary(lmer(EF~age+gender+(1|state)+(1|schoolID)+depriv+depriv*gender,data=all.data.new)) # ns
+# 
+# summary(lmer(TP~age+gender+(1|state)+(1|schoolID)+threat+threat*gender,data=all.data.new)) # ns
+# summary(lmer(TP~age+gender+(1|state)+(1|schoolID)+depriv+depriv*gender,data=all.data.new)) # ns
+```
 
-summary(lmer(ALERT~age+gender+(1|state)+(1|schoolID)+threat+depriv+threat*gender+depriv*gender,data=all.data.new)) # 0.055
+### Look for specificity on the type of ACE
+#### Note that the correlation between threat and deprivation here is only 0.386
+```{r}
+# cor.test(all.data.new$threat,all.data.new$depriv)
+# summary(lmer(EF~age+gender+(1|state)+(1|schoolID)+threat+depriv,data=all.data.new)) # specific to depriv ***
+# summary(lmer(WM~age+gender+(1|state)+(1|schoolID)+threat+depriv,data=all.data.new)) # specific to depriv ***
+# summary(lmer(TP~age+gender+(1|state)+(1|schoolID)+threat+depriv,data=all.data.new)) # both threat * and depriv ***
+```
 
-summary(lmer(IC~age+gender+(1|state)+(1|schoolID)+threat,data=all.data.new)) # ns
-summary(lmer(IC~age+gender+(1|state)+(1|schoolID)+depriv,data=all.data.new)) # ns
+## Create a correlation matrix of all the important variables
+### Since the cognitive variables are more highly correlated with each other, we won't test specificity in a single model
+```{r}
+# important.variables <- all.data.new[,c("age","gender","threat","depriv","EF","WM","TP","IC")]
+# important.variables$gender <- as.numeric(important.variables$gender)
+# colnames(important.variables)<-c("Age","Gender","Threat","Depriv","Exec. Fxn","Working Mem","Temp. Proc.","Inhib. Cont.")
+# corrplot(cor(important.variables,use="complete.obs"),method=c("number"), tl.col = "black", col=brewer.pal(n=8, name="Spectral"))
+```
+
+### Non-significant:
+```{r}
+# summary(lmer(ALERT~age+gender+(1|state)+(1|schoolID)+threat,data=all.data.new)) #ns
+# summary(lmer(ORIENT~age+gender+(1|state)+(1|schoolID)+threat,data=all.data.new)) #ns
+# summary(lmer(CONFLICT~age+gender+(1|state)+(1|schoolID)+threat,data=all.data.new)) #ns
+# 
+# summary(lmer(ALERT~age+gender+(1|state)+(1|schoolID)+depriv,data=all.data.new)) #ns
+# summary(lmer(ORIENT~age+gender+(1|state)+(1|schoolID)+depriv,data=all.data.new)) #ns
+# summary(lmer(CONFLICT~age+gender+(1|state)+(1|schoolID)+depriv,data=all.data.new)) #ns
+# 
+# summary(lmer(ALERT~age+gender+(1|state)+(1|schoolID)+threat+depriv+threat*gender+depriv*gender,data=all.data.new)) # 0.055
+# 
+# summary(lmer(IC~age+gender+(1|state)+(1|schoolID)+threat,data=all.data.new)) # ns
+# summary(lmer(IC~age+gender+(1|state)+(1|schoolID)+depriv,data=all.data.new)) # ns
+```
+
+### Look for specificity on Physical vs Emotional Neglect (as an replication of ABCD findings)
+```{r}
+# Calculate emotional neglect variable by averaging across relevant items (the "depriv" one will represent physical neglect)
+all.data.complete<-all.data.complete[all.data.complete$fat38a<50,]
+all.data.complete$emo_neglect <- -rowMeans(data.frame(as.numeric(all.data.complete$fat38a)/3,as.numeric(all.data.complete$fat39a)/3),na.rm=TRUE) #,as.numeric(all.data.complete$fes18),as.numeric(all.data.complete$fes1),as.numeric(all.data.complete$fes42),as.numeric(all.data.complete$fes48))
+
+# Verify that correlation is low: it's 0.222
+cor.test(all.data.complete$depriv,all.data.complete$emo_neglect)
+
+# Test specificity
+summary(lmer(EF~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete)) # both sig
+summary(lmer(WM~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete)) # both sig
+summary(lmer(TP~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete)) # both sig 
+summary(lmer(IC~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete)) # just depriv
+
+p.adjust(c(0.005610,1.72e-09,0.0030,3.22e-08,0.0111,5.23e-09,0.323230,0.014438),method="bonferroni")
+
+# try restricting age to ABCD range:
+all.data.complete.ageres <- all.data.complete[all.data.complete$age<11.1,]
+all.data.complete.ageres <- all.data.complete.ageres[all.data.complete.ageres$age>8.9,]
+all.data.complete.ageres<-all.data.complete.ageres[all.data.complete.ageres$fat38a<50,]
+all.data.complete.ageres$emo_neglect <- -rowMeans(data.frame(as.numeric(all.data.complete.ageres$fat38a)/3,as.numeric(all.data.complete.ageres$fat39a)/3),na.rm=TRUE) 
+cor.test(all.data.complete.ageres$depriv,all.data.complete.ageres$emo_neglect)
+
+# Test specificity
+summary(lmer(EF~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres)) # both sig
+summary(lmer(WM~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres)) # both sig
+summary(lmer(TP~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres)) # both sig 
+summary(lmer(IC~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres)) # just depriv
+
+p.adjust(c(0.0202,3.91e-05,0.0556,1.12e-06,0.020554,0.000262,0.4224,0.0588),method="bonferroni") 
+```
+
+## Create a correlation matrix of all the important variables
+### Since the cognitive variables are more highly correlated with each other, we won't test specificity in a single model
+```{r}
+important.variables <- all.data.complete.ageres[,c("age","gender","emo_neglect","depriv","EF","WM","TP","IC")]
+important.variables$gender <- as.numeric(important.variables$gender)
+colnames(important.variables)<-c("Age","Gender","EmoNeglect","PhysNeglect","Exec. Fxn","Working Mem","Temp. Proc.","Inhib. Cont.")
+corrplot(cor(important.variables,use="complete.obs"),method=c("number"), tl.col = "black", col=brewer.pal(n=8, name="Spectral"))
+```
+
+## Plots
+```{r}
+cols <- brewer.pal(10,"Paired")
+
+ png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/BHRC_PhysNeg_TP.png",
+     width = 3000, 
+     height = 3000,
+     res = 850)
+ggplot(all.data.complete.ageres, aes(x=depriv,y=TP)) +
+  geom_point(colour=cols[2],size=1) +
+  geom_smooth(method=lm,color="black") + xlab("Physical Neglect") + ylab("Temporal Processing") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
+dev.off()
+
+ png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/BHRC_PhysNeg_EF.png",
+     width = 3000, 
+     height = 3000,
+     res = 850)
+ggplot(all.data.complete.ageres, aes(x=depriv,y=EF)) +
+  geom_point(colour=cols[4],size=1) +
+  geom_smooth(method=lm,color="black") + xlab("Physical Neglect") + ylab("Exec.
+Fxn.") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
+dev.off()
+
+ png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/BHRC_PhysNeg_WM.png",
+     width = 3000, 
+     height = 3000,
+     res = 850)
+ggplot(all.data.complete.ageres, aes(x=depriv,y=WM)) +
+  geom_point(colour=cols[8],size=1) +
+  geom_smooth(method=lm,color="black") + xlab("Physical Neglect") + ylab("Working Memory") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
+dev.off()
+
+ png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/BHRC_PhysNeg_IC.png",
+     width = 3000, 
+     height = 3000,
+     res = 850)
+ggplot(all.data.complete.ageres, aes(x=depriv,y=IC)) +
+  geom_point(colour=cols[10],size=1) +
+  geom_smooth(method=lm,color="black") + xlab("Physical Neglect") + ylab("Inhibitory Control") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
+dev.off()
+
+ png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/BHRC_EmoNeg_TP.png",
+     width = 3000, 
+     height = 3000,
+     res = 850)
+ggplot(all.data.complete.ageres, aes(x=emo_neglect,y=TP)) +
+  geom_point(colour=cols[2],size=1) +
+  geom_smooth(method=lm,color="black") + xlab("Emotional Neglect") + ylab("Temporal Processing") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
+dev.off()
+
+ png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/BHRC_EmoNeg_EF.png",
+     width = 3000, 
+     height = 3000,
+     res = 850)
+ggplot(all.data.complete.ageres, aes(x=emo_neglect,y=EF)) +
+  geom_point(colour=cols[4],size=1) +
+  geom_smooth(method=lm,color="black") + xlab("Emotional Neglect") + ylab("Exec.
+Fxn.") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
+dev.off()
+
+ png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/BHRC_EmoNeg_WM.png",
+     width = 3000, 
+     height = 3000,
+     res = 850)
+ggplot(all.data.complete.ageres, aes(x=emo_neglect,y=WM)) +
+  geom_point(colour=cols[8],size=1) +
+  geom_smooth(method=lm,color="black") + xlab("Emotional Neglect") + ylab("Working Memory") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
+dev.off()
+
+ png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/BHRC_EmoNeg_IC.png",
+     width = 3000, 
+     height = 3000,
+     res = 850)
+ggplot(all.data.complete.ageres, aes(x=emo_neglect,y=IC)) +
+  geom_point(colour=cols[10],size=1) +
+  geom_smooth(method=lm,color="black") + xlab("Emotional Neglect") + ylab("Inhibitory Control") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
+dev.off()
 ```
@@
 ravlt.baseline<-ravlt[ravlt$eventname=="baseline_year_1_arm_1",]
-merged.data3 <- merge(merged.data2,ravlt.baseline[, c("subjectkey", setdiff(colnames(ravlt.baseline),colnames(merged.data2)))],by="subjectkey")
-trauma<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/Strife/abcd_ptsd01.txt",header=TRUE)
-trauma.baseline<-trauma[trauma$eventname=="baseline_year_1_arm_1",]
-combined.data <- merge(merged.data3,trauma.baseline[, c("subjectkey", setdiff(colnames(trauma.baseline),colnames(merged.data3)))],by="subjectkey")
+combined.data <- merge(merged.data2,ravlt.baseline[, c("subjectkey", setdiff(colnames(ravlt.baseline),colnames(merged.data2)))],by="subjectkey")
+# trauma<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/Strife/abcd_ptsd01.txt",header=TRUE)
+# trauma.baseline<-trauma[trauma$eventname=="baseline_year_1_arm_1",]
+# combined.data <- merge(merged.data3,trauma.baseline[, c("subjectkey", setdiff(colnames(trauma.baseline),colnames(merged.data3)))],by="subjectkey")
 combined.data$nihtbx_flanker_uncorrected <- as.numeric(combined.data$nihtbx_flanker_uncorrected)
@@
 
-# Calculate types of ACEs
-combined.data.noOutliers[,224:240]<-as.numeric(unlist(combined.data.noOutliers[,224:240]))
-
-# Calculation of subscore with items related to physical and sexual abuse
-combined.data.noOutliers$abuse <- rowSums(data.frame(as.numeric(combined.data.noOutliers$ksads_ptsd_raw_761_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_762_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_763_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_767_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_768_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_769_p)),na.rm=TRUE)
-
-# Calculation of subscore with items related to trauma (car accidents, natural disasters, loss, etc.)
-combined.data.noOutliers$trauma <- rowSums(data.frame(as.numeric(combined.data.noOutliers$ksads_ptsd_raw_754_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_755_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_756_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_757_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_758_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_759_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_760_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_766_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_770_p)),na.rm=TRUE)
-
-# Calculation of total score from the KSADS items
-combined.data.noOutliers$totalACEs <- rowSums(data.frame(as.numeric(combined.data.noOutliers$ksads_ptsd_raw_754_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_755_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_756_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_757_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_758_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_759_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_760_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_761_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_762_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_763_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_764_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_765_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_766_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_767_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_768_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_769_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_770_p)),na.rm=TRUE)
+# # Calculate types of ACEs
+# combined.data.noOutliers[,224:240]<-as.numeric(unlist(combined.data.noOutliers[,224:240]))
+# 
+# # Calculation of subscore with items related to physical and sexual abuse
+# combined.data.noOutliers$abuse <- rowSums(data.frame(as.numeric(combined.data.noOutliers$ksads_ptsd_raw_761_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_762_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_763_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_767_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_768_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_769_p)),na.rm=TRUE)
+# 
+# # Calculation of subscore with items related to trauma (car accidents, natural disasters, loss, etc.)
+# combined.data.noOutliers$trauma <- rowSums(data.frame(as.numeric(combined.data.noOutliers$ksads_ptsd_raw_754_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_755_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_756_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_757_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_758_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_759_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_760_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_766_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_770_p)),na.rm=TRUE)
+# 
+# # Calculation of total score from the KSADS items
+# combined.data.noOutliers$totalACEs <- rowSums(data.frame(as.numeric(combined.data.noOutliers$ksads_ptsd_raw_754_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_755_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_756_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_757_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_758_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_759_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_760_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_761_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_762_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_763_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_764_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_765_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_766_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_767_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_768_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_769_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_770_p)),na.rm=TRUE)
 
@@
 family.baseline<-family[family$eventname=="baseline_year_1_arm_1",]
-abcd.data <- merge(combined.data.noOutliers,family.baseline[, c("subjectkey", setdiff(colnames(family.baseline),colnames(combined.data.noOutliers)))],by="subjectkey")
+abcd.data.almost <- merge(combined.data.noOutliers,family.baseline[, c("subjectkey", setdiff(colnames(family.baseline),colnames(combined.data.noOutliers)))],by="subjectkey")
 
@@
 
-abcd.data<-merge(abcd.data,neglect.data[,c("subjectkey", setdiff(colnames(neglect.data),colnames(abcd.data)))],by="subjectkey")
+abcd.data<-merge(abcd.data.almost,neglect.data[,c("subjectkey", setdiff(colnames(neglect.data),colnames(abcd.data.almost)))],by="subjectkey")
 
 # Calculate subscales of deprivation (emotional and physical neglect) - see this ref for motivation https://www.sciencedirect.com/science/article/pii/S2352289518300821
-abcd.data$acceptance <- rowSums(data.frame(as.numeric(abcd.data$crpbi_parent1_y),as.numeric(abcd.data$crpbi_parent2_y),as.numeric(abcd.data$crpbi_parent3_y),as.numeric(abcd.data$crpbi_parent4_y),as.numeric(abcd.data$crpbi_parent5_y)))
+abcd.data$acceptance <- rowMeans(data.frame(as.numeric(abcd.data$crpbi_parent1_y),as.numeric(abcd.data$crpbi_parent2_y),as.numeric(abcd.data$crpbi_parent3_y),as.numeric(abcd.data$crpbi_parent4_y),as.numeric(abcd.data$crpbi_parent5_y)))
 
-abcd.data$monitoring <- rowSums(data.frame(as.numeric(abcd.data$parent_monitor_q1_y),as.numeric(abcd.data$parent_monitor_q2_y),as.numeric(abcd.data$parent_monitor_q3_y),as.numeric(abcd.data$parent_monitor_q4_y),as.numeric(abcd.data$parent_monitor_q5_y)))
+abcd.data$monitoring <- rowMeans(data.frame(as.numeric(abcd.data$parent_monitor_q1_y),as.numeric(abcd.data$parent_monitor_q2_y),as.numeric(abcd.data$parent_monitor_q3_y),as.numeric(abcd.data$parent_monitor_q4_y),as.numeric(abcd.data$parent_monitor_q5_y)))
 
-# Binarize the four ACEs subtypes (2 "Threat" types: Abuse and Trauma; 2 "Deprivation" types: Emotional Neglect and Physical Neglect)
-abcd.data$abuse.binary <- factor(abcd.data$abuse>=1,labels = c("No Abuse","Abuse"))
-abcd.data$abuse.binary.numeric <- as.numeric(abcd.data$abuse.binary)
-abcd.data$trauma.binary <- factor(abcd.data$trauma>=1,labels = c("No Trauma","Trauma"))
-abcd.data$trauma.binary.numeric <- as.numeric(abcd.data$trauma.binary)
-
-median.monitoring = median(na.omit(abcd.data$monitoring))
-median.acceptance = median(na.omit(abcd.data$acceptance))
-abcd.data$monitoring.binary <- factor(abcd.data$monitoring<20,labels = c("Low Physical Neglect","High Physical Neglect"))
-abcd.data$monitoring.binary.numeric <- as.numeric(abcd.data$monitoring.binary)
-abcd.data$acceptance.binary <- factor(abcd.data$acceptance<7.5,labels = c("Low Emotional Neglect","High Emotional Neglect"))
-abcd.data$acceptance.binary.numeric <- as.numeric(abcd.data$acceptance.binary)
+# # Binarize the four ACEs subtypes (2 "Threat" types: Abuse and Trauma; 2 "Deprivation" types: Emotional Neglect and Physical Neglect)
+# abcd.data$abuse.binary <- factor(abcd.data$abuse>=1,labels = c("No Abuse","Abuse"))
+# abcd.data$abuse.binary.numeric <- as.numeric(abcd.data$abuse.binary)
+# abcd.data$trauma.binary <- factor(abcd.data$trauma>=1,labels = c("No Trauma","Trauma"))
+# abcd.data$trauma.binary.numeric <- as.numeric(abcd.data$trauma.binary)
+# 
+# median.monitoring = median(na.omit(abcd.data$monitoring))
+# median.acceptance = median(na.omit(abcd.data$acceptance))
+# abcd.data$monitoring.binary <- factor(abcd.data$monitoring<20,labels = c("Low Physical Neglect","High Physical Neglect"))
+# abcd.data$monitoring.binary.numeric <- as.numeric(abcd.data$monitoring.binary)
+# abcd.data$acceptance.binary <- factor(abcd.data$acceptance<7.5,labels = c("Low Emotional Neglect","High Emotional Neglect"))
+# abcd.data$acceptance.binary.numeric <- as.numeric(abcd.data$acceptance.binary)
 ```
@@
 ```{r}
+# 
+# data.long <- gather(abcd.data, CogType, CogScore, thompson_PC1,thompson_PC2,thompson_PC3, factor_key=TRUE)
+# 
+# names(data.long)[names(data.long) == 'acceptance.binary.numeric'] <- 'depriv.emo'
+# names(data.long)[names(data.long) == 'monitoring.binary.numeric'] <- 'depriv.phys'
+# names(data.long)[names(data.long) == 'trauma.binary.numeric'] <- 'threat.trauma'
+# names(data.long)[names(data.long) == 'abuse.binary.numeric'] <- 'threat.abuse'
+# 
+# abcd.long <- gather(data.long, ACEsType, ACEsScore, depriv.emo,depriv.phys,threat.abuse,threat.trauma, factor_key=TRUE)
+# abcd.long.complete <- abcd.long[complete.cases(abcd.long[,c("CogType","CogScore","ACEsType","ACEsScore")]),c("CogType","CogScore","ACEsType","ACEsScore","interview_age","sex","rel_family_id")]
+# 
+# ggplot(data=abcd.long.complete, aes(x=ACEsScore,y=CogScore,fill=interaction(ACEsType,CogType))) +
+#   geom_bar(stat="identity",position="dodge") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+# panel.background = element_blank(), axis.line = element_line(colour = "black")) +xlab("ACEs") + ylab("Cognition") +coord_cartesian(ylim=c(250,325)) + facet_grid(abcd.long.complete$ACEsType~abcd.long.complete$CogType) + theme(legend.position = "none")
 
-data.long <- gather(abcd.data, CogType, CogScore, thompson_PC1,thompson_PC2,thompson_PC3, factor_key=TRUE)
-abcd.long <- gather(data.long, ACEsType, ACEsScore, acceptance.binary.numeric,monitoring.binary.numeric,abuse.binary.numeric,trauma.binary.numeric, factor_key=TRUE)
+```
 
-abcd.long.complete <- abcd.long[complete.cases(abcd.long[,c("CogType","CogScore","ACEsType","ACEsScore")]),c("CogType","CogScore","ACEsType","ACEsScore","interview_age","sex","rel_family_id")]
-
-ggplot(data=abcd.long.complete, aes(x=ACEsScore,y=CogScore,fill=interaction(ACEsType,CogType))) +
-  geom_bar(stat="identity",position="dodge") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
-panel.background = element_blank(), axis.line = element_line(colour = "black")) +xlab("ACEs") + ylab("Cognition") +coord_cartesian(ylim=c(250,325)) + facet_grid(abcd.long.complete$ACEsType~abcd.long.complete$CogType)
-
+## Create a correlation matrix of all the important variables
+```{r}
+important.variables2 <- abcd.data[,c("interview_age","sex","acceptance","monitoring","thompson_PC1","thompson_PC2","thompson_PC3")]
+important.variables2$sex <- as.numeric(as.factor(important.variables2$sex))
+colnames(important.variables2)<-c("Age","Sex","EmoNeglect","PhysNeglect","Gen. Cog.","EF","Learning/Mem")
+corrplot(cor(important.variables2,use="complete.obs"),method=c("number"), tl.col = "black", col=brewer.pal(n=8, name="Spectral"))
 ```
@@
 ```{r}
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+acceptance+monitoring,data=abcd.data))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+acceptance+monitoring,data=abcd.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+acceptance+monitoring,data=abcd.data))
 
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+acceptance.binary+monitoring.binary+abuse.binary+trauma.binary,data=abcd.data))
-p.adjust(c(0.615, 2e-16,0.035,6.96e-11),method="bonferroni")
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+acceptance.binary+monitoring.binary+abuse.binary+trauma.binary,data=abcd.data))
+# p.adjust(c(0.615, 2e-16,0.035,6.96e-11),method="bonferroni")
+# # PC1 is related to physical neglect *** and trauma ***
+# 
+# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+acceptance.binary+monitoring.binary+abuse.binary+trauma.binary,data=abcd.data))
+# p.adjust(c(0.389, 7.47e-15,0.0096,4.39e-7),method="bonferroni")
+# # PC1 is related to physical neglect ***, abuse *, and trauma ***
+# 
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+acceptance.binary+monitoring.binary+abuse.binary+trauma.binary,data=abcd.data))
+# p.adjust(c(0.034, 2e-16,0.014,6.18e-8),method="bonferroni")
+# # PC3 is related to physical neglect *** and trauma ***
+```
 
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+acceptance.binary+monitoring.binary+abuse.binary+trauma.binary,data=abcd.data))
-p.adjust(c(0.389, 7.47e-15,0.0096,4.39e-7),method="bonferroni")
+### no significant interactions with sex
+```{r}
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary+monitoring.binary*sex,data=abcd.data))
+# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+monitoring.binary+monitoring.binary*sex,data=abcd.data))
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary+monitoring.binary*sex,data=abcd.data))
+# 
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+abuse.binary+abuse.binary*sex,data=abcd.data))
+# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+abuse.binary+abuse.binary*sex,data=abcd.data))
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+abuse.binary+abuse.binary*sex,data=abcd.data))
+# 
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary+trauma.binary*sex,data=abcd.data))
+# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+trauma.binary+trauma.binary*sex,data=abcd.data))
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+trauma.binary+trauma.binary*sex,data=abcd.data))
+# 
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+acceptance.binary+acceptance.binary*sex,data=abcd.data))
+# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+acceptance.binary+acceptance.binary*sex,data=abcd.data))
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+acceptance.binary+acceptance.binary*sex,data=abcd.data))
+```
 
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+acceptance.binary+monitoring.binary+abuse.binary+trauma.binary,data=abcd.data))
-p.adjust(c(0.034, 2e-16,0.014,6.18e-8),method="bonferroni")
+### models split out by ACE type
+```{r}
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+acceptance.binary,data=abcd.data))
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=abcd.data)) # ***
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+abuse.binary,data=abcd.data)) # ***
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary,data=abcd.data)) # ***
+# 
+# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+acceptance.binary,data=abcd.data))
+# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=abcd.data)) # ***
+# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+abuse.binary,data=abcd.data)) # **
+# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+trauma.binary,data=abcd.data)) # ***
+# 
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+acceptance.binary,data=abcd.data)) # **
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=abcd.data)) # ***
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+abuse.binary,data=abcd.data)) # **
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+trauma.binary,data=abcd.data)) # ***
+```
 
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary+monitoring.binary*sex,data=abcd.data))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+monitoring.binary+monitoring.binary*sex,data=abcd.data))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary+monitoring.binary*sex,data=abcd.data))
+## Plots
+```{r}
+cols <- brewer.pal(10,"Paired")
 
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+abuse.binary+abuse.binary*sex,data=abcd.data))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+abuse.binary+abuse.binary*sex,data=abcd.data))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+abuse.binary+abuse.binary*sex,data=abcd.data))
+ png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/ABCD_PhysNeg_PC1.png",
+     width = 3000, 
+     height = 3000,
+     res = 850)
+ggplot(abcd.data, aes(x=-monitoring,y=thompson_PC1)) +
+  geom_point(colour=cols[2],size=1) +
+  geom_smooth(method=lm,color="black") + xlab("Physical Neglect") + ylab("PC1: General Cognition") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
+dev.off()
 
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary+trauma.binary*sex,data=abcd.data))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+trauma.binary+trauma.binary*sex,data=abcd.data))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+trauma.binary+trauma.binary*sex,data=abcd.data))
+ png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/ABCD_PhysNeg_PC2.png",
+     width = 3000, 
+     height = 3000,
+     res = 850)
+ggplot(abcd.data, aes(x=-monitoring,y=thompson_PC2)) +
+  geom_point(colour=cols[4],size=1) +
+  geom_smooth(method=lm,color="black") + xlab("Physical Neglect") + ylab("PC2: Exec.
+Fxn.") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
+dev.off()
 
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+acceptance.binary+acceptance.binary*sex,data=abcd.data))
+ png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/ABCD_PhysNeg_PC3.png",
+     width = 3000, 
+     height = 3000,
+     res = 850)
+ggplot(abcd.data, aes(x=-monitoring,y=thompson_PC3)) +
+  geom_point(colour=cols[8],size=1) +
+  geom_smooth(method=lm,color="black") + xlab("Physical Neglect") + ylab("PC3: Learning/Memory") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
+dev.off()
 
-summary(lmer(CogScore~interview_age+sex+(1|rel_family_id)+acceptance.binary+CogType+CogType*acceptance.binary,data=data.long))
-summary(lmer(CogScore~interview_age+sex+(1|rel_family_id)+monitoring.binary+CogType+CogType*monitoring.binary,data=data.long))
-summary(lmer(CogScore~interview_age+sex+(1|rel_family_id)+abuse.binary+CogType+CogType*abuse.binary,data=data.long))
-summary(lmer(CogScore~interview_age+sex+(1|rel_family_id)+trauma.binary+CogType+CogType*trauma.binary,data=data.long))
+ png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/ABCD_EmoNeg_PC1.png",
+     width = 3000, 
+     height = 3000,
+     res = 850)
+ggplot(abcd.data, aes(x=-acceptance,y=thompson_PC1)) +
+  geom_point(colour=cols[2],size=1) +
+  geom_smooth(method=lm,color="black") + xlab("Emotional Neglect") + ylab("PC1: General Cognition") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
+dev.off()
 
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+acceptance.binary,data=abcd.data))
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=abcd.data))
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+abuse.binary,data=abcd.data))
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary,data=abcd.data))
+ png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/ABCD_EmoNeg_PC2.png",
+     width = 3000, 
+     height = 3000,
+     res = 850)
+ggplot(abcd.data, aes(x=-acceptance,y=thompson_PC2)) +
+  geom_point(colour=cols[4],size=1) +
+  geom_smooth(method=lm,color="black") + xlab("Emotional Neglect") + ylab("PC2: Exec.
+Fxn.") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
+dev.off()
 
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+acceptance.binary,data=abcd.data))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=abcd.data))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+abuse.binary,data=abcd.data))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+trauma.binary,data=abcd.data))
-
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+acceptance.binary,data=abcd.data))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=abcd.data))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+abuse.binary,data=abcd.data))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+trauma.binary,data=abcd.data))
-
+ png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/PhysEmoNeglect_ABCD_BHRC/Scatterplots/ABCD_EmoNeg_PC3.png",
+     width = 3000, 
+     height = 3000,
+     res = 850)
+ggplot(abcd.data, aes(x=-acceptance,y=thompson_PC3)) +
+  geom_point(colour=cols[8],size=1) +
+  geom_smooth(method=lm,color="black") + xlab("Emotional Neglect") + ylab("PC3: Learning/Memory") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
+dev.off()
 ```

### 2022-01-26 cubic_scripts/Individualize_ciftiSurf_resampledGroCon_justRest.m
Added cubic scripts
These scripts run the PFNs/gradients pipeline and extract the mean FD

@@ -1,0 +1,54 @@
+function Individualize_ciftiSurf_resampledGroCon_justRest(subj)
+% Based on the group atlas, creating each subject's individual specific atlas
+ProjectFolder = '/cbica/projects/abcdfnets/results'
+
+ResultantFolder = [ProjectFolder '/SingleParcel_1by1_Rest'];
+mkdir(ResultantFolder);
+
+PrepDataFile = [ProjectFolder '/SingleParcellation/CreatePrepData.mat'];
+
+resId = 'IndividualParcel_Final';
+% 7/2/21 - subbed in filled initResamp instead of "initResamp.mat"
+initName = [ProjectFolder '/SingleParcellation/RobustInitialization_Cifti_Surf/initResamp.mat'];
+
+K = 17;
+
+% Use parameter in Hongming's NeuroImage paper, except for alphaL which we have expanded to account for the reduced smoothin in DCAN's pipeline
+alphaS21 = 1;
+alphaL = 300;
+vxI = 1;
+spaR = 1;
+ard = 0;
+iterNum = 30;
+eta = 0;
+calcGrp = 0;
+parforOn = 0;
+
+
+RawDataFolder = '/scratch/abcdfnets/nda-abcd-s3-downloader/August_2021_DL/derivatives/abcd-hcp-pipeline';
+subj_dtseries=['/scratch/abcdfnets/nda-abcd-s3-downloader/August_2021_DL/derivatives/abcd-hcp-pipeline/*/*/*/' subj '_ses-baselineYear1Arm1_task-rest_p2mm_masked.dtseries.nii*'];
+CiftiCell = g_ls(subj_dtseries)
+
+
+% Parcellate the subject - load filepath, subject name, and 
+[Fold, ~, ~] = fileparts(CiftiCell{1});
+FoldStr = strsplit(Fold, '/');
+ID_Str = FoldStr{8};
+ResultantFolder_I = [ResultantFolder '/' ID_Str];
+ResultFile_check = dir([ResultantFolder_I, '/**/final*.mat']);
+
+% check for existing directory
+if ~exist(ResultantFolder_I, 'dir')
+   mkdir(ResultantFolder_I);
+end
+IDMatFile = [ResultantFolder_I '/ID.mat'];
+save(IDMatFile, 'ID_Str');
+
+sbjListFile = [ResultantFolder_I '/sbjListAllFile.txt'];
[…]

### 2022-01-26 cubic_scripts/OffHours_wrapper_ASK_getFD.py

@@ -1,0 +1,43 @@
+import subprocess
+import time
+import datetime
+import os
+# grab some subjs as list
+my_file = open("/cbica/projects/abcdfnets/scripts/combined_PFNs_PGs/twins_not_yet_run_012622.txt", "r")
+content = my_file.read()
+content_list = content. split("\n")
+# remove last line (blank)
+content_list.pop()
+# feed em' in as subjects
+subjects = content_list
+# only first(last) 1048 ran?
+# anddd it died after another 2630 subjs. 2071 left to run.
+# and it died again (9/24/21). 1833 left to run
+#subjects = subjects[0:1833]
+# while there are more than 0 subjects left to run
+while len(subjects)>0:
+  # grab qsub info, get number of jobs being run
+  qstat = subprocess.check_output(['qstat'],shell=True).decode().split('/bin/python')[0]
+  que = len(qstat.split('\n'))-3
+  # if we are using less than 5 job slots (one is occupied by this script)
+  if que < 8:
+    # see if it is the weekend, 0, 1, 2, 3, and 4 are weekday, 5 and 6 are weekend
+    weekno = datetime.datetime.today().weekday()
+    # see if it is before 9 or after 5 
+    Hour = time.localtime().tm_hour 
+    # if weekend OR after 6 PM OR before 9 AM
+    if weekno > 4 or Hour < 9 or Hour > 16 :
+      newsub = subjects.pop()
+      # adding new condition: if gradient file does not exist
+      # gradFile='/cbica/projects/abcdfnets/results/wave_output/' + str(newsub) + '/' + str(newsub) + '_PG_LR_32k.dscalar.nii'
+      # if not os.path.exists(gradFile):
+      # submit job (if above conditions are met)
+      subprocess.run(["qsub","-l","h_vmem=15G,s_vmem=14G","qsubMatlab_ASK_getFD.sh",newsub])
+      time.sleep(60) #wait a minute
+    # added this to run 3 subjs (1 slot for this job) during ON hours
+    elif que < 4:
+      newsub = subjects.pop()
+      # gradFile='/cbica/projects/abcdfnets/results/wave_output/' + str(newsub) + '/' + str(newsub) + '_PG_LR_32k.dscalar.nii'
+      # if not os.path.exists(gradFile):
+      subprocess.run(["qsub","-l","h_vmem=15G,s_vmem=14G","qsubMatlab_ASK_getFD.sh",newsub])
+      time.sleep(60) #wait a minute

### 2022-01-26 PaperOutline_ACEsCog.Rmd
added site covariate
added random effect for ABCD site - results don't change

@@
 
+# also add in the variable for site ID to use as a covariate
+site_info <- readRDS("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/DEAP-siteID.rds")
+site.baseline<-site_info[site_info$event_name=="baseline_year_1_arm_1",]
+colnames(site.baseline)[1]<-"subjectkey"
+abcd.data.withFamAndSite <- merge(abcd.data.almost,site.baseline[,c("subjectkey", setdiff(colnames(site.baseline),colnames(abcd.data.almost)))],by="subjectkey")
+
 emo.neglect <-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/neglect/crpbi01.txt",header=TRUE)
@@
 
-abcd.data<-merge(abcd.data.almost,neglect.data[,c("subjectkey", setdiff(colnames(neglect.data),colnames(abcd.data.almost)))],by="subjectkey")
+abcd.data<-merge(abcd.data.withFamAndSite,neglect.data[,c("subjectkey", setdiff(colnames(neglect.data),colnames(abcd.data.withFamAndSite)))],by="subjectkey")
 
@@
 ```{r}
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+acceptance+monitoring,data=abcd.data))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+acceptance+monitoring,data=abcd.data))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+acceptance+monitoring,data=abcd.data))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data))
 

### 2022-02-02 PaperOutline_ACEsCog.Rmd
add sensitivity, effect sizes, mediations, items
added sensitivity analyses, effect sizes, mediation analyses, item-level analyses

@@
 
-# Verify that correlation is low: it's 0.222
-cor.test(all.data.complete$depriv,all.data.complete$emo_neglect)
-
-# Test specificity
-summary(lmer(EF~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete)) # both sig
-summary(lmer(WM~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete)) # both sig
-summary(lmer(TP~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete)) # both sig 
-summary(lmer(IC~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete)) # just depriv
-
-p.adjust(c(0.005610,1.72e-09,0.0030,3.22e-08,0.0111,5.23e-09,0.323230,0.014438),method="bonferroni")
+# # Test specificity
+# summary(lmer(EF~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete)) # both sig
+# summary(lmer(WM~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete)) # both sig
+# summary(lmer(TP~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete)) # both sig 
+# summary(lmer(IC~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete)) # just depriv 
+# 
+# p.adjust(c(0.005610,1.72e-09,0.0030,3.22e-08,0.0111,5.23e-09,0.323230,0.014438),method="bonferroni")
 
@@
 all.data.complete.ageres$emo_neglect <- -rowMeans(data.frame(as.numeric(all.data.complete.ageres$fat38a)/3,as.numeric(all.data.complete.ageres$fat39a)/3),na.rm=TRUE)
+
+# Verify that correlation is low: it's 0.236
 cor.test(all.data.complete.ageres$depriv,all.data.complete.ageres$emo_neglect)
@@
 # Test specificity
-summary(lmer(EF~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres)) # both sig
-summary(lmer(WM~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres)) # both sig
-summary(lmer(TP~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres)) # both sig 
-summary(lmer(IC~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres)) # just depriv
+summary(lmer(EF~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres)) # just depriv
+summary(lmer(WM~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres)) # just depriv
+summary(lmer(TP~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres)) # just depriv
+summary(lmer(IC~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres)) # neither
 
 p.adjust(c(0.0202,3.91e-05,0.0556,1.12e-06,0.020554,0.000262,0.4224,0.0588),method="bonferroni") 
+```
+
+# Get effect sizes
+```{r}
+library("effectsize")
+model1<-anova(lmer(EF~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres))
+model2<-anova(lmer(WM~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres))
+model3<-anova(lmer(TP~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres))
+model4<-anova(lmer(IC~age+gender+(1|state)+(1|schoolID)+emo_neglect+depriv,data=all.data.complete.ageres))
+
+eta2_emo_EF <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
+eta2_phy_EF <- F_to_eta2(model1[4,]$`F value`,model1[4,]$NumDF,model1[4,]$DenDF)
+eta2_emo_WM <- F_to_eta2(model2[3,]$`F value`,model2[3,]$NumDF,model2[3,]$DenDF)
+eta2_phy_WM <- F_to_eta2(model2[4,]$`F value`,model2[4,]$NumDF,model2[4,]$DenDF)
+eta2_emo_TP <- F_to_eta2(model3[3,]$`F value`,model3[3,]$NumDF,model3[3,]$DenDF)
+eta2_phy_TP <- F_to_eta2(model3[4,]$`F value`,model3[4,]$NumDF,model3[4,]$DenDF)
+eta2_emo_IC <- F_to_eta2(model4[3,]$`F value`,model4[3,]$NumDF,model4[3,]$DenDF)
+eta2_phy_IC <- F_to_eta2(model4[4,]$`F value`,model4[4,]$NumDF,model4[4,]$DenDF)
+
+eta2_emo_EF[1]
+eta2_phy_EF[1]
+eta2_emo_WM[1]
+eta2_phy_WM[1]
+eta2_emo_TP[1]
+eta2_phy_TP[1]
+eta2_emo_IC[1]
+eta2_phy_IC[1]
+
 ```
@@
 ggplot(all.data.complete.ageres, aes(x=emo_neglect,y=TP)) +
-  geom_point(colour=cols[2],size=1) +
+  geom_point(position="jitter",colour=cols[2],size=1) +
   geom_smooth(method=lm,color="black") + xlab("Emotional Neglect") + ylab("Temporal Processing") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
@@
 ggplot(all.data.complete.ageres, aes(x=emo_neglect,y=EF)) +
-  geom_point(colour=cols[4],size=1) +
+  geom_point(position="jitter",colour=cols[4],size=1) +
   geom_smooth(method=lm,color="black") + xlab("Emotional Neglect") + ylab("Exec.
@@
 ggplot(all.data.complete.ageres, aes(x=emo_neglect,y=WM)) +
-  geom_point(colour=cols[8],size=1) +
+  geom_point(position="jitter",colour=cols[8],size=1) +
   geom_smooth(method=lm,color="black") + xlab("Emotional Neglect") + ylab("Working Memory") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
@@
 ggplot(all.data.complete.ageres, aes(x=emo_neglect,y=IC)) +
-  geom_point(colour=cols[10],size=1) +
+  geom_point(position="jitter",colour=cols[10],size=1) +
   geom_smooth(method=lm,color="black") + xlab("Emotional Neglect") + ylab("Inhibitory Control") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
 dev.off()
+```
+
+# Demographics info
+```{r}
+# Gender (1, Male|2, Female)
+sum(all.data.complete.ageres$gender==1,na.rm=TRUE)
+round(sum(all.data.complete.ageres$gender==1,na.rm=TRUE)/dim(all.data.complete.ageres)[1],2)
+sum(all.data.complete.ageres$gender==2,na.rm=TRUE)
+round(sum(all.data.complete.ageres$gender==2,na.rm=TRUE)/dim(all.data.complete.ageres)[1],2)
+
+# Skin Color (1, White | 2, Black | 3, Between white and black (brown) | 4, Indigenous | 5, Asian | 99, Does not know)
+sum(all.data.complete.ageres$skincolor==1,na.rm=TRUE)
+round(sum(all.data.complete.ageres$skincolor==1,na.rm=TRUE)/dim(all.data.complete.ageres)[1],2)
+sum(all.data.complete.ageres$skincolor==2,na.rm=TRUE)
+round(sum(all.data.complete.ageres$skincolor==2,na.rm=TRUE)/dim(all.data.complete.ageres)[1],2)
+sum(all.data.complete.ageres$skincolor==3,na.rm=TRUE)
+round(sum(all.data.complete.ageres$skincolor==3,na.rm=TRUE)/dim(all.data.complete.ageres)[1],2)
+sum(all.data.complete.ageres$skincolor==4,na.rm=TRUE)
+round(sum(all.data.complete.ageres$skincolor==4,na.rm=TRUE)/dim(all.data.complete.ageres)[1],2)
+sum(all.data.complete.ageres$skincolor==5,na.rm=TRUE)
+round(sum(all.data.complete.ageres$skincolor==5,na.rm=TRUE)/dim(all.data.complete.ageres)[1],2)
+
+# How far did the head of the family study?
+# 99, Does not know|1, Without study (illiterate)|2, Elementary school incomplete (did not finish the former 8th grade)|3, Elementary school completed (finished the former 8th grade)|4, Incomplete high school (did not finish the former high school)|5, High school (finished the former high school)|6, Incomplete higher education (did not finish college)|7, Higher education (finished college)|8, Higher education with postgraduate studies (master's / doctorate / specialization)
+
+# NOTE: get ab6 variable for this ^ from the scale dom_s06_treat_w0w2
 ```
@@
 # # PC3 is related to physical neglect *** and trauma ***
+
+## Separate models for physical and emotional neglect:
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data)) # ***
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data)) # ***
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data)) # ***
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance,data=abcd.data)) # **
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance,data=abcd.data)) # .
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance,data=abcd.data)) # **
+```
+
+# Get effect sizes
+```{r}
+library("effectsize")
+model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data))
+model2<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data))
+model3<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data))
+
+eta2_emo_PC1 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
+eta2_phy_PC1 <- F_to_eta2(model1[4,]$`F value`,model1[4,]$NumDF,model1[4,]$DenDF)
+eta2_emo_PC2 <- F_to_eta2(model2[3,]$`F value`,model2[3,]$NumDF,model2[3,]$DenDF)
+eta2_phy_PC2 <- F_to_eta2(model2[4,]$`F value`,model2[4,]$NumDF,model2[4,]$DenDF)
+eta2_emo_PC3 <- F_to_eta2(model3[3,]$`F value`,model3[3,]$NumDF,model3[3,]$DenDF)
+eta2_phy_PC3 <- F_to_eta2(model3[4,]$`F value`,model3[4,]$NumDF,model3[4,]$DenDF)
+
+eta2_emo_PC1[1]
+eta2_phy_PC1[1]
+eta2_emo_PC2[1]
+eta2_phy_PC2[1]
+eta2_emo_PC3[1]
+eta2_phy_PC3[1]
+
+# effect sizes for separate models of physical and emotional neglect:
+model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data))
+model2<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data))
+model3<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data))
+model4<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance,data=abcd.data))
+model5<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance,data=abcd.data))
+model6<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance,data=abcd.data))
+
+eta2_emo_PC1 <- F_to_eta2(model4[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
+eta2_phy_PC1 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
+eta2_emo_PC2 <- F_to_eta2(model5[3,]$`F value`,model2[3,]$NumDF,model2[3,]$DenDF)
+eta2_phy_PC2 <- F_to_eta2(model2[3,]$`F value`,model2[3,]$NumDF,model2[3,]$DenDF)
+eta2_emo_PC3 <- F_to_eta2(model6[3,]$`F value`,model3[3,]$NumDF,model3[3,]$DenDF)
+eta2_phy_PC3 <- F_to_eta2(model3[3,]$`F value`,model3[3,]$NumDF,model3[3,]$DenDF)
+
+eta2_emo_PC1[1]
+eta2_phy_PC1[1]
+eta2_emo_PC2[1]
+eta2_phy_PC2[1]
+eta2_emo_PC3[1]
+eta2_phy_PC3[1]
+
+```
+
+### Look at specific items within parental warmth and parental monitoring:
+```{r}
+abcd.data$crpbi_parent1_y<-as.numeric(abcd.data$crpbi_parent1_y)
+abcd.data$crpbi_parent2_y<-as.numeric(abcd.data$crpbi_parent2_y)
+abcd.data$crpbi_parent3_y<-as.numeric(abcd.data$crpbi_parent3_y)
+abcd.data$crpbi_parent4_y<-as.numeric(abcd.data$crpbi_parent4_y)
+abcd.data$crpbi_parent5_y<-as.numeric(abcd.data$crpbi_parent5_y)
+abcd.data$parent_monitor_q1_y<-as.numeric(abcd.data$parent_monitor_q1_y)
+abcd.data$parent_monitor_q2_y<-as.numeric(abcd.data$parent_monitor_q2_y)
+abcd.data$parent_monitor_q3_y<-as.numeric(abcd.data$parent_monitor_q3_y)
+abcd.data$parent_monitor_q4_y<-as.numeric(abcd.data$parent_monitor_q4_y)
+abcd.data$parent_monitor_q5_y<-as.numeric(abcd.data$parent_monitor_q5_y)
+
+important.variables3 <- abcd.data[,c("crpbi_parent1_y","crpbi_parent2_y","crpbi_parent3_y","crpbi_parent4_y","crpbi_parent5_y")]
+colnames(important.variables3)<-c("Feel better talking worries","Smiles at me","Feel better when upset","Shows love","Easy to talk to")
+corrplot(cor(important.variables3,use="complete.obs"),method=c("number"), tl.col = "black", col=brewer.pal(n=8, name="Spectral"))
+
+important.variables4 <- abcd.data[,c("parent_monitor_q1_y","parent_monitor_q2_y","parent_monitor_q3_y","parent_monitor_q4_y","parent_monitor_q5_y")]
+colnames(important.variables4)<-c("Know where you are","Know who you're with","Know how to contact","Talk over plans","Dinner together")
+corrplot(cor(important.variables4,use="complete.obs"),method=c("number"), tl.col = "black", col=brewer.pal(n=8, name="Spectral"))
+
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+parent_monitor_q1_y+parent_monitor_q2_y+parent_monitor_q3_y+parent_monitor_q4_y+parent_monitor_q5_y,data=abcd.data)) # all significant *** (Q4 opp direction)
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+parent_monitor_q1_y+parent_monitor_q2_y+parent_monitor_q3_y+parent_monitor_q4_y+parent_monitor_q5_y,data=abcd.data)) # all but Q3 sig (Q4 opp direction)
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+parent_monitor_q1_y+parent_monitor_q2_y+parent_monitor_q3_y+parent_monitor_q4_y+parent_monitor_q5_y,data=abcd.data)) # all significant (Q4 opp direction)
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+crpbi_parent1_y+crpbi_parent2_y+crpbi_parent3_y+crpbi_parent4_y+crpbi_parent5_y,data=abcd.data)) # Q2, Q4, Q5 significant (Q5 opp direction)
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+crpbi_parent1_y+crpbi_parent2_y+crpbi_parent3_y+crpbi_parent4_y+crpbi_parent5_y,data=abcd.data)) # Q2, Q4, Q5 significant (Q5 opp direction)
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+crpbi_parent1_y+crpbi_parent2_y+crpbi_parent3_y+crpbi_parent4_y+crpbi_parent5_y,data=abcd.data)) # Q2, Q4, Q5 significant (Q5 opp direction)
+
+```
+
+# look for mediation: SES --> caregiving --> cognition
+```{r}
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data))
+# partial mediation!
+
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data))
+# partial mediation!
+
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data))
+# partial mediation!
+
+# Simplify household income variable:
+abcd.data$household.income.simple <- ifelse(abcd.data$household.income=="[>=100K]",1,0)
+
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income.simple,data=abcd.data))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income.simple+monitoring,data=abcd.data))
+# partial mediation!
+
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income.simple,data=abcd.data))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income.simple+monitoring,data=abcd.data))
+# partial mediation!
+
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income.simple,data=abcd.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income.simple+monitoring,data=abcd.data))
+# partial mediation!
+
+# Test for significance of mediation models with bootstrapping
+bs_indir = c()
+for (i in 1:10){
+  thisSample <- sample(c(1:dim(abcd.data)[1]),dim(abcd.data)[1],replace=TRUE)
+  pathc<-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income.simple,data=abcd.data[thisSample,]))
+  pathcp<-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income.simple+monitoring,data=abcd.data[thisSample,]))
+  indir<-pathc$coefficients[4]-pathcp$coefficients[5]
+  bs_indir <- c(bs_indir,indir)
+}
+t.test(bs_indir,conf.level=0.95)
+## Significant partial mediation
+
+bs_indir = c()
+for (i in 1:10){
+  thisSample <- sample(c(1:dim(abcd.data)[1]),dim(abcd.data)[1],replace=TRUE)
+  pathc<-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income.simple,data=abcd.data[thisSample,]))
+  pathcp<-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income.simple+monitoring,data=abcd.data[thisSample,]))
+  indir<-pathc$coefficients[4]-pathcp$coefficients[5]
+  bs_indir <- c(bs_indir,indir)
+}
+t.test(bs_indir,conf.level=0.95)
+## Significant partial mediation
+
+bs_indir = c()
+for (i in 1:10){
+  thisSample <- sample(c(1:dim(abcd.data)[1]),dim(abcd.data)[1],replace=TRUE)
+  pathc<-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income.simple,data=abcd.data[thisSample,]))
+  pathcp<-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income.simple+monitoring,data=abcd.data[thisSample,]))
+  indir<-pathc$coefficients[4]-pathcp$coefficients[5]
+  bs_indir <- c(bs_indir,indir)
+}
+t.test(bs_indir,conf.level=0.95)
+## Significant partial mediation
 ```
@@
 ggplot(abcd.data, aes(x=-monitoring,y=thompson_PC1)) +
-  geom_point(colour=cols[2],size=1) +
+  geom_point(position="jitter",colour=cols[2],size=1) +
   geom_smooth(method=lm,color="black") + xlab("Physical Neglect") + ylab("PC1: General Cognition") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
@@
 ggplot(abcd.data, aes(x=-monitoring,y=thompson_PC2)) +
-  geom_point(colour=cols[4],size=1) +
+  geom_point(position="jitter",colour=cols[4],size=1) +
   geom_smooth(method=lm,color="black") + xlab("Physical Neglect") + ylab("PC2: Exec.
@@
 ggplot(abcd.data, aes(x=-monitoring,y=thompson_PC3)) +
-  geom_point(colour=cols[8],size=1) +
+  geom_point(position="jitter",colour=cols[8],size=1) +
   geom_smooth(method=lm,color="black") + xlab("Physical Neglect") + ylab("PC3: Learning/Memory") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
@@
 ggplot(abcd.data, aes(x=-acceptance,y=thompson_PC1)) +
-  geom_point(colour=cols[2],size=1) +
+  geom_point(position="jitter",colour=cols[2],size=1) +
   geom_smooth(method=lm,color="black") + xlab("Emotional Neglect") + ylab("PC1: General Cognition") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
@@
 ggplot(abcd.data, aes(x=-acceptance,y=thompson_PC2)) +
-  geom_point(colour=cols[4],size=1) +
+  geom_point(position="jitter",colour=cols[4],size=1) +
   geom_smooth(method=lm,color="black") + xlab("Emotional Neglect") + ylab("PC2: Exec.
@@
 ggplot(abcd.data, aes(x=-acceptance,y=thompson_PC3)) +
-  geom_point(colour=cols[8],size=1) +
+  geom_point(position="jitter",colour=cols[8],size=1) +
   geom_smooth(method=lm,color="black") + xlab("Emotional Neglect") + ylab("PC3: Learning/Memory") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))
@@
 ```
+
+# Sandbox to test some covariates in ABCD
+```{r}
+
+# Race/Ethnicity (1 = White; 2 = Black; 3 = Hispanic; 4 = Asian; 5 = Other)
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race_ethnicity+acceptance+monitoring,data=abcd.data))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race_ethnicity+acceptance+monitoring,data=abcd.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race_ethnicity+acceptance+monitoring,data=abcd.data))
+
+# Race 6 level (1: White | 2: Black | 3: Asian | 4: AIAN/NHPI | 5: Other | 6: Mixed)
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+acceptance+monitoring,data=abcd.data))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+acceptance+monitoring,data=abcd.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+acceptance+monitoring,data=abcd.data))
+
+# Language/Reading ability
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+as.numeric(nihtbx_reading_agecorrected)+acceptance+monitoring,data=abcd.data))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+as.numeric(nihtbx_reading_agecorrected)+race_ethnicity+acceptance+monitoring,data=abcd.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+as.numeric(nihtbx_reading_agecorrected)+race_ethnicity+acceptance+monitoring,data=abcd.data))
+
+# Parent's highest degree of education
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+acceptance+monitoring,data=abcd.data))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+acceptance+monitoring,data=abcd.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+acceptance+monitoring,data=abcd.data))
+
+# Household income
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+acceptance+monitoring,data=abcd.data))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+acceptance+monitoring,data=abcd.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+acceptance+monitoring,data=abcd.data))
+
+```
+
+# Get demographics info
+```{r}
+abcd.data.noNA2 <- abcd.data[!is.na(abcd.data$acceptance),]
+abcd.data.noNA <- abcd.data.noNA2[!is.na(abcd.data.noNA2$monitoring),]
+
+sum(abcd.data.noNA$household.income=="[<50K]",na.rm=TRUE)
+mean(abcd.data.noNA[abcd.data.noNA$household.income=="[<50K]",]$acceptance,na.rm=TRUE)
+sd(abcd.data.noNA[abcd.data.noNA$household.income=="[<50K]",]$acceptance,na.rm=TRUE)
+mean(abcd.data.noNA[abcd.data.noNA$household.income=="[<50K]",]$monitoring,na.rm=TRUE)
+sd(abcd.data.noNA[abcd.data.noNA$household.income=="[<50K]",]$monitoring,na.rm=TRUE)
+
+sum(abcd.data.noNA$household.income=="[>=50K & <100K]",na.rm=TRUE)
+mean(abcd.data.noNA[abcd.data.noNA$household.income=="[>=50K & <100K]",]$acceptance,na.rm=TRUE)
+sd(abcd.data.noNA[abcd.data.noNA$household.income=="[>=50K & <100K]",]$acceptance,na.rm=TRUE)
+mean(abcd.data.noNA[abcd.data.noNA$household.income=="[>=50K & <100K]",]$monitoring,na.rm=TRUE)
+sd(abcd.data.noNA[abcd.data.noNA$household.income=="[>=50K & <100K]",]$monitoring,na.rm=TRUE)
+
+sum(abcd.data.noNA$household.income=="[>=100K]",na.rm=TRUE)
+mean(abcd.data.noNA[abcd.data.noNA$household.income=="[>=100K]",]$acceptance,na.rm=TRUE)
+sd(abcd.data.noNA[abcd.data.noNA$household.income=="[>=100K]",]$acceptance,na.rm=TRUE)
+mean(abcd.data.noNA[abcd.data.noNA$household.income=="[>=100K]",]$monitoring,na.rm=TRUE)
+sd(abcd.data.noNA[abcd.data.noNA$household.income=="[>=100K]",]$monitoring,na.rm=TRUE)
+
+summary(aov(acceptance~household.income,data=abcd.data.noNA)) # ***
+
+sum(abcd.data.noNA$high.educ=="< HS Diploma",na.rm=TRUE)
+mean(abcd.data.noNA[abcd.data.noNA$high.educ=="< HS Diploma",]$acceptance,na.rm=TRUE)
+sd(abcd.data.noNA[abcd.data.noNA$high.educ=="< HS Diploma",]$acceptance,na.rm=TRUE)
+mean(abcd.data.noNA[abcd.data.noNA$high.educ=="< HS Diploma",]$monitoring,na.rm=TRUE)
+sd(abcd.data.noNA[abcd.data.noNA$high.educ=="< HS Diploma",]$monitoring,na.rm=TRUE)
+
+sum(abcd.data.noNA$high.educ=="HS Diploma/GED",na.rm=TRUE)
+mean(abcd.data.noNA[abcd.data.noNA$high.educ=="HS Diploma/GED",]$acceptance,na.rm=TRUE)
+sd(abcd.data.noNA[abcd.data.noNA$high.educ=="HS Diploma/GED",]$acceptance,na.rm=TRUE)
+mean(abcd.data.noNA[abcd.data.noNA$high.educ=="HS Diploma/GED",]$monitoring,na.rm=TRUE)
+sd(abcd.data.noNA[abcd.data.noNA$high.educ=="HS Diploma/GED",]$monitoring,na.rm=TRUE)
+
+sum(abcd.data.noNA$high.educ=="Some College",na.rm=TRUE)
+mean(abcd.data.noNA[abcd.data.noNA$high.educ=="Some College",]$acceptance,na.rm=TRUE)
+sd(abcd.data.noNA[abcd.data.noNA$high.educ=="Some College",]$acceptance,na.rm=TRUE)
+mean(abcd.data.noNA[abcd.data.noNA$high.educ=="Some College",]$monitoring,na.rm=TRUE)
+sd(abcd.data.noNA[abcd.data.noNA$high.educ=="Some College",]$monitoring,na.rm=TRUE)
+
+sum(abcd.data.noNA$high.educ=="Bachelor",na.rm=TRUE)
+mean(abcd.data.noNA[abcd.data.noNA$high.educ=="Bachelor",]$acceptance,na.rm=TRUE)
+sd(abcd.data.noNA[abcd.data.noNA$high.educ=="Bachelor",]$acceptance,na.rm=TRUE)
+mean(abcd.data.noNA[abcd.data.noNA$high.educ=="Bachelor",]$monitoring,na.rm=TRUE)
+sd(abcd.data.noNA[abcd.data.noNA$high.educ=="Bachelor",]$monitoring,na.rm=TRUE)
+
+sum(abcd.data.noNA$high.educ=="Post Graduate Degree",na.rm=TRUE)
+mean(abcd.data.noNA[abcd.data.noNA$high.educ=="Post Graduate Degree",]$acceptance,na.rm=TRUE)
+sd(abcd.data.noNA[abcd.data.noNA$high.educ=="Post Graduate Degree",]$acceptance,na.rm=TRUE)
+mean(abcd.data.noNA[abcd.data.noNA$high.educ=="Post Graduate Degree",]$monitoring,na.rm=TRUE)
+sd(abcd.data.noNA[abcd.data.noNA$high.educ=="Post Graduate Degree",]$monitoring,na.rm=TRUE)
+
+summary(aov(acceptance~high.educ,data=abcd.data.noNA)) # ***
+
+#(1 = White; 2 = Black; 3 = Hispanic; 4 = Asian; 5 = Other)
+sum(abcd.data.noNA$race_ethnicity=="1",na.rm=TRUE)
+round(mean(abcd.data.noNA[abcd.data.noNA$race_ethnicity=="1",]$acceptance,na.rm=TRUE),2)
+round(sd(abcd.data.noNA[abcd.data.noNA$race_ethnicity=="1",]$acceptance,na.rm=TRUE),2)
+round(mean(abcd.data.noNA[abcd.data.noNA$race_ethnicity=="1",]$monitoring,na.rm=TRUE),2)
+round(sd(abcd.data.noNA[abcd.data.noNA$race_ethnicity=="1",]$monitoring,na.rm=TRUE),2)
+
+sum(abcd.data.noNA$race_ethnicity=="2",na.rm=TRUE)
+round(mean(abcd.data.noNA[abcd.data.noNA$race_ethnicity=="2",]$acceptance,na.rm=TRUE),2)
+round(sd(abcd.data.noNA[abcd.data.noNA$race_ethnicity=="2",]$acceptance,na.rm=TRUE),2)
+round(mean(abcd.data.noNA[abcd.data.noNA$race_ethnicity=="2",]$monitoring,na.rm=TRUE),2)
+round(sd(abcd.data.noNA[abcd.data.noNA$race_ethnicity=="2",]$monitoring,na.rm=TRUE),2)
+
+sum(abcd.data.noNA$race_ethnicity=="3",na.rm=TRUE)
+round(mean(abcd.data.noNA[abcd.data.noNA$race_ethnicity=="3",]$acceptance,na.rm=TRUE),2)
+round(sd(abcd.data.noNA[abcd.data.noNA$race_ethnicity=="3",]$acceptance,na.rm=TRUE),2)
+round(mean(abcd.data.noNA[abcd.data.noNA$race_ethnicity=="3",]$monitoring,na.rm=TRUE),2)
+round(sd(abcd.data.noNA[abcd.data.noNA$race_ethnicity=="3",]$monitoring,na.rm=TRUE),2)
+
+sum(abcd.data.noNA$race_ethnicity=="4",na.rm=TRUE)
+round(mean(abcd.data.noNA[abcd.data.noNA$race_ethnicity=="4",]$acceptance,na.rm=TRUE),2)
+round(sd(abcd.data.noNA[abcd.data.noNA$race_ethnicity=="4",]$acceptance,na.rm=TRUE),2)
+round(mean(abcd.data.noNA[abcd.data.noNA$race_ethnicity=="4",]$monitoring,na.rm=TRUE),2)
+round(sd(abcd.data.noNA[abcd.data.noNA$race_ethnicity=="4",]$monitoring,na.rm=TRUE),2)
+
+sum(abcd.data.noNA$race_ethnicity=="5",na.rm=TRUE)
+round(mean(abcd.data.noNA[abcd.data.noNA$race_ethnicity=="5",]$acceptance,na.rm=TRUE),2)
+round(sd(abcd.data.noNA[abcd.data.noNA$race_ethnicity=="5",]$acceptance,na.rm=TRUE),2)
+round(mean(abcd.data.noNA[abcd.data.noNA$race_ethnicity=="5",]$monitoring,na.rm=TRUE),2)
+round(sd(abcd.data.noNA[abcd.data.noNA$race_ethnicity=="5",]$monitoring,na.rm=TRUE),2)
+
+sum(abcd.data.noNA$sex=="F",na.rm=TRUE)
+round(mean(abcd.data.noNA[abcd.data.noNA$sex=="F",]$acceptance,na.rm=TRUE),2)
+round(sd(abcd.data.noNA[abcd.data.noNA$sex=="F",]$acceptance,na.rm=TRUE),2)
+round(mean(abcd.data.noNA[abcd.data.noNA$sex=="F",]$monitoring,na.rm=TRUE),2)
+round(sd(abcd.data.noNA[abcd.data.noNA$sex=="F",]$monitoring,na.rm=TRUE),2)
+
+sum(abcd.data.noNA$sex=="M",na.rm=TRUE)
+round(mean(abcd.data.noNA[abcd.data.noNA$sex=="M",]$acceptance,na.rm=TRUE),2)
+round(sd(abcd.data.noNA[abcd.data.noNA$sex=="M",]$acceptance,na.rm=TRUE),2)
+round(mean(abcd.data.noNA[abcd.data.noNA$sex=="M",]$monitoring,na.rm=TRUE),2)
+round(sd(abcd.data.noNA[abcd.data.noNA$sex=="M",]$monitoring,na.rm=TRUE),2)
+```
+
+# Repeat of all analyses within each race category separately:
+```{r}
+# Race 6 level (1: White | 2: Black | 3: Asian | 4: AIAN/NHPI | 5: Other | 6: Mixed)
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data[abcd.data$race.6level=="Black",]))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data[abcd.data$race.6level=="Black",])) # does not replicate
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data[abcd.data$race.6level=="Black",])) # does not replicate
+
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data[abcd.data$race.6level=="White",]))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data[abcd.data$race.6level=="White",]))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data[abcd.data$race.6level=="White",]))
+
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data[abcd.data$race.6level=="Asian",]))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data[abcd.data$race.6level=="Asian",])) # does not replicate
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data[abcd.data$race.6level=="Asian",])) # does not replicate
+
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data[abcd.data$race.6level=="AIAN/NHPI",])) # not enough subjects
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data[abcd.data$race.6level=="AIAN/NHPI",])) # not enough subjects
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data[abcd.data$race.6level=="AIAN/NHPI",])) # not enough subjects
+
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data[abcd.data$race.6level=="Other",]))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data[abcd.data$race.6level=="Other",])) # does not replicate
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data[abcd.data$race.6level=="Other",])) # does not replicate
+
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data[abcd.data$race.6level=="Mixed",]))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data[abcd.data$race.6level=="Mixed",]))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data[abcd.data$race.6level=="Mixed",]))
+```

### 2022-02-21 PaperOutline_ACEsCog.Rmd
item-level analysis of deprivation
deprivation factor score broken down into SES variables and neglect variables

@@
 
+```
+
+## Try a different calculation for "parental monitoring" to try to match ABCD (note: this is really a conceptual stretch...):
+```{r}
+all.data.complete.ageres$monitoring <- rowMeans(data.frame(as.numeric(all.data.complete.ageres$fes18),as.numeric(all.data.complete.ageres$fes48)),na.rm=TRUE)
+
+# Verify that correlation is low: it's 0.247
+cor.test(all.data.complete.ageres$monitoring,all.data.complete.ageres$emo_neglect)
+
+# Test specificity
+summary(lmer(EF~age+gender+(1|state)+(1|schoolID)+emo_neglect+monitoring,data=all.data.complete.ageres[all.data.complete.ageres$selection==1,])) # just monitoring
+summary(lmer(WM~age+gender+(1|state)+(1|schoolID)+emo_neglect+monitoring,data=all.data.complete.ageres[all.data.complete.ageres$selection==1,])) # just monitoring
+summary(lmer(TP~age+gender+(1|state)+(1|schoolID)+emo_neglect+monitoring,data=all.data.complete.ageres[all.data.complete.ageres$selection==1,])) # monitoring .
+summary(lmer(IC~age+gender+(1|state)+(1|schoolID)+emo_neglect+monitoring,data=all.data.complete.ageres[all.data.complete.ageres$selection==1,])) # monitoring .
+
+plot(all.data.complete.ageres[all.data.complete.ageres$selection==1,]$monitoring,all.data.complete.ageres[all.data.complete.ageres$selection==1,]$EF)
+```
+
+# Try using just the physical neglect part of the deprivation score rather than the whole thing (which includes SES)
+# From Mauricio from Julia: deprivation =~ minstlevel_4cat + abepstrat_r.w0 + pphyneg_r.w0 + cphysneg_r.w0 + faincome_qr.w0 + fstatus_r.w0
+```{r}
+# merge in new items (NOTE: SUBJECT COUNT DROPS TO N=914)
+deprivation_subitems <- readRDS("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/DeprivationScores_BHRC/jschafer_p2_prodata_20211003.rds")
+colnames(deprivation_subitems)[1]<-"SUBJECTID"
+all.data.ageres.dep <- merge(all.data.complete.ageres,deprivation_subitems[,c("SUBJECTID", setdiff(colnames(deprivation_subitems),colnames(all.data.complete.ageres)))],by="SUBJECTID")
+
+# child report of physical neglect score: all.data.ageres.dep$cphysneg_r.w0
+
+# Verify that correlation is low: it's 0.015
+cor.test(all.data.ageres.dep$cphysneg_r.w0,all.data.ageres.dep$emo_neglect)
+
+# Test specificity
+summary(lmer(EF~age+gender+(1|state)+(1|schoolID)+emo_neglect+cphysneg_r.w0,data=all.data.ageres.dep)) # just emo neglect
+summary(lmer(WM~age+gender+(1|state)+(1|schoolID)+emo_neglect+cphysneg_r.w0,data=all.data.ageres.dep)) # just emo neglect
+summary(lmer(TP~age+gender+(1|state)+(1|schoolID)+emo_neglect+cphysneg_r.w0,data=all.data.ageres.dep)) # just emo neglect
+summary(lmer(IC~age+gender+(1|state)+(1|schoolID)+emo_neglect+cphysneg_r.w0,data=all.data.ageres.dep)) # neither
+
+# So it's not really due to the neglect variable here, what about ses?
+summary(lmer(EF~age+gender+(1|state)+(1|schoolID)+emo_neglect+fstatus_r.w0,data=all.data.ageres.dep)) # just emo neglect
+summary(lmer(WM~age+gender+(1|state)+(1|schoolID)+emo_neglect+fstatus_r.w0,data=all.data.ageres.dep)) # just emo neglect
+summary(lmer(TP~age+gender+(1|state)+(1|schoolID)+emo_neglect+fstatus_r.w0,data=all.data.ageres.dep)) # just emo neglect
+summary(lmer(IC~age+gender+(1|state)+(1|schoolID)+emo_neglect+fstatus_r.w0,data=all.data.ageres.dep)) # neither
+
+summary(lmer(EF~age+gender+(1|state)+(1|schoolID)+emo_neglect+faincome_qr.w0,data=all.data.ageres.dep)) # just emo neglect
+summary(lmer(WM~age+gender+(1|state)+(1|schoolID)+emo_neglect+faincome_qr.w0,data=all.data.ageres.dep)) # just emo neglect
+summary(lmer(TP~age+gender+(1|state)+(1|schoolID)+emo_neglect+faincome_qr.w0,data=all.data.ageres.dep)) # just emo neglect
+summary(lmer(IC~age+gender+(1|state)+(1|schoolID)+emo_neglect+faincome_qr.w0,data=all.data.ageres.dep)) # neither
 ```
@@
 
+# make sure monitoring and acceptance are on the same scale so we can compare effect sizes:
+abcd.data$acceptance<-(((abcd.data$acceptance-1)/2)*4)+1
+
 # # Binarize the four ACEs subtypes (2 "Threat" types: Abuse and Trauma; 2 "Deprivation" types: Emotional Neglect and Physical Neglect)
@@
 ## Significant partial mediation
+```
+
+### Is parental monitoring related to increased stress exposures? Nope!
+```{r}
+ksads.data<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/Strife/abcd_ptsd01.txt",header=TRUE)
+ksads.baseline<-ksads.data[ksads.data$eventname=="baseline_year_1_arm_1",]
+abcd.data.with.ksads <- merge(abcd.data,ksads.baseline[, c("subjectkey", setdiff(colnames(ksads.baseline),colnames(abcd.data)))],by="subjectkey")
+
+abcd.data.with.ksads$totalACEs <- rowSums(data.frame(as.numeric(abcd.data.with.ksads$ksads_ptsd_raw_754_p),as.numeric(abcd.data.with.ksads$ksads_ptsd_raw_755_p),as.numeric(abcd.data.with.ksads$ksads_ptsd_raw_756_p),as.numeric(abcd.data.with.ksads$ksads_ptsd_raw_757_p),as.numeric(abcd.data.with.ksads$ksads_ptsd_raw_758_p),as.numeric(abcd.data.with.ksads$ksads_ptsd_raw_759_p),as.numeric(abcd.data.with.ksads$ksads_ptsd_raw_760_p),as.numeric(abcd.data.with.ksads$ksads_ptsd_raw_761_p),as.numeric(abcd.data.with.ksads$ksads_ptsd_raw_762_p),as.numeric(abcd.data.with.ksads$ksads_ptsd_raw_763_p),as.numeric(abcd.data.with.ksads$ksads_ptsd_raw_764_p),as.numeric(abcd.data.with.ksads$ksads_ptsd_raw_765_p),as.numeric(abcd.data.with.ksads$ksads_ptsd_raw_766_p),as.numeric(abcd.data.with.ksads$ksads_ptsd_raw_767_p),as.numeric(abcd.data.with.ksads$ksads_ptsd_raw_768_p),as.numeric(abcd.data.with.ksads$ksads_ptsd_raw_769_p),as.numeric(abcd.data.with.ksads$ksads_ptsd_raw_770_p)),na.rm=TRUE)
+
+summary(lmer(totalACEs~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.with.ksads))
+```
+
+# Adding adoption as a covariate 
+```{r}
+adoption.int.ext<-readRDS("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/DEAP-adoption-internalizing-externalizing.rds")
+adoption.int.ext<-adoption.int.ext[adoption.int.ext$event_name=="baseline_year_1_arm_1",]
+abcd.data.with.intext <- merge(abcd.data,adoption.int.ext[, c("src_subject_id", setdiff(colnames(adoption.int.ext),colnames(abcd.data)))],by="src_subject_id")
+
+abcd.data.with.intext$adopted <- ifelse(!is.na(abcd.data.with.intext$demo_adopt_age_p),1,0)
+
+summary(lmer(thompson_PC1~interview_age+sex+adopted+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data.with.intext))
+summary(lmer(thompson_PC2~interview_age+sex+adopted+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data.with.intext))
+summary(lmer(thompson_PC3~interview_age+sex+adopted+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data.with.intext))
+
+summary(lmer(acceptance~interview_age+sex+adopted+(1|rel_family_id)+(1|abcd_site),data=abcd.data.with.intext))
+summary(lmer(monitoring~interview_age+sex+adopted+(1|rel_family_id)+(1|abcd_site),data=abcd.data.with.intext))
+
+```
+
+## looking for double dissociation with internalizing/externalizing symptoms (it's not really there)
+```{r}
+summary(lmer(cbcl_scr_syn_internal_r~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data.with.intext))
+summary(lmer(cbcl_scr_syn_external_r~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data.with.intext))
+
+summary(lmer(cbcl_scr_syn_internal_r~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance,data=abcd.data.with.intext))
+summary(lmer(cbcl_scr_syn_internal_r~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.with.intext))
+summary(lmer(cbcl_scr_syn_external_r~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance,data=abcd.data.with.intext))
+summary(lmer(cbcl_scr_syn_external_r~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.with.intext))
+
+# what about other measures from CBCL?
+cbcls <-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/aseba/abcd_cbcls01.txt",header=TRUE)
+cbcls.baseline<-cbcls[cbcls$eventname=="baseline_year_1_arm_1",]
+abcd.data.cbcls <- merge(abcd.data,cbcls.baseline[, c("subjectkey", setdiff(colnames(cbcls.baseline),colnames(abcd.data)))],by="subjectkey")
+abcd.data.cbcls$cbcl_scr_syn_anxdep_r<-as.numeric(abcd.data.cbcls$cbcl_scr_syn_anxdep_r)
+abcd.data.cbcls$cbcl_scr_syn_aggressive_r<-as.numeric(abcd.data.cbcls$cbcl_scr_syn_aggressive_r)
+abcd.data.cbcls$cbcl_scr_syn_social_r<-as.numeric(abcd.data.cbcls$cbcl_scr_syn_social_r)
+abcd.data.cbcls$cbcl_scr_syn_thought_r<-as.numeric(abcd.data.cbcls$cbcl_scr_syn_thought_r)
+abcd.data.cbcls$cbcl_scr_syn_somatic_r<-as.numeric(abcd.data.cbcls$cbcl_scr_syn_somatic_r)
+abcd.data.cbcls$cbcl_scr_syn_withdep_r<-as.numeric(abcd.data.cbcls$cbcl_scr_syn_withdep_r)
+abcd.data.cbcls$cbcl_scr_syn_rulebreak_r<-as.numeric(abcd.data.cbcls$cbcl_scr_syn_rulebreak_r)
+
+summary(lmer(cbcl_scr_syn_aggressive_r~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data.cbcls))
+
+abcd.data.cbcls$cbcl_scr_dsm5_depress_r<-as.numeric(abcd.data.cbcls$cbcl_scr_dsm5_depress_r)
+abcd.data.cbcls$cbcl_scr_dsm5_anxdisord_r<-as.numeric(abcd.data.cbcls$cbcl_scr_dsm5_anxdisord_r)
+abcd.data.cbcls$cbcl_scr_dsm5_adhd_r<-as.numeric(abcd.data.cbcls$cbcl_scr_dsm5_adhd_r)
+abcd.data.cbcls$cbcl_scr_dsm5_opposit_r<-as.numeric(abcd.data.cbcls$cbcl_scr_dsm5_opposit_r)
+
+summary(lmer(cbcl_scr_dsm5_opposit_r~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data.cbcls))
+
+```
+
+### What about parental warmth x monitoring?
+```{r}
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance*monitoring,data=abcd.data)) # *
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance*monitoring,data=abcd.data)) #
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance*monitoring,data=abcd.data)) # .
 ```

### 2022-02-21 ABCD_OHBM_PFN_Analyses.Rmd
random effects
included random effects for both family and site in ABCD analyses

--- 2021-11-19 ABCD_OHBM_PFN_Analyses.Rmd
@@
 library(lmerTest)
+library(mediation)
+library(ggcorrplot)
+library(corrplot)
+library(RColorBrewer)
+library(glmnet)
+library(mgcv)
+library(gamm4)
 ```
@@
 
-combined.data <- merge(data.clean,abcd_imgincl01[, c("subjectkey",'imgincl_t1w_include')],by="subjectkey")
+combined.data <- merge(data.clean,abcd_imgincl01[, c("subjectkey",'imgincl_t1w_include')],by="subjectkey") # n=4,614
+
 ```
@@
 combined.data.noOutliers <- combined.data[combined.data$thompson_PC1>(mean_PC1-sd3_PC1) & combined.data$thompson_PC1<(mean_PC1+sd3_PC1) & combined.data$thompson_PC2>(mean_PC2-sd3_PC2) & combined.data$thompson_PC2<(mean_PC2+sd3_PC2) & combined.data$thompson_PC3>(mean_PC3-sd3_PC3) & combined.data$thompson_PC3<(mean_PC3+sd3_PC3),]
+
+# n=4,579
 ```
@@
 
-combined.data.noOutliers[,224:240]<-as.numeric(unlist(combined.data.noOutliers[,224:240]))
+# combined.data.noOutliers[,224:240]<-as.numeric(unlist(combined.data.noOutliers[,224:240]))
+# 
+# # Calculation of subscore with items related to physical and sexual abuse
+# combined.data.noOutliers$abuse <- rowSums(data.frame(as.numeric(combined.data.noOutliers$ksads_ptsd_raw_761_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_762_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_763_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_767_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_768_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_769_p)),na.rm=TRUE)
+# 
+# # Calculation of subscore with items related to trauma (car accidents, natural disasters, loss, etc.)
+# combined.data.noOutliers$trauma <- rowSums(data.frame(as.numeric(combined.data.noOutliers$ksads_ptsd_raw_754_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_755_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_756_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_757_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_758_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_759_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_760_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_766_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_770_p)),na.rm=TRUE)
+# 
+# # Remember to add in this variable about family structure so we can use it as a covariate
+# family <-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/ses/acspsw03.txt",header=TRUE)
+# family.baseline<-family[family$eventname=="baseline_year_1_arm_1",]
+# abcd.data <- merge(combined.data.noOutliers,family.baseline[, c("subjectkey", setdiff(colnames(family.baseline),colnames(combined.data.noOutliers)))],by="subjectkey")
+# 
+# emo.neglect <-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/neglect/crpbi01.txt",header=TRUE)
+# emo.neglect.baseline<-emo.neglect[emo.neglect$eventname=="baseline_year_1_arm_1",]
+# phy.neglect <-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/neglect/pmq01.txt",header=TRUE)
+# phy.neglect.baseline<-phy.neglect[phy.neglect$eventname=="baseline_year_1_arm_1",]
+# neglect.data <- merge(emo.neglect.baseline,phy.neglect.baseline[, c("subjectkey", setdiff(colnames(phy.neglect.baseline),colnames(emo.neglect.baseline)))],by="subjectkey")
+# 
+# abcd.data<-merge(abcd.data,neglect.data[,c("subjectkey", setdiff(colnames(neglect.data),colnames(abcd.data)))],by="subjectkey")
+# 
+# # Calculate subscales of deprivation (emotional and physical neglect) - see this ref for motivation https://www.sciencedirect.com/science/article/pii/S2352289518300821
+# abcd.data$acceptance <- rowSums(data.frame(as.numeric(abcd.data$crpbi_parent1_y),as.numeric(abcd.data$crpbi_parent2_y),as.numeric(abcd.data$crpbi_parent3_y),as.numeric(abcd.data$crpbi_parent4_y),as.numeric(abcd.data$crpbi_parent5_y)))
+# 
+# abcd.data$monitoring <- rowSums(data.frame(as.numeric(abcd.data$parent_monitor_q1_y),as.numeric(abcd.data$parent_monitor_q2_y),as.numeric(abcd.data$parent_monitor_q3_y),as.numeric(abcd.data$parent_monitor_q4_y),as.numeric(abcd.data$parent_monitor_q5_y)))
+# 
+# abcd.data$abuse.binary <- factor(abcd.data$abuse>=1,labels = c("No Abuse","Abuse"))
+# abcd.data$abuse.binary.numeric <- as.numeric(abcd.data$abuse.binary)
+# abcd.data$trauma.binary <- factor(abcd.data$trauma>=1,labels = c("No Trauma","Trauma"))
+# abcd.data$trauma.binary.numeric <- as.numeric(abcd.data$trauma.binary)
+# 
+# median.monitoring = median(na.omit(abcd.data$monitoring))
+# median.acceptance = median(na.omit(abcd.data$acceptance))
+# abcd.data$monitoring.binary <- factor(abcd.data$monitoring<20,labels = c("Low Physical Neglect","High Physical Neglect"))
+# abcd.data$monitoring.binary.numeric <- as.numeric(abcd.data$monitoring.binary)
+# abcd.data$acceptance.binary <- factor(abcd.data$acceptance<7.5,labels = c("Low Emotional Neglect","High Emotional Neglect"))
+# abcd.data$acceptance.binary.numeric <- as.numeric(abcd.data$acceptance.binary)
+```
 
-# Calculation of subscore with items related to physical and sexual abuse
-combined.data.noOutliers$abuse <- rowSums(data.frame(as.numeric(combined.data.noOutliers$ksads_ptsd_raw_761_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_762_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_763_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_767_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_768_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_769_p)),na.rm=TRUE)
-
-# Calculation of subscore with items related to trauma (car accidents, natural disasters, loss, etc.)
-combined.data.noOutliers$trauma <- rowSums(data.frame(as.numeric(combined.data.noOutliers$ksads_ptsd_raw_754_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_755_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_756_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_757_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_758_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_759_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_760_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_766_p),as.numeric(combined.data.noOutliers$ksads_ptsd_raw_770_p)),na.rm=TRUE)
+# More data prep (family ID, site ID, total FPN score, train/test)
+```{r}
+# calculate a total FPN score
+combined.data$totalFPN <- rowSums(data.frame(as.numeric(combined.data$df4),as.numeric(combined.data$df16),as.numeric(combined.data$df18)))
 
@@
 family.baseline<-family[family$eventname=="baseline_year_1_arm_1",]
-abcd.data <- merge(combined.data.noOutliers,family.baseline[, c("subjectkey", setdiff(colnames(family.baseline),colnames(combined.data.noOutliers)))],by="subjectkey")
+abcd.data.almost <- merge(combined.data,family.baseline[, c("subjectkey", setdiff(colnames(family.baseline),colnames(combined.data)))],by="subjectkey")
 
-emo.neglect <-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/neglect/crpbi01.txt",header=TRUE)
-emo.neglect.baseline<-emo.neglect[emo.neglect$eventname=="baseline_year_1_arm_1",]
-phy.neglect <-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/neglect/pmq01.txt",header=TRUE)
-phy.neglect.baseline<-phy.neglect[phy.neglect$eventname=="baseline_year_1_arm_1",]
-neglect.data <- merge(emo.neglect.baseline,phy.neglect.baseline[, c("subjectkey", setdiff(colnames(phy.neglect.baseline),colnames(emo.neglect.baseline)))],by="subjectkey")
-
-abcd.data<-merge(abcd.data,neglect.data[,c("subjectkey", setdiff(colnames(neglect.data),colnames(abcd.data)))],by="subjectkey")
-
-# Calculate subscales of deprivation (emotional and physical neglect) - see this ref for motivation https://www.sciencedirect.com/science/article/pii/S2352289518300821
-abcd.data$acceptance <- rowSums(data.frame(as.numeric(abcd.data$crpbi_parent1_y),as.numeric(abcd.data$crpbi_parent2_y),as.numeric(abcd.data$crpbi_parent3_y),as.numeric(abcd.data$crpbi_parent4_y),as.numeric(abcd.data$crpbi_parent5_y)))
-
-abcd.data$monitoring <- rowSums(data.frame(as.numeric(abcd.data$parent_monitor_q1_y),as.numeric(abcd.data$parent_monitor_q2_y),as.numeric(abcd.data$parent_monitor_q3_y),as.numeric(abcd.data$parent_monitor_q4_y),as.numeric(abcd.data$parent_monitor_q5_y)))
-
-abcd.data$abuse.binary <- factor(abcd.data$abuse>=1,labels = c("No Abuse","Abuse"))
-abcd.data$abuse.binary.numeric <- as.numeric(abcd.data$abuse.binary)
-abcd.data$trauma.binary <- factor(abcd.data$trauma>=1,labels = c("No Trauma","Trauma"))
-abcd.data$trauma.binary.numeric <- as.numeric(abcd.data$trauma.binary)
-
-median.monitoring = median(na.omit(abcd.data$monitoring))
-median.acceptance = median(na.omit(abcd.data$acceptance))
-abcd.data$monitoring.binary <- factor(abcd.data$monitoring<20,labels = c("Low Physical Neglect","High Physical Neglect"))
-abcd.data$monitoring.binary.numeric <- as.numeric(abcd.data$monitoring.binary)
-abcd.data$acceptance.binary <- factor(abcd.data$acceptance<7.5,labels = c("Low Emotional Neglect","High Emotional Neglect"))
-abcd.data$acceptance.binary.numeric <- as.numeric(abcd.data$acceptance.binary)
-
-# calculate a total FPN score
-combined.data.noOutliers$totalFPN <- rowSums(data.frame(as.numeric(combined.data.noOutliers$df4),as.numeric(combined.data.noOutliers$df16),as.numeric(combined.data.noOutliers$df18)))
+# also add in the variable for site ID to use as a covariate
+site_info <- readRDS("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/DEAP-siteID.rds")
+site.baseline<-site_info[site_info$event_name=="baseline_year_1_arm_1",]
+colnames(site.baseline)[1]<-"subjectkey"
+abcd.data.withFamAndSite <- merge(abcd.data.almost,site.baseline[,c("subjectkey", setdiff(colnames(site.baseline),colnames(abcd.data.almost)))],by="subjectkey")
 
@@
 trainIDs <- read.csv("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/train.csv")
-train.data <- merge(combined.data.noOutliers,trainIDs,by="subjectkey") # n=2,149
-test.data <- combined.data.noOutliers[!is.element(combined.data.noOutliers$subjectkey,trainIDs$subjectkey),] #n=2,424
+train.data <- merge(abcd.data.withFamAndSite,trainIDs,by="subjectkey") # n=2,290
+test.data <- abcd.data.withFamAndSite[!is.element(abcd.data.withFamAndSite$subjectkey,trainIDs$subjectkey),] #n=2,323
 ```
@@
 
+# Network 17 is specifically associated with PC1 and not PC2 or PC3
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+df18,data=train.data)) #***
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+df18,data=train.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+df18,data=train.data))
+
+# Network 15 is specifically associated with PC1 and PC3 but not PC2
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+df16,data=train.data)) #**
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+df16,data=train.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+df16,data=train.data)) #**
+
+# Network 3 is not associated with any of the PCs
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+df4,data=train.data)) 
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+df4,data=train.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+df4,data=train.data))
 ```
+
+```{r}
+# # We already know that trauma and physical neglect are associated with impairment in PC1
+# # Physical neglect is also associated with impairment in PC3
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary,data=train.data)) #**
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=train.data)) #***
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=train.data)) #***
+# 
+# 
+# # Are any subtypes of ACEs associated with PFN topography?
+# summary(lmer(totalFPN~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=train.data)) # ns
+# summary(lmer(totalFPN~interview_age+sex+(1|rel_family_id)+acceptance.binary,data=train.data)) # ns
+# summary(lmer(totalFPN~interview_age+sex+(1|rel_family_id)+abuse.binary,data=train.data)) # ns
+# summary(lmer(totalFPN~interview_age+sex+(1|rel_family_id)+trauma.binary,data=train.data)) # ns
+# 
+# summary(lmer(df18~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=train.data)) # ns
+# summary(lmer(df18~interview_age+sex+(1|rel_family_id)+acceptance.binary,data=train.data)) # ns
+# summary(lmer(df18~interview_age+sex+(1|rel_family_id)+abuse.binary,data=train.data)) # ns
+# summary(lmer(df18~interview_age+sex+(1|rel_family_id)+trauma.binary,data=train.data)) # ns
+# 
+# summary(lmer(df16~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=train.data)) # ns (0.056)
+# summary(lmer(df16~interview_age+sex+(1|rel_family_id)+acceptance.binary,data=train.data)) # ns
+# summary(lmer(df16~interview_age+sex+(1|rel_family_id)+abuse.binary,data=train.data)) # ns
+# summary(lmer(df16~interview_age+sex+(1|rel_family_id)+trauma.binary,data=train.data)) # ns
+# 
+# summary(lmer(df4~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=train.data)) # ns
+# summary(lmer(df4~interview_age+sex+(1|rel_family_id)+acceptance.binary,data=train.data)) # ns
+# summary(lmer(df4~interview_age+sex+(1|rel_family_id)+abuse.binary,data=train.data)) # ns
+# summary(lmer(df4~interview_age+sex+(1|rel_family_id)+trauma.binary,data=train.data)) # ns
+
+```
+
+# Mediation analyses -- these are significant!
+```{r}
+# Mediation: trauma --> Network 17 --> PC1 (path C does decrease) *
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary,data=train.data))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary+df18,data=train.data))
+
+bs_indir = c()
+for (i in 1:1000){
+  thisSample <- sample(c(1:length(train.data$subjectkey)),length(train.data$subjectkey),replace=TRUE)
+  pathc<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary,data=train.data[thisSample,])
+  pathcp<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary+df18,data=train.data[thisSample,])
+  indir<-fixef(pathc)[4]-fixef(pathcp)[5]
+  bs_indir <- c(bs_indir,indir)
+}
+t.test(bs_indir,conf.level=0.95)
+
+# Mediation: trauma --> Network 15 --> PC1 (path C does not decrease)
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary,data=train.data))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary+df16,data=train.data))
+
+# Mediation: physical neglect --> Network 17 --> PC1 (path C does decrease) *
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=train.data))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary+df18,data=train.data))
+
+bs_indir = c()
+for (i in 1:1000){
+  thisSample <- sample(c(1:length(train.data$subjectkey)),length(train.data$subjectkey),replace=TRUE)
+  pathc<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=train.data[thisSample,])
+  pathcp<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary+df18,data=train.data[thisSample,])
+  indir<-fixef(pathc)[4]-fixef(pathcp)[5]
+  bs_indir <- c(bs_indir,indir)
+}
+t.test(bs_indir,conf.level=0.95)
+
+# Mediation: physical neglect --> Network 15 --> PC1 (path C does not decrease)
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=train.data))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary+df16,data=train.data))
+
+# Mediation: physical neglect --> Network 17 --> PC3 (path C does decrease) *
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=train.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary+df18,data=train.data))
+
+bs_indir = c()
+for (i in 1:1000){
+  thisSample <- sample(c(1:length(train.data$subjectkey)),length(train.data$subjectkey),replace=TRUE)
+  pathc<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=train.data[thisSample,])
+  pathcp<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary+df18,data=train.data[thisSample,])
+  indir<-fixef(pathc)[4]-fixef(pathcp)[5]
+  bs_indir <- c(bs_indir,indir)
+}
+t.test(bs_indir,conf.level=0.95)
+
+# Mediation: physical neglect --> Network 15 --> PC3 (path C does not decrease)
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=train.data))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary+df16,data=train.data))
+
+```
+
+# No moderations were significant
+```{r}
+# # Moderation: trauma * Network 17 --> PC1
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary*df18,data=train.data))
+# 
+# # Moderation: trauma * Network 15 --> PC1
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary*df16,data=train.data))
+# 
+# # Moderation: physical neglect * Network 17 --> PC1
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary*df18,data=train.data))
+# 
+# # Moderation: physical neglect * Network 15 --> PC1
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary*df16,data=train.data))
+# 
+# # Moderation: physical neglect * Network 17 --> PC3
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary*df18,data=train.data))
+# 
+# # Moderation: physical neglect * Network 15 --> PC3 
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary*df16,data=train.data))
+# 
+# 
+# # Moderation: sex * trauma * Network 17 --> PC1
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary*df18*sex,data=train.data))
+# 
+# # Moderation: sex * trauma * Network 15 --> PC1
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary*df16*sex,data=train.data))
+# 
+# # Moderation: sex * physical neglect * Network 17 --> PC1
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary*df18*sex,data=train.data))
+# 
+# # Moderation: sex * physical neglect * Network 15 --> PC1
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary*df16*sex,data=train.data))
+# 
+# # Moderation: sex * physical neglect * Network 17 --> PC3
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary*df18*sex,data=train.data))
+# 
+# # Moderation: sex * physical neglect * Network 15 --> PC3 
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary*df16*sex,data=train.data))
+```
+
+# Analyses of total FPN
+```{r}
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+totalFPN,data=train.data)) #**
+# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+totalFPN,data=train.data)) #ns
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+totalFPN,data=train.data)) #ns
+# 
+# summary(lmer(totalFPN~interview_age+sex+(1|rel_family_id)+monitoring.binary,data=train.data)) #ns
+# summary(lmer(totalFPN~interview_age+sex+(1|rel_family_id)+acceptance.binary,data=train.data)) #ns
+# summary(lmer(totalFPN~interview_age+sex+(1|rel_family_id)+abuse.binary,data=train.data)) #ns
+# summary(lmer(totalFPN~interview_age+sex+(1|rel_family_id)+trauma.binary,data=train.data)) #ns
+# 
+# summary(lmer(totalFPN~interview_age+sex+(1|rel_family_id)+monitoring.binary*sex,data=train.data)) #ns
+# summary(lmer(totalFPN~interview_age+sex+(1|rel_family_id)+acceptance.binary*sex,data=train.data)) #ns
+# summary(lmer(totalFPN~interview_age+sex+(1|rel_family_id)+abuse.binary*sex,data=train.data)) #ns
+# summary(lmer(totalFPN~interview_age+sex+(1|rel_family_id)+trauma.binary*sex,data=train.data)) #ns
+
+```
+
+# Port data over to matlab (womp) so I can run the Canlab multilevel mediation toolbox 
+```{r}
+write.csv(train.data,file="trainData_forMatlab.csv")
+write.csv(test.data,file="testData_forMatlab.csv")
+```
+
+# Create a correlation matrix of all the important variables
+```{r}
+# important.variables <- train.data[,c("interview_age","monitoring","acceptance","abuse","trauma","df2","df3","df4","df5","df6","df7","df8","df9","df10","df11","df12","df13","df14","df15","df16","df17","df18","thompson_PC1","thompson_PC2","thompson_PC3")]
+# 
+# colnames(important.variables)<-c("Age","Phys Neglect","Emo Neglect","Abuse","Trauma","PFN 1","PFN 2","PFN 3","PFN 4","PFN 5","PFN 6","PFN 7","PFN 8","PFN 9","PFN 10","PFN 11","PFN 12","PFN 13","PFN 14","PFN 15","PFN 16","PFN 17","General Cog (PC1)","Exec Fxn (PC2)","Learn/Mem (PC3)")
+# 
+# png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/ABCD_PFNs_ACES_Cog_CorrMatrix.png",
+#     width = 8000, 
+#     height = 4000,
+#     res=300)
+# corrplot(cor(important.variables,use="complete.obs"),method=c("number"), tl.col = "black", col=brewer.pal(n=8, name="Spectral"))
+# dev.off() 
+```
+
+# Create a correlation matrix of just the cognitive and PFN variables
+```{r}
+important.variables <- train.data[,c("interview_age","df2","df3","df4","df5","df6","df7","df8","df9","df10","df11","df12","df13","df14","df15","df16","df17","df18","thompson_PC1","thompson_PC2","thompson_PC3")]
+
+colnames(important.variables)<-c("Age","PFN 1","PFN 2","PFN 3","PFN 4","PFN 5","PFN 6","PFN 7","PFN 8","PFN 9","PFN 10","PFN 11","PFN 12","PFN 13","PFN 14","PFN 15","PFN 16","PFN 17","General Cog (PC1)","Exec Fxn (PC2)","Learn/Mem (PC3)")
+
+png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/ABCD_PFNs_Cog_CorrMatrix.png",
+    width = 8000, 
+    height = 4000,
+    res=300)
+corrplot(cor(important.variables,use="complete.obs"),method=c("number"), tl.col = "black", col=brewer.pal(n=8, name="Spectral"))
+dev.off() 
+```
+
+## Cui et al. 2020 replications
+```{r}
+correlation<-cor.test(combined.data[combined.data$df18>3000,]$thompson_PC1,combined.data[combined.data$df18>3000,]$df18)
+png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/CuiRep_PC1_PFN17.png",
+    width = 4000, 
+    height = 4000,
+    res=1000)
+ggplot(data=combined.data[combined.data$df18>3000,],aes(thompson_PC1,df18))+geom_point(size=1,colour='gold')+geom_smooth(method=lm,colour='gray')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+panel.background = element_blank(), axis.line = element_line(colour = "black")) + ylab('Network 17') + xlab('Thompson PC1: General Cognition') + ggtitle(paste("r=",as.character(round(correlation$estimate,3)),", p=",as.character(round(correlation$p.value,3))))
+dev.off()
+
+correlation <- cor.test(combined.data$thompson_PC1,combined.data$df16)
+png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/CuiRep_PC1_PFN15.png",
+    width = 4000, 
+    height = 4000,
+    res=1000)
+ggplot(data=combined.data,aes(thompson_PC1,df16))+geom_point(size=1,colour='gold')+geom_smooth(method=lm,colour='gray')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Network 15') + xlab('Thompson PC1: General Cognition') + ggtitle(paste("r=",as.character(round(correlation$estimate,3)),", p=",as.character(round(correlation$p.value,3))))
+dev.off()
+
+correlation<-cor.test(combined.data$thompson_PC1,combined.data$df3)
+png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/CuiRep_PC1_PFN2.png",
+    width = 4000, 
+    height = 4000,
+    res=1000)
+ggplot(data=combined.data,aes(thompson_PC1,df3))+geom_point(size=1,colour='steel blue')+geom_smooth(method=lm,colour='gray')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Network 2') + xlab('Thompson PC1: General Cognition') + ggtitle(paste("r=",as.character(round(correlation$estimate,3)),", p=",as.character(round(correlation$p.value,3))))
+dev.off()
+
+correlation<-cor.test(combined.data$interview_age,combined.data$df5)
+png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/CuiRep_Age_PFN4.png",
+    width = 4000, 
+    height = 4000,
+    res=1000)
+ggplot(data=combined.data,aes(interview_age,df5))+geom_point(size=1,colour='steel blue')+geom_smooth(method=lm,colour='gray')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Network 4') + xlab('Age')  + ggtitle(paste("r=",as.character(round(correlation$estimate,3)),", p=",as.character(round(correlation$p.value,3))))
+dev.off()
+
+correlation<-cor.test(combined.data$interview_age,combined.data$df11)
+png("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/CuiRep_Age_PFN10.png",
+    width = 4000, 
+    height = 4000,
+    res=1000)
+ggplot(data=combined.data,aes(interview_age,df11))+geom_point(size=1,colour='purple')+geom_smooth(method=lm,colour='gray')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Network 10') + xlab('Age') + ggtitle(paste("r=",as.character(round(correlation$estimate,3)),", p=",as.character(round(correlation$p.value,3))))
+dev.off()
+
+```
+
+## Attempt at predictive modeling to see if we can predict the 3 independent domains of cognition from all the PFNs
+# PC1
+```{r}
+base_model<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site),data=train.data)
+pfn_model<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+df2+df3+df4+df5+df6+df7+df8+df9+df10+df11+df12+df13+df14+df15+df16+df17+df18,data=train.data)
+anova(base_model,pfn_model,test="Chisq")
+
+# Lasso to just use the PFNs that are relevant:
+x=model.matrix(lm(thompson_PC1~df2+df3+df4+df5+df6+df7+df8+df9+df10+df11+df12+df13+df14+df15+df16+df17+df18,data=train.data))
+y=train.data[!is.na(train.data$thompson_PC1),]$thompson_PC1
+
+#Use a second train/validation division to select the "lambda" for the lasso.
+set.seed(42894)
+train=sample(seq(2165),721,replace=FALSE)
+lasso.tr=glmnet(x[train,],y[train])
+pred=predict(lasso.tr,x[-train,])
+rmse=sqrt(apply((y[-train]-pred)^2,2,mean))
+plot(log(lasso.tr$lambda),rmse,type="b",xlab="Log(lambda")
+lam.best=lasso.tr$lambda[order(rmse)[1]] # extracting the best lambda - this extracts that component -- order puts them in order
+coef(lasso.tr,s=lam.best)
+
+# Test whether the model significantly improves over not having PFNs included
+base_model<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site),data=train.data)
+pfn_model_lasso<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+df4+df5+df6+df7+df8+df10+df11+df13+df15+df16+df18,data=train.data)
+anova(base_model,pfn_model_lasso,test="Chisq")
+
+# Test whether the model can predict cognition in held out test data
+pred.thompsonPC1<-predict(pfn_model_lasso,newdata=test.data[!is.na(test.data$thompson_PC1),c("interview_age","sex","rel_family_id","abcd_site","df4","df5","df6","df7","df8","df10","df11","df13","df15","df16","df18")],allow.new.levels=TRUE)
+plot(test.data[!is.na(test.data$thompson_PC1),]$thompson_PC1,pred.thompsonPC1)
+cor.test(test.data[!is.na(test.data$thompson_PC1),]$thompson_PC1,pred.thompsonPC1)
+```
+
+# PC2
+```{r}
+base_model<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site),data=train.data)
+pfn_model<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+df2+df3+df4+df5+df6+df7+df8+df9+df10+df11+df12+df13+df14+df15+df16+df17+df18,data=train.data)
+anova(base_model,pfn_model,test="Chisq")
+
+# Lasso to just use the PFNs that are relevant:
+x=model.matrix(lm(thompson_PC2~df2+df3+df4+df5+df6+df7+df8+df9+df10+df11+df12+df13+df14+df15+df16+df17+df18,data=train.data))
+y=train.data[!is.na(train.data$thompson_PC2),]$thompson_PC2
+
+#Use a second train/validation division to select the "lambda" for the lasso.
+set.seed(42894)
+train=sample(seq(2165),721,replace=FALSE)
+lasso.tr=glmnet(x[train,],y[train])
+pred=predict(lasso.tr,x[-train,])
+rmse=sqrt(apply((y[-train]-pred)^2,2,mean))
+plot(log(lasso.tr$lambda),rmse,type="b",xlab="Log(lambda")
+lam.best=lasso.tr$lambda[order(rmse)[1]] # extracting the best lambda - this extracts that component -- order puts them in order
+coef(lasso.tr,s=lam.best)
+
+# Test whether the model significantly improves over not having PFNs included
+base_model<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site),data=train.data)
+pfn_model_lasso<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+df2+df5+df7+df8+df10+df11+df12+df14+df17,data=train.data)
+anova(base_model,pfn_model_lasso,test="Chisq")
+
+# Test whether the model can predict cognition in held out test data
+pred.thompsonPC2<-predict(pfn_model_lasso,newdata=test.data[!is.na(test.data$thompson_PC2),c("interview_age","sex","rel_family_id","abcd_site","df2","df5","df7","df8","df10","df11","df12","df14","df17")],allow.new.levels=TRUE)
+plot(test.data[!is.na(test.data$thompson_PC2),]$thompson_PC2,pred.thompsonPC2)
+cor.test(test.data[!is.na(test.data$thompson_PC2),]$thompson_PC2,pred.thompsonPC2)
+```
+
+# PC3
+```{r}
+base_model<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site),data=train.data)
+pfn_model<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+df2+df3+df4+df5+df6+df7+df8+df9+df10+df11+df12+df13+df14+df15+df16+df17+df18,data=train.data)
+anova(base_model,pfn_model,test="Chisq")
+
+# Lasso to just use the PFNs that are relevant:
+x=model.matrix(lm(thompson_PC3~df2+df3+df4+df5+df6+df7+df8+df9+df10+df11+df12+df13+df14+df15+df16+df17+df18,data=train.data))
+y=train.data[!is.na(train.data$thompson_PC3),]$thompson_PC3
+
+#Use a second train/validation division to select the "lambda" for the lasso.
+set.seed(42894)
+train=sample(seq(2165),721,replace=FALSE)
+lasso.tr=glmnet(x[train,],y[train])
+pred=predict(lasso.tr,x[-train,])
+rmse=sqrt(apply((y[-train]-pred)^2,2,mean))
+plot(log(lasso.tr$lambda),rmse,type="b",xlab="Log(lambda")
+lam.best=lasso.tr$lambda[order(rmse)[1]] # extracting the best lambda - this extracts that component -- order puts them in order
+coef(lasso.tr,s=lam.best)
+
+# Test whether the model significantly improves over not having PFNs included
+base_model<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site),data=train.data)
+pfn_model_lasso<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+df2+df5+df6+df7+df8+df10+df11+df15+df16+df18,data=train.data)
+anova(base_model,pfn_model_lasso,test="Chisq")
+
+# Test whether the model can predict cognition in held out test data
+pred.thompsonPC3<-predict(pfn_model_lasso,newdata=test.data[!is.na(test.data$thompson_PC3),c("interview_age","sex","rel_family_id","abcd_site","df2","df5","df6","df7","df8","df10","df11","df15","df16","df18")],allow.new.levels=TRUE)
+plot(test.data[!is.na(test.data$thompson_PC3),]$thompson_PC3,pred.thompsonPC3)
+cor.test(test.data[!is.na(test.data$thompson_PC3),]$thompson_PC3,pred.thompsonPC3)
+```
+
+# A random attempt at using GAMs:
+```{r}
+train.data$rel_family_id <- as.factor(train.data$rel_family_id)
+gam1<-gamm4(thompson_PC1~s(interview_age)+sex+s(rel_family_id,bs="re")+s(abcd_site,bs="re"),data=train.data,method="REML")
+summary(gam1)
+gam2<-gamm4(thompson_PC1~s(interview_age)+sex+s(rel_family_id,bs="re")+s(abcd_site,bs="re")+df2+df3+df4+df5+df6+df7+df8+df9+df10+df11+df12+df13+df14+df15+df16+df17+df18,data=train.data,method="REML")
+summary(gam2)
+anova(gam1,gam2,test="Chisq")
+AIC(gam1,gam2)
+
+gam2<-gam(thompson_PC1~interview_age+sex+df2+df3+df4+df5+df6+df7+df8+df9+df10+df11+df12+df13+df14+df15+df16+df17+df18,data=train.data,method="REML")
+summary(gam2)
+
+```

### 2022-03-02 SES_Caregiving_Cognition.Rmd
all analyses for paper

---
title: "SES_Caregiving_Cognition"
author: "Arielle Keller"
date: "2/28/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(width=250)
library(tidyr)
library(dplyr)
library(ggplot2)
library(lsr)
library(lme4)
library(lmerTest)
library(mediation)
library(ggcorrplot)
library(corrplot)
library(RColorBrewer)
library(glmnet)
library(mgcv)
library(gamm4)
library(readr)
library(effectsize)
library(broom)
library(knitr)
library(sjPlot)
```

# Load data
```{r}
nihtb<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/NihTB/abcd_tbss01.txt",header=TRUE)
nihtb.baseline<-nihtb[nihtb$eventname=="baseline_year_1_arm_1",]
lmt<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/Thomp/lmtp201.txt",header=TRUE)
lmt.baseline<-lmt[lmt$eventname=="baseline_year_1_arm_1",]
merged.data2 <- merge(nihtb.baseline,lmt.baseline[, c("subjectkey", setdiff(colnames(lmt.baseline),colnames(nihtb.baseline)))],by="subjectkey")
ravlt<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/Thomp/abcd_ps01.txt",header=TRUE)
ravlt.baseline<-ravlt[ravlt$eventname=="baseline_year_1_arm_1",]
merged.data3 <- merge(merged.data2,ravlt.baseline[, c("subjectkey", setdiff(colnames(ravlt.baseline),colnames(merged.data2)))],by="subjectkey")
trauma<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/Strife/abcd_ptsd01.txt",header=TRUE)
trauma.baseline<-trauma[trauma$eventname=="baseline_year_1_arm_1",]
combined.data <- merge(merged.data3,trauma.baseline[, c("subjectkey", setdiff(colnames(trauma.baseline),colnames(merged.data3)))],by="subjectkey")
```

# Organize behavioral data
```{r}
# Coerce data types
combined.data$nihtbx_flanker_uncorrected <- as.numeric(combined.data$nihtbx_flanker_uncorrected)
combined.data$nihtbx_picvocab_uncorrected <- as.numeric(combined.data$nihtbx_picvocab_uncorrected)
combined.data$nihtbx_list_uncorrected <- as.numeric(combined.data$nihtbx_list_uncorrected)
combined.data$nihtbx_pattern_uncorrected <- as.numeric(combined.data$nihtbx_pattern_uncorrected)
combined.data$nihtbx_cardsort_uncorrected <- as.numeric(combined.data$nihtbx_cardsort_uncorrected)
combined.data$nihtbx_picture_uncorrected <- as.numeric(combined.data$nihtbx_picture_uncorrected)
combined.data$nihtbx_reading_uncorrected <- as.numeric(combined.data$nihtbx_reading_uncorrected)
combined.data$lmt_scr_perc_correct <- as.numeric(combined.data$lmt_scr_perc_correct)
combined.data$pea_ravlt_sd_trial_i_tc <- as.numeric(combined.data$pea_ravlt_sd_trial_i_tc)
combined.data$pea_ravlt_sd_trial_ii_tc <- as.numeric(combined.data$pea_ravlt_sd_trial_ii_tc)
combined.data$pea_ravlt_sd_trial_iii_tc <- as.numeric(combined.data$pea_ravlt_sd_trial_iii_tc)
combined.data$pea_ravlt_sd_trial_iv_tc <- as.numeric(combined.data$pea_ravlt_sd_trial_iv_tc)
combined.data$pea_ravlt_sd_trial_v_tc <- as.numeric(combined.data$pea_ravlt_sd_trial_v_tc)
combined.data$interview_age <- as.numeric(combined.data$interview_age)

ind_pea_ravlt = c(which(names(combined.data)=="pea_ravlt_sd_trial_i_tc"),which(names(combined.data)=="pea_ravlt_sd_trial_ii_tc"),
	which(names(combined.data)=="pea_ravlt_sd_trial_iii_tc"),which(names(combined.data)=="pea_ravlt_sd_trial_iv_tc"),
	which(names(combined.data)=="pea_ravlt_sd_trial_v_tc")); names(combined.data)[ind_pea_ravlt]; summary(combined.data[,ind_pea_ravlt])
combined.data$pea_ravlt_ld = apply(combined.data[,ind_pea_ravlt],1,sum)

combined.data$pea_ravlt_ld <- as.numeric(combined.data$pea_ravlt_ld)

# Rename according to Thompson 2018 code
names(combined.data)[which(names(combined.data)=="nihtbx_picvocab_uncorrected")] = "PicVocab"
names(combined.data)[which(names(combined.data)=="nihtbx_flanker_uncorrected")] = "Flanker"
names(combined.data)[which(names(combined.data)=="nihtbx_list_uncorrected")] = "List"
names(combined.data)[which(names(combined.data)=="nihtbx_cardsort_uncorrected")] = "CardSort"
names(combined.data)[which(names(combined.data)=="nihtbx_pattern_uncorrected")] = "Pattern"
names(combined.data)[which(names(combined.data)=="nihtbx_picture_uncorrected")] = "Picture"
names(combined.data)[which(names(combined.data)=="nihtbx_reading_uncorrected")] = "Reading"
names(combined.data)[which(names(combined.data)=="pea_ravlt_ld")] = "RAVLT"
names(combined.data)[which(names(combined.data)=="lmt_scr_perc_correct")] = "LMT"
```

# Calculate Thompson factor scores
```{r}
combined.data$thompson_PC1 <- (0.754*combined.data$PicVocab)+(0.213*combined.data$Flanker)+(0.471*combined.data$List)+(0.205*combined.data$CardSort)+(0.015*combined.data$Pattern)+(0.012*combined.data$Picture)+(0.82*combined.data$Reading)+(0.306*combined.data$RAVLT)+(0.5*combined.data$LMT)

combined.data$thompson_PC2 <- (0.065*combined.data$PicVocab)+(0.712*combined.data$Flanker)+(0.148*combined.data$List)+(0.71*combined.data$CardSort)+(0.813*combined.data$Pattern)+(0.135*combined.data$Picture)+(0.12*combined.data$Reading)+(0.125*combined.data$RAVLT)+(0.299*combined.data$LMT)

combined.data$thompson_PC3 <- (0.19*combined.data$PicVocab)+(0.067*combined.data$Flanker)+(0.493*combined.data$List)+(0.232*combined.data$CardSort)+(0.085*combined.data$Pattern)+(0.863*combined.data$Picture)+(0.122*combined.data$Reading)+(0.712*combined.data$RAVLT)+(0.068*combined.data$LMT)

# Remove outliers
mean_PC1 <- mean(combined.data$thompson_PC1,na.rm=TRUE)
mean_PC2 <- mean(combined.data$thompson_PC2,na.rm=TRUE)
mean_PC3 <- mean(combined.data$thompson_PC3,na.rm=TRUE)
sd3_PC1 <- sd(combined.data$thompson_PC1,na.rm=TRUE)*3
sd3_PC2 <- sd(combined.data$thompson_PC2,na.rm=TRUE)*3
sd3_PC3 <- sd(combined.data$thompson_PC3,na.rm=TRUE)*3
sum(combined.data$thompson_PC1 >= mean_PC1+sd3_PC1,na.rm=TRUE) # 8 outliers
sum(combined.data$thompson_PC2 >= mean_PC2+sd3_PC2,na.rm=TRUE) # 2 outliers
sum(combined.data$thompson_PC3 >= mean_PC3+sd3_PC3,na.rm=TRUE) # 0 outliers
sum(combined.data$thompson_PC1 <= mean_PC1-sd3_PC1,na.rm=TRUE) # 10 outliers
sum(combined.data$thompson_PC2 <= mean_PC2-sd3_PC2,na.rm=TRUE) # 17 outliers
sum(combined.data$thompson_PC3 <= mean_PC3-sd3_PC3,na.rm=TRUE) # 7 outliers
combined.data.noOutliers <- combined.data[combined.data$thompson_PC1>(mean_PC1-sd3_PC1) & combined.data$thompson_PC1<(mean_PC1+sd3_PC1) & combined.data$thompson_PC2>(mean_PC2-sd3_PC2) & combined.data$thompson_PC2<(mean_PC2+sd3_PC2) & combined.data$thompson_PC3>(mean_PC3-sd3_PC3) & combined.data$thompson_PC3<(mean_PC3+sd3_PC3),]

# n=11,781
```

# Add in Parental Warmth and Monitoring
```{r}
warmth <-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/neglect/crpbi01.txt",header=TRUE)
warmth.baseline<-warmth[warmth$eventname=="baseline_year_1_arm_1",]
monitoring.data <-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/neglect/pmq01.txt",header=TRUE)
monitoring.baseline<-monitoring.data[monitoring.data$eventname=="baseline_year_1_arm_1",]
parenting.data <- merge(warmth.baseline,monitoring.baseline[, c("subjectkey", setdiff(colnames(monitoring.baseline),colnames(warmth.baseline)))],by="subjectkey")

abcd.data<-merge(combined.data.noOutliers,parenting.data[,c("subjectkey", setdiff(colnames(parenting.data),colnames(combined.data.noOutliers)))],by="subjectkey")

abcd.data$warmth <- rowMeans(data.frame(as.numeric(abcd.data$crpbi_parent1_y),as.numeric(abcd.data$crpbi_parent2_y),as.numeric(abcd.data$crpbi_parent3_y),as.numeric(abcd.data$crpbi_parent4_y),as.numeric(abcd.data$crpbi_parent5_y)))

abcd.data$monitoring <- rowMeans(data.frame(as.numeric(abcd.data$parent_monitor_q1_y),as.numeric(abcd.data$parent_monitor_q2_y),as.numeric(abcd.data$parent_monitor_q3_y),as.numeric(abcd.data$parent_monitor_q4_y),as.numeric(abcd.data$parent_monitor_q5_y)))

# make sure monitoring and acceptance are on the same scale so we can compare effect sizes:
abcd.data$warmth<-(((abcd.data$warmth-1)/2)*4)+1

# n=10,966
```

# Add in Family and Site covariates
```{r}
# Remember to add in this variable about family structure so we can use it as a covariate
family <-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/ses/acspsw03.txt",header=TRUE)
family.baseline<-family[family$eventname=="baseline_year_1_arm_1",]
abcd.data.almost <- merge(abcd.data,family.baseline[, c("subjectkey", setdiff(colnames(family.baseline),colnames(abcd.data)))],by="subjectkey")

# also add in the variable for site ID to use as a covariate
site_info <- readRDS("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/DEAP-siteID.rds")
site.baseline<-site_info[site_info$event_name=="baseline_year_1_arm_1",]
colnames(site.baseline)[1]<-"subjectkey"
abcd.data.almost2 <- merge(abcd.data.almost,site.baseline[,c("subjectkey", setdiff(colnames(site.baseline),colnames(abcd.data.almost)))],by="subjectkey")
```

# Load train/test split from UMinn
```{r}
traintest<-read_tsv("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/participants.tsv")
traintest.baseline<-traintest[traintest$session_id=="ses-baselineYear1Arm1",c("participant_id","matched_group")]
colnames(traintest.baseline)[1]<-c("subjectkey")
traintest.baseline$subjectkey <- gsub(pattern="sub-NDAR",replacement="NDAR_", traintest.baseline$subjectkey)
traintest.baseline<-traintest.baseline %>% distinct()
abcd.data.traintest <- merge(abcd.data.almost2,traintest.baseline,by="subjectkey")
abcd.data.train <- abcd.data.traintest[abcd.data.traintest$matched_group==1,] # n=5,367
abcd.data.test <- abcd.data.traintest[abcd.data.traintest$matched_group==2,] # 5,312
```

## How do caregiving behaviors relate to cognition?
### Monitoring is positively related to all 3 cognitive variables but warmth is not
```{r}
cor.test(abcd.data.train$warmth,abcd.data.train$monitoring) # they are correlated at r=0.362

summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train))

summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train))

summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train))

# Get effect sizes
model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train))
eta2_w <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
eta2_m <- F_to_eta2(model1[4,]$`F value`,model1[4,]$NumDF,model1[4,]$DenDF)
model1<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train))
eta2_w <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
eta2_m <- F_to_eta2(model1[4,]$`F value`,model1[4,]$NumDF,model1[4,]$DenDF)
model1<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train))
eta2_w <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
eta2_m <- F_to_eta2(model1[4,]$`F value`,model1[4,]$NumDF,model1[4,]$DenDF)

model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train))
eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
model1<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train))
eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
model1<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train))
eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)

model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train))
eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
model1<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train))
eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
model1<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train))
eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)

# Print models to table
mod1<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train)
mod2<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train)
mod3<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train)
mod4<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train)
mod5<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train)
mod6<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train)
mod7<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train)
mod8<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train)
mod9<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train)
tab_model(mod1,mod2,mod3,pred.labels = c("Intercept","Age","Sex","Warmth","Monitoring"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_Monitoring_TableX.doc")
tab_model(mod4,mod5,mod6,pred.labels = c("Intercept","Age","Sex","Warmth"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific", file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_TableX.doc")
tab_model(mod7,mod8,mod9,pred.labels = c("Intercept","Age","Sex","Monitoring"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific", file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_TableX.doc")
```

## How does SES relate to cognition?
### It's significantly associated with all cognitive variables 
```{r}
summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train))

# Get effect sizes
model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train))
eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
model1<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train))
eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
model1<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train))
eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)

# print results to table
mod10<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train)
mod11<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train)
mod12<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train)
tab_model(mod10,mod11,mod12,pred.labels = c("Intercept","Age","Sex","Household Income [50K-100K]","Household Income [>=100K]"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Income_TableX.doc")

```

## Is SES associated with differences in parenting behaviors?
### SES is related to diffferences in monitoring but NOT differences in warmth (doesn't pass correction)
```{r}
summary(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train))
summary(lmer(warmth~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train))

# Get effect sizes
model1<-anova(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train))
eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
model1<-anova(lmer(warmth~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train))
eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)

mod13<-lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train)
mod14<-lmer(warmth~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train)
tab_model(mod13,mod14,pred.labels = c("Intercept","Age","Sex","Household Income [50K-100K]","Household Income [>=100K]"),dv.labels=c("Monitoring","Warmth"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Income_Caregiving_TableX.doc")

```

## Look at mediation SES --> monitoring --> PC1
```{r}
summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train))
summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train))

# partial mediation is significant!
bs_indir = c()
for (i in 1:1000){
  thisSample <- sample(c(1:length(abcd.data.train$subjectkey)),length(abcd.data.train$subjectkey),replace=TRUE)
  pathc<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train[thisSample,])
  pathcp<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train[thisSample,])
  indir<-fixef(pathc)[5]-fixef(pathcp)[5]
  bs_indir <- c(bs_indir,indir)
}
t.test(bs_indir,conf.level=0.95)
# t = 94.813, df = 999, p-value < 2.2e-16
# alternative hypothesis: true mean is not equal to 0
# 95 percent confidence interval:
#  0.3131269 0.3263624
# sample estimates:
# mean of x 
# 0.3197447

```

## Look at mediation SES --> monitoring --> PC2
```{r}
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train))

# partial mediation is significant!
bs_indir = c()
for (i in 1:1000){
  thisSample <- sample(c(1:length(abcd.data.train$subjectkey)),length(abcd.data.train$subjectkey),replace=TRUE)
  pathc<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train[thisSample,])
  pathcp<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train[thisSample,])
  indir<-fixef(pathc)[5]-fixef(pathcp)[5]
  bs_indir <- c(bs_indir,indir)
}
t.test(bs_indir,conf.level=0.95)
# t = 27.513, df = 999, p-value < 2.2e-16
# alternative hypothesis: true mean is not equal to 0
# 95 percent confidence interval:
#  0.1060481 0.1223373
# sample estimates:
# mean of x 
# 0.1141927

```

## Look at mediation SES --> monitoring --> PC3
```{r}
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train))

# partial mediation is significant!
bs_indir = c()
for (i in 1:1000){
  thisSample <- sample(c(1:length(abcd.data.train$subjectkey)),length(abcd.data.train$subjectkey),replace=TRUE)
  pathc<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train[thisSample,])
  pathcp<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train[thisSample,])
  indir<-fixef(pathc)[5]-fixef(pathcp)[5]
  bs_indir <- c(bs_indir,indir)
}
t.test(bs_indir,conf.level=0.95)

# t = 72.373, df = 999, p-value < 2.2e-16
# alternative hypothesis: true mean is not equal to 0
# 95 percent confidence interval:
#  0.2864221 0.3023873
# sample estimates:
# mean of x 
# 0.2944047 
```

# Make mediation table:
```{r}
moda<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train)
modb<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train)
modc<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train)
modd<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train)
mode<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train)
modf<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train)

tab_model(moda,modc,mode,pred.labels = c("Intercept","Age","Sex","Household Income [50K-100K]","Household Income [>=100K]"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Mediation1_TableX.doc")

tab_model(modb,modd,modf,pred.labels = c("Intercept","Age","Sex","Household Income [50K-100K]","Household Income [>=100K]","Monitoring"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Mediation2_TableX.doc")
```

# Simplified mediation analyses (>50K vs <50K) for the purpose of the figure
```{r}
abcd.data.train$simple.income <- ifelse(abcd.data.train$household.income=="[<50K]","Low","High")
summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+simple.income,data=abcd.data.train))
summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+simple.income+monitoring,data=abcd.data.train))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+simple.income,data=abcd.data.train))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+simple.income+monitoring,data=abcd.data.train))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+simple.income,data=abcd.data.train))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+simple.income+monitoring,data=abcd.data.train))

abcd.data.train$simple.income2 <- ifelse(abcd.data.train$household.income=="[>=100K]","High","Low")
summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+simple.income2,data=abcd.data.train))
summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+simple.income2+monitoring,data=abcd.data.train))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+simple.income2,data=abcd.data.train))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+simple.income2+monitoring,data=abcd.data.train))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+simple.income2,data=abcd.data.train))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+simple.income2+monitoring,data=abcd.data.train))

summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train))

summary(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+simple.income,data=abcd.data.train))
```

# Create a correlation matrix showing relatioships among variables
```{r}
important.variables <- abcd.data.traintest[,c("warmth","monitoring","thompson_PC1","thompson_PC2","thompson_PC3")]
colnames(important.variables)<-c("Caregiver Warmth","Caregiver Monitoring","General Cognition","Executive Function","Learning/Memory")
corrplot(cor(important.variables,use="complete.obs"),method=c("number"), tl.col = "black", col=brewer.pal(n=8, name="Spectral"))
```

### Look at specific items within parental warmth and parental monitoring:
```{r}
abcd.data.traintest$crpbi_parent1_y<-as.numeric(abcd.data.traintest$crpbi_parent1_y)
abcd.data.traintest$crpbi_parent2_y<-as.numeric(abcd.data.traintest$crpbi_parent2_y)
abcd.data.traintest$crpbi_parent3_y<-as.numeric(abcd.data.traintest$crpbi_parent3_y)
abcd.data.traintest$crpbi_parent4_y<-as.numeric(abcd.data.traintest$crpbi_parent4_y)
abcd.data.traintest$crpbi_parent5_y<-as.numeric(abcd.data.traintest$crpbi_parent5_y)
abcd.data.traintest$parent_monitor_q1_y<-as.numeric(abcd.data.traintest$parent_monitor_q1_y)
abcd.data.traintest$parent_monitor_q2_y<-as.numeric(abcd.data.traintest$parent_monitor_q2_y)
abcd.data.traintest$parent_monitor_q3_y<-as.numeric(abcd.data.traintest$parent_monitor_q3_y)
abcd.data.traintest$parent_monitor_q4_y<-as.numeric(abcd.data.traintest$parent_monitor_q4_y)
abcd.data.traintest$parent_monitor_q5_y<-as.numeric(abcd.data.traintest$parent_monitor_q5_y)

important.variables3 <- abcd.data.traintest[,c("crpbi_parent1_y","crpbi_parent2_y","crpbi_parent3_y","crpbi_parent4_y","crpbi_parent5_y")]
colnames(important.variables3)<-c("Feel better talking worries","Smiles at me","Feel better when upset","Shows love","Easy to talk to")
corrplot(cor(important.variables3,use="complete.obs"),method=c("number"), tl.col = "black", col=brewer.pal(n=8, name="Spectral"))

important.variables4 <- abcd.data.traintest[,c("parent_monitor_q1_y","parent_monitor_q2_y","parent_monitor_q3_y","parent_monitor_q4_y","parent_monitor_q5_y")]
colnames(important.variables4)<-c("Know where you are","Know who you're with","Know how to contact","Talk over plans","Dinner together")
corrplot(cor(important.variables4,use="complete.obs"),method=c("number"), tl.col = "black", col=brewer.pal(n=8, name="Spectral"))

summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+parent_monitor_q1_y+parent_monitor_q2_y+parent_monitor_q3_y+parent_monitor_q4_y+parent_monitor_q5_y,data=abcd.data.traintest)) # all significant *** (Q4 opp direction)
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+parent_monitor_q1_y+parent_monitor_q2_y+parent_monitor_q3_y+parent_monitor_q4_y+parent_monitor_q5_y,data=abcd.data.traintest)) # all but Q3 sig (Q4 opp direction)
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+parent_monitor_q1_y+parent_monitor_q2_y+parent_monitor_q3_y+parent_monitor_q4_y+parent_monitor_q5_y,data=abcd.data.traintest)) # all significant (Q4 opp direction)

summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+crpbi_parent1_y+crpbi_parent2_y+crpbi_parent3_y+crpbi_parent4_y+crpbi_parent5_y,data=abcd.data.traintest)) # Q2, Q4, Q5 significant (Q5 opp direction)
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+crpbi_parent1_y+crpbi_parent2_y+crpbi_parent3_y+crpbi_parent4_y+crpbi_parent5_y,data=abcd.data.traintest)) # Q2, Q4, Q5 significant (Q5 opp direction)
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+crpbi_parent1_y+crpbi_parent2_y+crpbi_parent3_y+crpbi_parent4_y+crpbi_parent5_y,data=abcd.data.traintest)) # Q2, Q4, Q5 significant (Q5 opp direction)

# make tables
mod15<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+parent_monitor_q1_y+parent_monitor_q2_y+parent_monitor_q3_y+parent_monitor_q4_y+parent_monitor_q5_y,data=abcd.data.traintest)
mod16<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+parent_monitor_q1_y+parent_monitor_q2_y+parent_monitor_q3_y+parent_monitor_q4_y+parent_monitor_q5_y,data=abcd.data.traintest)
mod17<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+parent_monitor_q1_y+parent_monitor_q2_y+parent_monitor_q3_y+parent_monitor_q4_y+parent_monitor_q5_y,data=abcd.data.traintest)
tab_model(mod15,mod16,mod17,pred.labels = c("Intercept","Age","Sex","Know where you are","Know who you're with","Know how to contact","Talk over plans","Dinner together"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Items_TableX.doc")
```

### Is parental monitoring related to increased stress exposures?
```{r}
abcd.data.traintest$totalACEs <- rowSums(data.frame(as.numeric(abcd.data.traintest$ksads_ptsd_raw_754_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_755_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_756_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_757_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_758_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_759_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_760_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_761_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_762_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_763_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_764_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_765_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_766_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_767_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_768_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_769_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_770_p)),na.rm=TRUE)

summary(lmer(totalACEs~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.traintest))
```

### Sensitivity analyses
```{r}
# Race 6 level (1: White | 2: Black | 3: Asian | 4: AIAN/NHPI | 5: Other | 6: Mixed)
summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+monitoring,data=abcd.data.train))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+monitoring,data=abcd.data.train))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+monitoring,data=abcd.data.train))

summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+household.income,data=abcd.data.train))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+household.income,data=abcd.data.train))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+household.income,data=abcd.data.train))

summary(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+household.income,data=abcd.data.train))

# Parent's highest degree of education
summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+monitoring,data=abcd.data.train))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+monitoring,data=abcd.data.train))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+monitoring,data=abcd.data.train))

summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+household.income,data=abcd.data.train))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+household.income,data=abcd.data.train))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+household.income,data=abcd.data.train))

summary(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+household.income,data=abcd.data.train))

# Add some more variables:
addvar<-readRDS("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/DEAP-discrim-marriage.rds")
addvar.baseline<-addvar[addvar$event_name=="baseline_year_1_arm_1",]
colnames(addvar.baseline)[1]<-"subjectkey"
abcd.addvar <- merge(abcd.data.train,addvar.baseline[, c("subjectkey", setdiff(colnames(addvar.baseline),colnames(abcd.data.train)))],by="subjectkey")

# Parents Married or Living Together
summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+monitoring,data=abcd.addvar))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+monitoring,data=abcd.addvar))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+monitoring,data=abcd.addvar))

summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+household.income,data=abcd.addvar))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+household.income,data=abcd.addvar))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+household.income,data=abcd.addvar))

summary(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+household.income,data=abcd.addvar))

# print tables for supplement
mod18<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+monitoring,data=abcd.data.train)
mod19<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+monitoring,data=abcd.data.train)
mod20<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+monitoring,data=abcd.data.train)
mod21<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+monitoring,data=abcd.data.train)
mod22<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+monitoring,data=abcd.data.train)
mod23<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+monitoring,data=abcd.data.train)
mod24<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+monitoring,data=abcd.addvar)
mod25<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+monitoring,data=abcd.addvar)
mod26<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+monitoring,data=abcd.addvar)
tab_model(mod18,mod19,mod20,pred.labels = c("Intercept","Age","Sex","White","Black","Asian","AIAN/NHPI","Other","Mixed","Monitoring"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Sens_Race_TableX.doc")
tab_model(mod21,mod22,mod23,pred.labels = c("Intercept","Age","Sex","HS Diploma/GED","Some College","Bachelor","Post Graduate","Monitoring"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Sens_Edu_TableX.doc")
tab_model(mod24,mod25,mod26,pred.labels = c("Intercept","Age","Sex","Married/Living Together","Monitoring"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Sens_Mar_TableX.doc")
```

# Generate Figures
```{r}
png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC1.png",
    width = 4000, 
    height = 3000,
    res=1000)
ggplot(data=subset(abcd.data.train,!is.na(household.income)),aes(household.income,thompson_PC1))+geom_boxplot(aes(household.income,thompson_PC1),color=rgb(33/255,80/255,113/255))+coord_cartesian(ylim = c(170, 320))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Household Income')
dev.off()

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC2.png",
    width = 4000, 
    height = 3000,
    res=1000)
ggplot(data=subset(abcd.data.train,!is.na(household.income)),aes(household.income,thompson_PC2))+geom_boxplot(aes(household.income,thompson_PC2),color=rgb(64/255,141/255,151/255))+coord_cartesian(ylim = c(170, 320))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Household Income')
dev.off()

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC3.png",
    width = 4000, 
    height = 3000,
    res=1000)
ggplot(data=subset(abcd.data.train,!is.na(household.income)),aes(household.income,thompson_PC3))+geom_boxplot(aes(household.income,thompson_PC3),color=rgb(157/255,207/255,160/255))+coord_cartesian(ylim = c(170, 320))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Household Income')
dev.off()

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_PC1.png",
    width = 2500, 
    height = 3000,
    res=700)
ggplot(data=abcd.data.train,aes(monitoring,thompson_PC1))+geom_point(position="jitter",size=1,colour=rgb(33/255,80/255,113/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Monitoring')
dev.off()

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_PC2.png",
    width = 2500, 
    height = 3000,
    res=700)
ggplot(data=abcd.data.train,aes(monitoring,thompson_PC2))+geom_point(position="jitter",size=1,colour=rgb(64/255,141/255,151/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Monitoring')
dev.off()

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_PC3.png",
    width = 2500, 
    height = 3000,
    res=700)
ggplot(data=abcd.data.train,aes(monitoring,thompson_PC3))+geom_point(position="jitter",size=1,colour=rgb(157/255,207/255,160/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Monitoring')
dev.off()

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_PC1.png",
    width = 2500, 
    height = 3000,
    res=700)
ggplot(data=abcd.data.train,aes(warmth,thompson_PC1))+geom_point(position="jitter",size=1,colour=rgb(33/255,80/255,113/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Warmth')
dev.off()

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_PC2.png",
    width = 2500, 
    height = 3000,
    res=700)
ggplot(data=abcd.data.train,aes(warmth,thompson_PC2))+geom_point(position="jitter",size=1,colour=rgb(64/255,141/255,151/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Warmth')
dev.off()

png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_PC3.png",
    width = 2500, 
    height = 3000,
    res=700)
ggplot(data=abcd.data.train,aes(warmth,thompson_PC3))+geom_point(position="jitter",size=1,colour=rgb(157/255,207/255,160/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Warmth')
dev.off()

df.summary <- subset(abcd.data.train,!is.na(household.income)) %>%
     group_by(household.income) %>%
     summarise(
         se = sd(warmth, na.rm = TRUE)/sqrt(length(warmth)),
         warmth = mean(warmth,na.rm=TRUE))
png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_SES.png",
    width = 4000, 
    height = 2000,
    res=700)
ggplot(data=df.summary,aes(household.income,warmth,fill=as.factor(household.income)))+geom_bar(position = "dodge",stat = "identity")+coord_cartesian(ylim = c(3.5, 5))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Warmth') + xlab('Household Income') + scale_fill_manual(values = c(rgb(145/255,69/255,93/255),rgb(206/255,118/255,119/255),rgb(227/255,180/255,150/255))) + geom_errorbar(aes(ymin=warmth-se, ymax=warmth+se), width=.2,position=position_dodge(.9))
dev.off()

df.summary <- subset(abcd.data.train,!is.na(household.income)) %>%
     group_by(household.income) %>%
     summarise(
         se = sd(monitoring, na.rm = TRUE)/sqrt(length(monitoring)),
         monitoring = mean(monitoring,na.rm=TRUE))
png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_SES.png",
    width = 4000, 
    height = 2000,
    res=700)
ggplot(data=df.summary,aes(household.income,monitoring,fill=as.factor(household.income)))+geom_bar(position = "dodge",stat = "identity")+coord_cartesian(ylim = c(3.5, 5))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Monitoring') + xlab('Household Income') + scale_fill_manual(values = c(rgb(145/255,69/255,93/255),rgb(206/255,118/255,119/255),rgb(227/255,180/255,150/255))) + geom_errorbar(aes(ymin=monitoring-se, ymax=monitoring+se), width=.2,position=position_dodge(.9))
dev.off() 
```

# Generalizability!
```{r}
mod31<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.test)
mod32<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.test)
mod33<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.test)

tab_model(mod31,mod32,mod33,digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific")

mod34<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.test)
mod35<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.test)
mod36<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.test)

tab_model(mod34,mod35,mod36,digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific")

summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.test))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.test))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.test))

summary(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.test))
summary(lmer(warmth~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.test))

summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.test))
summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.test))
bs_indir = c()
for (i in 1:1000){
  thisSample <- sample(c(1:length(abcd.data.test$subjectkey)),length(abcd.data.test$subjectkey),replace=TRUE)
  pathc<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.test[thisSample,])
  pathcp<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.test[thisSample,])
  indir<-fixef(pathc)[5]-fixef(pathcp)[5]
  bs_indir <- c(bs_indir,indir)
}
t.test(bs_indir,conf.level=0.95)
# t = 139.74, df = 999, p-value < 2.2e-16
# alternative hypothesis: true mean is not equal to 0
# 95 percent confidence interval:
#  0.4791434 0.4927918
# sample estimates:
# mean of x 
# 0.4859676

summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.test))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.test))
bs_indir = c()
for (i in 1:1000){
  thisSample <- sample(c(1:length(abcd.data.test$subjectkey)),length(abcd.data.test$subjectkey),replace=TRUE)
  pathc<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.test[thisSample,])
  pathcp<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.test[thisSample,])
  indir<-fixef(pathc)[5]-fixef(pathcp)[5]
  bs_indir <- c(bs_indir,indir)
}
t.test(bs_indir,conf.level=0.95)
# t = 91.84, df = 999, p-value < 2.2e-16
# alternative hypothesis: true mean is not equal to 0
# 95 percent confidence interval:
#  0.3852340 0.4020561
# sample estimates:
# mean of x 
#  0.393645

summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.test))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.test))
bs_indir = c()
for (i in 1:1000){
  thisSample <- sample(c(1:length(abcd.data.test$subjectkey)),length(abcd.data.test$subjectkey),replace=TRUE)
  pathc<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.test[thisSample,])
  pathcp<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.test[thisSample,])
  indir<-fixef(pathc)[5]-fixef(pathcp)[5]
  bs_indir <- c(bs_indir,indir)
}
t.test(bs_indir,conf.level=0.95)
# t = 111.61, df = 999, p-value < 2.2e-16
# alternative hypothesis: true mean is not equal to 0
# 95 percent confidence interval:
#  0.4880340 0.5055023
# sample estimates:
# mean of x 
# 0.4967681 
```

### 2022-03-16 SES_Caregiving_Cognition.Rmd
added figures and tables

@@
 # make sure monitoring and acceptance are on the same scale so we can compare effect sizes:
-abcd.data$warmth<-(((abcd.data$warmth-1)/2)*4)+1
+#abcd.data$warmth<-(((abcd.data$warmth-1)/2)*4)+1
+
+# Replace this rescaling with z-scoring ^
+abcd.data$warmth<-((abcd.data$warmth-mean(abcd.data$warmth,na.rm=TRUE))/sd(abcd.data$warmth,na.rm=TRUE))
+abcd.data$monitoring<-((abcd.data$monitoring-mean(abcd.data$monitoring,na.rm=TRUE))/sd(abcd.data$monitoring,na.rm=TRUE))
 
@@
 
+# Make a demographics table
+```{r}
+library(Gmisc)
+demo_table <- abcd.data.traintest %>%
+  mutate(matched_group = factor(matched_group, levels = 1:2, labels = c("Discovery", "Replication"))) %>%
+#subset(matched_group<3) %>%
+  set_column_labels(interview_age = "Age (Months)",
+                    sex = "Sex",
+                    race.6level = "Race",
+                    household.income = "Household Income",
+                    monitoring = "Caregiver Monitoring",
+                    warmth = "Caregiver Warmth",
+                    thompson_PC1 = "General Cognition",
+                    thompson_PC2 = "Executive Function",
+                    thompson_PC3 = "Learning/Memory",
+                    high.educ = "Parent Education") %>%
+getDescriptionStatsBy(interview_age, 
+                        sex,
+                        thompson_PC1,
+                        thompson_PC2,
+                        thompson_PC3,
+                        monitoring,
+                        warmth,
+                        household.income,
+                        race.6level,
+                        high.educ,
+                        add_total_col = TRUE, statistics=TRUE,
+                        by = matched_group)
+
+demo_table
+```
+
 ## How do caregiving behaviors relate to cognition?
@@
 
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth+monitoring,data=abcd.data.train))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth+monitoring,data=abcd.data.train))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth+monitoring,data=abcd.data.train))
 
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth,data=abcd.data.train))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth,data=abcd.data.train))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth,data=abcd.data.train))
 
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train))
 
 # Get effect sizes
-model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train))
+model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth+monitoring,data=abcd.data.train))
 eta2_w <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
 eta2_m <- F_to_eta2(model1[4,]$`F value`,model1[4,]$NumDF,model1[4,]$DenDF)
-model1<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train))
+model1<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth+monitoring,data=abcd.data.train))
 eta2_w <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
 eta2_m <- F_to_eta2(model1[4,]$`F value`,model1[4,]$NumDF,model1[4,]$DenDF)
-model1<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train))
+model1<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth+monitoring,data=abcd.data.train))
 eta2_w <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
@@
 
-model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train))
+model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth,data=abcd.data.train))
 eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
-model1<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train))
+model1<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth,data=abcd.data.train))
 eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
-model1<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train))
+model1<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth,data=abcd.data.train))
 eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
 
-model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train))
+model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train))
 eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
-model1<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train))
+model1<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train))
 eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
-model1<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train))
+model1<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train))
 eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
@@
 # Print models to table
-mod1<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train)
-mod2<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train)
-mod3<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train)
-mod4<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train)
-mod5<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train)
-mod6<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train)
-mod7<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train)
-mod8<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train)
-mod9<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train)
+mod1<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth+monitoring,data=abcd.data.train)
+mod2<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth+monitoring,data=abcd.data.train)
+mod3<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth+monitoring,data=abcd.data.train)
+mod4<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth,data=abcd.data.train)
+mod5<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth,data=abcd.data.train)
+mod6<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+warmth,data=abcd.data.train)
+mod7<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train)
+mod8<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train)
+mod9<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train)
 tab_model(mod1,mod2,mod3,pred.labels = c("Intercept","Age","Sex","Warmth","Monitoring"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
-Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_Monitoring_TableX.doc")
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="numeric",file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_Monitoring_TableX.doc")
 tab_model(mod4,mod5,mod6,pred.labels = c("Intercept","Age","Sex","Warmth"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
-Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific", file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_TableX.doc")
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="numeric", file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_TableX.doc")
 tab_model(mod7,mod8,mod9,pred.labels = c("Intercept","Age","Sex","Monitoring"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
-Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific", file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_TableX.doc")
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="numeric", file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_TableX.doc")
 ```
@@
 
+png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC1_violin.png",
+    width = 4000, 
+    height = 3000,
+    res=1000)
+ggplot(data=subset(abcd.data.train,!is.na(household.income)),aes(household.income,thompson_PC1))+geom_violin(aes(household.income,thompson_PC1),fill=rgb(33/255,80/255,113/255),trim=FALSE)+geom_boxplot(aes(household.income,thompson_PC1),width=0.2)+coord_cartesian(ylim = c(160, 320))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Household Income')
+dev.off()
+
 png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC2.png",
@@
 ggplot(data=subset(abcd.data.train,!is.na(household.income)),aes(household.income,thompson_PC2))+geom_boxplot(aes(household.income,thompson_PC2),color=rgb(64/255,141/255,151/255))+coord_cartesian(ylim = c(170, 320))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Household Income')
+dev.off()
+
+png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC2_violin.png",
+    width = 4000, 
+    height = 3000,
+    res=1000)
+ggplot(data=subset(abcd.data.train,!is.na(household.income)),aes(household.income,thompson_PC2))+geom_violin(aes(household.income,thompson_PC2),fill=rgb(64/255,141/255,151/255),trim=FALSE)+geom_boxplot(aes(household.income,thompson_PC2),width=0.2)+coord_cartesian(ylim = c(160, 320))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
 panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Household Income')
@@
 
+png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC3_violin.png",
+    width = 4000, 
+    height = 3000,
+    res=1000)
+ggplot(data=subset(abcd.data.train,!is.na(household.income)),aes(household.income,thompson_PC3))+geom_violin(aes(household.income,thompson_PC3),fill=rgb(157/255,207/255,160/255),trim=FALSE)+geom_boxplot(aes(household.income,thompson_PC3),width=0.2)+coord_cartesian(ylim = c(160, 320))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Household Income')
+dev.off()
+
 png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_PC1.png",
-    width = 2500, 
-    height = 3000,
-    res=700)
-ggplot(data=abcd.data.train,aes(monitoring,thompson_PC1))+geom_point(position="jitter",size=1,colour=rgb(33/255,80/255,113/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Monitoring')
+    width = 2600, 
+    height = 3100,
+    res=800)
+ggplot(data=abcd.data.train,aes(monitoring,thompson_PC1))+geom_point(position="jitter",size=1,colour=rgb(33/255,80/255,113/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Monitoring (z)')
 dev.off()
@@
 png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_PC2.png",
-    width = 2500, 
-    height = 3000,
-    res=700)
-ggplot(data=abcd.data.train,aes(monitoring,thompson_PC2))+geom_point(position="jitter",size=1,colour=rgb(64/255,141/255,151/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Monitoring')
+    width = 2600, 
+    height = 3100,
+    res=800)
+ggplot(data=abcd.data.train,aes(monitoring,thompson_PC2))+geom_point(position="jitter",size=1,colour=rgb(64/255,141/255,151/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Monitoring (z)')
 dev.off()
@@
 png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_PC3.png",
-    width = 2500, 
-    height = 3000,
-    res=700)
-ggplot(data=abcd.data.train,aes(monitoring,thompson_PC3))+geom_point(position="jitter",size=1,colour=rgb(157/255,207/255,160/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Monitoring')
+    width = 2600, 
+    height = 3100,
+    res=800)
+ggplot(data=abcd.data.train,aes(monitoring,thompson_PC3))+geom_point(position="jitter",size=1,colour=rgb(157/255,207/255,160/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Monitoring (z)')
 dev.off()
@@
 png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_PC1.png",
-    width = 2500, 
-    height = 3000,
-    res=700)
-ggplot(data=abcd.data.train,aes(warmth,thompson_PC1))+geom_point(position="jitter",size=1,colour=rgb(33/255,80/255,113/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Warmth')
+    width = 2600, 
+    height = 3100,
+    res=800)
+ggplot(data=abcd.data.train,aes(warmth,thompson_PC1))+geom_point(position="jitter",size=1,colour=rgb(33/255,80/255,113/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Warmth (z)')
 dev.off()
@@
 png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_PC2.png",
-    width = 2500, 
-    height = 3000,
-    res=700)
-ggplot(data=abcd.data.train,aes(warmth,thompson_PC2))+geom_point(position="jitter",size=1,colour=rgb(64/255,141/255,151/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Warmth')
+    width = 2600, 
+    height = 3100,
+    res=800)
+ggplot(data=abcd.data.train,aes(warmth,thompson_PC2))+geom_point(position="jitter",size=1,colour=rgb(64/255,141/255,151/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Warmth (z)')
 dev.off()
@@
 png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_PC3.png",
-    width = 2500, 
-    height = 3000,
-    res=700)
-ggplot(data=abcd.data.train,aes(warmth,thompson_PC3))+geom_point(position="jitter",size=1,colour=rgb(157/255,207/255,160/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Warmth')
+    width = 2600, 
+    height = 3100,
+    res=800)
+ggplot(data=abcd.data.train,aes(warmth,thompson_PC3))+geom_point(position="jitter",size=1,colour=rgb(157/255,207/255,160/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Warmth (z)')
 dev.off()
@@
     res=700)
-ggplot(data=df.summary,aes(household.income,warmth,fill=as.factor(household.income)))+geom_bar(position = "dodge",stat = "identity")+coord_cartesian(ylim = c(3.5, 5))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Warmth') + xlab('Household Income') + scale_fill_manual(values = c(rgb(145/255,69/255,93/255),rgb(206/255,118/255,119/255),rgb(227/255,180/255,150/255))) + geom_errorbar(aes(ymin=warmth-se, ymax=warmth+se), width=.2,position=position_dodge(.9))
+ggplot(data=df.summary,aes(household.income,warmth,fill=as.factor(household.income)))+geom_bar(position = "dodge",stat = "identity")+coord_cartesian(ylim = c(-0.25, 0.25))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Warmth (z)') + xlab('Household Income') + scale_fill_manual(values = c(rgb(145/255,69/255,93/255),rgb(206/255,118/255,119/255),rgb(227/255,180/255,150/255))) + geom_errorbar(aes(ymin=warmth-se, ymax=warmth+se), width=.2,position=position_dodge(.9))
 dev.off()
@@
     res=700)
-ggplot(data=df.summary,aes(household.income,monitoring,fill=as.factor(household.income)))+geom_bar(position = "dodge",stat = "identity")+coord_cartesian(ylim = c(3.5, 5))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Monitoring') + xlab('Household Income') + scale_fill_manual(values = c(rgb(145/255,69/255,93/255),rgb(206/255,118/255,119/255),rgb(227/255,180/255,150/255))) + geom_errorbar(aes(ymin=monitoring-se, ymax=monitoring+se), width=.2,position=position_dodge(.9))
+ggplot(data=df.summary,aes(household.income,monitoring,fill=as.factor(household.income)))+geom_bar(position = "dodge",stat = "identity")+coord_cartesian(ylim = c(-0.25, 0.25))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Monitoring (z)') + xlab('Household Income') + scale_fill_manual(values = c(rgb(145/255,69/255,93/255),rgb(206/255,118/255,119/255),rgb(227/255,180/255,150/255))) + geom_errorbar(aes(ymin=monitoring-se, ymax=monitoring+se), width=.2,position=position_dodge(.9))
 dev.off()
+
+save_train_data<-data.frame(abcd.data.train$thompson_PC1,abcd.data.train$thompson_PC2,abcd.data.train$thompson_PC3,abcd.data.train$warmth,abcd.data.train$monitoring)
+save_test_data<-data.frame(abcd.data.test$thompson_PC1,abcd.data.test$thompson_PC2,abcd.data.test$thompson_PC3,abcd.data.test$warmth,abcd.data.test$monitoring)
+write.csv(save_train_data,"/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/traintest_figs/data_from_R_train.csv")
+write.csv(save_test_data,"/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/traintest_figs/data_from_R_test.csv")
+
 ```
@@
 ```
+
+# Generate Figures - TEST DATA
+```{r}
+png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC1_test.png",
+    width = 4000, 
+    height = 3000,
+    res=1000)
+ggplot(data=subset(abcd.data.test,!is.na(household.income)),aes(household.income,thompson_PC1))+geom_boxplot(aes(household.income,thompson_PC1),color=rgb(33/255,80/255,113/255))+coord_cartesian(ylim = c(170, 320))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Household Income')
+dev.off()
+
+png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC2_test.png",
+    width = 4000, 
+    height = 3000,
+    res=1000)
+ggplot(data=subset(abcd.data.test,!is.na(household.income)),aes(household.income,thompson_PC2))+geom_boxplot(aes(household.income,thompson_PC2),color=rgb(64/255,141/255,151/255))+coord_cartesian(ylim = c(170, 320))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Household Income')
+dev.off()
+
+png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC3_test.png",
+    width = 4000, 
+    height = 3000,
+    res=1000)
+ggplot(data=subset(abcd.data.test,!is.na(household.income)),aes(household.income,thompson_PC3))+geom_boxplot(aes(household.income,thompson_PC3),color=rgb(157/255,207/255,160/255))+coord_cartesian(ylim = c(170, 320))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Household Income')
+dev.off()
+
+png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_PC1_test.png",
+    width = 2600, 
+    height = 3100,
+    res=800)
+ggplot(data=abcd.data.test,aes(monitoring,thompson_PC1))+geom_point(position="jitter",size=1,colour=rgb(33/255,80/255,113/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Monitoring (z)')
+dev.off()
+
+png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_PC2_test.png",
+    width = 2600, 
+    height = 3100,
+    res=800)
+ggplot(data=abcd.data.test,aes(monitoring,thompson_PC2))+geom_point(position="jitter",size=1,colour=rgb(64/255,141/255,151/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Monitoring (z)')
+dev.off()
+
+png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_PC3_test.png",
+    width = 2600, 
+    height = 3100,
+    res=800)
+ggplot(data=abcd.data.test,aes(monitoring,thompson_PC3))+geom_point(position="jitter",size=1,colour=rgb(157/255,207/255,160/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Monitoring (z)')
+dev.off()
+
+png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_PC1_test.png",
+    width = 2600, 
+    height = 3100,
+    res=800)
+ggplot(data=abcd.data.test,aes(warmth,thompson_PC1))+geom_point(position="jitter",size=1,colour=rgb(33/255,80/255,113/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Warmth (z)')
+dev.off()
+
+png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_PC2_test.png",
+    width = 2600, 
+    height = 3100,
+    res=800)
+ggplot(data=abcd.data.test,aes(warmth,thompson_PC2))+geom_point(position="jitter",size=1,colour=rgb(64/255,141/255,151/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Warmth (z)')
+dev.off()
+
+png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_PC3_test.png",
+    width = 2600, 
+    height = 3100,
+    res=800)
+ggplot(data=abcd.data.test,aes(warmth,thompson_PC3))+geom_point(position="jitter",size=1,colour=rgb(157/255,207/255,160/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Warmth (z)')
+dev.off()
+
+df.summary <- subset(abcd.data.test,!is.na(household.income)) %>%
+     group_by(household.income) %>%
+     summarise(
+         se = sd(warmth, na.rm = TRUE)/sqrt(length(warmth)),
+         warmth = mean(warmth,na.rm=TRUE))
+png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_SES_test.png",
+    width = 4000, 
+    height = 2000,
+    res=700)
+ggplot(data=df.summary,aes(household.income,warmth,fill=as.factor(household.income)))+geom_bar(position = "dodge",stat = "identity")+coord_cartesian(ylim = c(3.5, 5))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Warmth') + xlab('Household Income') + scale_fill_manual(values = c(rgb(145/255,69/255,93/255),rgb(206/255,118/255,119/255),rgb(227/255,180/255,150/255))) + geom_errorbar(aes(ymin=warmth-se, ymax=warmth+se), width=.2,position=position_dodge(.9))
+dev.off()
+
+df.summary <- subset(abcd.data.test,!is.na(household.income)) %>%
+     group_by(household.income) %>%
+     summarise(
+         se = sd(monitoring, na.rm = TRUE)/sqrt(length(monitoring)),
+         monitoring = mean(monitoring,na.rm=TRUE))
+png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_SES_test.png",
+    width = 4000, 
+    height = 2000,
+    res=700)
+ggplot(data=df.summary,aes(household.income,monitoring,fill=as.factor(household.income)))+geom_bar(position = "dodge",stat = "identity")+coord_cartesian(ylim = c(3.5, 5))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Monitoring') + xlab('Household Income') + scale_fill_manual(values = c(rgb(145/255,69/255,93/255),rgb(206/255,118/255,119/255),rgb(227/255,180/255,150/255))) + geom_errorbar(aes(ymin=monitoring-se, ymax=monitoring+se), width=.2,position=position_dodge(.9))
+dev.off() 
+```

### 2022-06-10 SES_Caregiving_Cognition.Rmd
final copy for ms submission

--- 2022-03-02 SES_Caregiving_Cognition.Rmd
@@
 ```{r}
-nihtb<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/NihTB/abcd_tbss01.txt",header=TRUE)
+nihtb<-read.table("/Users/askeller/Documents/Kellernet_PrelimAnalysis/NihTB/abcd_tbss01.txt",header=TRUE)
 nihtb.baseline<-nihtb[nihtb$eventname=="baseline_year_1_arm_1",]
-lmt<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/Thomp/lmtp201.txt",header=TRUE)
+lmt<-read.table("/Users/askeller/Documents/Kellernet_PrelimAnalysis/Thomp/lmtp201.txt",header=TRUE)
 lmt.baseline<-lmt[lmt$eventname=="baseline_year_1_arm_1",]
 merged.data2 <- merge(nihtb.baseline,lmt.baseline[, c("subjectkey", setdiff(colnames(lmt.baseline),colnames(nihtb.baseline)))],by="subjectkey")
-ravlt<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/Thomp/abcd_ps01.txt",header=TRUE)
+ravlt<-read.table("/Users/askeller/Documents/Kellernet_PrelimAnalysis/Thomp/abcd_ps01.txt",header=TRUE)
 ravlt.baseline<-ravlt[ravlt$eventname=="baseline_year_1_arm_1",]
 merged.data3 <- merge(merged.data2,ravlt.baseline[, c("subjectkey", setdiff(colnames(ravlt.baseline),colnames(merged.data2)))],by="subjectkey")
-trauma<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/Strife/abcd_ptsd01.txt",header=TRUE)
+trauma<-read.table("/Users/askeller/Documents/Kellernet_PrelimAnalysis/Strife/abcd_ptsd01.txt",header=TRUE)
 trauma.baseline<-trauma[trauma$eventname=="baseline_year_1_arm_1",]
@@
 
-# Calculate Thompson factor scores
+## Instead of calculating the Thompson factor scores ourselves, use the summary scores from DEAP
+# also add in variables for residential income
 ```{r}
-combined.data$thompson_PC1 <- (0.754*combined.data$PicVocab)+(0.213*combined.data$Flanker)+(0.471*combined.data$List)+(0.205*combined.data$CardSort)+(0.015*combined.data$Pattern)+(0.012*combined.data$Picture)+(0.82*combined.data$Reading)+(0.306*combined.data$RAVLT)+(0.5*combined.data$LMT)
+newdata<-readRDS("/Users/askeller/Documents/Kellernet_PrelimAnalysis/DEAP-data-download_ThompsonScores_ResFamIncome.rds")
+newdata.baseline<-newdata[newdata$event_name=="baseline_year_1_arm_1",]
+colnames(newdata.baseline)[1]<-"subjectkey"
+all.data <- merge(combined.data,newdata.baseline[,c("subjectkey", setdiff(colnames(newdata.baseline),colnames(combined.data)))],by="subjectkey")
 
-combined.data$thompson_PC2 <- (0.065*combined.data$PicVocab)+(0.712*combined.data$Flanker)+(0.148*combined.data$List)+(0.71*combined.data$CardSort)+(0.813*combined.data$Pattern)+(0.135*combined.data$Picture)+(0.12*combined.data$Reading)+(0.125*combined.data$RAVLT)+(0.299*combined.data$LMT)
+# # Calculate Thompson factor scores
+# 
+# combined.data$thompson_PC1 <- (0.754*combined.data$PicVocab)+(0.213*combined.data$Flanker)+(0.471*combined.data$List)+(0.205*combined.data$CardSort)+(0.015*combined.data$Pattern)+(0.012*combined.data$Picture)+(0.82*combined.data$Reading)+(0.306*combined.data$RAVLT)+(0.5*combined.data$LMT)
+# 
+# combined.data$thompson_PC2 <- (0.065*combined.data$PicVocab)+(0.712*combined.data$Flanker)+(0.148*combined.data$List)+(0.71*combined.data$CardSort)+(0.813*combined.data$Pattern)+(0.135*combined.data$Picture)+(0.12*combined.data$Reading)+(0.125*combined.data$RAVLT)+(0.299*combined.data$LMT)
+# 
+# combined.data$thompson_PC3 <- (0.19*combined.data$PicVocab)+(0.067*combined.data$Flanker)+(0.493*combined.data$List)+(0.232*combined.data$CardSort)+(0.085*combined.data$Pattern)+(0.863*combined.data$Picture)+(0.122*combined.data$Reading)+(0.712*combined.data$RAVLT)+(0.068*combined.data$LMT)
+# 
+# # Remove outliers
+# mean_PC1 <- mean(combined.data$thompson_PC1,na.rm=TRUE)
+# mean_PC2 <- mean(combined.data$thompson_PC2,na.rm=TRUE)
+# mean_PC3 <- mean(combined.data$thompson_PC3,na.rm=TRUE)
+# sd3_PC1 <- sd(combined.data$thompson_PC1,na.rm=TRUE)*3
+# sd3_PC2 <- sd(combined.data$thompson_PC2,na.rm=TRUE)*3
+# sd3_PC3 <- sd(combined.data$thompson_PC3,na.rm=TRUE)*3
+# sum(combined.data$thompson_PC1 >= mean_PC1+sd3_PC1,na.rm=TRUE) # 8 outliers
+# sum(combined.data$thompson_PC2 >= mean_PC2+sd3_PC2,na.rm=TRUE) # 2 outliers
+# sum(combined.data$thompson_PC3 >= mean_PC3+sd3_PC3,na.rm=TRUE) # 0 outliers
+# sum(combined.data$thompson_PC1 <= mean_PC1-sd3_PC1,na.rm=TRUE) # 10 outliers
+# sum(combined.data$thompson_PC2 <= mean_PC2-sd3_PC2,na.rm=TRUE) # 17 outliers
+# sum(combined.data$thompson_PC3 <= mean_PC3-sd3_PC3,na.rm=TRUE) # 7 outliers
+# combined.data.noOutliers <- combined.data[combined.data$thompson_PC1>(mean_PC1-sd3_PC1) & combined.data$thompson_PC1<(mean_PC1+sd3_PC1) & combined.data$thompson_PC2>(mean_PC2-sd3_PC2) & combined.data$thompson_PC2<(mean_PC2+sd3_PC2) & combined.data$thompson_PC3>(mean_PC3-sd3_PC3) & combined.data$thompson_PC3<(mean_PC3+sd3_PC3),]
 
-combined.data$thompson_PC3 <- (0.19*combined.data$PicVocab)+(0.067*combined.data$Flanker)+(0.493*combined.data$List)+(0.232*combined.data$CardSort)+(0.085*combined.data$Pattern)+(0.863*combined.data$Picture)+(0.122*combined.data$Reading)+(0.712*combined.data$RAVLT)+(0.068*combined.data$LMT)
-
-# Remove outliers
-mean_PC1 <- mean(combined.data$thompson_PC1,na.rm=TRUE)
-mean_PC2 <- mean(combined.data$thompson_PC2,na.rm=TRUE)
-mean_PC3 <- mean(combined.data$thompson_PC3,na.rm=TRUE)
-sd3_PC1 <- sd(combined.data$thompson_PC1,na.rm=TRUE)*3
-sd3_PC2 <- sd(combined.data$thompson_PC2,na.rm=TRUE)*3
-sd3_PC3 <- sd(combined.data$thompson_PC3,na.rm=TRUE)*3
-sum(combined.data$thompson_PC1 >= mean_PC1+sd3_PC1,na.rm=TRUE) # 8 outliers
-sum(combined.data$thompson_PC2 >= mean_PC2+sd3_PC2,na.rm=TRUE) # 2 outliers
-sum(combined.data$thompson_PC3 >= mean_PC3+sd3_PC3,na.rm=TRUE) # 0 outliers
-sum(combined.data$thompson_PC1 <= mean_PC1-sd3_PC1,na.rm=TRUE) # 10 outliers
-sum(combined.data$thompson_PC2 <= mean_PC2-sd3_PC2,na.rm=TRUE) # 17 outliers
-sum(combined.data$thompson_PC3 <= mean_PC3-sd3_PC3,na.rm=TRUE) # 7 outliers
-combined.data.noOutliers <- combined.data[combined.data$thompson_PC1>(mean_PC1-sd3_PC1) & combined.data$thompson_PC1<(mean_PC1+sd3_PC1) & combined.data$thompson_PC2>(mean_PC2-sd3_PC2) & combined.data$thompson_PC2<(mean_PC2+sd3_PC2) & combined.data$thompson_PC3>(mean_PC3-sd3_PC3) & combined.data$thompson_PC3<(mean_PC3+sd3_PC3),]
-
-# n=11,781
 ```
@@
 ```{r}
-warmth <-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/neglect/crpbi01.txt",header=TRUE)
+warmth <-read.table("/Users/askeller/Documents/Kellernet_PrelimAnalysis/neglect/crpbi01.txt",header=TRUE)
 warmth.baseline<-warmth[warmth$eventname=="baseline_year_1_arm_1",]
-monitoring.data <-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/neglect/pmq01.txt",header=TRUE)
+monitoring.data <-read.table("/Users/askeller/Documents/Kellernet_PrelimAnalysis/neglect/pmq01.txt",header=TRUE)
 monitoring.baseline<-monitoring.data[monitoring.data$eventname=="baseline_year_1_arm_1",]
@@
 
-abcd.data<-merge(combined.data.noOutliers,parenting.data[,c("subjectkey", setdiff(colnames(parenting.data),colnames(combined.data.noOutliers)))],by="subjectkey")
+abcd.data<-merge(all.data,parenting.data[,c("subjectkey", setdiff(colnames(parenting.data),colnames(all.data)))],by="subjectkey")
 
@@
 # Remember to add in this variable about family structure so we can use it as a covariate
-family <-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/ses/acspsw03.txt",header=TRUE)
+family <-read.table("/Users/askeller/Documents/Kellernet_PrelimAnalysis/ses/acspsw03.txt",header=TRUE)
 family.baseline<-family[family$eventname=="baseline_year_1_arm_1",]
@@
 # also add in the variable for site ID to use as a covariate
-site_info <- readRDS("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/DEAP-siteID.rds")
+site_info <- readRDS("/Users/askeller/Documents/Kellernet_PrelimAnalysis/DEAP-siteID.rds")
 site.baseline<-site_info[site_info$event_name=="baseline_year_1_arm_1",]
@@
 abcd.data.almost2 <- merge(abcd.data.almost,site.baseline[,c("subjectkey", setdiff(colnames(site.baseline),colnames(abcd.data.almost)))],by="subjectkey")
+
+# exclude participants with missing cognitive data
+abcd.data.almost3<-abcd.data.almost2[complete.cases(abcd.data.almost2$neurocog_pc1.bl),] # drop 11,875 to 11,039
+abcd.data.almost4<-abcd.data.almost3[complete.cases(abcd.data.almost3$neurocog_pc2.bl),]
+abcd.data.almost5<-abcd.data.almost4[complete.cases(abcd.data.almost4$neurocog_pc3.bl),] # still 11,039
+
+# exclude for missing warmth/monitoring data
+abcd.data.almost6<-abcd.data.almost5[complete.cases(abcd.data.almost5$warmth),] # drop to 11,018
+abcd.data.almost7<-abcd.data.almost6[complete.cases(abcd.data.almost6$monitoring),] # drop to 11,016
+
+# exclude for missing household income, residential income, and parents' education
+abcd.data.almost8<-abcd.data.almost7[complete.cases(abcd.data.almost7$reshist_addr1_adi_income),] # drop to 10,381
+abcd.data.almost9<-abcd.data.almost8[complete.cases(abcd.data.almost8$household.income),] # drop to 9,521
+abcd.data.almost10<-abcd.data.almost9[complete.cases(abcd.data.almost9$high.educ),] # drop to 9,517
+
+# for simplicity, rename thompson variables
+colnames(abcd.data.almost10)<-gsub("neurocog_pc1.bl","thompson_PC1",colnames(abcd.data.almost10))
+colnames(abcd.data.almost10)<-gsub("neurocog_pc2.bl","thompson_PC2",colnames(abcd.data.almost10))
+colnames(abcd.data.almost10)<-gsub("neurocog_pc3.bl","thompson_PC3",colnames(abcd.data.almost10))
+```
+
+# Exclude cognitive outliers
+```{r}
+abcd.data.almost11<-abcd.data.almost10[abcd.data.almost10$thompson_PC1<3,]
+abcd.data.almost12<-abcd.data.almost11[abcd.data.almost11$thompson_PC1>-3,]
+
+abcd.data.almost13<-abcd.data.almost12[abcd.data.almost12$thompson_PC2<3,]
+abcd.data.almost14<-abcd.data.almost13[abcd.data.almost13$thompson_PC2>-3,]
+
+abcd.data.almost15<-abcd.data.almost14[abcd.data.almost14$thompson_PC3<3,]
+abcd.data.almost16<-abcd.data.almost15[abcd.data.almost15$thompson_PC3>-3,]
+
+# 9,510 (only lose 7 subj)
 ```
@@
 ```{r}
-traintest<-read_tsv("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/participants.tsv")
+traintest<-read_tsv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/participants.tsv")
 traintest.baseline<-traintest[traintest$session_id=="ses-baselineYear1Arm1",c("participant_id","matched_group")]
@@
 traintest.baseline<-traintest.baseline %>% distinct()
-abcd.data.traintest <- merge(abcd.data.almost2,traintest.baseline,by="subjectkey")
-abcd.data.train <- abcd.data.traintest[abcd.data.traintest$matched_group==1,] # n=5,367
-abcd.data.test <- abcd.data.traintest[abcd.data.traintest$matched_group==2,] # 5,312
+abcd.data.traintest <- merge(abcd.data.almost16,traintest.baseline,by="subjectkey")
+abcd.data.train <- abcd.data.traintest[abcd.data.traintest$matched_group==1,] # n=4,664
+abcd.data.test <- abcd.data.traintest[abcd.data.traintest$matched_group==2,] # 4,596
+```
+
+# Make a demographics table
+```{r}
+library(Gmisc)
+demo_table <- abcd.data.traintest %>%
+  mutate(matched_group = factor(matched_group, levels = 1:2, labels = c("Discovery", "Replication"))) %>%
+#subset(matched_group<3) %>%
+  set_column_labels(interview_age = "Age (Months)",
+                    sex = "Sex",
+                    race.6level = "Race",
+                    household.income = "Household Income",
+                    reshist_addr1_adi_income = "Neighborhood Income",
+                    monitoring = "Caregiver Monitoring",
+                    warmth = "Caregiver Warmth",
+                    thompson_PC1 = "General Cognition",
+                    thompson_PC2 = "Executive Function",
+                    thompson_PC3 = "Learning/Memory",
+                    high.educ = "Parent Education") %>%
+getDescriptionStatsBy(interview_age, 
+                        sex,
+                        thompson_PC1,
+                        thompson_PC2,
+                        thompson_PC3,
+                        monitoring,
+                        warmth,
+                        reshist_addr1_adi_income,
+                        household.income,
+                        race.6level,
+                        high.educ,
+                        add_total_col = TRUE, statistics=TRUE,
+                        by = matched_group)
+
+demo_table
 ```
@@
 ```{r}
-cor.test(abcd.data.train$warmth,abcd.data.train$monitoring) # they are correlated at r=0.362
+cor.test(abcd.data.train$warmth,abcd.data.train$monitoring) # they are correlated at r=0.365
 
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth+monitoring,data=abcd.data.train))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth+monitoring,data=abcd.data.train)) # NO LONGER SIGNIFICANT
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth+monitoring,data=abcd.data.train))
 
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth,data=abcd.data.train))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth,data=abcd.data.train))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth,data=abcd.data.train))
 
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+monitoring,data=abcd.data.train))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+monitoring,data=abcd.data.train)) # NO LONGER SIGNIFICANT
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+monitoring,data=abcd.data.train))
 
 # Get effect sizes
-model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train))
+model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth+monitoring,data=abcd.data.train))
 eta2_w <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
 eta2_m <- F_to_eta2(model1[4,]$`F value`,model1[4,]$NumDF,model1[4,]$DenDF)
-model1<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train))
+model1<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth+monitoring,data=abcd.data.train))
 eta2_w <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
 eta2_m <- F_to_eta2(model1[4,]$`F value`,model1[4,]$NumDF,model1[4,]$DenDF)
-model1<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train))
+model1<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth+monitoring,data=abcd.data.train))
 eta2_w <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
@@
 
-model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train))
+model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth,data=abcd.data.train))
 eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
-model1<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train))
+model1<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth,data=abcd.data.train))
 eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
-model1<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train))
+model1<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth,data=abcd.data.train))
 eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
 
-model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train))
+model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+monitoring,data=abcd.data.train))
 eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
-model1<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train))
+model1<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+monitoring,data=abcd.data.train))
 eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
-model1<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train))
+model1<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+monitoring,data=abcd.data.train))
 eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
@@
 # Print models to table
-mod1<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train)
-mod2<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train)
-mod3<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth+monitoring,data=abcd.data.train)
-mod4<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train)
-mod5<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train)
-mod6<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.train)
-mod7<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train)
-mod8<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train)
-mod9<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train)
-tab_model(mod1,mod2,mod3,pred.labels = c("Intercept","Age","Sex","Warmth","Monitoring"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
-Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_Monitoring_TableX.doc")
-tab_model(mod4,mod5,mod6,pred.labels = c("Intercept","Age","Sex","Warmth"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
-Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific", file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_TableX.doc")
-tab_model(mod7,mod8,mod9,pred.labels = c("Intercept","Age","Sex","Monitoring"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
-Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific", file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_TableX.doc")
+mod1<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth+monitoring,data=abcd.data.train)
+mod2<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth+monitoring,data=abcd.data.train)
+mod3<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth+monitoring,data=abcd.data.train)
+mod4<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth,data=abcd.data.train)
+mod5<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth,data=abcd.data.train)
+mod6<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth,data=abcd.data.train)
+mod7<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+monitoring,data=abcd.data.train)
+mod8<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+monitoring,data=abcd.data.train)
+mod9<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+monitoring,data=abcd.data.train)
+tab_model(mod1,mod2,mod3,pred.labels = c("Intercept","Age","Sex","Household Income [50K-100K]","Household Income [>100K]","Neighborhood Income","Parent Educ: HS Diploma/GED","Parent Educ: Some College","Parent Educ: Bachelor","Parent Educ: Post Graduate","Caregiver Warmth","Caregiver Monitoring"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_Monitoring_TableX.doc")
+tab_model(mod4,mod5,mod6,pred.labels = c("Intercept","Age","Sex","Household Income [50K-100K]","Household Income [>100K]","Neighborhood Income","Parent Educ: HS Diploma/GED","Parent Educ: Some College","Parent Educ: Bachelor","Parent Educ: Post Graduate","Caregiver Warmth"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific", file = "/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_TableX.doc")
+tab_model(mod7,mod8,mod9,pred.labels = c("Intercept","Age","Sex","Household Income [50K-100K]","Household Income [>100K]","Neighborhood Income","Parent Educ: HS Diploma/GED","Parent Educ: Some College","Parent Educ: Bachelor","Parent Educ: Post Graduate","Caregiver Monitoring"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific", file = "/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_TableX.doc")
 ```
@@
 ```{r}
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.train))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.train))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.train))
 
 # Get effect sizes
-model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train))
+model1<-anova(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.train))
 eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
-model1<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train))
+model1<-anova(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.train))
 eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
-model1<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train))
+model1<-anova(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.train))
 eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
@@
 # print results to table
-mod10<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train)
-mod11<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train)
-mod12<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train)
-tab_model(mod10,mod11,mod12,pred.labels = c("Intercept","Age","Sex","Household Income [50K-100K]","Household Income [>=100K]"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
-Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Income_TableX.doc")
+mod10<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.train)
+mod11<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.train)
+mod12<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.train)
+#tab_model(mod10,mod11,mod12,pred.labels = c("Intercept","Age","Sex","Neighborhood Income","Parent Educ: HS Diploma/GED","Parent Educ: Some College","Parent Educ: Bachelor","Parent Educ: Post Graduate","Household Income [50K-100K]","Household Income [>100K]",),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Income_TableX.doc")
 
@@
 
+# test whether any of the socio-economic variables are related to BOTH cognition AND monitoring in BOTH discovery/rep samples
+```{r}
+mod41<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ,data=abcd.data.train)
+mod42<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ,data=abcd.data.test)
+mod43<-lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ,data=abcd.data.train)
+mod44<-lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ,data=abcd.data.test)
+
+tab_model(mod41,mod42,mod43,mod44,pred.labels = c("Intercept","Age","Sex","Household Income [50K-100K]","Household Income [>100K]","Neighborhood Income","Parent Educ: HS Diploma/GED","Parent Educ: Some College","Parent Educ: Bachelor","Parent Educ: Post Graduate"),dv.labels=c("Cog Train","Cog Test","Mon Train","Mon Test"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific", file = "/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_threeVars_allModels.doc")
+```
+
 ## Is SES associated with differences in parenting behaviors?
-### SES is related to diffferences in monitoring but NOT differences in warmth (doesn't pass correction)
+### SES is related to differences in monitoring but NOT differences in warmth (doesn't pass correction)
 ```{r}
-summary(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train))
-summary(lmer(warmth~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train))
+summary(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.train))
+summary(lmer(warmth~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.train))
 
 # Get effect sizes
-model1<-anova(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train))
+model1<-anova(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.train))
 eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
-model1<-anova(lmer(warmth~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train))
+model1<-anova(lmer(warmth~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.train))
 eta2 <- F_to_eta2(model1[3,]$`F value`,model1[3,]$NumDF,model1[3,]$DenDF)
 
-mod13<-lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train)
-mod14<-lmer(warmth~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train)
-tab_model(mod13,mod14,pred.labels = c("Intercept","Age","Sex","Household Income [50K-100K]","Household Income [>=100K]"),dv.labels=c("Monitoring","Warmth"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
-Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Income_Caregiving_TableX.doc")
+mod13<-lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.train)
+
+tab_model(mod10,mod13,pred.labels = c("Intercept","Age","Sex","Neighborhood Income","Parent Educ: HS Diploma/GED","Parent Educ: Some College","Parent Educ: Bachelor","Parent Educ: Post Graduate","Household Income [50K-100K]","Household Income [>=100K]"),dv.labels=c("General Cognition","Caregiver Monitoring"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Income_GenCog_Monitoring.doc")
+
+# tab_model(mod13,mod14,pred.labels = c("Intercept","Age","Sex","Household Income [50K-100K]","Household Income [>=100K]"),dv.labels=c("Monitoring","Warmth"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Income_Caregiving_TableX.doc")
 
@@
 ```{r}
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train))
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train))
+#abcd.data.train$simple.income <- relevel(as.factor(ifelse(abcd.data.train$household.income=="[<50K]","Low","High")),"Low")
+abcd.data.train$simple.income2 <- relevel(as.factor(ifelse(abcd.data.train$household.income=="[>=100K]","High","Low")),"Low")
 
-# partial mediation is significant!
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income2,data=abcd.data.train))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income2+monitoring,data=abcd.data.train))
+
+abcd.data.test$simple.income2 <- relevel(as.factor(ifelse(abcd.data.test$household.income=="[>=100K]","High","Low")),"Low")
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income2,data=abcd.data.test))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income2+monitoring,data=abcd.data.test))
+
+summary(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income2,data=abcd.data.train))
+summary(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income2,data=abcd.data.test))
+
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+monitoring,data=abcd.data.train))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+monitoring,data=abcd.data.test))
+
 bs_indir = c()
@@
   thisSample <- sample(c(1:length(abcd.data.train$subjectkey)),length(abcd.data.train$subjectkey),replace=TRUE)
-  pathc<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train[thisSample,])
-  pathcp<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train[thisSample,])
-  indir<-fixef(pathc)[5]-fixef(pathcp)[5]
+  pathc<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income2,data=abcd.data.train[thisSample,])
+  pathcp<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income2+monitoring,data=abcd.data.train[thisSample,])
+  indir<-fixef(pathc)[9]-fixef(pathcp)[9]
   bs_indir <- c(bs_indir,indir)
@@
 t.test(bs_indir,conf.level=0.95)
-# t = 94.813, df = 999, p-value < 2.2e-16
+
+# data:  bs_indir
+# t = 53.831, df = 999, p-value < 2.2e-16
 # alternative hypothesis: true mean is not equal to 0
 # 95 percent confidence interval:
-#  0.3131269 0.3263624
+#  0.004476561 0.004815285
 # sample estimates:
 #   mean of x 
-# 0.3197447
+# 0.004645923
 
+bs_indir_test = c()
+for (i in 1:1000){
+  thisSample <- sample(c(1:length(abcd.data.test$subjectkey)),length(abcd.data.test$subjectkey),replace=TRUE)
+  pathc<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income2,data=abcd.data.test[thisSample,])
+  pathcp<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income2+monitoring,data=abcd.data.test[thisSample,])
+  indir<-fixef(pathc)[9]-fixef(pathcp)[9]
+  bs_indir_test <- c(bs_indir_test,indir)
+}
+t.test(bs_indir_test,conf.level=0.95)
+
+# data:  bs_indir_test
+# t = 65.514, df = 999, p-value < 2.2e-16
+# alternative hypothesis: true mean is not equal to 0
+# 95 percent confidence interval:
+#  0.006248254 0.006634122
+# sample estimates:
+#   mean of x 
+# 0.006441188 
 ```
@@
 ```{r}
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train))
-
-# partial mediation is significant!
-bs_indir = c()
-for (i in 1:1000){
-  thisSample <- sample(c(1:length(abcd.data.train$subjectkey)),length(abcd.data.train$subjectkey),replace=TRUE)
-  pathc<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train[thisSample,])
-  pathcp<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train[thisSample,])
-  indir<-fixef(pathc)[5]-fixef(pathcp)[5]
-  bs_indir <- c(bs_indir,indir)
-}
-t.test(bs_indir,conf.level=0.95)
-# t = 27.513, df = 999, p-value < 2.2e-16
-# alternative hypothesis: true mean is not equal to 0
-# 95 percent confidence interval:
-#  0.1060481 0.1223373
-# sample estimates:
-# mean of x 
-# 0.1141927
+# #abcd.data.train$simple.income <- relevel(as.factor(ifelse(abcd.data.train$household.income=="[<50K]","Low","High")),"Low")
+# abcd.data.train$simple.income2 <- relevel(as.factor(ifelse(abcd.data.train$household.income=="[>=100K]","High","Low")),"Low")
+# 
+# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income2,data=abcd.data.train))
+# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income2+monitoring,data=abcd.data.train))
+# 
+# 
+# bs_indir = c()
+# for (i in 1:1000){
+#   thisSample <- sample(c(1:length(abcd.data.train$subjectkey)),length(abcd.data.train$subjectkey),replace=TRUE)
+#   pathc<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income2,data=abcd.data.train[thisSample,])
+#   pathcp<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income2+monitoring,data=abcd.data.train[thisSample,])
+#   indir<-fixef(pathc)[9]-fixef(pathcp)[9]
+#   bs_indir <- c(bs_indir,indir)
+# }
+# t.test(bs_indir,conf.level=0.95)
+# 
+#
 
@@
 ```{r}
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train))
+# #abcd.data.train$simple.income <- relevel(as.factor(ifelse(abcd.data.train$household.income=="[<50K]","Low","High")),"Low")
+# abcd.data.train$simple.income2 <- relevel(as.factor(ifelse(abcd.data.train$household.income=="[>=100K]","High","Low")),"Low")
+# 
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income2,data=abcd.data.train))
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income2+monitoring,data=abcd.data.train))
+# 
+# 
+# bs_indir = c()
+# for (i in 1:1000){
+#   thisSample <- sample(c(1:length(abcd.data.train$subjectkey)),length(abcd.data.train$subjectkey),replace=TRUE)
+#   pathc<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income2,data=abcd.data.train[thisSample,])
+#   pathcp<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income2+monitoring,data=abcd.data.train[thisSample,])
+#   indir<-fixef(pathc)[9]-fixef(pathcp)[9]
+#   bs_indir <- c(bs_indir,indir)
+# }
+# t.test(bs_indir,conf.level=0.95)
+# 
+#
 
-# partial mediation is significant!
-bs_indir = c()
-for (i in 1:1000){
-  thisSample <- sample(c(1:length(abcd.data.train$subjectkey)),length(abcd.data.train$subjectkey),replace=TRUE)
-  pathc<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train[thisSample,])
-  pathcp<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train[thisSample,])
-  indir<-fixef(pathc)[5]-fixef(pathcp)[5]
-  bs_indir <- c(bs_indir,indir)
-}
-t.test(bs_indir,conf.level=0.95)
-
-# t = 72.373, df = 999, p-value < 2.2e-16
-# alternative hypothesis: true mean is not equal to 0
-# 95 percent confidence interval:
-#  0.2864221 0.3023873
-# sample estimates:
-# mean of x 
-# 0.2944047 
 ```
 
-# Make mediation table:
+# Make mediation table: # NOTE: NEED TO REDO THESE WITH THE NEW VARIABLES AND COVARIATES - MAKE SURE TO CHANGE THE COEFFICIENT NUMBERS
 ```{r}
-moda<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train)
-modb<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train)
-modc<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train)
-modd<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train)
-mode<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.train)
-modf<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.train)
+moda<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.train)
+modb<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income+monitoring,data=abcd.data.train)
+modc<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.train)
+modd<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income+monitoring,data=abcd.data.train)
+mode<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.train)
+modf<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income+monitoring,data=abcd.data.train)
 
 tab_model(moda,modc,mode,pred.labels = c("Intercept","Age","Sex","Household Income [50K-100K]","Household Income [>=100K]"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
-Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Mediation1_TableX.doc")
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Mediation1_TableX.doc")
 
 tab_model(modb,modd,modf,pred.labels = c("Intercept","Age","Sex","Household Income [50K-100K]","Household Income [>=100K]","Monitoring"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
-Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Mediation2_TableX.doc")
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Mediation2_TableX.doc")
 ```
@@
 ```{r}
-abcd.data.train$simple.income <- ifelse(abcd.data.train$household.income=="[<50K]","Low","High")
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+simple.income,data=abcd.data.train))
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+simple.income+monitoring,data=abcd.data.train))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+simple.income,data=abcd.data.train))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+simple.income+monitoring,data=abcd.data.train))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+simple.income,data=abcd.data.train))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+simple.income+monitoring,data=abcd.data.train))
+# abcd.data.train$simple.income <- ifelse(abcd.data.train$household.income=="[<50K]","Low","High")
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income,data=abcd.data.train))
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income+monitoring,data=abcd.data.train))
+# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income,data=abcd.data.train))
+# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income+monitoring,data=abcd.data.train))
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income,data=abcd.data.train))
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income+monitoring,data=abcd.data.train))
+# 
+# 
+# abcd.data.train$simple.income2 <- ifelse(abcd.data.train$household.income=="[>=100K]","High","Low")
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income2,data=abcd.data.train))
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income2+monitoring,data=abcd.data.train))
+# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income2,data=abcd.data.train))
+# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income2+monitoring,data=abcd.data.train))
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income2,data=abcd.data.train))
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income2+monitoring,data=abcd.data.train))
+# 
+# 
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+monitoring,data=abcd.data.train))
+# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+monitoring,data=abcd.data.train))
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+monitoring,data=abcd.data.train))
 
-abcd.data.train$simple.income2 <- ifelse(abcd.data.train$household.income=="[>=100K]","High","Low")
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+simple.income2,data=abcd.data.train))
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+simple.income2+monitoring,data=abcd.data.train))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+simple.income2,data=abcd.data.train))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+simple.income2+monitoring,data=abcd.data.train))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+simple.income2,data=abcd.data.train))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+simple.income2+monitoring,data=abcd.data.train))
-
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.train))
-
-summary(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+simple.income,data=abcd.data.train))
+# summary(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+simple.income,data=abcd.data.train))
 ```
@@
 ```{r}
-important.variables <- abcd.data.traintest[,c("warmth","monitoring","thompson_PC1","thompson_PC2","thompson_PC3")]
-colnames(important.variables)<-c("Caregiver Warmth","Caregiver Monitoring","General Cognition","Executive Function","Learning/Memory")
+important.variables <- abcd.data.traintest[,c("interview_age","reshist_addr1_adi_income","warmth","monitoring","thompson_PC1","thompson_PC2","thompson_PC3")]
+colnames(important.variables)<-c("Age","Neighborhood Income","Caregiver Warmth","Caregiver Monitoring","General Cognition","Executive Function","Learning/Memory")
 corrplot(cor(important.variables,use="complete.obs"),method=c("number"), tl.col = "black", col=brewer.pal(n=8, name="Spectral"))
@@
 
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+parent_monitor_q1_y+parent_monitor_q2_y+parent_monitor_q3_y+parent_monitor_q4_y+parent_monitor_q5_y,data=abcd.data.traintest)) # all significant *** (Q4 opp direction)
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+parent_monitor_q1_y+parent_monitor_q2_y+parent_monitor_q3_y+parent_monitor_q4_y+parent_monitor_q5_y,data=abcd.data.traintest)) # all but Q3 sig (Q4 opp direction)
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+parent_monitor_q1_y+parent_monitor_q2_y+parent_monitor_q3_y+parent_monitor_q4_y+parent_monitor_q5_y,data=abcd.data.traintest)) # all significant (Q4 opp direction)
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+household.income+high.educ+parent_monitor_q1_y+parent_monitor_q2_y+parent_monitor_q3_y+parent_monitor_q4_y+parent_monitor_q5_y,data=abcd.data.traintest)) # all significant *** (Q4 opp direction)
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+household.income+high.educ+parent_monitor_q1_y+parent_monitor_q2_y+parent_monitor_q3_y+parent_monitor_q4_y+parent_monitor_q5_y,data=abcd.data.traintest)) # only q2 sig
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+household.income+high.educ+parent_monitor_q1_y+parent_monitor_q2_y+parent_monitor_q3_y+parent_monitor_q4_y+parent_monitor_q5_y,data=abcd.data.traintest)) # all but q3 significant (Q4 opp direction)
 
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+crpbi_parent1_y+crpbi_parent2_y+crpbi_parent3_y+crpbi_parent4_y+crpbi_parent5_y,data=abcd.data.traintest)) # Q2, Q4, Q5 significant (Q5 opp direction)
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+crpbi_parent1_y+crpbi_parent2_y+crpbi_parent3_y+crpbi_parent4_y+crpbi_parent5_y,data=abcd.data.traintest)) # Q2, Q4, Q5 significant (Q5 opp direction)
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+crpbi_parent1_y+crpbi_parent2_y+crpbi_parent3_y+crpbi_parent4_y+crpbi_parent5_y,data=abcd.data.traintest)) # Q2, Q4, Q5 significant (Q5 opp direction)
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+crpbi_parent1_y+crpbi_parent2_y+crpbi_parent3_y+crpbi_parent4_y+crpbi_parent5_y,data=abcd.data.traintest)) # Q2, Q4, Q5 significant (Q5 opp direction)
+# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+crpbi_parent1_y+crpbi_parent2_y+crpbi_parent3_y+crpbi_parent4_y+crpbi_parent5_y,data=abcd.data.traintest)) # Q2, Q4, Q5 significant (Q5 opp direction)
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+crpbi_parent1_y+crpbi_parent2_y+crpbi_parent3_y+crpbi_parent4_y+crpbi_parent5_y,data=abcd.data.traintest)) # Q2, Q4, Q5 significant (Q5 opp direction)
+#
 
 # make tables
-mod15<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+parent_monitor_q1_y+parent_monitor_q2_y+parent_monitor_q3_y+parent_monitor_q4_y+parent_monitor_q5_y,data=abcd.data.traintest)
-mod16<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+parent_monitor_q1_y+parent_monitor_q2_y+parent_monitor_q3_y+parent_monitor_q4_y+parent_monitor_q5_y,data=abcd.data.traintest)
-mod17<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+parent_monitor_q1_y+parent_monitor_q2_y+parent_monitor_q3_y+parent_monitor_q4_y+parent_monitor_q5_y,data=abcd.data.traintest)
-tab_model(mod15,mod16,mod17,pred.labels = c("Intercept","Age","Sex","Know where you are","Know who you're with","Know how to contact","Talk over plans","Dinner together"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
-Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Items_TableX.doc")
+abcd.data.traintest$simple.income2 <- relevel(as.factor(ifelse(abcd.data.traintest$household.income=="[>=100K]","High","Low")),"Low")
+
+mod15<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+simple.income2+high.educ+parent_monitor_q1_y+parent_monitor_q2_y+parent_monitor_q3_y+parent_monitor_q4_y+parent_monitor_q5_y,data=abcd.data.traintest)
+#mod16<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+household.income+high.educ+parent_monitor_q1_y+parent_monitor_q2_y+parent_monitor_q3_y+parent_monitor_q4_y+parent_monitor_q5_y,data=abcd.data.traintest)
+#mod17<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+household.income+high.educ+parent_monitor_q1_y+parent_monitor_q2_y+parent_monitor_q3_y+parent_monitor_q4_y+parent_monitor_q5_y,data=abcd.data.traintest)
+tab_model(mod15,pred.labels = c("Intercept","Age","Sex","Neighborhood Income","Household Income (>100K)","HS Diploma/GED","Some College","Bachelor","Post Graduate","Know where you are","Know who you're with","Know how to contact","Talk over plans","Dinner together"),dv.labels=c("General Cognition"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Items_TableX.doc")
+
+mod16<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+household.income+high.educ+parent_monitor_q1_y+parent_monitor_q2_y+parent_monitor_q3_y+parent_monitor_q4_y+parent_monitor_q5_y,data=abcd.data.traintest)
+tab_model(mod16,pred.labels = c("Intercept","Age","Sex","Neighborhood Income","Household Income [50K-100K]","Household Income [>100K]","Parent Educ: HS Diploma/GED","Parent Educ: Some College","Parent Educ: Bachelor","Parent Educ: Post Graduate","Q1.
+Know where you are","Q2.
+Know who you're with","Q3.
+Know how to contact","Q4.
+Talk over plans","Q5.
+Dinner together"),dv.labels=c("General Cognition"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
+Error",show.intercept=TRUE,show.ci = FALSE,p.style="scientific",file = "/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Items_TableX.doc")
+
+# try the same thing but with the question number coded as a factor to look at an interaction
+monitoring_qs <- abcd.data.traintest[,c("subjectkey","parent_monitor_q1_y","parent_monitor_q2_y","parent_monitor_q3_y","parent_monitor_q4_y","parent_monitor_q5_y")]
+library("reshape2")
+test<-melt(monitoring_qs)
+merged.dataset<-merge(test,abcd.data.traintest,by="subjectkey")
+merged.dataset$variable=as.factor(merged.dataset$variable)
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+household.income+high.educ+value*variable,data=merged.dataset))
+mod100<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+household.income+high.educ+value*variable,data=merged.dataset)
+tab_model(mod100,pred.labels = c("Intercept","Age","Sex","Neighborhood Income","Household Income1","Household Income2","HS Diploma/GED","Some College","Bachelor","Post Graduate","Know where you are","Know who you're with","Know how to contact","Talk over plans","Dinner together"),dv.labels=c("General Cognition"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Items_TableX.doc")
+
 ```
@@
 abcd.data.traintest$totalACEs <- rowSums(data.frame(as.numeric(abcd.data.traintest$ksads_ptsd_raw_754_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_755_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_756_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_757_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_758_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_759_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_760_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_761_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_762_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_763_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_764_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_765_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_766_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_767_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_768_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_769_p),as.numeric(abcd.data.traintest$ksads_ptsd_raw_770_p)),na.rm=TRUE)
-
-summary(lmer(totalACEs~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.traintest))
+# 
+summary(lmer(totalACEs~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+household.income+high.educ+monitoring,data=abcd.data.traintest))
 ```
@@
 ```{r}
-# Race 6 level (1: White | 2: Black | 3: Asian | 4: AIAN/NHPI | 5: Other | 6: Mixed)
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+monitoring,data=abcd.data.train))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+monitoring,data=abcd.data.train))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+monitoring,data=abcd.data.train))
-
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+household.income,data=abcd.data.train))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+household.income,data=abcd.data.train))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+household.income,data=abcd.data.train))
-
-summary(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+household.income,data=abcd.data.train))
-
-# Parent's highest degree of education
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+monitoring,data=abcd.data.train))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+monitoring,data=abcd.data.train))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+monitoring,data=abcd.data.train))
-
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+household.income,data=abcd.data.train))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+household.income,data=abcd.data.train))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+household.income,data=abcd.data.train))
-
-summary(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+household.income,data=abcd.data.train))
-
-# Add some more variables:
-addvar<-readRDS("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/DEAP-discrim-marriage.rds")
-addvar.baseline<-addvar[addvar$event_name=="baseline_year_1_arm_1",]
-colnames(addvar.baseline)[1]<-"subjectkey"
-abcd.addvar <- merge(abcd.data.train,addvar.baseline[, c("subjectkey", setdiff(colnames(addvar.baseline),colnames(abcd.data.train)))],by="subjectkey")
-
-# Parents Married or Living Together
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+monitoring,data=abcd.addvar))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+monitoring,data=abcd.addvar))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+monitoring,data=abcd.addvar))
-
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+household.income,data=abcd.addvar))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+household.income,data=abcd.addvar))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+household.income,data=abcd.addvar))
-
-summary(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+household.income,data=abcd.addvar))
-
-# print tables for supplement
-mod18<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+monitoring,data=abcd.data.train)
-mod19<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+monitoring,data=abcd.data.train)
-mod20<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+monitoring,data=abcd.data.train)
-mod21<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+monitoring,data=abcd.data.train)
-mod22<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+monitoring,data=abcd.data.train)
-mod23<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+monitoring,data=abcd.data.train)
-mod24<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+monitoring,data=abcd.addvar)
-mod25<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+monitoring,data=abcd.addvar)
-mod26<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+monitoring,data=abcd.addvar)
-tab_model(mod18,mod19,mod20,pred.labels = c("Intercept","Age","Sex","White","Black","Asian","AIAN/NHPI","Other","Mixed","Monitoring"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
-Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Sens_Race_TableX.doc")
-tab_model(mod21,mod22,mod23,pred.labels = c("Intercept","Age","Sex","HS Diploma/GED","Some College","Bachelor","Post Graduate","Monitoring"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
-Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Sens_Edu_TableX.doc")
-tab_model(mod24,mod25,mod26,pred.labels = c("Intercept","Age","Sex","Married/Living Together","Monitoring"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
-Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Sens_Mar_TableX.doc")
+# # Race 6 level (1: White | 2: Black | 3: Asian | 4: AIAN/NHPI | 5: Other | 6: Mixed)
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+monitoring,data=abcd.data.train))
+# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+monitoring,data=abcd.data.train))
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+monitoring,data=abcd.data.train))
+# 
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+household.income,data=abcd.data.train))
+# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+household.income,data=abcd.data.train))
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+household.income,data=abcd.data.train))
+# 
+# summary(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+household.income,data=abcd.data.train))
+# 
+# 
+# # Parent's highest degree of education
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+monitoring,data=abcd.data.train))
+# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+monitoring,data=abcd.data.train))
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+monitoring,data=abcd.data.train))
+# 
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+household.income,data=abcd.data.train))
+# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+household.income,data=abcd.data.train))
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+household.income,data=abcd.data.train))
+# 
+# summary(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+household.income,data=abcd.data.train))
+# 
+# # Add some more variables:
+# addvar<-readRDS("/Users/askeller/Documents/Kellernet_PrelimAnalysis/DEAP-discrim-marriage.rds")
+# addvar.baseline<-addvar[addvar$event_name=="baseline_year_1_arm_1",]
+# colnames(addvar.baseline)[1]<-"subjectkey"
+# abcd.addvar <- merge(abcd.data.train,addvar.baseline[, c("subjectkey", setdiff(colnames(addvar.baseline),colnames(abcd.data.train)))],by="subjectkey")
+# 
+# # Parents Married or Living Together
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+monitoring,data=abcd.addvar))
+# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+monitoring,data=abcd.addvar))
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+monitoring,data=abcd.addvar))
+# 
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+household.income,data=abcd.addvar))
+# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+household.income,data=abcd.addvar))
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+household.income,data=abcd.addvar))
+# 
+# summary(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+household.income,data=abcd.addvar))
+# 
+# 
+# # print tables for supplement
+# mod18<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+monitoring,data=abcd.data.train)
+# mod19<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+monitoring,data=abcd.data.train)
+# mod20<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+race.6level+monitoring,data=abcd.data.train)
+# mod21<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+monitoring,data=abcd.data.train)
+# mod22<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+monitoring,data=abcd.data.train)
+# mod23<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+high.educ+monitoring,data=abcd.data.train)
+# mod24<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+monitoring,data=abcd.addvar)
+# mod25<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+monitoring,data=abcd.addvar)
+# mod26<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+married.or.livingtogether+monitoring,data=abcd.addvar)
+# tab_model(mod18,mod19,mod20,pred.labels = c("Intercept","Age","Sex","White","Black","Asian","AIAN/NHPI","Other","Mixed","Monitoring"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Sens_Race_TableX.doc")
+# tab_model(mod21,mod22,mod23,pred.labels = c("Intercept","Age","Sex","HS Diploma/GED","Some College","Bachelor","Post Graduate","Monitoring"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Sens_Edu_TableX.doc")
+# tab_model(mod24,mod25,mod26,pred.labels = c("Intercept","Age","Sex","Married/Living Together","Monitoring"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Sens_Mar_TableX.doc")
 ```
@@
 ```{r}
-png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC1.png",
+# png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC1.png",
+#     width = 4000, 
+#     height = 3000,
+#     res=1000)
+# ggplot(data=subset(abcd.data.train,!is.na(household.income)),aes(household.income,thompson_PC1))+geom_boxplot(aes(household.income,thompson_PC1),color=rgb(33/255,80/255,113/255))+coord_cartesian(ylim = c(170, 320))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+# panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Household Income')
+# dev.off()
+
+png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC1_violin.png",
     width = 4000, 
@@
     res=1000)
-ggplot(data=subset(abcd.data.train,!is.na(household.income)),aes(household.income,thompson_PC1))+geom_boxplot(aes(household.income,thompson_PC1),color=rgb(33/255,80/255,113/255))+coord_cartesian(ylim = c(170, 320))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+ggplot(data=subset(abcd.data.train,!is.na(household.income)),aes(household.income,thompson_PC1))+geom_violin(aes(household.income,thompson_PC1),fill=rgb(33/255,80/255,113/255),trim=FALSE)+geom_boxplot(aes(household.income,thompson_PC1),width=0.2)+coord_cartesian(ylim = c(-3, 3))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
 panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Household Income')
@@
 
-png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC2.png",
+# png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC2.png",
+#     width = 4000, 
+#     height = 3000,
+#     res=1000)
+# ggplot(data=subset(abcd.data.train,!is.na(household.income)),aes(household.income,thompson_PC2))+geom_boxplot(aes(household.income,thompson_PC2),color=rgb(64/255,141/255,151/255))+coord_cartesian(ylim = c(170, 320))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+# panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Household Income')
+# dev.off()
+
+png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC2_violin.png",
     width = 4000, 
@@
     res=1000)
-ggplot(data=subset(abcd.data.train,!is.na(household.income)),aes(household.income,thompson_PC2))+geom_boxplot(aes(household.income,thompson_PC2),color=rgb(64/255,141/255,151/255))+coord_cartesian(ylim = c(170, 320))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+ggplot(data=subset(abcd.data.train,!is.na(household.income)),aes(household.income,thompson_PC2))+geom_violin(aes(household.income,thompson_PC2),fill=rgb(64/255,141/255,151/255),trim=FALSE)+geom_boxplot(aes(household.income,thompson_PC2),width=0.2)+coord_cartesian(ylim = c(-3, 3))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
 panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Household Income')
@@
 
-png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC3.png",
+# png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC3.png",
+#     width = 4000, 
+#     height = 3000,
+#     res=1000)
+# ggplot(data=subset(abcd.data.train,!is.na(household.income)),aes(household.income,thompson_PC3))+geom_boxplot(aes(household.income,thompson_PC3),color=rgb(157/255,207/255,160/255))+coord_cartesian(ylim = c(-3, 3))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+# panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Household Income')
+# dev.off()
+
+png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC3_violin.png",
     width = 4000, 
@@
     res=1000)
-ggplot(data=subset(abcd.data.train,!is.na(household.income)),aes(household.income,thompson_PC3))+geom_boxplot(aes(household.income,thompson_PC3),color=rgb(157/255,207/255,160/255))+coord_cartesian(ylim = c(170, 320))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+ggplot(data=subset(abcd.data.train,!is.na(household.income)),aes(household.income,thompson_PC3))+geom_violin(aes(household.income,thompson_PC3),fill=rgb(157/255,207/255,160/255),trim=FALSE)+geom_boxplot(aes(household.income,thompson_PC3),width=0.2)+coord_cartesian(ylim = c(-3, 3))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
 panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Household Income')
@@
 
-png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_PC1.png",
-    width = 2500, 
-    height = 3000,
-    res=700)
-ggplot(data=abcd.data.train,aes(monitoring,thompson_PC1))+geom_point(position="jitter",size=1,colour=rgb(33/255,80/255,113/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Monitoring')
+png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/FigPanels/BiggerTextSize_051522/Monitoring_PC1.png",
+    width = 2600, 
+    height = 3100,
+    res=1200)
+ggplot(data=abcd.data.train,aes(monitoring,thompson_PC1))+geom_point(position="jitter",size=0.5,colour=rgb(33/255,80/255,113/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Monitoring (z)') +coord_cartesian(xlim = c(-5.6,1.1), ylim = c(-3, 3))
 dev.off()
 
-png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_PC2.png",
-    width = 2500, 
-    height = 3000,
-    res=700)
-ggplot(data=abcd.data.train,aes(monitoring,thompson_PC2))+geom_point(position="jitter",size=1,colour=rgb(64/255,141/255,151/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Monitoring')
+png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/FigPanels/BiggerTextSize_051522/Monitoring_PC2.png",
+    width = 2600, 
+    height = 3100,
+    res=1200)
+ggplot(data=abcd.data.train,aes(monitoring,thompson_PC2))+geom_point(position="jitter",size=0.5,colour=rgb(64/255,141/255,151/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Monitoring (z)') +coord_cartesian(xlim = c(-5.6,1.1), ylim = c(-3, 3))
 dev.off()
 
-png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_PC3.png",
-    width = 2500, 
-    height = 3000,
-    res=700)
-ggplot(data=abcd.data.train,aes(monitoring,thompson_PC3))+geom_point(position="jitter",size=1,colour=rgb(157/255,207/255,160/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Monitoring')
+png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/FigPanels/BiggerTextSize_051522/Monitoring_PC3.png",
+    width = 2600, 
+    height = 3100,
+    res=1200)
+ggplot(data=abcd.data.train,aes(monitoring,thompson_PC3))+geom_point(position="jitter",size=0.5,colour=rgb(157/255,207/255,160/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Monitoring (z)') +coord_cartesian(xlim = c(-5.6,1.1), ylim = c(-2.5, 2.5))
 dev.off()
 
-png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_PC1.png",
-    width = 2500, 
-    height = 3000,
-    res=700)
-ggplot(data=abcd.data.train,aes(warmth,thompson_PC1))+geom_point(position="jitter",size=1,colour=rgb(33/255,80/255,113/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Warmth')
+png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/FigPanels/BiggerTextSize_051522/Warmth_PC1.png",
+    width = 2600, 
+    height = 3100,
+    res=1200)
+ggplot(data=abcd.data.train,aes(warmth,thompson_PC1))+geom_point(position="jitter",size=0.5,colour=rgb(33/255,80/255,113/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Warmth (z)') +coord_cartesian(xlim = c(-5.6,1.1), ylim = c(-3, 3))
 dev.off()
 
-png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_PC2.png",
-    width = 2500, 
-    height = 3000,
-    res=700)
-ggplot(data=abcd.data.train,aes(warmth,thompson_PC2))+geom_point(position="jitter",size=1,colour=rgb(64/255,141/255,151/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Warmth')
+png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/FigPanels/BiggerTextSize_051522/Warmth_PC2.png",
+    width = 2600, 
+    height = 3100,
+    res=1200)
+ggplot(data=abcd.data.train,aes(warmth,thompson_PC2))+geom_point(position="jitter",size=0.5,colour=rgb(64/255,141/255,151/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Warmth (z)') +coord_cartesian(xlim = c(-5.6,1.1), ylim = c(-3, 3))
 dev.off()
 
-png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_PC3.png",
-    width = 2500, 
-    height = 3000,
-    res=700)
-ggplot(data=abcd.data.train,aes(warmth,thompson_PC3))+geom_point(position="jitter",size=1,colour=rgb(157/255,207/255,160/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Warmth')
+png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/FigPanels/BiggerTextSize_051522/Warmth_PC3.png",
+    width = 2600, 
+    height = 3100,
+    res=1200)
+ggplot(data=abcd.data.train,aes(warmth,thompson_PC3))+geom_point(position="jitter",size=0.5,colour=rgb(157/255,207/255,160/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Warmth (z)') +coord_cartesian(xlim = c(-5.6,1.1), ylim = c(-2.5, 2.5))
 dev.off()
@@
          warmth = mean(warmth,na.rm=TRUE))
-png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_SES.png",
+png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_SES.png",
     width = 4000, 
@@
          monitoring = mean(monitoring,na.rm=TRUE))
-png("/Users/ariellekeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_SES.png",
+png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_SES.png",
     width = 4000, 
@@
     res=700)
-ggplot(data=df.summary,aes(household.income,monitoring,fill=as.factor(household.income)))+geom_bar(position = "dodge",stat = "identity")+coord_cartesian(ylim = c(3.5, 5))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Monitoring') + xlab('Household Income') + scale_fill_manual(values = c(rgb(145/255,69/255,93/255),rgb(206/255,118/255,119/255),rgb(227/255,180/255,150/255))) + geom_errorbar(aes(ymin=monitoring-se, ymax=monitoring+se), width=.2,position=position_dodge(.9))
+ggplot(data=df.summary,aes(household.income,monitoring,fill=as.factor(household.income)))+geom_bar(position = "dodge",stat = "identity")+coord_cartesian(ylim = c(-0.25, 0.25))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Monitoring (z)') + xlab('Household Income') + scale_fill_manual(values = c(rgb(145/255,69/255,93/255),rgb(206/255,118/255,119/255),rgb(227/255,180/255,150/255))) + geom_errorbar(aes(ymin=monitoring-se, ymax=monitoring+se), width=.2,position=position_dodge(.9))
 dev.off()
+
+save_train_data<-data.frame(abcd.data.train$thompson_PC1,abcd.data.train$thompson_PC2,abcd.data.train$thompson_PC3,abcd.data.train$warmth,abcd.data.train$monitoring)
+save_test_data<-data.frame(abcd.data.test$thompson_PC1,abcd.data.test$thompson_PC2,abcd.data.test$thompson_PC3,abcd.data.test$warmth,abcd.data.test$monitoring)
+write.csv(save_train_data,"/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/traintest_figs/data_from_R_train.csv")
+write.csv(save_test_data,"/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/traintest_figs/data_from_R_test.csv")
+
 ```
@@
 ```{r}
-mod31<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.test)
-mod32<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.test)
-mod33<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+warmth,data=abcd.data.test)
+mod31<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+household.income+high.educ+warmth,data=abcd.data.test)
+mod32<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+household.income+high.educ+warmth,data=abcd.data.test)
+mod33<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+household.income+high.educ+warmth,data=abcd.data.test)
 
-tab_model(mod31,mod32,mod33,digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific")
+tab_model(mod31,mod32,mod33,digits=3,digits.p=3,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific")
 
-mod34<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.test)
-mod35<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.test)
-mod36<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+monitoring,data=abcd.data.test)
+mod34<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+household.income+high.educ+monitoring,data=abcd.data.test)
+mod35<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+household.income+high.educ+monitoring,data=abcd.data.test)
+mod36<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+household.income+high.educ+monitoring,data=abcd.data.test)
 
-tab_model(mod34,mod35,mod36,digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific")
+tab_model(mod34,mod35,mod36,digits=3,digits.p=3,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific")
 
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.test))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.test))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.test))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.test))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.test))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.test))
 
-summary(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.test))
-summary(lmer(warmth~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.test))
+summary(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.test))
+summary(lmer(warmth~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.test))
 
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.test))
-summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.test))
-bs_indir = c()
-for (i in 1:1000){
-  thisSample <- sample(c(1:length(abcd.data.test$subjectkey)),length(abcd.data.test$subjectkey),replace=TRUE)
-  pathc<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.test[thisSample,])
-  pathcp<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.test[thisSample,])
-  indir<-fixef(pathc)[5]-fixef(pathcp)[5]
-  bs_indir <- c(bs_indir,indir)
-}
-t.test(bs_indir,conf.level=0.95)
-# t = 139.74, df = 999, p-value < 2.2e-16
-# alternative hypothesis: true mean is not equal to 0
-# 95 percent confidence interval:
-#  0.4791434 0.4927918
-# sample estimates:
-# mean of x 
-# 0.4859676
+mod54<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+household.income+high.educ+warmth+monitoring,data=abcd.data.test)
+mod55<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+household.income+high.educ+warmth+monitoring,data=abcd.data.test)
+mod56<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+household.income+high.educ+warmth+monitoring,data=abcd.data.test)
 
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.test))
-summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.test))
-bs_indir = c()
-for (i in 1:1000){
-  thisSample <- sample(c(1:length(abcd.data.test$subjectkey)),length(abcd.data.test$subjectkey),replace=TRUE)
-  pathc<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.test[thisSample,])
-  pathcp<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.test[thisSample,])
-  indir<-fixef(pathc)[5]-fixef(pathcp)[5]
-  bs_indir <- c(bs_indir,indir)
-}
-t.test(bs_indir,conf.level=0.95)
-# t = 91.84, df = 999, p-value < 2.2e-16
-# alternative hypothesis: true mean is not equal to 0
-# 95 percent confidence interval:
-#  0.3852340 0.4020561
-# sample estimates:
-# mean of x 
-#  0.393645
+tab_model(mod54,mod55,mod56,digits=3,digits.p=3,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific")
 
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.test))
-summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.test))
-bs_indir = c()
-for (i in 1:1000){
-  thisSample <- sample(c(1:length(abcd.data.test$subjectkey)),length(abcd.data.test$subjectkey),replace=TRUE)
-  pathc<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income,data=abcd.data.test[thisSample,])
-  pathcp<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+monitoring,data=abcd.data.test[thisSample,])
-  indir<-fixef(pathc)[5]-fixef(pathcp)[5]
-  bs_indir <- c(bs_indir,indir)
-}
-t.test(bs_indir,conf.level=0.95)
-# t = 111.61, df = 999, p-value < 2.2e-16
-# alternative hypothesis: true mean is not equal to 0
-# 95 percent confidence interval:
-#  0.4880340 0.5055023
-# sample estimates:
-# mean of x 
-# 0.4967681 
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.test))
+# summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income+monitoring,data=abcd.data.test))
+# 
+# # NEED TO REDO THIS WITH NEW MODELS!!!
+# bs_indir = c()
+# for (i in 1:1000){
+#   thisSample <- sample(c(1:length(abcd.data.test$subjectkey)),length(abcd.data.test$subjectkey),replace=TRUE)
+#   pathc<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.test[thisSample,])
+#   pathcp<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income+monitoring,data=abcd.data.test[thisSample,])
+#   indir<-fixef(pathc)[5]-fixef(pathcp)[5]
+#   bs_indir <- c(bs_indir,indir)
+# }
+# t.test(bs_indir,conf.level=0.95)
+
+# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.test))
+# summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income+monitoring,data=abcd.data.test))
+# 
+# # NEED TO REDO THIS WITH NEW MODELS!!!
+# bs_indir = c()
+# for (i in 1:1000){
+#   thisSample <- sample(c(1:length(abcd.data.test$subjectkey)),length(abcd.data.test$subjectkey),replace=TRUE)
+#   pathc<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.test[thisSample,])
+#   pathcp<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income+monitoring,data=abcd.data.test[thisSample,])
+#   indir<-fixef(pathc)[5]-fixef(pathcp)[5]
+#   bs_indir <- c(bs_indir,indir)
+# }
+# t.test(bs_indir,conf.level=0.95)
+
+# 
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.test))
+# summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income+monitoring,data=abcd.data.test))
+# 
+# # NEED TO REDO THIS WITH NEW MODELS!!!
+# bs_indir = c()
+# for (i in 1:1000){
+#   thisSample <- sample(c(1:length(abcd.data.test$subjectkey)),length(abcd.data.test$subjectkey),replace=TRUE)
+#   pathc<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.test[thisSample,])
+#   pathcp<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income+monitoring,data=abcd.data.test[thisSample,])
+#   indir<-fixef(pathc)[5]-fixef(pathcp)[5]
+#   bs_indir <- c(bs_indir,indir)
+# }
+# t.test(bs_indir,conf.level=0.95)
 ```
+
+# Generate Figures - TEST DATA
+```{r}
+png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC1_violin_test.png",
+    width = 4000, 
+    height = 3000,
+    res=1000)
+ggplot(data=subset(abcd.data.test,!is.na(household.income)),aes(household.income,thompson_PC1))+geom_violin(aes(household.income,thompson_PC1),fill=rgb(33/255,80/255,113/255),trim=FALSE)+geom_boxplot(aes(household.income,thompson_PC1),width=0.2)+coord_cartesian(ylim = c(-3, 3))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Household Income')
+dev.off()
+
+png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC2_violin_test.png",
+    width = 4000, 
+    height = 3000,
+    res=1000)
+ggplot(data=subset(abcd.data.test,!is.na(household.income)),aes(household.income,thompson_PC2))+geom_violin(aes(household.income,thompson_PC2),fill=rgb(64/255,141/255,151/255),trim=FALSE)+geom_boxplot(aes(household.income,thompson_PC2),width=0.2)+coord_cartesian(ylim = c(-3, 3))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Household Income')
+dev.off()
+
+png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/SES_PC3_violin_test.png",
+    width = 4000, 
+    height = 3000,
+    res=1000)
+ggplot(data=subset(abcd.data.test,!is.na(household.income)),aes(household.income,thompson_PC3))+geom_violin(aes(household.income,thompson_PC3),fill=rgb(157/255,207/255,160/255),trim=FALSE)+geom_boxplot(aes(household.income,thompson_PC3),width=0.2)+coord_cartesian(ylim = c(-3, 3))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Household Income')
+dev.off()
+
+png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/FigPanels/BiggerTextSize_051522/Monitoring_PC1_test.png",
+    width = 2600, 
+    height = 3100,
+    res=1200)
+ggplot(data=abcd.data.test,aes(monitoring,thompson_PC1))+geom_point(position="jitter",size=0.5,colour=rgb(33/255,80/255,113/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Monitoring (z)') +coord_cartesian(xlim = c(-6.5,1.1), ylim = c(-3, 3))
+dev.off()
+
+png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/FigPanels/BiggerTextSize_051522/Monitoring_PC2_test.png",
+    width = 2600, 
+    height = 3100,
+    res=1200)
+ggplot(data=abcd.data.test,aes(monitoring,thompson_PC2))+geom_point(position="jitter",size=0.5,colour=rgb(64/255,141/255,151/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Monitoring (z)') +coord_cartesian(xlim = c(-6.5,1.1), ylim = c(-3, 3))
+dev.off()
+
+png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/FigPanels/BiggerTextSize_051522/Monitoring_PC3_test.png",
+    width = 2600, 
+    height = 3100,
+    res=1200)
+ggplot(data=abcd.data.test,aes(monitoring,thompson_PC3))+geom_point(position="jitter",size=0.5,colour=rgb(157/255,207/255,160/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Monitoring (z)') +coord_cartesian(xlim = c(-6.5,1.1), ylim = c(-2.5, 2.5))
+dev.off()
+
+png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/FigPanels/BiggerTextSize_051522/Warmth_PC1_test.png",
+    width = 2600, 
+    height = 3100,
+    res=1200)
+ggplot(data=abcd.data.test,aes(warmth,thompson_PC1))+geom_point(position="jitter",size=0.5,colour=rgb(33/255,80/255,113/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Warmth (z)') +coord_cartesian(xlim = c(-6.5,1.1), ylim = c(-3, 3))
+dev.off()
+
+png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/FigPanels/BiggerTextSize_051522/Warmth_PC2_test.png",
+    width = 2600, 
+    height = 3100,
+    res=1200)
+ggplot(data=abcd.data.test,aes(warmth,thompson_PC2))+geom_point(position="jitter",size=0.5,colour=rgb(64/255,141/255,151/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Warmth (z)') +coord_cartesian(xlim = c(-6.5,1.1), ylim = c(-3, 3))
+dev.off()
+
+png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/FigPanels/BiggerTextSize_051522/Warmth_PC3_test.png",
+    width = 2600, 
+    height = 3100,
+    res=1200)
+ggplot(data=abcd.data.test,aes(warmth,thompson_PC3))+geom_point(position="jitter",size=0.5,colour=rgb(157/255,207/255,160/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Warmth (z)') +coord_cartesian(xlim = c(-6.5,1.1), ylim = c(-2.5, 2.5))
+dev.off()
+
+df.summary <- subset(abcd.data.test,!is.na(household.income)) %>%
+     group_by(household.income) %>%
+     summarise(
+         se = sd(warmth, na.rm = TRUE)/sqrt(length(warmth)),
+         warmth = mean(warmth,na.rm=TRUE))
+png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Warmth_SES_test.png",
+    width = 4000, 
+    height = 2000,
+    res=700)
+ggplot(data=df.summary,aes(household.income,warmth,fill=as.factor(household.income)))+geom_bar(position = "dodge",stat = "identity")+coord_cartesian(ylim = c(-0.25, 0.25))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Warmth (z)') + xlab('Household Income') + scale_fill_manual(values = c(rgb(145/255,69/255,93/255),rgb(206/255,118/255,119/255),rgb(227/255,180/255,150/255))) + geom_errorbar(aes(ymin=warmth-se, ymax=warmth+se), width=.2,position=position_dodge(.9))
+dev.off()
+
+df.summary <- subset(abcd.data.test,!is.na(household.income)) %>%
+     group_by(household.income) %>%
+     summarise(
+         se = sd(monitoring, na.rm = TRUE)/sqrt(length(monitoring)),
+         monitoring = mean(monitoring,na.rm=TRUE))
+png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Monitoring_SES_test.png",
+    width = 4000, 
+    height = 2000,
+    res=700)
+ggplot(data=df.summary,aes(household.income,monitoring,fill=as.factor(household.income)))+geom_bar(position = "dodge",stat = "identity")+coord_cartesian(ylim = c(-0.25, 0.25))+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Monitoring (z)') + xlab('Household Income') + scale_fill_manual(values = c(rgb(145/255,69/255,93/255),rgb(206/255,118/255,119/255),rgb(227/255,180/255,150/255))) + geom_errorbar(aes(ymin=monitoring-se, ymax=monitoring+se), width=.2,position=position_dodge(.9))
+dev.off() 
+```
+
+# exploration of some potential explanations for the effect of income-->monitoring
+```{r}
+siblings_jobs <- readRDS("/Users/askeller/Documents/Kellernet_PrelimAnalysis/DEAP-sibs-jobs2.rds")
+siblings_jobs.baseline<-siblings_jobs[siblings_jobs$event_name=="baseline_year_1_arm_1",]
+colnames(siblings_jobs.baseline)[1]<-"subjectkey"
+
+siblings_jobs.baseline$both_caregivers_fulltime <- ifelse((siblings_jobs.baseline$demo_prnt_empl_time_p=="Full time" & siblings_jobs.baseline$demo_prtnr_empl_time_p=="Full time"),1,0)
+
+siblings_jobs.baseline$have_stay_at_home_parent <- ifelse((siblings_jobs.baseline$demo_prnt_empl_p=="Stay at Home Parent" | siblings_jobs.baseline$demo_prtnr_empl_p=="Stay at Home Parent"),1,0)
+
+siblings_jobs.baseline$num_sibs <-
+
+abcd.data.train2 <- merge(abcd.data.train,siblings_jobs.baseline[,c("subjectkey", setdiff(colnames(siblings_jobs.baseline),colnames(abcd.data.train)))],by="subjectkey")
+abcd.data.test2 <- merge(abcd.data.test,siblings_jobs.baseline[,c("subjectkey", setdiff(colnames(siblings_jobs.baseline),colnames(abcd.data.test)))],by="subjectkey")
+abcd.data.traintest2 <- merge(abcd.data.traintest,siblings_jobs.baseline[,c("subjectkey", setdiff(colnames(siblings_jobs.baseline),colnames(abcd.data.traintest)))],by="subjectkey")
+
+summary(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income+both_caregivers_fulltime,data=abcd.data.traintest2))
+summary(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+both_caregivers_fulltime,data=abcd.data.traintest2))
+
+summary(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+both_caregivers_fulltime,data=abcd.data.traintest2))
+
+summary(lmer(both_caregivers_fulltime~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income,data=abcd.data.traintest2))
+
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+household.income+both_caregivers_fulltime,data=abcd.data.traintest2))
+
+summary(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+both_caregivers_fulltime,data=abcd.data.traintest2))
+summary(lmer(monitoring~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+have_stay_at_home_parent,data=abcd.data.traintest2))
+
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+monitoring,data=abcd.data.train2))
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+high.educ+have_stay_at_home_parent*monitoring,data=abcd.data.train2))
+
+#sibs <- readRDS("/Users/askeller/Documents/Kellernet_PrelimAnalysis/DEAP-brosis.rds")
+
+```
+
+# What about abuse?
+```{r}
+# Compute a ksads "abuse" variable" and a total score
+# These are the items that will go into this score (they're the physical and sexual abuse variables)
+# 761, 762, 763, 767, 768, 769
+abcd.data.train$abuse <- rowSums(data.frame(as.numeric(abcd.data.train$ksads_ptsd_raw_761_p),as.numeric(abcd.data.train$ksads_ptsd_raw_762_p),as.numeric(abcd.data.train$ksads_ptsd_raw_763_p),as.numeric(abcd.data.train$ksads_ptsd_raw_767_p),as.numeric(abcd.data.train$ksads_ptsd_raw_768_p),as.numeric(abcd.data.train$ksads_ptsd_raw_769_p)),na.rm=TRUE)
+
+abcd.data.test$abuse <- rowSums(data.frame(as.numeric(abcd.data.test$ksads_ptsd_raw_761_p),as.numeric(abcd.data.test$ksads_ptsd_raw_762_p),as.numeric(abcd.data.test$ksads_ptsd_raw_763_p),as.numeric(abcd.data.test$ksads_ptsd_raw_767_p),as.numeric(abcd.data.test$ksads_ptsd_raw_768_p),as.numeric(abcd.data.test$ksads_ptsd_raw_769_p)),na.rm=TRUE)
+
+abcd.data.train$abuse_binary <- ifelse(abcd.data.train$abuse>0,1,0)
+abcd.data.test$abuse_binary <- ifelse(abcd.data.test$abuse>0,1,0)
+
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+abuse_binary,data=abcd.data.train))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+abuse_binary,data=abcd.data.train))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+abuse_binary,data=abcd.data.train))
+
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+abuse_binary,data=abcd.data.test))
+summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+abuse_binary,data=abcd.data.test))
+summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+abuse_binary,data=abcd.data.test))
+
+# df.summary <- subset(abcd.data.train,!is.na(abuse_binary)) %>%
+#      group_by(abuse_binary) %>%
+#      summarise(
+#          se = sd(thompson_PC1, na.rm = TRUE)/sqrt(length(thompson_PC1)),
+#          thompson_PC1 = mean(thompson_PC1,na.rm=TRUE))
+# png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Abuse_PC1_train.png",
+#     width = 4000, 
+#     height = 2000,
+#     res=700)
+# ggplot(data=df.summary,aes(abuse_binary,thompson_PC1,fill=as.factor(abuse_binary)))+geom_bar(position = "dodge",stat = "identity")+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Abuse') + scale_fill_manual(values = c(rgb(145/255,69/255,93/255),rgb(206/255,118/255,119/255),rgb(227/255,180/255,150/255))) + geom_errorbar(aes(ymin=thompson_PC1-se, ymax=thompson_PC1+se), width=.2,position=position_dodge(.9))
+# dev.off() 
+# #+coord_cartesian(ylim = c(-0.25, 0.25))
+# 
+# 
+# df.summary <- subset(abcd.data.train,!is.na(abuse_binary)) %>%
+#      group_by(abuse_binary) %>%
+#      summarise(
+#          se = sd(thompson_PC2, na.rm = TRUE)/sqrt(length(thompson_PC2)),
+#          thompson_PC2 = mean(thompson_PC2,na.rm=TRUE))
+# png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Abuse_PC2_train.png",
+#     width = 4000, 
+#     height = 2000,
+#     res=700)
+# ggplot(data=df.summary,aes(abuse_binary,thompson_PC2,fill=as.factor(abuse_binary)))+geom_bar(position = "dodge",stat = "identity")+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function') + xlab('Abuse') + scale_fill_manual(values = c(rgb(145/255,69/255,93/255),rgb(206/255,118/255,119/255),rgb(227/255,180/255,150/255))) + geom_errorbar(aes(ymin=thompson_PC2-se, ymax=thompson_PC2+se), width=.2,position=position_dodge(.9))
+# dev.off() 
+# 
+# 
+# df.summary <- subset(abcd.data.train,!is.na(abuse_binary)) %>%
+#      group_by(abuse_binary) %>%
+#      summarise(
+#          se = sd(thompson_PC3, na.rm = TRUE)/sqrt(length(thompson_PC3)),
+#          thompson_PC3 = mean(thompson_PC3,na.rm=TRUE))
+# png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Abuse_PC3_train.png",
+#     width = 4000, 
+#     height = 2000,
+#     res=700)
+# ggplot(data=df.summary,aes(abuse_binary,thompson_PC3,fill=as.factor(abuse_binary)))+geom_bar(position = "dodge",stat = "identity")+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory') + xlab('Abuse') + scale_fill_manual(values = c(rgb(145/255,69/255,93/255),rgb(206/255,118/255,119/255),rgb(227/255,180/255,150/255))) + geom_errorbar(aes(ymin=thompson_PC3-se, ymax=thompson_PC3+se), width=.2,position=position_dodge(.9))
+# dev.off()
+
+# Print models to table
+mod41<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+abuse_binary,data=abcd.data.train)
+mod42<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+abuse_binary,data=abcd.data.train)
+mod43<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+abuse_binary,data=abcd.data.train)
+mod44<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+abuse_binary,data=abcd.data.test)
+mod45<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+abuse_binary,data=abcd.data.test)
+mod46<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+abuse_binary,data=abcd.data.test)
+tab_model(mod41,mod42,mod43,pred.labels = c("Intercept","Age","Sex","Household Income [50K-100K]","Household Income [>100K]","Neighborhood Income","Parent Educ: HS Diploma/GED","Parent Educ: Some College","Parent Educ: Bachelor","Parent Educ: Post Graduate","Abuse"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Abuse_Table_Train.doc")
+tab_model(mod44,mod45,mod46,pred.labels = c("Intercept","Age","Sex","Household Income [50K-100K]","Household Income [>100K]","Neighborhood Income","Parent Educ: HS Diploma/GED","Parent Educ: Some College","Parent Educ: Bachelor","Parent Educ: Post Graduate","Abuse"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific", file = "/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Abuse_Table_Test.doc")
+
+mod51<-lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+monitoring+abuse_binary,data=abcd.data.train)
+mod52<-lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+monitoring+abuse_binary,data=abcd.data.train)
+mod53<-lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+monitoring+abuse_binary,data=abcd.data.train)
+tab_model(mod51,mod52,mod53,pred.labels = c("Intercept","Age","Sex","Household Income [50K-100K]","Household Income [>100K]","Neighborhood Income","Parent Educ: HS Diploma/GED","Parent Educ: Some College","Parent Educ: Bachelor","Parent Educ: Post Graduate","Caregiver Monitoring","Abuse"),dv.labels=c("General Cognition","Executive Function","Learning/Memory"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific",file = "/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Abuse_Table_WithMonitoring_Train.doc")
+
+```
+
+# make some images showing the item-level analyses
+```{r}
+
+df.summary <- subset(abcd.data.traintest,!is.na(parent_monitor_q1_y)) %>%
+     group_by(parent_monitor_q1_y) %>%
+     summarise(
+         se = sd(thompson_PC1, na.rm = TRUE)/sqrt(length(thompson_PC1)),
+         thompson_PC1 = mean(thompson_PC1,na.rm=TRUE))
+png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Item1_PC1_traintest.png",
+    width = 4000,
+    height = 2000,
+    res=700)
+ggplot(data=df.summary,aes(parent_monitor_q1_y,thompson_PC1,fill=as.factor(parent_monitor_q1_y)))+geom_bar(position = "dodge",stat = "identity")+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Item 1: Know where you are') + scale_fill_manual(values = sequential_hcl(5,"RedOr")) + geom_errorbar(aes(ymin=thompson_PC1-se, ymax=thompson_PC1+se), width=.2,position=position_dodge(.9))+coord_cartesian(ylim = c(-1.4, 0.2))
+dev.off()
+
+df.summary <- subset(abcd.data.traintest,!is.na(parent_monitor_q2_y)) %>%
+     group_by(parent_monitor_q2_y) %>%
+     summarise(
+         se = sd(thompson_PC1, na.rm = TRUE)/sqrt(length(thompson_PC1)),
+         thompson_PC1 = mean(thompson_PC1,na.rm=TRUE))
+png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Item2_PC1_traintest.png",
+    width = 4000,
+    height = 2000,
+    res=700)
+ggplot(data=df.summary,aes(parent_monitor_q2_y,thompson_PC1,fill=as.factor(parent_monitor_q2_y)))+geom_bar(position = "dodge",stat = "identity")+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Item 2: Know who you are with') + scale_fill_manual(values = sequential_hcl(5,"RedOr")) + geom_errorbar(aes(ymin=thompson_PC1-se, ymax=thompson_PC1+se), width=.2,position=position_dodge(.9))+coord_cartesian(ylim = c(-0.75, 0.2))
+dev.off()
+
+df.summary <- subset(abcd.data.traintest,!is.na(parent_monitor_q3_y)) %>%
+     group_by(parent_monitor_q3_y) %>%
+     summarise(
+         se = sd(thompson_PC1, na.rm = TRUE)/sqrt(length(thompson_PC1)),
+         thompson_PC1 = mean(thompson_PC1,na.rm=TRUE))
+png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Item3_PC1_traintest.png",
+    width = 4000,
+    height = 2000,
+    res=700)
+ggplot(data=df.summary,aes(parent_monitor_q3_y,thompson_PC1,fill=as.factor(parent_monitor_q3_y)))+geom_bar(position = "dodge",stat = "identity")+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Item 3: Know how to contact') + scale_fill_manual(values =sequential_hcl(5,"RedOr")) + geom_errorbar(aes(ymin=thompson_PC1-se, ymax=thompson_PC1+se), width=.2,position=position_dodge(.9))+coord_cartesian(ylim = c(-0.75, 0.2))
+dev.off()
+
+df.summary <- subset(abcd.data.traintest,!is.na(parent_monitor_q4_y)) %>%
+     group_by(parent_monitor_q4_y) %>%
+     summarise(
+         se = sd(thompson_PC1, na.rm = TRUE)/sqrt(length(thompson_PC1)),
+         thompson_PC1 = mean(thompson_PC1,na.rm=TRUE))
+png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Item4_PC1_traintest.png",
+    width = 4000,
+    height = 2000,
+    res=700)
+ggplot(data=df.summary,aes(parent_monitor_q4_y,thompson_PC1,fill=as.factor(parent_monitor_q4_y)))+geom_bar(position = "dodge",stat = "identity")+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Item 4: Talk over plans') + scale_fill_manual(values = sequential_hcl(5,"RedOr")) + geom_errorbar(aes(ymin=thompson_PC1-se, ymax=thompson_PC1+se), width=.2,position=position_dodge(.9))+coord_cartesian(ylim = c(-0.75, 0.2))
+dev.off()
+
+df.summary <- subset(abcd.data.traintest,!is.na(parent_monitor_q5_y)) %>%
+     group_by(parent_monitor_q5_y) %>%
+     summarise(
+         se = sd(thompson_PC1, na.rm = TRUE)/sqrt(length(thompson_PC1)),
+         thompson_PC1 = mean(thompson_PC1,na.rm=TRUE))
+png("/Users/askeller/Documents/Writing_InProgress/ParentalMonitoring_Cognition/Item5_PC1_traintest.png",
+    width = 4000,
+    height = 2000,
+    res=700)
+ggplot(data=df.summary,aes(parent_monitor_q5_y,thompson_PC1,fill=as.factor(parent_monitor_q5_y)))+geom_bar(position = "dodge",stat = "identity")+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition') + xlab('Item 5: Have dinner together') + scale_fill_manual(values = sequential_hcl(5,"RedOr")) + geom_errorbar(aes(ymin=thompson_PC1-se, ymax=thompson_PC1+se), width=.2,position=position_dodge(.9))+coord_cartesian(ylim = c(-0.75, 0.2))
+dev.off()
+```
+
+### REPEAT ITEM-LEVEL ANALYSES SEPARATELY IN DISCOVERY AND REPLICATION SAMPLES
+```{r}
+
+abcd.data.train$parent_monitor_q1_y<-as.numeric(abcd.data.train$parent_monitor_q1_y)
+abcd.data.train$parent_monitor_q2_y<-as.numeric(abcd.data.train$parent_monitor_q2_y)
+abcd.data.train$parent_monitor_q3_y<-as.numeric(abcd.data.train$parent_monitor_q3_y)
+abcd.data.train$parent_monitor_q4_y<-as.numeric(abcd.data.train$parent_monitor_q4_y)
+abcd.data.train$parent_monitor_q5_y<-as.numeric(abcd.data.train$parent_monitor_q5_y)
+
+abcd.data.test$parent_monitor_q1_y<-as.numeric(abcd.data.test$parent_monitor_q1_y)
+abcd.data.test$parent_monitor_q2_y<-as.numeric(abcd.data.test$parent_monitor_q2_y)
+abcd.data.test$parent_monitor_q3_y<-as.numeric(abcd.data.test$parent_monitor_q3_y)
+abcd.data.test$parent_monitor_q4_y<-as.numeric(abcd.data.test$parent_monitor_q4_y)
+abcd.data.test$parent_monitor_q5_y<-as.numeric(abcd.data.test$parent_monitor_q5_y)
+
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+household.income+high.educ+parent_monitor_q1_y+parent_monitor_q2_y+parent_monitor_q3_y+parent_monitor_q4_y+parent_monitor_q5_y,data=abcd.data.train)) # all significant except Q3
+
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+household.income+high.educ+parent_monitor_q1_y+parent_monitor_q2_y+parent_monitor_q3_y+parent_monitor_q4_y+parent_monitor_q5_y,data=abcd.data.test)) # all significant ***
+
+# try the same thing but with the question number coded as a factor to look at an interaction
+library("reshape2")
+
+monitoring_qs <- abcd.data.train[,c("subjectkey","parent_monitor_q1_y","parent_monitor_q2_y","parent_monitor_q3_y","parent_monitor_q4_y","parent_monitor_q5_y")]
+test<-melt(monitoring_qs)
+merged.dataset.train<-merge(test,abcd.data.train,by="subjectkey")
+merged.dataset.train$variable=as.factor(merged.dataset.train$variable)
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+household.income+high.educ+value*variable,data=merged.dataset.train))
+
+monitoring_qs <- abcd.data.test[,c("subjectkey","parent_monitor_q1_y","parent_monitor_q2_y","parent_monitor_q3_y","parent_monitor_q4_y","parent_monitor_q5_y")]
+test<-melt(monitoring_qs)
+merged.dataset.test<-merge(test,abcd.data.test,by="subjectkey")
+merged.dataset.test$variable=as.factor(merged.dataset.test$variable)
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+reshist_addr1_adi_income+household.income+high.educ+value*variable,data=merged.dataset.test))
+
+```
+
+## Analyses by Task
+```{r}
+
+# Equations pasted in here for reference:
+
+# combined.data$thompson_PC1 <- (0.754*combined.data$PicVocab)+(0.213*combined.data$Flanker)+(0.471*combined.data$List)+(0.205*combined.data$CardSort)+(0.015*combined.data$Pattern)+(0.012*combined.data$Picture)+(0.82*combined.data$Reading)+(0.306*combined.data$RAVLT)+(0.5*combined.data$LMT)
+# 
+# combined.data$thompson_PC2 <- (0.065*combined.data$PicVocab)+(0.712*combined.data$Flanker)+(0.148*combined.data$List)+(0.71*combined.data$CardSort)+(0.813*combined.data$Pattern)+(0.135*combined.data$Picture)+(0.12*combined.data$Reading)+(0.125*combined.data$RAVLT)+(0.299*combined.data$LMT)
+# 
+# combined.data$thompson_PC3 <- (0.19*combined.data$PicVocab)+(0.067*combined.data$Flanker)+(0.493*combined.data$List)+(0.232*combined.data$CardSort)+(0.085*combined.data$Pattern)+(0.863*combined.data$Picture)+(0.122*combined.data$Reading)+(0.712*combined.data$RAVLT)+(0.068*combined.data$LMT)
+
+summary(lmer(PicVocab~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth+monitoring,data=abcd.data.train)) # Warmth: ns / Montioring: ***
+summary(lmer(Flanker~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth+monitoring,data=abcd.data.train)) # Warmth: ns / Montioring: ns
+summary(lmer(List~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth+monitoring,data=abcd.data.train)) # Warmth:  ns / Montioring: ns
+summary(lmer(CardSort~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth+monitoring,data=abcd.data.train)) # Warmth: ns / Montioring: ns
+summary(lmer(Pattern~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth+monitoring,data=abcd.data.train)) # Warmth: ns / Montioring: ns
+summary(lmer(Picture~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth+monitoring,data=abcd.data.train)) # Warmth: ns / Montioring: ns
+summary(lmer(Reading~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth+monitoring,data=abcd.data.train)) # Warmth: ns / Montioring: ***
+summary(lmer(RAVLT~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth+monitoring,data=abcd.data.train)) # Warmth: ns / Montioring: **
+summary(lmer(LMT~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth+monitoring,data=abcd.data.train)) # Warmth: ns / Montioring: *
+
+summary(lmer(PicVocab~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth+monitoring,data=abcd.data.test)) # Warmth: ns / Montioring: ***
+summary(lmer(Flanker~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth+monitoring,data=abcd.data.test)) # Warmth: ns / Montioring: ns
+summary(lmer(List~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth+monitoring,data=abcd.data.test)) # Warmth:  ** / Montioring: ***
+summary(lmer(CardSort~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth+monitoring,data=abcd.data.test)) # Warmth: ns / Montioring: ***
+summary(lmer(Pattern~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth+monitoring,data=abcd.data.test)) # Warmth: ns / Montioring: *
+summary(lmer(Picture~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth+monitoring,data=abcd.data.test)) # Warmth: ns / Montioring: ns
+summary(lmer(Reading~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth+monitoring,data=abcd.data.test)) # Warmth: ns / Montioring: ***
+summary(lmer(RAVLT~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth+monitoring,data=abcd.data.test)) # Warmth: ns / Montioring: ***
+summary(lmer(LMT~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+warmth+monitoring,data=abcd.data.test)) # Warmth: ns / Montioring: *
+
+```
+
+# Moderation analyses
+```{r}
+summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+household.income+reshist_addr1_adi_income+high.educ+monitoring+monitoring*household.income,data=abcd.data.train))
+```
+
+# Compare excluded participants to included
+```{r}
+abcd.data.exclusion=abcd.data.almost
+abcd.data.exclusion$exclusion=ifelse(abcd.data.exclusion$subjectkey %in% abcd.data.traintest$subjectkey,1,2)
+
+library(Gmisc)
+demo_table <- abcd.data.exclusion %>%
+  mutate(exclusion = factor(exclusion, levels = 1:2, labels = c("Included", "Excluded"))) %>%
+#subset(matched_group<3) %>%
+  set_column_labels(interview_age = "Age (Months)",
+                    sex = "Sex",
+                    race.6level = "Race",
+                    household.income = "Household Income",
+                    reshist_addr1_adi_income = "Neighborhood Income",
+                    high.educ = "Parent Education") %>%
+getDescriptionStatsBy(interview_age, 
+                        sex,
+                        reshist_addr1_adi_income,
+                        household.income,
+                        race.6level,
+                        high.educ,
+                        add_total_col = TRUE, statistics=TRUE,
+                        by = exclusion)
+
+demo_table
+```
+
+<!-- # Calculate internal reliability using omega: -->
+<!-- ```{r} -->
+<!-- library(psych) -->
+<!-- library(GPArotation) -->
+<!-- monitoring_items <- as.matrix(data.frame(as.numeric(abcd.data.traintest$parent_monitor_q1_y),as.numeric(abcd.data.traintest$parent_monitor_q2_y),as.numeric(abcd.data.traintest$parent_monitor_q3_y),as.numeric(abcd.data.traintest$parent_monitor_q4_y),as.numeric(abcd.data.traintest$parent_monitor_q5_y))) -->
+<!-- omega(cor(monitoring_items),nfactors = 1) -->
+
+<!-- ``` -->

### 2022-06-10 ABCD_Flux22_PFN_Analyses.Rmd
analyses for flux abstract

---
title: "ABCD_Flux22_PFN_Analyses"
author: "Arielle Keller"
date: "3/21/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(width=250)
library(tidyr)
library(dplyr)
library(ggplot2)
library(lsr)
library(lme4)
library(lmerTest)
library(mediation)
library(ggcorrplot)
library(corrplot)
library(RColorBrewer)
library(glmnet)
library(mgcv)
library(gamm4)
library(readr)

library(devtools)
install_github("jfortin1/neuroCombatData")
install_github("jfortin1/neuroCombat_Rpackage")
library(neuroCombat)
```

# First load in the spatial extent of each PFN (they're in order, 1-17)
```{r}
pfn_sizes <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/All_PFN_sizes.csv") # n=9,132
# Change PFN column names so they're sensible
colnames(pfn_sizes)<-c("subjectkey","PFN1","PFN2","PFN3","PFN4","PFN5","PFN6","PFN7","PFN8","PFN9","PFN10","PFN11","PFN12","PFN13","PFN14","PFN15","PFN16","PFN17")
```

# Remove subjects based on the following criteria:
## 1) 8min of retained TRs (600 TRs)
## 2) ABCD Booleans for rest and T1
```{r}
num_TRs <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/num_TRs_by_subj_redo.csv")
data<-merge(pfn_sizes,num_TRs,by="subjectkey")
data.clean<-data[data$numTRs>=600,] # we go from 9,132 to 8,293 at this step

# Remove participants based on booleans from ABCD
abcd_imgincl01 <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/abcd_imgincl01.csv")
abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$eventnam=="baseline_year_1_arm_1",]
abcd_imgincl01 <- abcd_imgincl01[!abcd_imgincl01$visit=="",] # start here with 11,663 (8,287 of the 9,132 set)
abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_t1w_include==1,] # down to 11,124 (8,045 of the 9,132 set)
abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_rsfmri_include==1,] # down to 9,388 (7,475 of the 9,132 set)

combined.data <- merge(data.clean,abcd_imgincl01[, c("subjectkey",'imgincl_t1w_include')],by="subjectkey") # n=7,475
```

## Instead of calculating the Thompson factor scores ourselves, use the summary scores from DEAP
```{r}
newdata<-readRDS("/Users/askeller/Documents/Kellernet_PrelimAnalysis/DEAP-data-download_ThompsonScores_ResFamIncome.rds")
newdata.baseline<-newdata[newdata$event_name=="baseline_year_1_arm_1",]
colnames(newdata.baseline)[1]<-"subjectkey"
all.data <- merge(combined.data,newdata.baseline[,c("subjectkey", setdiff(colnames(newdata.baseline),colnames(combined.data)))],by="subjectkey")

# for simplicity, rename thompson variables
colnames(all.data)<-gsub("neurocog_pc1.bl","thompson_PC1",colnames(all.data))
colnames(all.data)<-gsub("neurocog_pc2.bl","thompson_PC2",colnames(all.data))
colnames(all.data)<-gsub("neurocog_pc3.bl","thompson_PC3",colnames(all.data)) # still at n=7,475
```

# Add in Family and Site covariates
```{r}
family <-read.table("/Users/askeller/Documents/Kellernet_PrelimAnalysis/ses/acspsw03.txt",header=TRUE)
family.baseline<-family[family$eventname=="baseline_year_1_arm_1",]
abcd.data.almost <- merge(all.data,family.baseline[, c("subjectkey", setdiff(colnames(family.baseline),colnames(all.data)))],by="subjectkey")
site_info <- readRDS("/Users/askeller/Documents/Kellernet_PrelimAnalysis/DEAP-siteID.rds")
site.baseline<-site_info[site_info$event_name=="baseline_year_1_arm_1",]
colnames(site.baseline)[1]<-"subjectkey"
abcd.data.almost2 <- merge(abcd.data.almost,site.baseline[,c("subjectkey", setdiff(colnames(site.baseline),colnames(abcd.data.almost)))],by="subjectkey") # n=7,474
```

# Add mean FD
```{r}
meanFD <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/PFN_Gradients_CombinedScript/getFD/meanFD_031822.csv")
colnames(meanFD)<-c("subjectkey","meanFD")
meanFD$subjectkey <- gsub(pattern="sub-NDAR",replacement="NDAR_", meanFD$subjectkey)
abcd.data <- merge(abcd.data.almost2,meanFD,by="subjectkey")

# n=7,461
```

# Load train/test split from UMinn
```{r}
traintest<-read_tsv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/participants.tsv")
traintest.baseline<-traintest[traintest$session_id=="ses-baselineYear1Arm1",c("participant_id","matched_group")]
colnames(traintest.baseline)[1]<-c("subjectkey")
traintest.baseline$subjectkey <- gsub(pattern="sub-NDAR",replacement="NDAR_", traintest.baseline$subjectkey)
traintest.baseline<-traintest.baseline %>% distinct()
abcd.data.traintest <- merge(abcd.data,traintest.baseline,by="subjectkey")
abcd.data.train <- abcd.data.traintest[abcd.data.traintest$matched_group==1,] # n=3,749
abcd.data.test <- abcd.data.traintest[abcd.data.traintest$matched_group==2,] # n=3,712
```

# Apply ComBat harmonization across ABCD sites separately for train and test sets
```{r}
# prep to make sure there are no empty levels
abcd.data.train$abcd_site<-droplevels(abcd.data.train$abcd_site)
abcd.data.test$abcd_site<-droplevels(abcd.data.test$abcd_site)

# harmonize TRAIN set 
batch <- abcd.data.train$abcd_site
abcd.data.train.toharmonize <- abcd.data.train[,c("PFN1","PFN2","PFN3","PFN4","PFN5","PFN6","PFN7","PFN8","PFN9","PFN10","PFN11","PFN12","PFN13","PFN14","PFN15","PFN16","PFN17","thompson_PC1","thompson_PC2","thompson_PC3","meanFD")]
mod <- model.matrix(~abcd.data.train$interview_age+abcd.data.train$sex+abcd.data.train$rel_family_id)
dat <- t(abcd.data.train.toharmonize)
abcd.data.combat <- neuroCombat(dat=dat,mod=mod,batch=batch,eb=FALSE)
dat.harmonized<-data.frame(t(abcd.data.combat$dat.combat))
abcd.data.noPFNsCog <- subset(abcd.data.train,select=-c(PFN1,PFN2,PFN3,PFN4,PFN5,PFN6,PFN7,PFN8,PFN9,PFN10,PFN11,PFN12,PFN13,PFN14,PFN15,PFN16,PFN17,thompson_PC1,thompson_PC2,thompson_PC3,meanFD))
abcd.data.train.harmonized <- cbind(abcd.data.noPFNsCog,dat.harmonized) # Add the harmonized data back into the main dataframe (BE AWARE THAT NOT ALL DATA IS HARMONIZED)

# harmonize TEST set 
batch <- abcd.data.test$abcd_site
abcd.data.test.toharmonize <- abcd.data.test[,c("PFN1","PFN2","PFN3","PFN4","PFN5","PFN6","PFN7","PFN8","PFN9","PFN10","PFN11","PFN12","PFN13","PFN14","PFN15","PFN16","PFN17","thompson_PC1","thompson_PC2","thompson_PC3","meanFD")]
mod <- model.matrix(~abcd.data.test$interview_age+abcd.data.test$sex+abcd.data.test$rel_family_id)
dat <- t(abcd.data.test.toharmonize)
abcd.data.combat <- neuroCombat(dat=dat,mod=mod,batch=batch,eb=FALSE)
dat.harmonized<-data.frame(t(abcd.data.combat$dat.combat))
abcd.data.noPFNsCog <- subset(abcd.data.test,select=-c(PFN1,PFN2,PFN3,PFN4,PFN5,PFN6,PFN7,PFN8,PFN9,PFN10,PFN11,PFN12,PFN13,PFN14,PFN15,PFN16,PFN17,thompson_PC1,thompson_PC2,thompson_PC3,meanFD))
abcd.data.test.harmonized <- cbind(abcd.data.noPFNsCog,dat.harmonized) # Add the harmonized data back into the main dataframe (BE AWARE THAT NOT ALL DATA IS HARMONIZED)

```

# fix age variable to be continuous
```{r}
abcd.data.train.harmonized$interview_age <- as.numeric(abcd.data.train.harmonized$interview_age)
abcd.data.test.harmonized$interview_age <- as.numeric(abcd.data.test.harmonized$interview_age)
abcd.data.traintest$interview_age <- as.numeric(abcd.data.traintest$interview_age)
```

# quick  analyses for flux abstract
```{r}
summary(lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
summary(lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
summary(lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))

summary(lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
summary(lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
summary(lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
```

# Make a demographics table
```{r}
# exclude n=488 subjects with missing cognitive data
abcd.data.for.ridge<-abcd.data.traintest[,c("subjectkey","thompson_PC1","thompson_PC2","thompson_PC3","matched_group","interview_age","sex","meanFD","abcd_site","rel_family_id")]

abcd.data.traintest<-abcd.data.traintest[complete.cases(abcd.data.for.ridge),]

library(Gmisc)
demo_table <- abcd.data.traintest %>%
  mutate(matched_group = factor(matched_group, levels = 1:2, labels = c("Discovery", "Replication"))) %>%
#subset(matched_group<3) %>%
  set_column_labels(interview_age = "Age (Months)",
                    sex = "Sex",
                    race.6level = "Race",
                    household.income = "Household Income",
                    thompson_PC1 = "General Cognition",
                    thompson_PC2 = "Executive Function",
                    thompson_PC3 = "Learning/Memory",
                    high.educ = "Parent Education") %>%
getDescriptionStatsBy(interview_age, 
                        sex,
                        thompson_PC1,
                        thompson_PC2,
                        thompson_PC3,
                        household.income,
                        race.6level,
                        high.educ,
                        add_total_col = TRUE, statistics=TRUE,
                        by = matched_group)

demo_table
```

# make figures to replicate Cui et al.
```{r}
correlation<-cor.test(abcd.data.train.harmonized$thompson_PC1,abcd.data.train.harmonized$PFN17)
png("/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_032322/PC1_PFN17_train.png",
    width = 3000, 
    height = 3000,
    res=1200)
ggplot(data=abcd.data.train.harmonized,aes(abcd.data.train.harmonized$thompson_PC1,abcd.data.train.harmonized$PFN17))+geom_point(size=0.1,colour="#F5BA2E")+geom_smooth(method=lm,colour="#F5BA2E")+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.text.x = element_text(color="black"),
    axis.ticks = element_line(color = "black"),axis.text.y = element_text(color="black")) +ylab('Total Representation') + xlab('General Cognition') + ggtitle(paste("r=",as.character(round(correlation$estimate,3)),", p=",as.character(round(correlation$p.value,3))))
dev.off()

correlation<-cor.test(abcd.data.train.harmonized$thompson_PC1,abcd.data.train.harmonized$PFN15)
png("/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_032322/PC1_PFN15_train.png",
    width = 3000, 
    height = 3000,
    res=1200)
ggplot(data=abcd.data.train.harmonized,aes(abcd.data.train.harmonized$thompson_PC1,abcd.data.train.harmonized$PFN15))+geom_point(size=0.1,colour="#F5BA2E")+geom_smooth(method=lm,colour="#F5BA2E")+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.text.x = element_text(color="black"),
    axis.ticks = element_line(color = "black"),axis.text.y = element_text(color="black")) +ylab('Total Representation') + xlab('General Cognition') + ggtitle(paste("r=",as.character(round(correlation$estimate,3)),", p=",as.character(round(correlation$p.value,3))))
dev.off()

correlation<-cor.test(abcd.data.test.harmonized$thompson_PC1,abcd.data.test.harmonized$PFN17)
png("/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_032322/PC1_PFN17_test.png",
    width = 3000, 
    height = 3000,
    res=1200)
ggplot(data=abcd.data.test.harmonized,aes(abcd.data.test.harmonized$thompson_PC1,abcd.data.test.harmonized$PFN17))+geom_point(size=0.1,colour="#F5BA2E")+geom_smooth(method=lm,colour="#F5BA2E")+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.text.x = element_text(color="black"),
    axis.ticks = element_line(color = "black"),axis.text.y = element_text(color="black")) +ylab('Total Representation') + xlab('General Cognition') + ggtitle(paste("r=",as.character(round(correlation$estimate,3)),", p=",as.character(round(correlation$p.value,3))))
dev.off()

correlation<-cor.test(abcd.data.test.harmonized$thompson_PC1,abcd.data.test.harmonized$PFN15)
png("/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_032322/PC1_PFN15_test.png",
    width = 3000, 
    height = 3000,
    res=1200)
ggplot(data=abcd.data.test.harmonized,aes(abcd.data.test.harmonized$thompson_PC1,abcd.data.test.harmonized$PFN15))+geom_point(size=0.1,colour="#F5BA2E")+geom_smooth(method=lm,colour="#F5BA2E")+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.text.x = element_text(color="black"),
    axis.ticks = element_line(color = "black"),axis.text.y = element_text(color="black")) +ylab('Total Representation') + xlab('General Cognition') + ggtitle(paste("r=",as.character(round(correlation$estimate,3)),", p=",as.character(round(correlation$p.value,3))))
dev.off()

correlation<-cor.test(abcd.data.train.harmonized$thompson_PC1,abcd.data.train.harmonized$PFN3)
png("/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_032322/PC1_PFN3_train.png",
    width = 3000, 
    height = 3000,
    res=1200)
ggplot(data=abcd.data.train.harmonized,aes(abcd.data.train.harmonized$thompson_PC1,abcd.data.train.harmonized$PFN3))+geom_point(size=0.1,colour="#F5BA2E")+geom_smooth(method=lm,colour="#F5BA2E")+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.text.x = element_text(color="black"),
    axis.ticks = element_line(color = "black"),axis.text.y = element_text(color="black")) +ylab('Total Representation') + xlab('General Cognition') + ggtitle(paste("r=",as.character(round(correlation$estimate,3)),", p=",as.character(round(correlation$p.value,3))))
dev.off()

correlation<-cor.test(abcd.data.test.harmonized$thompson_PC1,abcd.data.test.harmonized$PFN3)
png("/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_032322/PC1_PFN3_test.png",
    width = 3000, 
    height = 3000,
    res=1200)
ggplot(data=abcd.data.test.harmonized,aes(abcd.data.test.harmonized$thompson_PC1,abcd.data.test.harmonized$PFN3))+geom_point(size=0.1,colour="#F5BA2E")+geom_smooth(method=lm,colour="#F5BA2E")+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.text.x = element_text(color="black"),
    axis.ticks = element_line(color = "black"),axis.text.y = element_text(color="black")) +ylab('Total Representation') + xlab('General Cognition') + ggtitle(paste("r=",as.character(round(correlation$estimate,3)),", p=",as.character(round(correlation$p.value,3))))
dev.off()

```

### Replicate Cui bar graph:
```{r}
pfn1<-summary(lmer(PFN1~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn2<-summary(lmer(PFN2~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn3<-summary(lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized)) 
pfn4<-summary(lmer(PFN4~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn5<-summary(lmer(PFN5~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized)) 
pfn6<-summary(lmer(PFN6~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn7<-summary(lmer(PFN7~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized)) 
pfn8<-summary(lmer(PFN8~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn9<-summary(lmer(PFN9~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn10<-summary(lmer(PFN10~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn11<-summary(lmer(PFN11~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn12<-summary(lmer(PFN12~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn13<-summary(lmer(PFN13~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn14<-summary(lmer(PFN14~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn15<-summary(lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn16<-summary(lmer(PFN16~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
pfn17<-summary(lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))

p_vec<-c(pfn1$coefficients[5,5],pfn2$coefficients[5,5],pfn3$coefficients[5,5],pfn4$coefficients[5,5],pfn5$coefficients[5,5],pfn6$coefficients[5,5],pfn7$coefficients[5,5],pfn8$coefficients[5,5],pfn9$coefficients[5,5],pfn10$coefficients[5,5],pfn11$coefficients[5,5],pfn12$coefficients[5,5],pfn13$coefficients[5,5],pfn14$coefficients[5,5],pfn15$coefficients[5,5],pfn16$coefficients[5,5],pfn17$coefficients[5,5])

p_vec_adj <- p.adjust(p_vec, "bonferroni")
z_vec <- qnorm(p_vec/2,lower.tail = FALSE);

pos_neg<-c(pfn1$coefficients[5,1],pfn2$coefficients[5,1],pfn3$coefficients[5,1],pfn4$coefficients[5,1],pfn5$coefficients[5,1],pfn6$coefficients[5,1],pfn7$coefficients[5,1],pfn8$coefficients[5,1],pfn9$coefficients[5,1],pfn10$coefficients[5,1],pfn11$coefficients[5,1],pfn12$coefficients[5,1],pfn13$coefficients[5,1],pfn14$coefficients[5,1],pfn15$coefficients[5,1],pfn16$coefficients[5,1],pfn17$coefficients[5,1])
pos_neg <- ifelse(pos_neg>0,1,-1)

z_vec_pn <- z_vec*pos_neg
keep_p <- ifelse(p_vec_adj<.05,1,0)

```

### Replicate Cui bar graph (SAME THING IN TEST SET):
```{r}
pfn1<-summary(lmer(PFN1~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn2<-summary(lmer(PFN2~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn3<-summary(lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized)) 
pfn4<-summary(lmer(PFN4~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn5<-summary(lmer(PFN5~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized)) 
pfn6<-summary(lmer(PFN6~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn7<-summary(lmer(PFN7~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized)) 
pfn8<-summary(lmer(PFN8~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn9<-summary(lmer(PFN9~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn10<-summary(lmer(PFN10~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn11<-summary(lmer(PFN11~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn12<-summary(lmer(PFN12~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn13<-summary(lmer(PFN13~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn14<-summary(lmer(PFN14~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn15<-summary(lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn16<-summary(lmer(PFN16~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
pfn17<-summary(lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))

p_vec<-c(pfn1$coefficients[5,5],pfn2$coefficients[5,5],pfn3$coefficients[5,5],pfn4$coefficients[5,5],pfn5$coefficients[5,5],pfn6$coefficients[5,5],pfn7$coefficients[5,5],pfn8$coefficients[5,5],pfn9$coefficients[5,5],pfn10$coefficients[5,5],pfn11$coefficients[5,5],pfn12$coefficients[5,5],pfn13$coefficients[5,5],pfn14$coefficients[5,5],pfn15$coefficients[5,5],pfn16$coefficients[5,5],pfn17$coefficients[5,5])

p_vec_adj <- p.adjust(p_vec, "bonferroni")
z_vec <- qnorm(p_vec/2,lower.tail = FALSE);

pos_neg<-c(pfn1$coefficients[5,1],pfn2$coefficients[5,1],pfn3$coefficients[5,1],pfn4$coefficients[5,1],pfn5$coefficients[5,1],pfn6$coefficients[5,1],pfn7$coefficients[5,1],pfn8$coefficients[5,1],pfn9$coefficients[5,1],pfn10$coefficients[5,1],pfn11$coefficients[5,1],pfn12$coefficients[5,1],pfn13$coefficients[5,1],pfn14$coefficients[5,1],pfn15$coefficients[5,1],pfn16$coefficients[5,1],pfn17$coefficients[5,1])
pos_neg <- ifelse(pos_neg>0,1,-1)

z_vec_pn <- z_vec*pos_neg
keep_p <- ifelse(p_vec_adj<.05,1,0)

```

## Replicate Cui result showing topography across-individual variability by network
```{r}

# library(R.matlab)
# library(ggplot2);
# 
# ResultsFolder = '/data/jux/BBL/projects/pncSingleFuncParcel/Replication/Revision';
# AtlasFolder = paste0(ResultsFolder, '/SingleParcellation/SingleAtlas_Analysis');
# Variability_Visualize_Folder = paste0(AtlasFolder, '/Variability_Visualize');
# Variability_Mat = readMat(paste0(Variability_Visualize_Folder, '/VariabilityLoading_Median_17SystemMean.mat'));
# 
# AtlasLabel_Mat = readMat(paste0(AtlasFolder, '/Group_AtlasLabel.mat'));
# 
# AllData = data.frame(Variability = matrix(0, 17734, 1));
# AllData$Label = matrix(0, 17734, 1);
# for (i in c(1:17734))
# {
#   AllData$Variability[i] = Variability_Mat$VariabilityLoading.Median.17SystemMean.NoMedialWall[i];
#   AllData$Label[i] = AtlasLabel_Mat$sbj.AtlasLabel.NoMedialWall[i];
# }
# AllData$Variability = as.numeric(AllData$Variability);
# AllData$Label = as.factor(AllData$Label);
# 
# # Order the network by the median value
# MedianValue = matrix(0, 1, 17);
# for (i in c(1:17)) {
#   ind = which(AllData$Label == i);
#   MedianValue[i] = median(AllData$Variability[ind]);
# }
# # Store network variability for correlation with effect size
# writeMat(paste0(ResultsFolder, '/Corr_NetworkVariability_EffectSize/NetworkVariability.mat'), MedianValue = MedianValue);
# tmp = sort(MedianValue, index.return = TRUE);
# 
# ColorScheme = c("#E76178", "#7499C2", "#F5BA2E", "#7499C2", "#00A131",
#                 "#AF33AD", "#E443FF", "#E76178", "#E443FF", "#AF33AD",
#                 "#7499C2", "#E76178", "#7499C2", "#00A131", "#F5BA2E",
#                 "#4E31A8", "#F5BA2E");
# ColorScheme_XText = c("#AF33AD", "#AF33AD", "#7499C2", "#7499C2", "#4E31A8",
#                 "#7499C2", "#7499C2", "#F5BA2E", "#00A131", "#E76178",
#                 "#E443FF", "#E443FF", "#E76178", "#E76178", "#F5BA2E",
#                 "#00A131", "#F5BA2E");
# Order = c(10, 6, 4, 2, 16, 11, 13, 15, 5, 12, 7, 9, 8, 1, 17, 14, 3);
# ColorScheme_XText_New = ColorScheme_XText;
# for (i in c(1:17)) {
#   ind = which(Order == i);
#   ColorScheme_XText_New[ind] = ColorScheme_XText[i];
# }
# ggplot(AllData, aes(x = Label, y = Variability, fill = Label, color = Label)) + 
#       geom_violin(trim = FALSE) +
#       scale_color_manual(values = ColorScheme) + 
#       scale_fill_manual(values = ColorScheme) + 
#       labs(x = "Networks", y = "Across-subject Variability") + theme_classic() +
#       theme(axis.text.x = element_text(size = 22, color = ColorScheme_XText_New),
#             axis.text.y = element_text(size = 22, color = "black"),
#             axis.title = element_text(size = 22)) +
#       theme(axis.text.x = element_text(angle = 22, hjust = 1)) + 
#       theme(legend.position = "none") + 
#       scale_x_discrete(
#             limits = c(10, 6, 4, 2, 16, 11, 13, 15, 5, 12, 7, 9, 8, 1, 17, 14, 3),
#             labels = c("12", "11", "2", "6", "14", "7", "8", "17", "16", "9", 
#                        "13", "5", "15", "10", "3", "1", "4")) + 
#       geom_boxplot(width=0.1, fill = "white");
# ggsave('/data/jux/BBL/projects/pncSingleFuncParcel/Replication/Revisioni/Figures/Variability_Loading_Mean_Violin.tiff', width = 20, height = 15, dpi = 600, units = "cm");

```

### 2022-06-10 RidgeCode/get_data_for_ridge.R
adding script to get data

@@ -1,0 +1,84 @@
+
+# First load in the spatial extent of each PFN (they're in order, 1-17)
+# Then merge with the same datasets as above (NIH toolbox, trauma, etc.)
+pfn_sizes <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/All_PFN_sizes.csv")
+# Change PFN column names so they're sensible
+colnames(pfn_sizes)<-c("subjectkey","PFN1","PFN2","PFN3","PFN4","PFN5","PFN6","PFN7","PFN8","PFN9","PFN10","PFN11","PFN12","PFN13","PFN14","PFN15","PFN16","PFN17")
+
+# Load data
+newdata<-readRDS("/Users/askeller/Documents/Kellernet_PrelimAnalysis/DEAP-data-download_ThompsonScores_ResFamIncome.rds")
+newdata.baseline<-newdata[newdata$event_name=="baseline_year_1_arm_1",]
+colnames(newdata.baseline)[1]<-"subjectkey"
+all.data <- merge(pfn_sizes,newdata.baseline[,c("subjectkey", setdiff(colnames(newdata.baseline),colnames(pfn_sizes)))],by="subjectkey")
+
+
+
+# Remove subjects based on the following criteria:
+## 1) 8min of retained TRs (600 TRs)
+## 2) ABCD Booleans for rest and T1
+num_TRs <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/num_TRs_by_subj_redo.csv")
+data<-merge(all.data,num_TRs,by="subjectkey")
+data.clean<-data[data$numTRs>=600,] # we go from 9,132 to 8,293 at this step
+
+# Remove participants based on booleans from ABCD
+abcd_imgincl01 <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/abcd_imgincl01.csv")
+abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$eventnam=="baseline_year_1_arm_1",]
+abcd_imgincl01 <- abcd_imgincl01[!abcd_imgincl01$visit=="",] # start here with 11,663 (8,287 of the 9,132 set)
+abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_t1w_include==1,] # down to 11,124 (8,045 of the 9,132 set)
[…]

### 2022-06-10 CopiesOfCuiRepScripts/CuiColorMap.R
PFNs and Cognition Replication of Cui et al. 2020

@@ -1,0 +1,24 @@
+"#7499C2", 4
+"#7499C2", 13
+"#AF33AD", 10
+"#F5BA2E", 15
+"#7499C2", 2
+"#AF33AD", 6
+"#7499C2", 11
+"#E443FF", 7
+"#E76178", 8
+"#4E31A8", 16
+"#E76178", 12
+"#00A131", 14
+"#00A131", 5
+"#E76178", 1
+"#F5BA2E", 17
+"#F5BA2E", 3
+"#E443FF" 9
+
+
+
+
+
+
+

### 2022-06-10 CopiesOfCuiRepScripts/CuiRep_Fig6.R

@@ -1,0 +1,167 @@
+
+# This script has been adapted by ASK to recreate Figure 6 from Cui et al. 2020 using ABCD data
+
+library('R.matlab');
+library('mgcv');
+library('ggplot2');
+library('visreg');
+library('ggtext')
+
+# ProjectFolder <- '/data/jux/BBL/projects/pncSingleFuncParcel/Replication';
+# Behavior <- read.csv(paste0(ProjectFolder, '/data/n693_Behavior_20181219.csv'));
+# Behavior_New <- data.frame(BBLID = Behavior$bblid);
+# Behavior_New$AgeYears <- as.numeric(Behavior$ageAtScan1/12);
+# Motion <- (Behavior$restRelMeanRMSMotion + Behavior$nbackRelMeanRMSMotion + Behavior$idemoRelMeanRMSMotion)/3;
+# Behavior_New$Motion <- as.numeric(Motion);
+# Behavior_New$Sex_factor <- as.factor(Behavior$sex);
+# Behavior_New$F1_Exec_Comp_Res_Accuracy <- as.numeric(Behavior$F1_Exec_Comp_Res_Accuracy);
+# AtlasLoading_Folder <- paste0(ProjectFolder, '/Revision/SingleParcellation/SingleAtlas_Analysis/FinalAtlasLoading');
+# 
+# SubjectsQuantity = 693;
+# FeaturesQuantity = 17734;
+# # Extract Loading
+# Data_Size <- SubjectsQuantity * FeaturesQuantity * 17;
+# Data_All <- matrix(0, 1, Data_Size);
+# dim(Data_All) <- c(SubjectsQuantity, FeaturesQuantity, 17);
+# BBLID <- Behavior_New$BBLID;
+# for (i in c(1:length(BBLID)))
+# {
+#   print(i);
+#   AtlasLoading_File <- paste0(AtlasLoading_Folder, '/', as.character(BBLID[i]), '.mat');
+#   Data <- readMat(AtlasLoading_File);
+#   Data_All[i,,] <- Data$sbj.AtlasLoading.NoMedialWall;
+# }
+# 
+# Gam_Z_Vector_Age_WholeNetworkSum <- matrix(0, 1, 17);
+# Gam_P_Vector_Age_WholeNetworkSum <- matrix(0, 1, 17);
+# Gam_P_Vector_Cognition_WholeNetworkSum <- matrix(0, 1, 17);
[…]

### 2022-06-10 CopiesOfCuiRepScripts/CuiRep_GetVariability.m

@@ -1,0 +1,98 @@
+%
+% For variability of probability atlas:
+% Using MADM=median(|x(i) - median(x)|) to calculate variability
+% For variability of hard label atlas:
+% See: 
+%   https://stats.stackexchange.com/questions/221332/variance-of-a-distribution-of-multi-level-categorical-data
+%
+
+clear
+WorkingFolder = '/data/jux/BBL/projects/pncSingleFuncParcel/Replication/Revision/SingleParcellation/SingleAtlas_Analysis';
+
+SubjectsFolder = '/share/apps/freesurfer/6.0.0/subjects/fsaverage5';
+surfML = '/data/jux/BBL/projects/pncSingleFuncParcel/Replication/data/SNR_Mask/subjects/fsaverage5/lh.Mask_SNR.label';
+mwIndVec_l = read_medial_wall_label(surfML);
+Index_l = setdiff([1:10242], mwIndVec_l); % 10,242 refers to vertices in fsaverage5 
+surfMR = '/data/jux/BBL/projects/pncSingleFuncParcel/Replication/data/SNR_Mask/subjects/fsaverage5/rh.Mask_SNR.label';
+mwIndVec_r = read_medial_wall_label(surfMR);
+Index_r = setdiff([1:10242], mwIndVec_r);
+
+%
+% Variability of probability atlas
+%
+LoadingFolder = [WorkingFolder '/FinalAtlasLoading'];
+DataCell = g_ls([LoadingFolder '/*.mat']);
+for i = 1:length(DataCell)
+  i
+  tmp = load(DataCell{i});
+  for j = 1:17
+    cmd = ['sbj_Loading_lh_Matrix_' num2str(j) '(i, :) = tmp.sbj_AtlasLoading_lh(j, :);'];
+    eval(cmd);
+    cmd = ['sbj_Loading_rh_Matrix_' num2str(j) '(i, :) = tmp.sbj_AtlasLoading_rh(j, :);'];
+    eval(cmd);
+  end
+end
+%
+Variability_Visualize_Folder = [WorkingFolder '/Variability_Visualize'];
+mkdir(Variability_Visualize_Folder);
+Variability_All_lh = zeros(17, 10242);
+Variability_All_rh = zeros(17, 10242);
+for m = 1:17
+  m
+  for n = 1:10242
+    % left hemi
+    cmd = ['tmp_data = sbj_Loading_lh_Matrix_' num2str(m) '(:, n);'];
+    eval(cmd);
[…]

### 2022-06-10 CopiesOfCuiRepScripts/CuiRep_Step_4th_Weight_Visualize_Workbench_EFAccuracy_RandomCV.m

@@ -1,0 +1,159 @@
+
+
+clear all
+
+% Add package to read NPY files into matlab
+addpath('/Users/askeller/Documents/npy-matlab/')
+
+% note: the coefs matrix is 10 rows (folds) x 1010004 (weights at each of 59,412 vertices for each of 17 networks)
+coefs = readNPY('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_Mar2922/all_network/thompson_PC1_coefs.npy');
+
+% Average over 10 folds
+coefs_avg = mean(coefs,1);
+
+
+
+% ReplicationFolder = '/data/jux/BBL/projects/pncSingleFuncParcel/Replication';
+% PredictionFolder = [ReplicationFolder '/Revision/PredictionAnalysis/AtlasLoading/'];
+% Results_Cell = g_ls([PredictionFolder '/2Fold_RandomCV_EFAccuracy/Time_*/Fold_*_Score.mat']);
+% for i = 1:length(Results_Cell)
+% tmp = load(Results_Cell{i});
+% w_Brain_EFAccuracy_AllModels(i, :) = tmp.w_Brain;
+% end
+%w_Brain_EFAccuracy = mean(w_Brain_EFAccuracy_AllModels);
+%VisualizeFolder = [PredictionFolder '/WeightVisualize_EFAccuracy_RandomCV'];
+%mkdir(VisualizeFolder);
+
+% SubjectsFolder = '/share/apps/freesurfer/6.0.0/subjects/fsaverage5';
+% % for surface data
+% surfML = '/data/jux/BBL/projects/pncSingleFuncParcel/Replication/data/SNR_Mask/subjects/fsaverage5/lh.Mask_SNR.label';
+% mwIndVec_l = read_medial_wall_label(surfML);
+% Index_l = setdiff([1:10242], mwIndVec_l);
+% surfMR = '/data/jux/BBL/projects/pncSingleFuncParcel/Replication/data/SNR_Mask/subjects/fsaverage5/rh.Mask_SNR.label';
+% mwIndVec_r = read_medial_wall_label(surfMR);
+% Index_r = setdiff([1:10242], mwIndVec_r);
+
+% load([PredictionFolder '/AtlasLoading_All_RemoveZero.mat']); % NonZeroIndex was here
+
+
+%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
[…]

### 2022-06-10 CopiesOfCuiRepScripts/Rep_SumWeights_EF.R

@@ -1,0 +1,177 @@
+# This is ASK's replication of Zaixu's script "Step_5th_SumWeights_EF.R" that 
+# will try to recapitulate Figure 7C in his 2020 Neuron paper showing the sum of 
+# the importance of topographic features by network. 
+
+
+library(R.matlab)
+library(ggplot2)
+
+
+#ResultsFolder = '/data/jux/BBL/projects/pncSingleFuncParcel/Replication/Revision';
+#PredictionFolder = paste0(ResultsFolder, '/PredictionAnalysis/AtlasLoading');
+WeightFolder = '/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_7C_SumLoadings/';
+Weight_EFAccuracy_Mat = readMat(paste0(WeightFolder, '/w_Brain_EFAccuracy_Matrix.mat'));
+Weight_EFAccuracy_Matrix = Weight_EFAccuracy_Mat$w.Brain.EFAccuracy.Matrix;
+
+#EFAccuracyEffect_Folder = paste0(ResultsFolder, '/GamAnalysis/AtlasLoading/CognitionEffects');
+# plot contributing weight for age prediction
+data <- data.frame(group = matrix(0, 34, 1));
+data$x <- matrix(0, 34, 1);
+data$y <- matrix(0, 34, 1);
+Pos_Weight <- matrix(0, 1, 17);
+for (i in c(1:17)){
+  EFAccuracyWeight_tmp = Weight_EFAccuracy_Matrix[i,];
+  data$group[i] = 'Below';
+  data$x[i] = i;
+  data$y[i] = sum(EFAccuracyWeight_tmp[which(EFAccuracyWeight_tmp > 0)]);
+  data$group[i + 17] = 'Above';
+  data$x[i + 17] = i;
+  data$y[i + 17] = sum(EFAccuracyWeight_tmp[which(EFAccuracyWeight_tmp < 0)]);
+  Pos_Weight[i] = data$y[i];
+}
+WeightSort <- sort(Pos_Weight, index.return = TRUE);
+Rank <- WeightSort$ix;
+data$x[1:17] <- data$x[1:17][Rank];
+data$y[1:17] <- data$y[1:17][Rank];
+data$x[18:34] <- data$x[18:34][Rank];
+data$y[18:34] <- data$y[18:34][Rank];
+data$x_New <- rbind(as.matrix(c(1:17)),as.matrix(c(1:17)));
+data$x_ <- as.character(data$x_New);
[…]

### 2022-06-10 CopiesOfCuiRepScripts/ViolinPlot_PFNvariability_CuiRep_FromOldLaptop.R

@@ -1,0 +1,70 @@
+# This code is copied and adapted for use with the ABCDFNETS data from Zaixu's script:
+# Step_10th_ViolinPlot_AtlasVariability_Loading.R (on the github pncSingleFuncParcel)
+
+library(R.matlab)
+library(ggplot2);
+
+ResultsFolder = '/Users/askeller/Documents/Kellernet_PrelimAnalysis/';
+AtlasFolder = paste0(ResultsFolder, 'SArank_PFNs/');
+Variability_Mat = readMat(paste0(ResultsFolder,'VariabilityByPFN_Trimmed.mat'));
+
+AtlasLabel_Mat = readMat(paste0(AtlasFolder, '/sbj_AtlasLabel_NoMedialWall_Keller.mat'));
+
+#Variability=as.matrix(Variability_Mat[1])
+
+AllData = data.frame(Variability = matrix(0, 59412, 1));
+AllData$Label = matrix(0, 59412, 1);
+for (i in c(1:59412))
+{
+  AllData$Variability[i] = Variability_Mat$Variability.All[i];
+  AllData$Label[i] = AtlasLabel_Mat$sbj.AtlasLabel.NoMedialWall[i];
+}
+AllData$Variability = as.numeric(AllData$Variability);
+AllData$Label = as.factor(AllData$Label);
+
+
+
+# NOTE: A.S.K ADDING A STEP HERE
+# In Zaixu's original version, this step was not present. I noticed that a lot of the variability values are exactly 0, and this is because a lot of the loading values are dropped to zero. We also are using fslr here which has 59K vertices, whereas Zaixu's version had far fewer. For now, I will eliminate vertices where the variability is exactly 0 (out to like 7 decimal places) since this very likely indicates the loading was zero for all subjects. 
+#AllData = AllData[AllData$Variability!=0.0000000,]
+AllData=AllData[complete.cases(AllData),]
+
+# Order the network by the median value 
+MedianValue = matrix(0, 1, 17);
+for (i in c(1:17)) {
+  ind = which(AllData$Label == i);
+  MedianValue[i] = median(AllData$Variability[ind],na.rm=TRUE);
+}
+tmp = sort(MedianValue, index.return = TRUE);
+
+
+ColorScheme = c("#E76178", "#7499C2", "#F5BA2E", "#7499C2", "#00A131",
[…]

### 2022-06-10 CopiesOfCuiRepScripts/variability_by_pfn3.m

@@ -1,0 +1,57 @@
+% This script will be used to replicate Cui et al. 2020 Neuron Figure 3B
+% (or at least prep the matrices we need to do so).
+
+
+clear all
+
+%file_pattern='/gpfs/fs001/cbica/projects/abcdfnets/results/SingleParcel_1by1/sub-NDARINV*/IndividualParcel_Final_sbj1_comp17_alphaS21_1_alphaL300_vxInfo1_ard0_eta0/final_UV.mat'
+file_pattern='/cbica/projects/abcdfnets/results/SingleParcel_1by1/sub-NDARINV*/IndividualParcel_Final_sbj1_comp17_alphaS21_1_alphaL300_vxInfo1_ard0_eta0/final_UV.mat'
+data_dir=dir(file_pattern);
+data_locations=fullfile({data_dir.folder}, {data_dir.name});
+
+% initialize matrices
+for eachNetwork1 = 1:17
+    eval(['sbj_by_vtx_network' num2str(eachNetwork1) ' = [];'])
+end
+
+
+% Get a separate subject x vertex matrix for each network
+for i = 1:length(data_locations)
+    i
+    UV=load(char(data_locations(i)));
+    V=UV.V; % The V matrix contains the loadings at each vertex by network
+    V=cell2mat(V);
+
+    % ASK is adding this for variability_by_pfn3 to see whether trimming
+    % these small loadings helps:
+
+    % apply ZC code from step 6th - subject AtlasLabel will have parcels for viz
+    V_Max = max(V);
+    trimInd = V ./ max(repmat(V_Max, size(V, 1), 1), eps) < 5e-2;
+    V(trimInd) = 0;
+    %sbj_AtlasLoading_NoMedialWall = V;
+    %[~, sbj_AtlasLabel_NoMedialWall] = max(sbj_AtlasLoading_NoMedialWall, [], 2);
+
+
+    % Loop through each network, get vtx x subj matrix, then transpose
+    for eachNetwork2 = 1:17
+        eval(['sbj_by_vtx_network' num2str(eachNetwork2) '=[sbj_by_vtx_network' num2str(eachNetwork2) ' V(:,eachNetwork2)];'])
+    end
+end
+
+
+% Loop through each network's subject x vertex matrix and calculate
+% the across-subject variability
+Variability_All = zeros(17, size(V,1)); % networks by vertices
+for m = 1:17
+    m
[…]

### 2022-06-10 CopiesOfCuiRepScripts/CuiRep_BarPlot.m
add bar plot script

@@ -1,0 +1,49 @@
+
+clear all
+
+z_vec = [-0.7272896 -3.0618619  3.2424142 -4.1576597  0.4844896  2.7263041  1.5161223  2.2195368 -0.2067699 -1.0122599 -1.1448722  1.2091494  2.3374685  1.1452890  3.4992115  1.0181162  4.2734299];
+z_vec_sorted = sort(z_vec);
+keep_p = [0 1 1 1 0 0 0 0 0 0 0 0 0 0 1 0 1];
+network_colors = [1 0.2 0.2; 0.4 0.6 0.8; 1 0.8 0.2; 0.4 0.6 0.8; 0 .4 0; 0.6 0 0.6; 1 0 0.8; 1 0.2 0.2; 1 0 0.8; 0.6 0 0.6; 0.4 0.6 0.8; 1 0.2 0.2; 0.4 0.6 0.8; 0 .4 0; 1 0.8 0.2; 0 0 0.6; 1 0.8 0.2];
+
+figure()
+for i = 1:17
+if keep_p(z_vec==z_vec_sorted(i))
+  bar(i,z_vec_sorted(i),'FaceColor',network_colors(z_vec==z_vec_sorted(i),1:3),'EdgeColor','w')
+hold on  
+else
+     bar(i,z_vec_sorted(i),'w','EdgeColor',network_colors(z_vec==z_vec_sorted(i),1:3))
+hold on  
+end
+end
+xticks([1:17])
+xticklabels({'4','2','11','10','1','9','5','16','14','12','7','8','13','6','3','15','17'})
+xlabel('Networks')
+ylabel('Cognition Association (Z)')
+axis([0 18 -4.5 6])
+
+
+%% SAME THING IN TEST SET
+
+clear all
+
+z_vec = [2.3579583 -1.3893710  3.0733065 -7.8620168  0.5033792  5.2102436 -0.7345963  0.9642072 -1.5014385  0.2726571  2.7748788 -0.4367185 -2.2333869  0.9093127  3.7563792  0.6383354  4.6654067];
+z_vec_sorted = sort(z_vec);
+keep_p = [0 0 1 1 0 1 0 0 0 0 0 0 0 0 1 0 1];
[…]

### 2022-08-30 Cui2020Rep_SumWeightsBarPlots.Rmd
supp fig S2
everything needed for supp fig S2

---
title: "Cui2020Rep_SumWeightsBarPlots"
output: html_document
date: '2022-08-30'
---

# This is ASK's replication of Zaixu's script "Step_5th_SumWeights_EF.R" that 
# will try to recapitulate Figure 7C in his 2020 Neuron paper showing the sum of 
# the importance of topographic features by network.

# load in libraries
```{r}
library(R.matlab)
library(ggplot2)
```

# PC1 - Discovery Sample
```{r}
# Set the folder with the results (note: results come from CuiRep_Step_4th_Weight_Visualize_Workbench_EFAccuracy_RandomCV.m)
WeightFolder = '/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_7C_SumLoadings/';
Weight_EFAccuracy_Mat = readMat(paste0(WeightFolder, '/w_Brain_PC1_testA.mat'));
Weight_EFAccuracy_Matrix = Weight_EFAccuracy_Mat$w.Brain.EFAccuracy.Matrix; # this is a 17 networks x 59412 vertices matrix

# loop through each of the 17 networks, designate values above and below zero
# Negative weights go in the first 1-17 indices, positive weights in 18-34
data <- data.frame(group = matrix(0, 34, 1));
data$x <- matrix(0, 34, 1);
data$y <- matrix(0, 34, 1);
Pos_Weight <- matrix(0, 1, 17);
for (i in c(1:17)){
  EFAccuracyWeight_tmp = Weight_EFAccuracy_Matrix[i,];
  data$group[i] = 'Below';
  data$x[i] = i;
  data$y[i] = sum(EFAccuracyWeight_tmp[which(EFAccuracyWeight_tmp > 0)]);
  data$group[i + 17] = 'Above';
  data$x[i + 17] = i;
  data$y[i + 17] = sum(EFAccuracyWeight_tmp[which(EFAccuracyWeight_tmp < 0)]);
  Pos_Weight[i] = data$y[i];
}
WeightSort <- sort(Pos_Weight, index.return = TRUE); # sort based on the positive weights
Rank <- WeightSort$ix;
data$x[1:17] <- data$x[1:17][Rank];
data$y[1:17] <- data$y[1:17][Rank];
data$x[18:34] <- data$x[18:34][Rank];
data$y[18:34] <- data$y[18:34][Rank];
data$x_New <- rbind(as.matrix(c(1:17)),as.matrix(c(1:17)));
data$x_ <- as.character(data$x_New);

ColorScheme_PFNs_InOrder <-c("#E76178","#7499C2","#F5BA2E","#7499C2","#00A131","#AF33AD","#E443FF","#E76178","#E443FF","#AF33AD","#7499C2","#E76178","#7499C2","#00A131","#F5BA2E","#4E31A8","#F5BA2E")

ColorScheme_XAxis <- ColorScheme_PFNs_InOrder[Rank] # for the X axis, just need them in order once
ColorScheme_Fill_Manual <- c(ColorScheme_XAxis,ColorScheme_XAxis) # for the bar plot, need them repeated

Fig <- ggplot(data, aes(x=x_New, y=y, fill = x_, alpha = group)) +
  geom_bar(stat = "identity", colour = "#000000", width = 0.8) +
  scale_fill_manual(limits = data$x_, values = ColorScheme_Fill_Manual) +
  scale_alpha_manual(limits = c('Above', 'Below'), values = c(0.3, 1)) +
  labs(x = "Networks", y = expression("Sum of Weights")) + theme_classic() +
  theme(axis.text.x = element_text(size= 27, color = ColorScheme_XAxis),
        axis.text.y = element_text(size= 31, color = "black"),
        axis.title=element_text(size = 31)) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_x_discrete(limits = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12,
                              13, 14, 15, 16, 17),
                   labels = as.character(Rank))
Fig
ggsave('/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_7C_SumLoadings/PC1_testA_PredictionWeight_Sum_Bar.tiff', width = 19, height = 15, dpi = 600, units = "cm")
```

# PC2 - Discovery Sample
```{r}
# Set the folder with the results (note: results come from CuiRep_Step_4th_Weight_Visualize_Workbench_EFAccuracy_RandomCV.m)
WeightFolder = '/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_7C_SumLoadings/';
Weight_EFAccuracy_Mat = readMat(paste0(WeightFolder, '/w_Brain_PC2_testA.mat'));
Weight_EFAccuracy_Matrix = Weight_EFAccuracy_Mat$w.Brain.EFAccuracy.Matrix; # this is a 17 networks x 59412 vertices matrix

# loop through each of the 17 networks, designate values above and below zero
# Negative weights go in the first 1-17 indices, positive weights in 18-34
data <- data.frame(group = matrix(0, 34, 1));
data$x <- matrix(0, 34, 1);
data$y <- matrix(0, 34, 1);
Pos_Weight <- matrix(0, 1, 17);
for (i in c(1:17)){
  EFAccuracyWeight_tmp = Weight_EFAccuracy_Matrix[i,];
  data$group[i] = 'Below';
  data$x[i] = i;
  data$y[i] = sum(EFAccuracyWeight_tmp[which(EFAccuracyWeight_tmp > 0)]);
  data$group[i + 17] = 'Above';
  data$x[i + 17] = i;
  data$y[i + 17] = sum(EFAccuracyWeight_tmp[which(EFAccuracyWeight_tmp < 0)]);
  Pos_Weight[i] = data$y[i];
}
WeightSort <- sort(Pos_Weight, index.return = TRUE); # sort based on the positive weights
Rank <- WeightSort$ix;
data$x[1:17] <- data$x[1:17][Rank];
data$y[1:17] <- data$y[1:17][Rank];
data$x[18:34] <- data$x[18:34][Rank];
data$y[18:34] <- data$y[18:34][Rank];
data$x_New <- rbind(as.matrix(c(1:17)),as.matrix(c(1:17)));
data$x_ <- as.character(data$x_New);

ColorScheme_PFNs_InOrder <-c("#E76178","#7499C2","#F5BA2E","#7499C2","#00A131","#AF33AD","#E443FF","#E76178","#E443FF","#AF33AD","#7499C2","#E76178","#7499C2","#00A131","#F5BA2E","#4E31A8","#F5BA2E")

ColorScheme_XAxis <- ColorScheme_PFNs_InOrder[Rank] # for the X axis, just need them in order once
ColorScheme_Fill_Manual <- c(ColorScheme_XAxis,ColorScheme_XAxis) # for the bar plot, need them repeated

Fig <- ggplot(data, aes(x=x_New, y=y, fill = x_, alpha = group)) +
  geom_bar(stat = "identity", colour = "#000000", width = 0.8) +
  scale_fill_manual(limits = data$x_, values = ColorScheme_Fill_Manual) +
  scale_alpha_manual(limits = c('Above', 'Below'), values = c(0.3, 1)) +
  labs(x = "Networks", y = expression("Sum of Weights")) + theme_classic() +
  theme(axis.text.x = element_text(size= 27, color = ColorScheme_XAxis),
        axis.text.y = element_text(size= 31, color = "black"),
        axis.title=element_text(size = 31)) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_x_discrete(limits = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12,
                              13, 14, 15, 16, 17),
                   labels = as.character(Rank))
Fig
ggsave('/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_7C_SumLoadings/PC2_testA_PredictionWeight_Sum_Bar.tiff', width = 19, height = 15, dpi = 600, units = "cm")
```

# PC3 - Discovery Sample
```{r}
# Set the folder with the results (note: results come from CuiRep_Step_4th_Weight_Visualize_Workbench_EFAccuracy_RandomCV.m)
WeightFolder = '/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_7C_SumLoadings/';
Weight_EFAccuracy_Mat = readMat(paste0(WeightFolder, '/w_Brain_PC3_testA.mat'));
Weight_EFAccuracy_Matrix = Weight_EFAccuracy_Mat$w.Brain.EFAccuracy.Matrix; # this is a 17 networks x 59412 vertices matrix

# loop through each of the 17 networks, designate values above and below zero
# Negative weights go in the first 1-17 indices, positive weights in 18-34
data <- data.frame(group = matrix(0, 34, 1));
data$x <- matrix(0, 34, 1);
data$y <- matrix(0, 34, 1);
Pos_Weight <- matrix(0, 1, 17);
for (i in c(1:17)){
  EFAccuracyWeight_tmp = Weight_EFAccuracy_Matrix[i,];
  data$group[i] = 'Below';
  data$x[i] = i;
  data$y[i] = sum(EFAccuracyWeight_tmp[which(EFAccuracyWeight_tmp > 0)]);
  data$group[i + 17] = 'Above';
  data$x[i + 17] = i;
  data$y[i + 17] = sum(EFAccuracyWeight_tmp[which(EFAccuracyWeight_tmp < 0)]);
  Pos_Weight[i] = data$y[i];
}
WeightSort <- sort(Pos_Weight, index.return = TRUE); # sort based on the positive weights
Rank <- WeightSort$ix;
data$x[1:17] <- data$x[1:17][Rank];
data$y[1:17] <- data$y[1:17][Rank];
data$x[18:34] <- data$x[18:34][Rank];
data$y[18:34] <- data$y[18:34][Rank];
data$x_New <- rbind(as.matrix(c(1:17)),as.matrix(c(1:17)));
data$x_ <- as.character(data$x_New);

ColorScheme_PFNs_InOrder <-c("#E76178","#7499C2","#F5BA2E","#7499C2","#00A131","#AF33AD","#E443FF","#E76178","#E443FF","#AF33AD","#7499C2","#E76178","#7499C2","#00A131","#F5BA2E","#4E31A8","#F5BA2E")

ColorScheme_XAxis <- ColorScheme_PFNs_InOrder[Rank] # for the X axis, just need them in order once
ColorScheme_Fill_Manual <- c(ColorScheme_XAxis,ColorScheme_XAxis) # for the bar plot, need them repeated

Fig <- ggplot(data, aes(x=x_New, y=y, fill = x_, alpha = group)) +
  geom_bar(stat = "identity", colour = "#000000", width = 0.8) +
  scale_fill_manual(limits = data$x_, values = ColorScheme_Fill_Manual) +
  scale_alpha_manual(limits = c('Above', 'Below'), values = c(0.3, 1)) +
  labs(x = "Networks", y = expression("Sum of Weights")) + theme_classic() +
  theme(axis.text.x = element_text(size= 27, color = ColorScheme_XAxis),
        axis.text.y = element_text(size= 31, color = "black"),
        axis.title=element_text(size = 31)) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_x_discrete(limits = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12,
                              13, 14, 15, 16, 17),
                   labels = as.character(Rank))
Fig
ggsave('/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_7C_SumLoadings/PC3_testA_PredictionWeight_Sum_Bar.tiff', width = 19, height = 15, dpi = 600, units = "cm")
```

### 2022-08-30 Cui2020Rep_SumWeightsBarPlots.Rmd
plots figure S2

@@
 ```
+
+# PC1 - Replication Sample
+```{r}
+# Set the folder with the results (note: results come from CuiRep_Step_4th_Weight_Visualize_Workbench_EFAccuracy_RandomCV.m)
+WeightFolder = '/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_7C_SumLoadings/';
+Weight_EFAccuracy_Mat = readMat(paste0(WeightFolder, '/w_Brain_PC1_testB.mat'));
+Weight_EFAccuracy_Matrix = Weight_EFAccuracy_Mat$w.Brain.EFAccuracy.Matrix; # this is a 17 networks x 59412 vertices matrix
+
+# loop through each of the 17 networks, designate values above and below zero
+# Negative weights go in the first 1-17 indices, positive weights in 18-34
+data <- data.frame(group = matrix(0, 34, 1));
+data$x <- matrix(0, 34, 1);
+data$y <- matrix(0, 34, 1);
+Pos_Weight <- matrix(0, 1, 17);
+for (i in c(1:17)){
+  EFAccuracyWeight_tmp = Weight_EFAccuracy_Matrix[i,];
+  data$group[i] = 'Below';
+  data$x[i] = i;
+  data$y[i] = sum(EFAccuracyWeight_tmp[which(EFAccuracyWeight_tmp > 0)]);
+  data$group[i + 17] = 'Above';
+  data$x[i + 17] = i;
+  data$y[i + 17] = sum(EFAccuracyWeight_tmp[which(EFAccuracyWeight_tmp < 0)]);
+  Pos_Weight[i] = data$y[i];
+}
+WeightSort <- sort(Pos_Weight, index.return = TRUE); # sort based on the positive weights
+Rank <- WeightSort$ix;
+data$x[1:17] <- data$x[1:17][Rank];
+data$y[1:17] <- data$y[1:17][Rank];
+data$x[18:34] <- data$x[18:34][Rank];
+data$y[18:34] <- data$y[18:34][Rank];
+data$x_New <- rbind(as.matrix(c(1:17)),as.matrix(c(1:17)));
+data$x_ <- as.character(data$x_New);
+
+ColorScheme_PFNs_InOrder <-c("#E76178","#7499C2","#F5BA2E","#7499C2","#00A131","#AF33AD","#E443FF","#E76178","#E443FF","#AF33AD","#7499C2","#E76178","#7499C2","#00A131","#F5BA2E","#4E31A8","#F5BA2E")
+
+ColorScheme_XAxis <- ColorScheme_PFNs_InOrder[Rank] # for the X axis, just need them in order once
+ColorScheme_Fill_Manual <- c(ColorScheme_XAxis,ColorScheme_XAxis) # for the bar plot, need them repeated
+
+Fig <- ggplot(data, aes(x=x_New, y=y, fill = x_, alpha = group)) +
+  geom_bar(stat = "identity", colour = "#000000", width = 0.8) +
+  scale_fill_manual(limits = data$x_, values = ColorScheme_Fill_Manual) +
+  scale_alpha_manual(limits = c('Above', 'Below'), values = c(0.3, 1)) +
+  labs(x = "Networks", y = expression("Sum of Weights")) + theme_classic() +
+  theme(axis.text.x = element_text(size= 27, color = ColorScheme_XAxis),
+        axis.text.y = element_text(size= 31, color = "black"),
+        axis.title=element_text(size = 31)) +
+  theme(legend.position = "none") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  scale_x_discrete(limits = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12,
+                              13, 14, 15, 16, 17),
+                   labels = as.character(Rank))
+Fig
+ggsave('/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_7C_SumLoadings/PC1_testB_PredictionWeight_Sum_Bar.tiff', width = 19, height = 15, dpi = 600, units = "cm")
+```
+
+# PC2 - Replication Sample
+```{r}
+# Set the folder with the results (note: results come from CuiRep_Step_4th_Weight_Visualize_Workbench_EFAccuracy_RandomCV.m)
+WeightFolder = '/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_7C_SumLoadings/';
+Weight_EFAccuracy_Mat = readMat(paste0(WeightFolder, '/w_Brain_PC2_testB.mat'));
+Weight_EFAccuracy_Matrix = Weight_EFAccuracy_Mat$w.Brain.EFAccuracy.Matrix; # this is a 17 networks x 59412 vertices matrix
+
+# loop through each of the 17 networks, designate values above and below zero
+# Negative weights go in the first 1-17 indices, positive weights in 18-34
+data <- data.frame(group = matrix(0, 34, 1));
+data$x <- matrix(0, 34, 1);
+data$y <- matrix(0, 34, 1);
+Pos_Weight <- matrix(0, 1, 17);
+for (i in c(1:17)){
+  EFAccuracyWeight_tmp = Weight_EFAccuracy_Matrix[i,];
+  data$group[i] = 'Below';
+  data$x[i] = i;
+  data$y[i] = sum(EFAccuracyWeight_tmp[which(EFAccuracyWeight_tmp > 0)]);
+  data$group[i + 17] = 'Above';
+  data$x[i + 17] = i;
+  data$y[i + 17] = sum(EFAccuracyWeight_tmp[which(EFAccuracyWeight_tmp < 0)]);
+  Pos_Weight[i] = data$y[i];
+}
+WeightSort <- sort(Pos_Weight, index.return = TRUE); # sort based on the positive weights
+Rank <- WeightSort$ix;
+data$x[1:17] <- data$x[1:17][Rank];
+data$y[1:17] <- data$y[1:17][Rank];
+data$x[18:34] <- data$x[18:34][Rank];
+data$y[18:34] <- data$y[18:34][Rank];
+data$x_New <- rbind(as.matrix(c(1:17)),as.matrix(c(1:17)));
+data$x_ <- as.character(data$x_New);
+
+ColorScheme_PFNs_InOrder <-c("#E76178","#7499C2","#F5BA2E","#7499C2","#00A131","#AF33AD","#E443FF","#E76178","#E443FF","#AF33AD","#7499C2","#E76178","#7499C2","#00A131","#F5BA2E","#4E31A8","#F5BA2E")
+
+ColorScheme_XAxis <- ColorScheme_PFNs_InOrder[Rank] # for the X axis, just need them in order once
+ColorScheme_Fill_Manual <- c(ColorScheme_XAxis,ColorScheme_XAxis) # for the bar plot, need them repeated
+
+Fig <- ggplot(data, aes(x=x_New, y=y, fill = x_, alpha = group)) +
+  geom_bar(stat = "identity", colour = "#000000", width = 0.8) +
+  scale_fill_manual(limits = data$x_, values = ColorScheme_Fill_Manual) +
+  scale_alpha_manual(limits = c('Above', 'Below'), values = c(0.3, 1)) +
+  labs(x = "Networks", y = expression("Sum of Weights")) + theme_classic() +
+  theme(axis.text.x = element_text(size= 27, color = ColorScheme_XAxis),
+        axis.text.y = element_text(size= 31, color = "black"),
+        axis.title=element_text(size = 31)) +
+  theme(legend.position = "none") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  scale_x_discrete(limits = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12,
+                              13, 14, 15, 16, 17),
+                   labels = as.character(Rank))
+Fig
+ggsave('/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_7C_SumLoadings/PC2_testB_PredictionWeight_Sum_Bar.tiff', width = 19, height = 15, dpi = 600, units = "cm")
+```
+
+# PC3 - Replication Sample
+```{r}
+# Set the folder with the results (note: results come from CuiRep_Step_4th_Weight_Visualize_Workbench_EFAccuracy_RandomCV.m)
+WeightFolder = '/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_7C_SumLoadings/';
+Weight_EFAccuracy_Mat = readMat(paste0(WeightFolder, '/w_Brain_PC3_testB.mat'));
+Weight_EFAccuracy_Matrix = Weight_EFAccuracy_Mat$w.Brain.EFAccuracy.Matrix; # this is a 17 networks x 59412 vertices matrix
+
+# loop through each of the 17 networks, designate values above and below zero
+# Negative weights go in the first 1-17 indices, positive weights in 18-34
+data <- data.frame(group = matrix(0, 34, 1));
+data$x <- matrix(0, 34, 1);
+data$y <- matrix(0, 34, 1);
+Pos_Weight <- matrix(0, 1, 17);
+for (i in c(1:17)){
+  EFAccuracyWeight_tmp = Weight_EFAccuracy_Matrix[i,];
+  data$group[i] = 'Below';
+  data$x[i] = i;
+  data$y[i] = sum(EFAccuracyWeight_tmp[which(EFAccuracyWeight_tmp > 0)]);
+  data$group[i + 17] = 'Above';
+  data$x[i + 17] = i;
+  data$y[i + 17] = sum(EFAccuracyWeight_tmp[which(EFAccuracyWeight_tmp < 0)]);
+  Pos_Weight[i] = data$y[i];
+}
+WeightSort <- sort(Pos_Weight, index.return = TRUE); # sort based on the positive weights
+Rank <- WeightSort$ix;
+data$x[1:17] <- data$x[1:17][Rank];
+data$y[1:17] <- data$y[1:17][Rank];
+data$x[18:34] <- data$x[18:34][Rank];
+data$y[18:34] <- data$y[18:34][Rank];
+data$x_New <- rbind(as.matrix(c(1:17)),as.matrix(c(1:17)));
+data$x_ <- as.character(data$x_New);
+
+ColorScheme_PFNs_InOrder <-c("#E76178","#7499C2","#F5BA2E","#7499C2","#00A131","#AF33AD","#E443FF","#E76178","#E443FF","#AF33AD","#7499C2","#E76178","#7499C2","#00A131","#F5BA2E","#4E31A8","#F5BA2E")
+
+ColorScheme_XAxis <- ColorScheme_PFNs_InOrder[Rank] # for the X axis, just need them in order once
+ColorScheme_Fill_Manual <- c(ColorScheme_XAxis,ColorScheme_XAxis) # for the bar plot, need them repeated
+
+Fig <- ggplot(data, aes(x=x_New, y=y, fill = x_, alpha = group)) +
+  geom_bar(stat = "identity", colour = "#000000", width = 0.8) +
+  scale_fill_manual(limits = data$x_, values = ColorScheme_Fill_Manual) +
+  scale_alpha_manual(limits = c('Above', 'Below'), values = c(0.3, 1)) +
+  labs(x = "Networks", y = expression("Sum of Weights")) + theme_classic() +
+  theme(axis.text.x = element_text(size= 27, color = ColorScheme_XAxis),
+        axis.text.y = element_text(size= 31, color = "black"),
+        axis.title=element_text(size = 31)) +
+  theme(legend.position = "none") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  scale_x_discrete(limits = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12,
+                              13, 14, 15, 16, 17),
+                   labels = as.character(Rank))
+Fig
+ggsave('/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_7C_SumLoadings/PC3_testB_PredictionWeight_Sum_Bar.tiff', width = 19, height = 15, dpi = 600, units = "cm")
+```

### 2022-08-31 transform_model_coefficients_to_sum_weights.m
Delete transform_model_coefficients_to_sum_weights.m

@@ -1,166 +1,0 @@
-%% PC1 - test in subsample A (Discovery)
-
-clear all
-
-% note: the coefs matrix is 1010004 (weights at each of 59,412 vertices for each of 17 networks)
-coefs = load('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/all_network/thompson_PC1_coefs_testA.mat');
-coefs = coefs.PC1_testA;
-
-VertexQuantity = 59412; % 17734;
-
-w_Brain_EFAccuracy_Abs = abs(coefs); %abs(w_Brain_EFAccuracy);
-[~, Sorted_IDs] = sort(w_Brain_EFAccuracy_Abs);
-w_Brain_EFAccuracy_FirstPercent = w_Brain_EFAccuracy_Abs;
-w_Brain_EFAccuracy_FirstPercent(Sorted_IDs(1:round(length(Sorted_IDs) * 0.75))) = 0;
-
-
-% Absolute sum weights
-w_Brain_EFAccuracy_All = zeros(1, VertexQuantity*17);
-w_Brain_EFAccuracy_All(w_Brain_EFAccuracy_FirstPercent>0) = coefs(w_Brain_EFAccuracy_FirstPercent>0);
-
-% Display weight of all regions
-for i = 1:17
-    w_Brain_EFAccuracy_Matrix(i, :) = w_Brain_EFAccuracy_All([(i - 1) * VertexQuantity + 1 : i * VertexQuantity]);
-end
-save(['/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_7C_SumLoadings/w_Brain_PC1_testA.mat'], 'w_Brain_EFAccuracy_Matrix');
-
-
-
-%% PC 2 - test in subsample A (Discovery)
-
-clear all
-
-% note: the coefs matrix is 1010004 (weights at each of 59,412 vertices for each of 17 networks)
-coefs = load('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/all_network/thompson_PC2_coefs_testA.mat');
-coefs = coefs.PC2_testA;
-
-VertexQuantity = 59412; % 17734;
-
-% Display the weight of the first 25% regions with the highest absolute weight
[…]

### 2022-08-31 predict_haufe.py
Delete predict_haufe.py

@@ -1,73 +1,0 @@
-import glob
-import h5py
-import numpy as np
-import os
-import pandas as pd
-from sklearn.linear_model import RidgeCV
-from sklearn.model_selection import GroupKFold
-from sklearn.linear_model import LinearRegression
-from sklearn import preprocessing
-import sys
-from scipy.stats import pearsonr
-
-"""
-hi. this is going to run ridge regression, you basically just need:
-
-working_dir: where you want your results saved, does not have to exist, we will make it
-feature_path: path to the actual features, should be a subject x features npy array
-phenotype_path: path to a csv with the to-be-predicted values
-phenotype_name: str of name of column in phenotype_path you want
-control_path: path to csv, regress these features from the features within each fold
-fold_group: most datasets have siblings/twins, represented as a family ID column, this names that column and prevents them from being split in train/test
-"""
-folds = 10
-working_dir = sys.argv[1]
-os.makedirs(working_dir,exist_ok=True)
-feature_path = sys.argv[2] 
-phenotype_path = sys.argv[3] 
-phenotype_name = sys.argv[4] #'thompson_PC1'
-control_path = sys.argv[5]
-fold_group = sys.argv[6]
-"""
-load the subject measures you want to control for
-"""
-phenotypes_control = pd.read_csv(control_path)
-"""
-load in all the feature weights
-"""
-features = np.load(feature_path).astype(np.float16)
-"""
-this is adapted from pennlinckit.utils.predict
-"""
-model_cv = GroupKFold(n_splits=folds)
-targets = pd.read_csv(phenotype_path)[phenotype_name].values.astype(np.float16)
-fold_group = pd.read_csv(phenotype_path)[fold_group].values.astype(np.float16)
-np.save('/{0}/{1}_targets.npy'.format(working_dir,phenotype_name),targets)
-assert targets.shape[0] == features.shape[0]
-prediction = np.zeros((targets.shape))
-coefs = np.zeros((folds,features.shape[1]))
-featimp_haufe = np.zeros((folds,features.shape[1]))
-alphas = np.zeros((folds))
-fold = 0
-for train, test in model_cv.split(features,targets,fold_group):
-    x_train,y_train,x_test,y_test = features[train].copy(),targets[train].copy(),features[test].copy(),targets[test].copy() #split up the data by train/test
[…]

### 2022-08-31 All_PFNs_size.m
Delete All_PFNs_size.m

@@ -1,58 +1,0 @@
-%file_pattern='/gpfs/fs001/cbica/projects/abcdfnets/results/SingleParcel_1by1/sub-NDARINV*/IndividualParcel_Final_sbj1_comp17_alphaS21_1_alphaL300_vxInfo1_ard0_eta0/final_UV.mat'
-file_pattern='/Users/ariellekeller/Documents/CubicMounts/sub-NDARINV*/IndividualParcel_Final_sbj1_comp17_alphaS21_1_alphaL300_vxInfo1_ard0_eta0/final_UV.mat'
-data_dir=dir(file_pattern);
-data_locations=fullfile({data_dir.folder}, {data_dir.name});
-
-% initialize table
-df=cell(length(data_locations),2);
-
-for i = 1:length(data_locations)
-	UV=load(char(data_locations(i)));
-	V=UV.V;
-	V2=V{:};
-% 	FP1=sum(V2(:,3));
-% 	FP2=sum(V2(:,15));
-% 	FP3=sum(V2(:,17));
-% 	FP_tot=FP1+FP2+FP3;
-	stringsplit=split(char(data_locations(i)),'/');
-	subjname=stringsplit(6);
-	df(i,1)=subjname;
-    for eachNetwork = 1:17
-	df(i,eachNetwork+1)=num2cell(sum(V2(:,eachNetwork)));
-    end
-	i
-end
-writetable(cell2table(df),'~/All_PFN_sizes_Rest_030722.csv')
-	
-
-
-
-
-%% doing this again for resting state only PFNs, but on cubic
-
-%file_pattern='/gpfs/fs001/cbica/projects/abcdfnets/results/SingleParcel_1by1/sub-NDARINV*/IndividualParcel_Final_sbj1_comp17_alphaS21_1_alphaL300_vxInfo1_ard0_eta0/final_UV.mat'
-file_pattern='/cbica/projects/abcdfnets/results/SingleParcel_1by1_Rest/sub-NDARINV*/IndividualParcel_Final_sbj1_comp17_alphaS21_1_alphaL300_vxInfo1_ard0_eta0/final_UV.mat'
-data_dir=dir(file_pattern);
-data_locations=fullfile({data_dir.folder}, {data_dir.name});
-
-% initialize table
-df=cell(length(data_locations),2);
-
-for i = 1:length(data_locations)
-	UV=load(char(data_locations(i)));
-	V=UV.V;
[…]

### 2022-08-31 SArank_by_PFN_workbench.R
Delete SArank_by_PFN_workbench.R

@@ -1,30 +1,0 @@
-
-
-library(gifti)
-library(R.matlab)
-library(RNifti)
-library(ciftiTools)
-ciftiTools.setOption('wb_path', '/Users/askeller/Documents/workbench/')
-library(ggplot2)
-
-PFNs_hardparcel<-read_cifti('/Users/askeller/Documents/Kellernet_PrelimAnalysis/hardparcel_group.dscalar.nii')
-map_SArank_lh <- PFNs_hardparcel$data$cortex_left
-map_SArank_rh <- PFNs_hardparcel$data$cortex_right
-
-SArank_byPFN <- read.csv('/Users/askeller/Documents/Kellernet_PrelimAnalysis/SpinTests/SArank_by_PFN.csv');
-SArank_byPFN <- SArank_byPFN$meanRank
-
-for (PFN in 1:17) {
-  map_SArank_lh[map_SArank_lh==PFN,1]=SArank_byPFN[PFN]
-  map_SArank_rh[map_SArank_rh==PFN,1]=SArank_byPFN[PFN]
-}
-
-PFNs_hardparcel_SArank <- PFNs_hardparcel
-
-PFNs_hardparcel_SArank$data$cortex_left <- map_SArank_lh
-PFNs_hardparcel_SArank$data$cortex_right <- map_SArank_rh
-
-write_cifti(PFNs_hardparcel_SArank,'/Users/askeller/Documents/Kellernet_PrelimAnalysis/PFNs_hardparcel_SArank')
-
-
-

### 2022-08-31 check_whether_families_cross_matched_samples.R
Delete check_whether_families_cross_matched_samples.R

@@ -1,10 +1,0 @@
-
-
-data<-read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/data_for_ridge_031822.csv")
-
-familyIDs_group1 <- data[data$matched_group==1,]$rel_family_id
-familyIDs_group2 <- data[data$matched_group==2,]$rel_family_id
-
-intersect(familyIDs_group1,familyIDs_group2)
-
-sum(familyIDs_group1==473)

### 2022-08-31 compare_predicted_actual_matchedsamples_clean.m
Delete compare_predicted_actual_matchedsamples_clean.m

@@ -1,277 +1,0 @@
-
-clear all
-
-% Add package to read NPY files into matlab
-addpath('/Users/askeller/Documents/npy-matlab/')
-
-% Load in prediction results
-folder_name='/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/all_network';
-file_name_pred1_samp1='thompson_PC1_prediction_testA.npy';
-file_name_pred2_samp1='thompson_PC2_prediction_testA.npy';
-file_name_pred3_samp1='thompson_PC3_prediction_testA.npy';
-file_name_pred1_samp2='thompson_PC1_prediction_testB.npy';
-file_name_pred2_samp2='thompson_PC2_prediction_testB.npy';
-file_name_pred3_samp2='thompson_PC3_prediction_testB.npy';
-pred_PC1_samp1 = readNPY([folder_name '/' file_name_pred1_samp1]);
-pred_PC2_samp1 = readNPY([folder_name '/' file_name_pred2_samp1]);
-pred_PC3_samp1 = readNPY([folder_name '/' file_name_pred3_samp1]);
-pred_PC1_samp2 = readNPY([folder_name '/' file_name_pred1_samp2]);
-pred_PC2_samp2 = readNPY([folder_name '/' file_name_pred2_samp2]);
-pred_PC3_samp2 = readNPY([folder_name '/' file_name_pred3_samp2]);
-
-% put predictions on same scale as actual
-pred_PC1_samp1 = zscore(pred_PC1_samp1);
-pred_PC2_samp1 = zscore(pred_PC2_samp1);
-pred_PC3_samp1 = zscore(pred_PC3_samp1);
-pred_PC1_samp2 = zscore(pred_PC1_samp2);
-pred_PC2_samp2 = zscore(pred_PC2_samp2);
-pred_PC3_samp2 = zscore(pred_PC3_samp2);
-
-% fourth column has the matched_group
-data_for_ridge=xlsread('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/data_for_ridge_081822.xls');
-
-% Load in actual cognitive scores
-actual_PC1 = data_for_ridge(:,1);
-actual_PC2 = data_for_ridge(:,2);
[…]

### 2022-08-31 compare_predicted_actual_matchedsamples.m
Delete compare_predicted_actual_matchedsamples.m

@@ -1,277 +1,0 @@
-
-clear all
-
-% Add package to read NPY files into matlab
-addpath('/Users/askeller/Documents/npy-matlab/')
-
-% Load in prediction results
-folder_name='/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/all_network';
-file_name_pred1_samp1='thompson_PC1_prediction_testA.npy';
-file_name_pred2_samp1='thompson_PC2_prediction_testA.npy';
-file_name_pred3_samp1='thompson_PC3_prediction_testA.npy';
-file_name_pred1_samp2='thompson_PC1_prediction_testB.npy';
-file_name_pred2_samp2='thompson_PC2_prediction_testB.npy';
-file_name_pred3_samp2='thompson_PC3_prediction_testB.npy';
-pred_PC1_samp1 = readNPY([folder_name '/' file_name_pred1_samp1]);
-pred_PC2_samp1 = readNPY([folder_name '/' file_name_pred2_samp1]);
-pred_PC3_samp1 = readNPY([folder_name '/' file_name_pred3_samp1]);
-pred_PC1_samp2 = readNPY([folder_name '/' file_name_pred1_samp2]);
-pred_PC2_samp2 = readNPY([folder_name '/' file_name_pred2_samp2]);
-pred_PC3_samp2 = readNPY([folder_name '/' file_name_pred3_samp2]);
-
-% put predictions on same scale as actual
-pred_PC1_samp1 = zscore(pred_PC1_samp1);
-pred_PC2_samp1 = zscore(pred_PC2_samp1);
-pred_PC3_samp1 = zscore(pred_PC3_samp1);
-pred_PC1_samp2 = zscore(pred_PC1_samp2);
-pred_PC2_samp2 = zscore(pred_PC2_samp2);
-pred_PC3_samp2 = zscore(pred_PC3_samp2);
-
-% fourth column has the matched_group
-data_for_ridge=xlsread('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/data_for_ridge_081822.xls');
-
-% Load in actual cognitive scores
-actual_PC1 = data_for_ridge(:,1);
-actual_PC2 = data_for_ridge(:,2);
[…]

### 2022-08-31 convert_numpy_arrays_to_mats.py
Delete convert_numpy_arrays_to_mats.py

@@ -1,27 +1,0 @@
-import numpy as np
-from scipy.io import savemat
-
-PC1_testA=np.load('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/all_network/thompson_PC1_coefs_testA.npy')
-mdic={"PC1_testA": PC1_testA}
-savemat('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/all_network/thompson_PC1_coefs_testA.mat',mdic)
-
-PC2_testA=np.load('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/all_network/thompson_PC2_coefs_testA.npy')
-mdic={"PC2_testA": PC2_testA}
-savemat('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/all_network/thompson_PC2_coefs_testA.mat',mdic)
-
-PC3_testA=np.load('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/all_network/thompson_PC3_coefs_testA.npy')
-mdic={"PC3_testA": PC3_testA}
-savemat('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/all_network/thompson_PC3_coefs_testA.mat',mdic)
-
-
-PC1_testB=np.load('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/all_network/thompson_PC1_coefs_testB.npy')
-mdic={"PC1_testB": PC1_testB}
-savemat('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/all_network/thompson_PC1_coefs_testB.mat',mdic)
-
-PC2_testB=np.load('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/all_network/thompson_PC2_coefs_testB.npy')
-mdic={"PC2_testB": PC2_testB}
-savemat('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/all_network/thompson_PC2_coefs_testB.mat',mdic)
-
[…]

### 2022-08-31 get_pred_acc_by_PFN.m
Delete get_pred_acc_by_PFN.m

@@ -1,367 +1,0 @@
-%% generate the brainmaps for prediction accuracy within each network.
-
-clear all
-
-% Add package to read NPY files into matlab
-addpath('/Users/askeller/Documents/npy-matlab/')
-
-% fourth column has the matched_group
-data_for_ridge=xlsread('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/data_for_ridge_081822.xls');
-
-% Load in actual cognitive scores
-actual_PC1 = data_for_ridge(:,1);
-actual_PC2 = data_for_ridge(:,2);
-actual_PC3 = data_for_ridge(:,3);
-
-% split data out by matched group
-actual_PC1_samp1 = actual_PC1(data_for_ridge(:,4)==1);
-actual_PC1_samp2 = actual_PC1(data_for_ridge(:,4)==2);
-actual_PC2_samp1 = actual_PC2(data_for_ridge(:,4)==1);
-actual_PC2_samp2 = actual_PC2(data_for_ridge(:,4)==2);
-actual_PC3_samp1 = actual_PC3(data_for_ridge(:,4)==1);
-actual_PC3_samp2 = actual_PC3(data_for_ridge(:,4)==2);
-
-% decision was to combine across the samples, so we will concatenate:
-actual_PC1 = [actual_PC1_samp1; actual_PC1_samp2];
-actual_PC2 = [actual_PC2_samp1; actual_PC2_samp2];
-actual_PC3 = [actual_PC3_samp1; actual_PC3_samp2];
-
-
-% matrix to collect R values by PFN
-Rvals_byPFN = zeros(17,3);
-
-
-% loop through each PFN and calculate the R value
-for eachPFN = 0:16
-
-eval(['folder_name=''/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/' num2str(eachPFN) '_network'';'])
-
-% Load the predicted cognitive scores from the ridge regression
-file_name_pred1_samp1='thompson_PC1_prediction_testA.npy';
-file_name_pred2_samp1='thompson_PC2_prediction_testA.npy';
-file_name_pred3_samp1='thompson_PC3_prediction_testA.npy';
[…]

### 2022-08-31 pred_acc_by_PFN_workbench.R
Delete pred_acc_by_PFN_workbench.R

@@ -1,47 +1,0 @@
-
-
-library(gifti)
-library(R.matlab)
-library(RNifti)
-library(ciftiTools)
-ciftiTools.setOption('wb_path', '/Users/askeller/Documents/workbench/')
-library(ggplot2)
-
-PFNs_hardparcel<-read_cifti('/Users/askeller/Documents/Kellernet_PrelimAnalysis/hardparcel_group.dscalar.nii')
-map_predacc_PC1_lh <- PFNs_hardparcel$data$cortex_left
-map_predacc_PC1_rh <- PFNs_hardparcel$data$cortex_right
-map_predacc_PC2_lh <- PFNs_hardparcel$data$cortex_left
-map_predacc_PC2_rh <- PFNs_hardparcel$data$cortex_right
-map_predacc_PC3_lh <- PFNs_hardparcel$data$cortex_left
-map_predacc_PC3_rh <- PFNs_hardparcel$data$cortex_right
-
-pred_acc <- readMat('/Users/askeller/Documents/Kellernet_PrelimAnalysis/pred_acc_by_PFN.mat');
-pred_acc <- pred_acc$Rvals.byPFN
-
-for (PFN in 1:17) {
-    map_predacc_PC1_lh[map_predacc_PC1_lh==PFN,1]=pred_acc[PFN,1]
-    map_predacc_PC2_lh[map_predacc_PC2_lh==PFN,1]=pred_acc[PFN,2]
-    map_predacc_PC3_lh[map_predacc_PC3_lh==PFN,1]=pred_acc[PFN,3]
-    
-    map_predacc_PC1_rh[map_predacc_PC1_rh==PFN,1]=pred_acc[PFN,1]
-    map_predacc_PC2_rh[map_predacc_PC2_rh==PFN,1]=pred_acc[PFN,2]
-    map_predacc_PC3_rh[map_predacc_PC3_rh==PFN,1]=pred_acc[PFN,3]
-}
-
-PFNs_hardparcel_PredAccPC1 <- PFNs_hardparcel
-PFNs_hardparcel_PredAccPC2 <- PFNs_hardparcel
-PFNs_hardparcel_PredAccPC3 <- PFNs_hardparcel
-
-PFNs_hardparcel_PredAccPC1$data$cortex_left <- map_predacc_PC1_lh
-PFNs_hardparcel_PredAccPC1$data$cortex_right <- map_predacc_PC1_rh
[…]

### 2022-08-31 get_thompson_scores.R
Delete get_thompson_scores.R

@@ -1,54 +1,0 @@
-
-# Load data
-nihtb<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/NihTB/abcd_tbss01.txt",header=TRUE)
-nihtb.baseline<-nihtb[nihtb$eventname=="baseline_year_1_arm_1",]
-lmt<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/Thomp/lmtp201.txt",header=TRUE)
-lmt.baseline<-lmt[lmt$eventname=="baseline_year_1_arm_1",]
-merged.data2 <- merge(nihtb.baseline,lmt.baseline[, c("subjectkey", setdiff(colnames(lmt.baseline),colnames(nihtb.baseline)))],by="subjectkey")
-ravlt<-read.table("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/Thomp/abcd_ps01.txt",header=TRUE)
-ravlt.baseline<-ravlt[ravlt$eventname=="baseline_year_1_arm_1",]
-combined.data <- merge(merged.data2,ravlt.baseline[, c("subjectkey", setdiff(colnames(ravlt.baseline),colnames(merged.data2)))],by="subjectkey")
-
-# Coerce data types
-combined.data$nihtbx_flanker_uncorrected <- as.numeric(combined.data$nihtbx_flanker_uncorrected)
-combined.data$nihtbx_picvocab_uncorrected <- as.numeric(combined.data$nihtbx_picvocab_uncorrected)
-combined.data$nihtbx_list_uncorrected <- as.numeric(combined.data$nihtbx_list_uncorrected)
-combined.data$nihtbx_pattern_uncorrected <- as.numeric(combined.data$nihtbx_pattern_uncorrected)
-combined.data$nihtbx_cardsort_uncorrected <- as.numeric(combined.data$nihtbx_cardsort_uncorrected)
-combined.data$nihtbx_picture_uncorrected <- as.numeric(combined.data$nihtbx_picture_uncorrected)
-combined.data$nihtbx_reading_uncorrected <- as.numeric(combined.data$nihtbx_reading_uncorrected)
-combined.data$lmt_scr_perc_correct <- as.numeric(combined.data$lmt_scr_perc_correct)
-combined.data$pea_ravlt_sd_trial_i_tc <- as.numeric(combined.data$pea_ravlt_sd_trial_i_tc)
[…]

### 2022-08-31 cubic_scripts/Individualize_ciftiSurf_resampledGroCon_justRest.m
Delete cubic_scripts directory

@@ -1,54 +1,0 @@
-function Individualize_ciftiSurf_resampledGroCon_justRest(subj)
-% Based on the group atlas, creating each subject's individual specific atlas
-ProjectFolder = '/cbica/projects/abcdfnets/results'
-
-ResultantFolder = [ProjectFolder '/SingleParcel_1by1_Rest'];
-mkdir(ResultantFolder);
-
-PrepDataFile = [ProjectFolder '/SingleParcellation/CreatePrepData.mat'];
-
-resId = 'IndividualParcel_Final';
-% 7/2/21 - subbed in filled initResamp instead of "initResamp.mat"
-initName = [ProjectFolder '/SingleParcellation/RobustInitialization_Cifti_Surf/initResamp.mat'];
-
-K = 17;
-
-% Use parameter in Hongming's NeuroImage paper, except for alphaL which we have expanded to account for the reduced smoothin in DCAN's pipeline
-alphaS21 = 1;
-alphaL = 300;
-vxI = 1;
-spaR = 1;
-ard = 0;
-iterNum = 30;
-eta = 0;
-calcGrp = 0;
-parforOn = 0;
-
-
-RawDataFolder = '/scratch/abcdfnets/nda-abcd-s3-downloader/August_2021_DL/derivatives/abcd-hcp-pipeline';
-subj_dtseries=['/scratch/abcdfnets/nda-abcd-s3-downloader/August_2021_DL/derivatives/abcd-hcp-pipeline/*/*/*/' subj '_ses-baselineYear1Arm1_task-rest_p2mm_masked.dtseries.nii*'];
-CiftiCell = g_ls(subj_dtseries)
-
-
-% Parcellate the subject - load filepath, subject name, and 
-[Fold, ~, ~] = fileparts(CiftiCell{1});
-FoldStr = strsplit(Fold, '/');
-ID_Str = FoldStr{8};
-ResultantFolder_I = [ResultantFolder '/' ID_Str];
-ResultFile_check = dir([ResultantFolder_I, '/**/final*.mat']);
-
-% check for existing directory
-if ~exist(ResultantFolder_I, 'dir')
-   mkdir(ResultantFolder_I);
-end
-IDMatFile = [ResultantFolder_I '/ID.mat'];
-save(IDMatFile, 'ID_Str');
-
-sbjListFile = [ResultantFolder_I '/sbjListAllFile.txt'];
[…]

### 2022-08-31 cubic_scripts/OffHours_wrapper_ASK.py

@@ -1,43 +1,0 @@
-import subprocess
-import time
-import datetime
-import os
-# grab some subjs as list
-my_file = open("/cbica/projects/abcdfnets/scripts/combined_PFNs_PGs/all_11878.txt", "r")
-content = my_file.read()
-content_list = content. split("\n")
-# remove last line (blank)
-content_list.pop()
-# feed em' in as subjects
-subjects = content_list
-# only first(last) 1048 ran?
-# anddd it died after another 2630 subjs. 2071 left to run.
-# and it died again (9/24/21). 1833 left to run
-#subjects = subjects[0:1833]
-# while there are more than 0 subjects left to run
-while len(subjects)>0:
-  # grab qsub info, get number of jobs being run
-  qstat = subprocess.check_output(['qstat'],shell=True).decode().split('/bin/python')[0]
-  que = len(qstat.split('\n'))-3
-  # if we are using less than 5 job slots (one is occupied by this script)
-  if que < 8:
-    # see if it is the weekend, 0, 1, 2, 3, and 4 are weekday, 5 and 6 are weekend
-    weekno = datetime.datetime.today().weekday()
-    # see if it is before 9 or after 5 
-    Hour = time.localtime().tm_hour 
-    # if weekend OR after 6 PM OR before 9 AM
-    if weekno > 4 or Hour < 9 or Hour > 16 :
-      newsub = subjects.pop()
-      # adding new condition: if gradient file does not exist
-      # gradFile='/cbica/projects/abcdfnets/results/wave_output/' + str(newsub) + '/' + str(newsub) + '_PG_LR_32k.dscalar.nii'
-      # if not os.path.exists(gradFile):
-      # submit job (if above conditions are met)
-      subprocess.run(["qsub","-l","h_vmem=15G,s_vmem=14G","qsubMatlab_ASK.sh",newsub])
-      time.sleep(60) #wait a minute
-    # added this to run 3 subjs (1 slot for this job) during ON hours
-    elif que < 4:
-      newsub = subjects.pop()
-      # gradFile='/cbica/projects/abcdfnets/results/wave_output/' + str(newsub) + '/' + str(newsub) + '_PG_LR_32k.dscalar.nii'
-      # if not os.path.exists(gradFile):
-      subprocess.run(["qsub","-l","h_vmem=15G,s_vmem=14G","qsubMatlab_ASK.sh",newsub])
-      time.sleep(60) #wait a minute

### 2022-08-31 cubic_scripts/OffHours_wrapper_ASK_arrays.py

@@ -1,60 +1,0 @@
-import subprocess
-import time
-import datetime
-import os
-def submit_array_job(script_path,array_start,array_end,RAM=4,threads=1):
-  """
-  submit and "array job", where you get a job with an ID from array_start to array_end
-  this lets you submit a script and iterate over an array in it.
-  in the script, use the function utils.get_sge_task_id to get the ID
-  """
-  sgedir = os.path.expanduser('~/sge/')
-  if os.path.isdir(sgedir) == False:
-    os.system('mkdir {0}'.format(sgedir))
-  command='qsub -t {0}-{1} -l h_vmem={2}G,s_vmem={2}G -pe threaded {3}\
-   -R y -N data -V -j y -b y -o ~/sge/ -e ~/sge/ python {4}'.format(array_start,array_end,RAM,threads,script_path)
-  os.system(command)
-
-# grab some subjs as list
-my_file = open("/cbica/projects/abcdfnets/scripts/combined_PFNs_PGs/subjects_from_manifest_01_28_22.txt", "r")
-content = my_file.read()
-content_list = content. split("\n")
-# remove last line (blank)
-content_list.pop()
-# feed em' in as subjects
-subjects = content_list
-# only first(last) 1048 ran?
-# anddd it died after another 2630 subjs. 2071 left to run.
-# and it died again (9/24/21). 1833 left to run
-#subjects = subjects[0:1833]
-# while there are more than 0 subjects left to run
-#while len(subjects)>0:
-  # grab qsub info, get number of jobs being run
-#  qstat = subprocess.check_output(['qstat'],shell=True).decode().split('/bin/python')[0]
-#  que = len(qstat.split('\n'))-3
-  # if we are using less than 5 job slots (one is occupied by this script)
-#  if que < 8:
-    # see if it is the weekend, 0, 1, 2, 3, and 4 are weekday, 5 and 6 are weekend
-#    weekno = datetime.datetime.today().weekday()
-    # see if it is before 9 or after 5 
-#    Hour = time.localtime().tm_hour 
-    # if weekend OR after 6 PM OR before 9 AM
-#    if weekno > 4 or Hour < 9 or Hour > 16 :
-#      newsub = subjects.pop()
-      # adding new condition: if gradient file does not exist
[…]

### 2022-08-31 cubic_scripts/OffHours_wrapper_ASK_getFD.py

@@ -1,43 +1,0 @@
-import subprocess
-import time
-import datetime
-import os
-# grab some subjs as list
-my_file = open("/cbica/projects/abcdfnets/scripts/combined_PFNs_PGs/twins_not_yet_run_012622.txt", "r")
-content = my_file.read()
-content_list = content. split("\n")
-# remove last line (blank)
-content_list.pop()
-# feed em' in as subjects
-subjects = content_list
-# only first(last) 1048 ran?
-# anddd it died after another 2630 subjs. 2071 left to run.
-# and it died again (9/24/21). 1833 left to run
-#subjects = subjects[0:1833]
-# while there are more than 0 subjects left to run
-while len(subjects)>0:
-  # grab qsub info, get number of jobs being run
-  qstat = subprocess.check_output(['qstat'],shell=True).decode().split('/bin/python')[0]
-  que = len(qstat.split('\n'))-3
-  # if we are using less than 5 job slots (one is occupied by this script)
-  if que < 8:
-    # see if it is the weekend, 0, 1, 2, 3, and 4 are weekday, 5 and 6 are weekend
-    weekno = datetime.datetime.today().weekday()
-    # see if it is before 9 or after 5 
-    Hour = time.localtime().tm_hour 
-    # if weekend OR after 6 PM OR before 9 AM
-    if weekno > 4 or Hour < 9 or Hour > 16 :
-      newsub = subjects.pop()
-      # adding new condition: if gradient file does not exist
-      # gradFile='/cbica/projects/abcdfnets/results/wave_output/' + str(newsub) + '/' + str(newsub) + '_PG_LR_32k.dscalar.nii'
-      # if not os.path.exists(gradFile):
-      # submit job (if above conditions are met)
-      subprocess.run(["qsub","-l","h_vmem=15G,s_vmem=14G","qsubMatlab_ASK_getFD.sh",newsub])
-      time.sleep(60) #wait a minute
-    # added this to run 3 subjs (1 slot for this job) during ON hours
-    elif que < 4:
-      newsub = subjects.pop()
-      # gradFile='/cbica/projects/abcdfnets/results/wave_output/' + str(newsub) + '/' + str(newsub) + '_PG_LR_32k.dscalar.nii'
-      # if not os.path.exists(gradFile):
-      subprocess.run(["qsub","-l","h_vmem=15G,s_vmem=14G","qsubMatlab_ASK_getFD.sh",newsub])
-      time.sleep(60) #wait a minute

### 2022-08-31 cubic_scripts/get_FD_ABCD.m

@@ -1,36 +1,0 @@
-function get_FD_ABCD(subj)
-%%% This function will take a single subject's NDAR name, download their fMRI data and motion masks, concatenate the fMRI data, mask according to Robert's instructions (.2mm FD, power outliers out), derive a single-subject parcellation based on Cui et al. 2020's group template, and delete the input fMRI data.
-
-% print subject being run
-subj
-
-% Add path to  miniconda for the python bits
-addpath(genpath('/cbica/projects/abcdfnets/miniconda3/bin/python/'))
-
-% add matlab path for used functions
-addpath(genpath('/cbica/projects/abcdfnets/scripts/code_nmf_cifti/tool_folder'));
-
-% tell it where AWS tools are for downloads
-system('export PATH=/cbica/projects/abcdfnets/aws/dist/:$PATH')
-
-% echo subj name into a .txt
-subjTxtCommand=['echo ' subj ' >> /cbica/projects/abcdfnets/nda-abcd-s3-downloader/' subj '.txt'];
-system(subjTxtCommand)
-
-% make output folder
-direcString=['/cbica/projects/abcdfnets/results/PGs_PFNs_output_justRest/' subj];
-mkdirCommand=['mkdir ' direcString];
-system(mkdirCommand)
-
-% download that one subject's data
-subjDlCommand=['/cbica/projects/abcdfnets/miniconda3/bin/python3 /cbica/projects/abcdfnets/nda-abcd-s3-downloader/download.py -i /cbica/projects/abcdfnets/nda-abcd-s3-downloader/datastructure_manifest_10_2.txt -o /scratch/abcdfnets/nda-abcd-s3-downloader/August_2021_DL/ -s /cbica/projects/abcdfnets/nda-abcd-s3-downloader/' subj '.txt -l /cbica/projects/abcdfnets/nda-abcd-s3-downloader/dl_logs -d /cbica/projects/abcdfnets/nda-abcd-s3-downloader/rest_subsets_justMotion.txt &']
-
-% note: downloader tool does not seem to communicate when it is done to matlab
-% added '&' and 'pause' so that matlab waits 5 minutes to proceed rather than getting caught up indefinitely
-system(subjDlCommand)
-pause(320)
-
-% Save motion mask from the downloaded data
-save_motion_mask(subj)
-
-end

### 2022-08-31 cubic_scripts/mat_to_dlabel_justRest.m

@@ -1,26 +1,0 @@
-function mat_to_dlabel_justRest(subj)
-
-%%%
-ProjectFolder = '/cbica/projects/abcdfnets/results';
-OutputFolder = ['/cbica/projects/abcdfnets/results/SingleParcel_1by1_Rest/' subj '/'];
-%%%
-
-% resampled V of interest (group or individ - CHANGE AS FIT TO MATCH NAME)
-finalUVFile=['/cbica/projects/abcdfnets/results/SingleParcel_1by1_Rest/' subj '/IndividualParcel_Final_sbj1_comp17_alphaS21_1_alphaL300_vxInfo1_ard0_eta0/final_UV.mat'];
-Loading_Mat=load(finalUVFile);
-V=Loading_Mat.V;
-% extract from struct
-V=V{:};
-
-% apply ZC code from step 6th - subject AtlasLabel will have parcels for viz
-V_Max = max(V);
-trimInd = V ./ max(repmat(V_Max, size(V, 1), 1), eps) < 5e-2;
-V(trimInd) = 0;
-sbj_AtlasLoading_NoMedialWall = V;
-[~, sbj_AtlasLabel_NoMedialWall] = max(sbj_AtlasLoading_NoMedialWall, [], 2);
-
-% cifti to replace cdata in
-HP=cifti_read('/cbica/projects/abcdfnets/results/SingleParcellation/RobustInitialization_Cifti_Surf/robust_initVHP.dscalar.nii');
-HP.cdata(1:59412)=sbj_AtlasLabel_NoMedialWall;
-outputfile=['/cbica/projects/abcdfnets/results/SingleParcel_1by1_Rest/' subj '/' subj '_Parcel.dscalar.nii'];
-cifti_write(HP,outputfile)

### 2022-08-31 cubic_scripts/preProc_PFNs_PGs_Delete.m

@@ -1,73 +1,0 @@
-function preProc_PFNs_PGs_Delete(subj)
-%%% This function will take a single subject's NDAR name, download their fMRI data and motion masks, concatenate the fMRI data, mask according to Robert's instructions (.2mm FD, power outliers out), derive a single-subject parcellation based on Cui et al. 2020's group template, and delete the input fMRI data.
-
-% print subject being run
-subj
-
-% ASK added 1/20/22 to check whether subject has already run:
-eval(['waveOutputFileCheck = ''/cbica/projects/abcdfnets/results/wave_output/' char(subj)  '/' char(subj)  '_PG1_index_rest.npy'';'])
-eval(['PFNoutputFileCheck = ''/cbica/projects/abcdfnets/results/SingleParcel_1by1_Rest/' char(subj) '/ID.mat'';'])
-if ~isfile(waveOutputFileCheck) || ~isfile(PFNoutputFileCheck) 
-
-% Add path to  miniconda for the python bits
-addpath(genpath('/cbica/projects/abcdfnets/miniconda3/bin/python/'))
-
-% add matlab path for used functions
-addpath(genpath('/cbica/projects/abcdfnets/scripts/code_nmf_cifti/tool_folder'));
-
-% tell it where AWS tools are for downloads
-system('export PATH=/cbica/projects/abcdfnets/aws/dist/:$PATH')
-
-% echo subj name into a .txt
-subjTxtCommand=['echo ' subj ' >> /cbica/projects/abcdfnets/nda-abcd-s3-downloader/' subj '.txt'];
-system(subjTxtCommand)
-
-% make output folder
-direcString=['/cbica/projects/abcdfnets/results/PGs_PFNs_output_justRest/' subj];
-mkdirCommand=['mkdir ' direcString];
-system(mkdirCommand)
-
-% download that one subject's data
[…]

### 2022-08-31 cubic_scripts/qsubMatlab_ASK.sh

@@ -1,1 +1,0 @@
-matlab -nodisplay -r "preProc_PFNs_PGs_Delete('${1}')"

### 2022-08-31 cubic_scripts/qsubMatlab_ASK_arrays.py

@@ -1,26 +1,0 @@
-import numpy as np
-from scipy.stats import pearsonr
-from sklearn.linear_model import RidgeCV
-from sklearn.model_selection import KFold
-from sklearn.neural_network import MLPRegressor
-from sklearn.linear_model import LinearRegression, LogisticRegression
-import subprocess
-import os
-import pickle
-import copy
-def get_sge_task_id():
-  sge_task_id = subprocess.check_output(['echo $SGE_TASK_ID'],shell=True).decode()
-  return int(sge_task_id)
-my_file = open("/cbica/projects/abcdfnets/scripts/combined_PFNs_PGs/subjects_from_manifest_01_28_22.txt", "r")
-content = my_file.read()
-content_list = content. split("\n")
-content_list.pop()
-subjects = content_list
-subject = subjects[get_sge_task_id()]
-#os.environ["subject"]=str(subject)
-#cmd = "set subject = " subject ""
-#os.system(cmd)
-print(subject)
-cmd = '''matlab -nodisplay -r "preProc_PFNs_PGs_Delete('{}')"'''.format(subject)
-print(cmd)
-os.system(cmd)

### 2022-08-31 cubic_scripts/qsubMatlab_ASK_getFD.sh

@@ -1,1 +1,0 @@
-matlab -nodisplay -r "get_FD_ABCD('${1}')"

### 2022-08-31 cubic_scripts/save_motion_mask.m

@@ -1,54 +1,0 @@
-function save_motion_mask(subj)
-% load in subj
-topleveldir='/scratch/abcdfnets/nda-abcd-s3-downloader/August_2021_DL/derivatives/abcd-hcp-pipeline/sub-*'
-direc=dir(topleveldir);
-% initialize empty vector for average length
-TRvecNum=[];
-% for each "task"
-tasks=["rest"]%,"MID","SST","nback"];
-for t=1:length(tasks)
-    task=tasks(t);
-    sname=subj;
-    fpParent=['/scratch/abcdfnets/nda-abcd-s3-downloader/August_2021_DL/derivatives/abcd-hcp-pipeline/' sname '/ses-baselineYear1Arm1/func/'];
-%    fp=strjoin([fpParent sname '_ses-baselineYear1Arm1_task-' task '_bold_desc-filtered_timeseries.dtseries.nii'],'');
-    % not flagging missing tasks for now, added this conditional to reflect that
-%    if exist(fp,'file')
-%         ts_cif=read_cifti(fp);
-%         ts=ts_cif.cdata;
-        % load in mask
-        masfp=strjoin([fpParent sname '_ses-baselineYear1Arm1_task-' task '_desc-filteredwithoutliers_motion_mask.mat'],'');
-        %if exist(masfp,'file')
-            
-            [status,message,messageId]=copyfile(masfp,'/cbica/projects/abcdfnets/scripts/combined_PFNs_PGs/saved_motion_masks/','f')
-            
-%             mask=load(masfp);
-%             % get to FD_thresh of .2 mm, corresponds to threshold 21
-%             maskp2mm=mask.motion_data{1,21}.combined_removal;
-%             TRwise_mask=logical(maskp2mm);
-%             % length of mask corresponds to number of TRs
-%             % 1 indicates flagged for FD over selected threshold, reverse 'em so 0 indicates removal
-%             TRwise_mask=~TRwise_mask;
-%             % remove TRs with corresp. flag
-%             masked_trs=ts(:,TRwise_mask);
-            % reconfig cifti metadata to reflect new number of TRs
-%             newciftiSize=size(masked_trs);
-%             newTRnum=newciftiSize(2);
-            %s-2 because we start at 3
-%             ts_cif.diminfo{2}.length=newTRnum;
-%             % overwrite TRs for new file
-%             ts_cif.cdata=masked_trs;
-            % set output filepath
[…]

### 2022-08-31 RidgeCode/compare_predicted_actual.m
Delete RidgeCode directory

@@ -1,239 +1,0 @@
-
-clear all
-
-% Add package to read NPY files into matlab
-addpath('/Users/askeller/Documents/npy-matlab/')
-
-folder_name='/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_Mar2922/all_network/';
-file_name_pred1='thompson_PC1_prediction.npy';
-file_name_pred2='thompson_PC2_prediction.npy';
-file_name_pred3='thompson_PC3_prediction.npy';
-
-pred_PC1 = readNPY([folder_name '/' file_name_pred1]);
-pred_PC2 = readNPY([folder_name '/' file_name_pred2]);
-pred_PC3 = readNPY([folder_name '/' file_name_pred3]);
-
-% put predictions on same scale as actual
-pred_PC1 = zscore(pred_PC1);
-pred_PC2 = zscore(pred_PC2);
-pred_PC3 = zscore(pred_PC3);
-
-
-actual_PC1=xlsread('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/PC1_targets.xls');
-actual_PC2=xlsread('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/PC2_targets.xls');
-actual_PC3=xlsread('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/PC3_targets.xls');
-
-
-% fourth column has the matched_group
-data_for_ridge=xlsread('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/data_for_ridge_032822.xls');
-
-% split data out by matched group to match Fig 7 in Cui 2020
-pred_PC1_samp1 = pred_PC1(data_for_ridge(:,4)==1);
-pred_PC1_samp2 = pred_PC1(data_for_ridge(:,4)==2);
-pred_PC2_samp1 = pred_PC2(data_for_ridge(:,4)==1);
-pred_PC2_samp2 = pred_PC2(data_for_ridge(:,4)==2);
-pred_PC3_samp1 = pred_PC3(data_for_ridge(:,4)==1);
-pred_PC3_samp2 = pred_PC3(data_for_ridge(:,4)==2);
[…]

### 2022-08-31 RidgeCode/get_data_for_ridge.R

@@ -1,84 +1,0 @@
-
-# First load in the spatial extent of each PFN (they're in order, 1-17)
-# Then merge with the same datasets as above (NIH toolbox, trauma, etc.)
-pfn_sizes <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/All_PFN_sizes.csv")
-# Change PFN column names so they're sensible
-colnames(pfn_sizes)<-c("subjectkey","PFN1","PFN2","PFN3","PFN4","PFN5","PFN6","PFN7","PFN8","PFN9","PFN10","PFN11","PFN12","PFN13","PFN14","PFN15","PFN16","PFN17")
-
-# Load data
-newdata<-readRDS("/Users/askeller/Documents/Kellernet_PrelimAnalysis/DEAP-data-download_ThompsonScores_ResFamIncome.rds")
-newdata.baseline<-newdata[newdata$event_name=="baseline_year_1_arm_1",]
-colnames(newdata.baseline)[1]<-"subjectkey"
-all.data <- merge(pfn_sizes,newdata.baseline[,c("subjectkey", setdiff(colnames(newdata.baseline),colnames(pfn_sizes)))],by="subjectkey")
-
-
-
-# Remove subjects based on the following criteria:
-## 1) 8min of retained TRs (600 TRs)
-## 2) ABCD Booleans for rest and T1
-num_TRs <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/num_TRs_by_subj_redo.csv")
-data<-merge(all.data,num_TRs,by="subjectkey")
-data.clean<-data[data$numTRs>=600,] # we go from 9,132 to 8,293 at this step
-
-# Remove participants based on booleans from ABCD
-abcd_imgincl01 <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/abcd_imgincl01.csv")
-abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$eventnam=="baseline_year_1_arm_1",]
-abcd_imgincl01 <- abcd_imgincl01[!abcd_imgincl01$visit=="",] # start here with 11,663 (8,287 of the 9,132 set)
-abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_t1w_include==1,] # down to 11,124 (8,045 of the 9,132 set)
[…]

### 2022-08-31 RidgeCode/get_data_for_ridge_restOnlyPFNs.R

@@ -1,89 +1,0 @@
-
-library(tidyr)
-library(dplyr)
-library(readr)
-
-# First load in the spatial extent of each PFN (they're in order, 1-17)
-# Then merge with the same datasets as above (NIH toolbox, trauma, etc.)
-pfn_sizes <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/All_PFN_sizes_Rest_081122.csv")
-# Change PFN column names so they're sensible
-colnames(pfn_sizes)<-c("subjectkey","PFN1","PFN2","PFN3","PFN4","PFN5","PFN6","PFN7","PFN8","PFN9","PFN10","PFN11","PFN12","PFN13","PFN14","PFN15","PFN16","PFN17")
-
-
-# Load data
-newdata<-readRDS("/Users/askeller/Documents/Kellernet_PrelimAnalysis/DEAP-data-download_ThompsonScores_ResFamIncome.rds")
-newdata.baseline<-newdata[newdata$event_name=="baseline_year_1_arm_1",]
-colnames(newdata.baseline)[1]<-"subjectkey"
-all.data <- merge(pfn_sizes,newdata.baseline[,c("subjectkey", setdiff(colnames(newdata.baseline),colnames(pfn_sizes)))],by="subjectkey")
-
-
-
-# Remove subjects based on the following criteria:
-## 1) 8min of retained TRs (600 TRs)
-## 2) ABCD Booleans for rest and T1
-num_TRs <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/num_TRs_by_subj_redo.csv")
-data<-merge(all.data,num_TRs,by="subjectkey")
-data.clean<-data[data$numTRs>=600,] # we go from 7,493 to 7,245 at this step
-
-# Remove participants based on booleans from ABCD
-abcd_imgincl01 <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/abcd_imgincl01.csv")
-abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$eventnam=="baseline_year_1_arm_1",]
-abcd_imgincl01 <- abcd_imgincl01[!abcd_imgincl01$visit=="",] # start here with 11,663
-abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_t1w_include==1,] # down to 11,124
-abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_rsfmri_include==1,] # down to 9,388
-
[…]

### 2022-08-31 RidgeCode/keller_proc_predict.py

@@ -1,22 +1,0 @@
-import sys
-import os
-
-homedir = sys.argv[1]
-tmpdir = sys.argv[2]
-network = sys.argv[3]
-phenotype_name = sys.argv[4]
-
-"""
-this makes the features and targets in tmpdir
-"""
-os.system('python /{0}/preprocess.py {1} {2}'.format(homedir,network,tmpdir))
-
-working_dir = homedir + '/results/{0}_network/'.format(network)
-feature_path = '/{0}/features_{1}.npy'.format(tmpdir,network)
-phenotype_path = '/{0}/phenotypes_target.csv'.format(tmpdir)
-control_path = '/{0}/phenotypes_control.csv'.format(tmpdir)
-
-"""
-this does the actual ridge regression
-"""
-os.system('python /{0}/predict_boot.py {1} {2} {3} {4} {5} rel_family_id'.format(homedir,working_dir,feature_path,phenotype_path,phenotype_name,control_path))

### 2022-08-31 RidgeCode/predict_boot_with_null.py

@@ -1,106 +1,0 @@
-import glob
-import h5py
-import numpy as np
-import os
-import pandas as pd
-from sklearn.linear_model import RidgeCV
-from sklearn.model_selection import GroupKFold
-from sklearn.linear_model import LinearRegression
-from sklearn import preprocessing
-import sys
-from scipy.stats import pearsonr
-
-"""
-hi. this is going to run ridge regression, you basically just need:
-
-working_dir: where you want your results saved, does not have to exist, we will make it
-feature_path: path to the actual features, should be a subject x features npy array
-phenotype_path: path to a csv with the to-be-predicted values
-phenotype_name: str of name of column in phenotype_path you want
-control_path: path to csv, regress these features from the features within each fold
-fold_group: in this instance, this is the ABCD train and test split, A for one group, B for the other
-"""
-folds = 100 #in this instance, this is how many times we want to run the model 
-working_dir = sys.argv[1] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/'
-os.makedirs(working_dir,exist_ok=True)
-feature_path = sys.argv[2]  #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles/features_0.npy'
-phenotype_path = sys.argv[3] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles/phenotypes_target.csv'
-phenotype_name = sys.argv[4] #'thompson_PC1'
-control_path = sys.argv[5] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles/phenotypes_control.csv'
-fold_group = 'matched_group' #sys.argv[6] # in this instance, this is the ABCD train and test split, A for one group, B for the other
-
-
-"""
-load the subject measures you want to control for
-"""
-phenotypes_control = pd.read_csv(control_path)
-"""
-load in all the feature weights
-"""
-features = np.load(feature_path).astype(np.float16)
-"""
-this is adapted from pennlinckit.utils.predict
-"""
-targets = pd.read_csv(phenotype_path)[phenotype_name].values.astype(np.float16)
-fold_group = pd.read_csv(phenotype_path)[fold_group].values.astype(np.float16)
[…]

### 2022-08-31 RidgeCode/predict_null_early_shuffle.py

@@ -1,102 +1,0 @@
-import glob
-import h5py
-import random
-import numpy as np
-import os
-import pandas as pd
-from sklearn.linear_model import RidgeCV
-from sklearn.model_selection import GroupKFold
-from sklearn.linear_model import LinearRegression
-from sklearn import preprocessing
-import sys
-from scipy.stats import pearsonr
-
-"""
-hi. this is going to run ridge regression, you basically just need:
-
-working_dir: where you want your results saved, does not have to exist, we will make it
-feature_path: path to the actual features, should be a subject x features npy array
-phenotype_path: path to a csv with the to-be-predicted values
-phenotype_name: str of name of column in phenotype_path you want
-control_path: path to csv, regress these features from the features within each fold
-fold_group: in this instance, this is the ABCD train and test split, A for one group, B for the other
-"""
-folds = 100 #in this instance, this is how many times we want to run the model 
-working_dir = sys.argv[1] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/'
-os.makedirs(working_dir,exist_ok=True)
-feature_path = sys.argv[2]  #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles/features_0.npy'
-phenotype_path = sys.argv[3] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles/phenotypes_target.csv'
-phenotype_name = sys.argv[4] #'thompson_PC1'
-control_path = sys.argv[5] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles/phenotypes_control.csv'
-fold_group = 'matched_group' #sys.argv[6] # in this instance, this is the ABCD train and test split, A for one group, B for the other
-
-
-"""
-load the subject measures you want to control for
-"""
-phenotypes_control = pd.read_csv(control_path)
-"""
-load in all the feature weights
-"""
-features = np.load(feature_path).astype(np.float16)
-"""
-this is adapted from pennlinckit.utils.predict
-"""
-targets = pd.read_csv(phenotype_path)[phenotype_name].values.astype(np.float16)
-fold_group = pd.read_csv(phenotype_path)[fold_group].values.astype(np.float16)
[…]

### 2022-08-31 RidgeCode/preprocess.py

@@ -1,60 +1,0 @@
-import glob
-import h5py
-import numpy as np
-import os
-import pandas as pd
-from sklearn import preprocessing
-import sys
-
-"""
-hi. this is going to read these in, you basically just need 
-subjects: path to subjects!
-data_path: path to the actual features
-phenotypes: path to a csv with the to-be-predicted and the noise
-"""
-data_path ='/gpfs/fs001/cbica/projects/abcdfnets/results/SingleParcel_1by1/sub-NDAR{0}/IndividualParcel_Final_sbj1_comp17_alphaS21_1_alphaL300_vxInfo1_ard0_eta0/final_UV.mat'
-control =['sex','meanFD','abcd_site','interview_age']
-try: network = int(sys.argv[1])
-except: network = sys.argv[1]
-outdir = sys.argv[2]
-os.makedirs(outdir,exist_ok=True)
-"""
-load the subject measures 
-"""
-phenotypes = pd.read_csv('/gpfs/fs001/cbica/projects/abcdfnets/data_for_ridge_032822.csv') #load
-#phenotypes['subjectkey'] = np.core.defchararray.strip(phenotypes.subjectkey.values.astype(str),'NDAR_') #strip
-phenotypes = phenotypes.sort_values('subjectkey') #sort 
-phenotypes['meanFD'] = phenotypes['meanFD'].values.astype(np.float16) #saves space
-
-"""
-convert categorical vars to numerical, ie dummy encoding, for sites and sex
-"""
-for c in ['sex','abcd_site']:
-    dumb = pd.get_dummies(phenotypes[c]).astype(np.int8)
-    phenotypes = pd.merge(left=phenotypes,right=dumb,left_index=True,right_index=True)
-    for d in dumb.columns:
-        control.append(d) #we get a lot more columns so we put them in
-    control.remove(c) # remove the original categorical
-
-"""
-load in all the feature weights
-"""
-features = []
-for subject in phenotypes.subjectkey.values:
-    if os.path.exists(data_path.format(subject)) == False:
-        phenotypes = phenotypes.drop(phenotypes.index[phenotypes.subjectkey==subject])
-        continue
-    f = h5py.File(data_path.format(subject), 'r')
-    f = np.array(f[f['V'][0][0]]).astype(np.float16)
-    if type(network) == int:
-        f = f[network]
-    features.append(f)
-features = np.array(features)
[…]

### 2022-08-31 RidgeCode/submit.py

@@ -1,23 +1,0 @@
-import os
-import sys
-import numpy as np
-"""
-this is the only script you actually should call, it will submit a job
-this job makes the features, and then does the regression. 
-only change the home_dir variable, everything else should run! 
-"""
-
-homedir = '/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/' #sys.argv[1] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/'
-
-tmpdir = '/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles_boot/' #os.environ['TMPDIR']
-networks = np.array(['all'])
-networks = np.append(networks,np.arange(0,17))
-
-for network in networks:
-    if network == 'all': 
-        GB = '200G'
-        continue
-    else: GB = '124G'
-    
-    for cog_score in ['thompson_PC1','thompson_PC2','thompson_PC3']:
-        os.system('qsub -l h_vmem={0},s_vmem={0} -N {1} -R y -V -j y -b y -o ~/sge/ -e ~/sge/ python {2}/keller_proc_predict.py {2} {3} {4} {5}'.format(GB,cog_score.split('_')[1],homedir,tmpdir,network,cog_score))

### 2022-08-31 Keller_RidgeScripts_081822/keller_proc_predict.py
Delete Keller_RidgeScripts_081822 directory

@@ -1,22 +1,0 @@
-import sys
-import os
-
-homedir = sys.argv[1]
-tmpdir = sys.argv[2]
-network = sys.argv[3]
-phenotype_name = sys.argv[4]
-
-"""
-this makes the features and targets in tmpdir
-"""
-os.system('python /{0}/preprocess.py {1} {2}'.format(homedir,network,tmpdir))
-
-working_dir = homedir + '/results_matchedsamples_081822/{0}_network/'.format(network)
-feature_path = '/{0}/features_{1}.npy'.format(tmpdir,network)
-phenotype_path = '/{0}/phenotypes_target.csv'.format(tmpdir)
-control_path = '/{0}/phenotypes_control.csv'.format(tmpdir)
-
-"""
-this does the actual ridge regression
-"""
-os.system('python /{0}/predict_matchedsamples.py {1} {2} {3} {4} {5} rel_family_id'.format(homedir,working_dir,feature_path,phenotype_path,phenotype_name,control_path))

### 2022-08-31 Keller_RidgeScripts_081822/keller_proc_predict_null.py

@@ -1,22 +1,0 @@
-import sys
-import os
-
-homedir = sys.argv[1]
-tmpdir = sys.argv[2]
-network = sys.argv[3]
-phenotype_name = sys.argv[4]
-
-"""
-this makes the features and targets in tmpdir
-"""
-os.system('python /{0}/preprocess.py {1} {2}'.format(homedir,network,tmpdir))
-
-working_dir = homedir + '/results_matchedsamples_null_081822/{0}_network/'.format(network)
-feature_path = '/{0}/features_{1}.npy'.format(tmpdir,network)
-phenotype_path = '/{0}/phenotypes_target.csv'.format(tmpdir)
-control_path = '/{0}/phenotypes_control.csv'.format(tmpdir)
-
-"""
-this does the actual ridge regression
-"""
-os.system('python /{0}/predict_matchedsamples_null.py {1} {2} {3} {4} {5} rel_family_id'.format(homedir,working_dir,feature_path,phenotype_path,phenotype_name,control_path))

### 2022-08-31 Keller_RidgeScripts_081822/predict_matchedsamples.py

@@ -1,108 +1,0 @@
-import glob
-import h5py
-import numpy as np
-import os
-import pandas as pd
-from sklearn.linear_model import RidgeCV
-from sklearn.model_selection import GroupKFold
-from sklearn.linear_model import LinearRegression
-from sklearn import preprocessing
-import sys
-from scipy.stats import pearsonr
-
-"""
-This script will run ridge regression. To run it, you need:
-
-working_dir: where you want your results saved, does not have to exist, we will make it
-feature_path: path to the actual features, should be a subject x features npy array
-phenotype_path: path to a csv with the to-be-predicted values
-phenotype_name: str of name of column in phenotype_path you want
-control_path: path to csv, regress these features from the features within each fold
-fold_group: in this instance, this is the ABCD train and test split, A for one group, B for the other
-
-"""
-
-working_dir = sys.argv[1] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/'
-os.makedirs(working_dir,exist_ok=True)
-feature_path = sys.argv[2]  #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles/features_0.npy'
-phenotype_path = sys.argv[3] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles/phenotypes_target.csv'
-phenotype_name = sys.argv[4] #'thompson_PC1'
-control_path = sys.argv[5] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles/phenotypes_control.csv'
-fold_group = 'matched_group' #sys.argv[6] # in this instance, this is the ABCD train and test split, A for one group, B for the other
-
-"""
-load the subject measures you want to control for
-"""
-phenotypes_control = pd.read_csv(control_path)
-"""
-load in all the feature weights
-"""
-features = np.load(feature_path).astype(np.float16)
-"""
-this is adapted from pennlinckit.utils.predict
-"""
-targets = pd.read_csv(phenotype_path)[phenotype_name].values.astype(np.float16)
-fold_group = pd.read_csv(phenotype_path)[fold_group].values.astype(np.float16)
[…]

### 2022-08-31 Keller_RidgeScripts_081822/predict_matchedsamples_bootstrap.py

@@ -1,99 +1,0 @@
-import glob
-import h5py
-import numpy as np
-import os
-import pandas as pd
-from sklearn.linear_model import RidgeCV
-from sklearn.model_selection import GroupKFold
-from sklearn.linear_model import LinearRegression
-from sklearn import preprocessing
-import sys
-from scipy.stats import pearsonr
-
-"""
-This script will run ridge regression. To run it, you need:
-
-working_dir: where you want your results saved, does not have to exist, we will make it
-feature_path: path to the actual features, should be a subject x features npy array
-phenotype_path: path to a csv with the to-be-predicted values
-phenotype_name: str of name of column in phenotype_path you want
-control_path: path to csv, regress these features from the features within each fold
-fold_group: in this instance, this is the ABCD train and test split, A for one group, B for the other
-
-"""
-
-folds = 100
-working_dir = sys.argv[1] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/'
-os.makedirs(working_dir,exist_ok=True)
-feature_path = sys.argv[2]  #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles/features_0.npy'
-phenotype_path = sys.argv[3] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles/phenotypes_target.csv'
-phenotype_name = sys.argv[4] #'thompson_PC1'
-control_path = sys.argv[5] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles/phenotypes_control.csv'
-fold_group = 'matched_group' #sys.argv[6] # in this instance, this is the ABCD train and test split, A for one group, B for the other
-
-"""
-load the subject measures you want to control for
-"""
-phenotypes_control = pd.read_csv(control_path)
-"""
-load in all the feature weights
-"""
-features = np.load(feature_path).astype(np.float16)
-"""
-this is adapted from pennlinckit.utils.predict
-"""
-targets = pd.read_csv(phenotype_path)[phenotype_name].values.astype(np.float16)
-fold_group = pd.read_csv(phenotype_path)[fold_group].values.astype(np.float16)
[…]

### 2022-08-31 Keller_RidgeScripts_081822/predict_matchedsamples_bootstrap_null.py

@@ -1,102 +1,0 @@
-import glob
-import h5py
-import numpy as np
-import os
-import pandas as pd
-from sklearn.linear_model import RidgeCV
-from sklearn.model_selection import GroupKFold
-from sklearn.linear_model import LinearRegression
-from sklearn import preprocessing
-import sys
-from scipy.stats import pearsonr
-
-"""
-This script will run ridge regression. To run it, you need:
-
-working_dir: where you want your results saved, does not have to exist, we will make it
-feature_path: path to the actual features, should be a subject x features npy array
-phenotype_path: path to a csv with the to-be-predicted values
-phenotype_name: str of name of column in phenotype_path you want
-control_path: path to csv, regress these features from the features within each fold
-fold_group: in this instance, this is the ABCD train and test split, A for one group, B for the other
-
-"""
-
-folds = 100
-working_dir = sys.argv[1] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/'
-os.makedirs(working_dir,exist_ok=True)
-feature_path = sys.argv[2]  #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles/features_0.npy'
-phenotype_path = sys.argv[3] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles/phenotypes_target.csv'
-phenotype_name = sys.argv[4] #'thompson_PC1'
-control_path = sys.argv[5] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles/phenotypes_control.csv'
-fold_group = 'matched_group' #sys.argv[6] # in this instance, this is the ABCD train and test split, A for one group, B for the other
-
-"""
-load the subject measures you want to control for
-"""
-phenotypes_control = pd.read_csv(control_path)
-"""
-load in all the feature weights
-"""
-features = np.load(feature_path).astype(np.float16)
-"""
-this is adapted from pennlinckit.utils.predict
-"""
-targets = pd.read_csv(phenotype_path)[phenotype_name].values.astype(np.float16)
-# shuffle the outcome variable
-targets = np.random.shuffle(targets)
-
[…]

### 2022-08-31 Keller_RidgeScripts_081822/predict_matchedsamples_null.py

@@ -1,103 +1,0 @@
-import glob
-import h5py
-import numpy as np
-import os
-import pandas as pd
-from sklearn.linear_model import RidgeCV
-from sklearn.model_selection import GroupKFold
-from sklearn.linear_model import LinearRegression
-from sklearn import preprocessing
-import sys
-from scipy.stats import pearsonr
-
-"""
-This script will run ridge regression. To run it, you need:
-
-working_dir: where you want your results saved, does not have to exist, we will make it
-feature_path: path to the actual features, should be a subject x features npy array
-phenotype_path: path to a csv with the to-be-predicted values
-phenotype_name: str of name of column in phenotype_path you want
-control_path: path to csv, regress these features from the features within each fold
-fold_group: in this instance, this is the ABCD train and test split, A for one group, B for the other
-
-"""
-
-folds = 100
-working_dir = sys.argv[1] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/'
-os.makedirs(working_dir,exist_ok=True)
-feature_path = sys.argv[2]  #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles/features_0.npy'
-phenotype_path = sys.argv[3] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles/phenotypes_target.csv'
-phenotype_name = sys.argv[4] #'thompson_PC1'
-control_path = sys.argv[5] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles/phenotypes_control.csv'
-fold_group = 'matched_group' #sys.argv[6] # in this instance, this is the ABCD train and test split, A for one group, B for the other
-
-"""
-load the subject measures you want to control for
-"""
-phenotypes_control = pd.read_csv(control_path)
-"""
-load in all the feature weights
-"""
-features = np.load(feature_path).astype(np.float16)
-"""
-this is adapted from pennlinckit.utils.predict
-"""
-targets = pd.read_csv(phenotype_path)[phenotype_name].values.astype(np.float16)
-fold_group = pd.read_csv(phenotype_path)[fold_group].values.astype(np.float16)
[…]

### 2022-08-31 Keller_RidgeScripts_081822/submit.py

@@ -1,23 +1,0 @@
-import os
-import sys
-import numpy as np
-"""
-this is the only script you actually should call, it will submit a job
-this job makes the features, and then does the regression. 
-only change the home_dir variable, everything else should run! 
-"""
-
-homedir = '/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller' #sys.argv[1] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/'
-
-tmpdir = '/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles_matchedsamples_081822/' #os.environ['TMPDIR']
-networks = np.array(['all'])
-networks = np.append(networks,np.arange(0,17))
-
-for network in networks:
-    if network == 'all': 
-        GB = '200G'
-        continue
-    else: GB = '124G'
-    
-    for cog_score in ['thompson_PC1','thompson_PC2','thompson_PC3']:
-        os.system('qsub -l h_vmem={0},s_vmem={0} -N {1} -R y -V -j y -b y -o ~/sge/ -e ~/sge/ python {2}/keller_proc_predict.py {2} {3} {4} {5}'.format(GB,cog_score.split('_')[1],homedir,tmpdir,network,cog_score))

### 2022-08-31 Keller_RidgeScripts_081822/submit_all.py

@@ -1,19 +1,0 @@
-import os
-import sys
-import numpy as np
-"""
-this is the only script you actually should call, it will submit a job
-this job makes the features, and then does the regression. 
-only change the home_dir variable, everything else should run! 
-"""
-
-homedir = '/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller' #sys.argv[1] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/'
-
-tmpdir = '/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles_matchedsamples_081822/' #os.environ['TMPDIR']
-networks = np.array(['all']) 
-network = 'all'
-
-GB = '200G'    
-
-for cog_score in ['thompson_PC1','thompson_PC2','thompson_PC3']:
-        os.system('qsub -l h_vmem={0},s_vmem={0} -N {1} -R y -V -j y -b y -o ~/sge/ -e ~/sge/ python {2}/keller_proc_predict.py {2} {3} {4} {5}'.format(GB,cog_score.split('_')[1],homedir,tmpdir,network,cog_score))

### 2022-08-31 Keller_RidgeScripts_081822/submit_all_null.py

@@ -1,19 +1,0 @@
-import os
-import sys
-import numpy as np
-"""
-this is the only script you actually should call, it will submit a job
-this job makes the features, and then does the regression. 
-only change the home_dir variable, everything else should run! 
-"""
-
-homedir = '/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller' #sys.argv[1] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/'
-
-tmpdir = '/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles_matchedsamples_null_081822/' #os.environ['TMPDIR']
-networks = np.array(['all']) 
-network = 'all'
-
-GB = '200G'    
-
-for cog_score in ['thompson_PC1','thompson_PC2','thompson_PC3']:
-        os.system('qsub -l h_vmem={0},s_vmem={0} -N {1} -R y -V -j y -b y -o ~/sge/ -e ~/sge/ python {2}/keller_proc_predict_null.py {2} {3} {4} {5}'.format(GB,cog_score.split('_')[1],homedir,tmpdir,network,cog_score))

### 2022-08-31 Step1_TotalCorticalRepresentation/Associations_PFN_Cognition.Rmd
Step1_TotalCorticalRepresentation

--- 2022-06-10 ABCD_Flux22_PFN_Analyses.Rmd
@@
 ---
-title: "ABCD_Flux22_PFN_Analyses"
+title: "Associations_PFN_Cognition"
 author: "Arielle Keller"
@@
 library(neuroCombat)
+
+library(R.matlab)
+library(mgcv)
+library(ggplot2)
+library(visreg)
+library(ggtext)
 ```
@@
 data<-merge(pfn_sizes,num_TRs,by="subjectkey")
-data.clean<-data[data$numTRs>=600,] # we go from 9,132 to 8,293 at this step
+data.clean<-data[data$numTRs>=600,]
 
@@
 abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$eventnam=="baseline_year_1_arm_1",]
-abcd_imgincl01 <- abcd_imgincl01[!abcd_imgincl01$visit=="",] # start here with 11,663 (8,287 of the 9,132 set)
-abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_t1w_include==1,] # down to 11,124 (8,045 of the 9,132 set)
-abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_rsfmri_include==1,] # down to 9,388 (7,475 of the 9,132 set)
+abcd_imgincl01 <- abcd_imgincl01[!abcd_imgincl01$visit=="",] 
+abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_t1w_include==1,]
+abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_rsfmri_include==1,]
 
-combined.data <- merge(data.clean,abcd_imgincl01[, c("subjectkey",'imgincl_t1w_include')],by="subjectkey") # n=7,475
+combined.data <- merge(data.clean,abcd_imgincl01[, c("subjectkey",'imgincl_t1w_include')],by="subjectkey") 
 ```
 
-## Instead of calculating the Thompson factor scores ourselves, use the summary scores from DEAP
+## Import the Thompson PC scores from DEAP
 ```{r}
@@
 colnames(all.data)<-gsub("neurocog_pc2.bl","thompson_PC2",colnames(all.data))
-colnames(all.data)<-gsub("neurocog_pc3.bl","thompson_PC3",colnames(all.data)) # still at n=7,475
+colnames(all.data)<-gsub("neurocog_pc3.bl","thompson_PC3",colnames(all.data))
 ```
@@
 colnames(site.baseline)[1]<-"subjectkey"
-abcd.data.almost2 <- merge(abcd.data.almost,site.baseline[,c("subjectkey", setdiff(colnames(site.baseline),colnames(abcd.data.almost)))],by="subjectkey") # n=7,474
+abcd.data.almost2 <- merge(abcd.data.almost,site.baseline[,c("subjectkey", setdiff(colnames(site.baseline),colnames(abcd.data.almost)))],by="subjectkey") 
 ```
@@
 abcd.data <- merge(abcd.data.almost2,meanFD,by="subjectkey")
-
-# n=7,461
 ```
 
-# Load train/test split from UMinn
+# Load discovery/replication matched samples 
 ```{r}
@@
 abcd.data.traintest <- merge(abcd.data,traintest.baseline,by="subjectkey")
-abcd.data.train <- abcd.data.traintest[abcd.data.traintest$matched_group==1,] # n=3,749
-abcd.data.test <- abcd.data.traintest[abcd.data.traintest$matched_group==2,] # n=3,712
+abcd.data.traintest<-abcd.data.traintest[!duplicated(abcd.data.traintest$subjectkey),] # remove duplicated subject
+abcd.data.train <- abcd.data.traintest[abcd.data.traintest$matched_group==1,] 
+abcd.data.test <- abcd.data.traintest[abcd.data.traintest$matched_group==2,] 
 ```
@@
 abcd.data.noPFNsCog <- subset(abcd.data.test,select=-c(PFN1,PFN2,PFN3,PFN4,PFN5,PFN6,PFN7,PFN8,PFN9,PFN10,PFN11,PFN12,PFN13,PFN14,PFN15,PFN16,PFN17,thompson_PC1,thompson_PC2,thompson_PC3,meanFD))
-abcd.data.test.harmonized <- cbind(abcd.data.noPFNsCog,dat.harmonized) # Add the harmonized data back into the main dataframe (BE AWARE THAT NOT ALL DATA IS HARMONIZED)
+abcd.data.test.harmonized <- cbind(abcd.data.noPFNsCog,dat.harmonized) # Add the harmonized data back into the main dataframe
 
@@
 
-# quick  analyses for flux abstract
+# linear mixed effects models associating general cognition with each fronto-parietal PFN
 ```{r}
@@
 ```{r}
-# exclude n=488 subjects with missing cognitive data
+# exclude subjects with missing cognitive data
 abcd.data.for.ridge<-abcd.data.traintest[,c("subjectkey","thompson_PC1","thompson_PC2","thompson_PC3","matched_group","interview_age","sex","meanFD","abcd_site","rel_family_id")]
@@
 
-### Replicate Cui bar graph:
+### Bar plot (Discovery Sample):
 ```{r}
@@
 
-z_vec_pn <- z_vec*pos_neg
+z_vec_pn_train <- z_vec*pos_neg
 keep_p <- ifelse(p_vec_adj<.05,1,0)
+
+z_vec_sorted = rank(z_vec_pn_train);
+
+# Using 7 colors scheme for bar plot
+# bar plot for cognition effects
+data <- data.frame(CognitionEffects_Z = as.numeric(z_vec_pn_train)) 
+data$EffectRank <- as.numeric(z_vec_sorted)
+BorderColor <- c("#E76178", "#7499C2", "#F5BA2E", "#7499C2", "#00A131",
+                 "#AF33AD", "#E443FF", "#E76178", "#E443FF", "#AF33AD",
+                 "#7499C2", "#E76178", "#7499C2", "#00A131", "#F5BA2E", 
+                 "#4E31A8", "#F5BA2E");
+LineType <- c("dashed", "solid", "solid", "solid", "dashed", "dashed",
+              "dashed", "dashed", "dashed", "dashed", "dashed", "dashed",
+              "dashed", "dashed", "solid", "dashed", "solid");
+Fig <- ggplot(data, aes(EffectRank, CognitionEffects_Z)) +
+  geom_bar(stat = "identity", fill=c("#FFFFFF", "#7499C2", "#F5BA2E",
+                                     "#7499C2", "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF",
+                                     "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF",
+                                     "#FFFFFF", "#F5BA2E", "#FFFFFF", "#F5BA2E"), 
+           colour = BorderColor, linetype = LineType, width = 0.8) + 
+  labs(x = "Networks", y = expression(paste("Cognition Association (", italic("Z"), ")"))) + theme_classic() +
+  theme(axis.text.x = ggtext::element_markdown(size= 27, color = BorderColor[c(4,2,11,10,1,9,5,16,14,12,7,8,13,6,3,15,17)]), 
+        axis.text.y = ggtext::element_markdown(size= 33, color = "black"), 
+        axis.title=ggtext::element_markdown(size = 33)) +
+  theme(axis.text.x = ggtext::element_markdown(angle = 45, hjust = 1)) +
+  scale_x_discrete(labels = c('4','2','11','10','1','9','5','16','14','12','7','8','13','6','3','15','17'),limits = c('5','2','15','1','7','14','11','12','6','4','3','10','13','9','16','8','17')) 
+Fig
+ggsave('/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_032322/NetworkSize_Loading_CogEffects.tiff', width = 19, height = 16, dpi = 600, units = "cm");
 
@@
 
-### Replicate Cui bar graph (SAME THING IN TEST SET):
+### Bar plot (Replication Sample):
 ```{r}
@@
 
-z_vec_pn <- z_vec*pos_neg
+z_vec_pn_test <- z_vec*pos_neg
 keep_p <- ifelse(p_vec_adj<.05,1,0)
 
-```
+z_vec_sorted = rank(z_vec_pn_test);
 
-## Replicate Cui result showing topography across-individual variability by network
-```{r}
-
-# library(R.matlab)
-# library(ggplot2);
-# 
-# ResultsFolder = '/data/jux/BBL/projects/pncSingleFuncParcel/Replication/Revision';
-# AtlasFolder = paste0(ResultsFolder, '/SingleParcellation/SingleAtlas_Analysis');
-# Variability_Visualize_Folder = paste0(AtlasFolder, '/Variability_Visualize');
-# Variability_Mat = readMat(paste0(Variability_Visualize_Folder, '/VariabilityLoading_Median_17SystemMean.mat'));
-# 
-# AtlasLabel_Mat = readMat(paste0(AtlasFolder, '/Group_AtlasLabel.mat'));
-# 
-# AllData = data.frame(Variability = matrix(0, 17734, 1));
-# AllData$Label = matrix(0, 17734, 1);
-# for (i in c(1:17734))
-# {
-#   AllData$Variability[i] = Variability_Mat$VariabilityLoading.Median.17SystemMean.NoMedialWall[i];
-#   AllData$Label[i] = AtlasLabel_Mat$sbj.AtlasLabel.NoMedialWall[i];
-# }
-# AllData$Variability = as.numeric(AllData$Variability);
-# AllData$Label = as.factor(AllData$Label);
-# 
-# # Order the network by the median value
-# MedianValue = matrix(0, 1, 17);
-# for (i in c(1:17)) {
-#   ind = which(AllData$Label == i);
-#   MedianValue[i] = median(AllData$Variability[ind]);
-# }
-# # Store network variability for correlation with effect size
-# writeMat(paste0(ResultsFolder, '/Corr_NetworkVariability_EffectSize/NetworkVariability.mat'), MedianValue = MedianValue);
-# tmp = sort(MedianValue, index.return = TRUE);
-# 
-# ColorScheme = c("#E76178", "#7499C2", "#F5BA2E", "#7499C2", "#00A131",
-#                 "#AF33AD", "#E443FF", "#E76178", "#E443FF", "#AF33AD",
-#                 "#7499C2", "#E76178", "#7499C2", "#00A131", "#F5BA2E",
-#                 "#4E31A8", "#F5BA2E");
-# ColorScheme_XText = c("#AF33AD", "#AF33AD", "#7499C2", "#7499C2", "#4E31A8",
-#                 "#7499C2", "#7499C2", "#F5BA2E", "#00A131", "#E76178",
-#                 "#E443FF", "#E443FF", "#E76178", "#E76178", "#F5BA2E",
-#                 "#00A131", "#F5BA2E");
-# Order = c(10, 6, 4, 2, 16, 11, 13, 15, 5, 12, 7, 9, 8, 1, 17, 14, 3);
-# ColorScheme_XText_New = ColorScheme_XText;
-# for (i in c(1:17)) {
-#   ind = which(Order == i);
-#   ColorScheme_XText_New[ind] = ColorScheme_XText[i];
-# }
-# ggplot(AllData, aes(x = Label, y = Variability, fill = Label, color = Label)) + 
-#       geom_violin(trim = FALSE) +
-#       scale_color_manual(values = ColorScheme) + 
-#       scale_fill_manual(values = ColorScheme) + 
-#       labs(x = "Networks", y = "Across-subject Variability") + theme_classic() +
-#       theme(axis.text.x = element_text(size = 22, color = ColorScheme_XText_New),
-#             axis.text.y = element_text(size = 22, color = "black"),
-#             axis.title = element_text(size = 22)) +
-#       theme(axis.text.x = element_text(angle = 22, hjust = 1)) + 
-#       theme(legend.position = "none") + 
-#       scale_x_discrete(
-#             limits = c(10, 6, 4, 2, 16, 11, 13, 15, 5, 12, 7, 9, 8, 1, 17, 14, 3),
-#             labels = c("12", "11", "2", "6", "14", "7", "8", "17", "16", "9", 
-#                        "13", "5", "15", "10", "3", "1", "4")) + 
-#       geom_boxplot(width=0.1, fill = "white");
-# ggsave('/data/jux/BBL/projects/pncSingleFuncParcel/Replication/Revisioni/Figures/Variability_Loading_Mean_Violin.tiff', width = 20, height = 15, dpi = 600, units = "cm");
+# Using 7 colors scheme for bar plot
+# bar plot for cognition effects
+data <- data.frame(CognitionEffects_Z = as.numeric(z_vec_pn_test)) 
+data$EffectRank <- as.numeric(z_vec_sorted)
+BorderColor <- c("#E76178", "#7499C2", "#F5BA2E", "#7499C2", "#00A131",
+                 "#AF33AD", "#E443FF", "#E76178", "#E443FF", "#AF33AD",
+                 "#7499C2", "#E76178", "#7499C2", "#00A131", "#F5BA2E", 
+                 "#4E31A8", "#F5BA2E");
+LineType <- c("dashed", "dashed", "solid", "solid", "dashed", "solid",
+              "dashed", "dashed", "dashed", "dashed", "dashed", "dashed",
+              "dashed", "dashed", "solid", "dashed", "solid");
+Fig <- ggplot(data, aes(EffectRank, CognitionEffects_Z)) +
+  geom_bar(stat = "identity", fill=c("#FFFFFF", "#FFFFFF", "#F5BA2E",
+                                     "#7499C2", "#FFFFFF", "#AF33AD", "#FFFFFF", "#FFFFFF",
+                                     "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF",
+                                     "#FFFFFF", "#F5BA2E", "#FFFFFF", "#F5BA2E"), 
+           colour = BorderColor, linetype = LineType, width = 0.8) + 
+  labs(x = "Networks", y = expression(paste("Cognition Association (", italic("Z"), ")"))) + theme_classic() +
+  theme(axis.text.x = ggtext::element_markdown(size= 27, color = BorderColor[c(4,13,9,2,7,12,10,5,16,14,8,1,11,3,15,17,6)]), 
+        axis.text.y = ggtext::element_markdown(size= 33, color = "black"), 
+        axis.title=ggtext::element_markdown(size = 33)) +
+  theme(axis.text.x = ggtext::element_markdown(angle = 45, hjust = 1)) +
+  scale_x_discrete(labels = c('4','13','9','2','7','12','10','5','16','14','8','1','11','3','15','17','6'),limits = c('12','4','14','1','8','17','5','11','3','7','13','6','2','10','15','9','16')) # + scale_y_continuous(limits = c(-4, 6), breaks = c(-4, -2, 0, 2, 4, 6));
+Fig
+ggsave('/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_032322/NetworkSize_Loading_CogEffects_test.tiff', width = 19, height = 16, dpi = 600, units = "cm");
 

### 2022-08-31 Step1_TotalCorticalRepresentation/calculate_PFN_size.m

@@ -1,0 +1,26 @@
+% This script will loop through the PFNs output and calculate the total
+% cortical representation (PFN "size") as the sum of loadings for each PFN
+
+file_pattern='/cbica/projects/abcdfnets/results/SingleParcel_1by1_Rest/sub-NDARINV*/IndividualParcel_Final_sbj1_comp17_alphaS21_1_alphaL300_vxInfo1_ard0_eta0/final_UV.mat'
+data_dir=dir(file_pattern);
+data_locations=fullfile({data_dir.folder}, {data_dir.name});
+
+% initialize table
+df=cell(length(data_locations),2);
+
+% loop through each data location to extract PFN size
+for i = 1:length(data_locations)
+	UV=load(char(data_locations(i))); % UV matrix is result of NMF
+	V=UV.V; % just take the V matrix with network loadings by vertex
+	V2=V{:};
+	stringsplit=split(char(data_locations(i)),'/');
+	subjname=stringsplit(9); % note this will depend on subject ID style
+	df(i,1)=subjname; % save out the sub ID
+    for eachNetwork = 1:17
+	df(i,eachNetwork+1)=num2cell(sum(V2(:,eachNetwork))); % sum loadings
+    end
+	i
+end
+
+writetable(cell2table(df),'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/All_PFN_sizes.csv')
+	

### 2022-08-31 CopiesOfCuiRepScripts/CuiColorMap.R
Delete CopiesOfCuiRepScripts directory

@@ -1,24 +1,0 @@
-"#7499C2", 4
-"#7499C2", 13
-"#AF33AD", 10
-"#F5BA2E", 15
-"#7499C2", 2
-"#AF33AD", 6
-"#7499C2", 11
-"#E443FF", 7
-"#E76178", 8
-"#4E31A8", 16
-"#E76178", 12
-"#00A131", 14
-"#00A131", 5
-"#E76178", 1
-"#F5BA2E", 17
-"#F5BA2E", 3
-"#E443FF" 9
-
-
-
-
-
-
-

### 2022-08-31 CopiesOfCuiRepScripts/CuiRep_BarPlot.m

@@ -1,49 +1,0 @@
-
-clear all
-
-z_vec = [-0.7272896 -3.0618619  3.2424142 -4.1576597  0.4844896  2.7263041  1.5161223  2.2195368 -0.2067699 -1.0122599 -1.1448722  1.2091494  2.3374685  1.1452890  3.4992115  1.0181162  4.2734299];
-z_vec_sorted = sort(z_vec);
-keep_p = [0 1 1 1 0 0 0 0 0 0 0 0 0 0 1 0 1];
-network_colors = [1 0.2 0.2; 0.4 0.6 0.8; 1 0.8 0.2; 0.4 0.6 0.8; 0 .4 0; 0.6 0 0.6; 1 0 0.8; 1 0.2 0.2; 1 0 0.8; 0.6 0 0.6; 0.4 0.6 0.8; 1 0.2 0.2; 0.4 0.6 0.8; 0 .4 0; 1 0.8 0.2; 0 0 0.6; 1 0.8 0.2];
-
-figure()
-for i = 1:17
-if keep_p(z_vec==z_vec_sorted(i))
-  bar(i,z_vec_sorted(i),'FaceColor',network_colors(z_vec==z_vec_sorted(i),1:3),'EdgeColor','w')
-hold on  
-else
-     bar(i,z_vec_sorted(i),'w','EdgeColor',network_colors(z_vec==z_vec_sorted(i),1:3))
-hold on  
-end
-end
-xticks([1:17])
-xticklabels({'4','2','11','10','1','9','5','16','14','12','7','8','13','6','3','15','17'})
-xlabel('Networks')
-ylabel('Cognition Association (Z)')
-axis([0 18 -4.5 6])
-
-
-%% SAME THING IN TEST SET
-
-clear all
-
-z_vec = [2.3579583 -1.3893710  3.0733065 -7.8620168  0.5033792  5.2102436 -0.7345963  0.9642072 -1.5014385  0.2726571  2.7748788 -0.4367185 -2.2333869  0.9093127  3.7563792  0.6383354  4.6654067];
-z_vec_sorted = sort(z_vec);
-keep_p = [0 0 1 1 0 1 0 0 0 0 0 0 0 0 1 0 1];
[…]

### 2022-08-31 CopiesOfCuiRepScripts/CuiRep_Fig6.R

@@ -1,167 +1,0 @@
-
-# This script has been adapted by ASK to recreate Figure 6 from Cui et al. 2020 using ABCD data
-
-library('R.matlab');
-library('mgcv');
-library('ggplot2');
-library('visreg');
-library('ggtext')
-
-# ProjectFolder <- '/data/jux/BBL/projects/pncSingleFuncParcel/Replication';
-# Behavior <- read.csv(paste0(ProjectFolder, '/data/n693_Behavior_20181219.csv'));
-# Behavior_New <- data.frame(BBLID = Behavior$bblid);
-# Behavior_New$AgeYears <- as.numeric(Behavior$ageAtScan1/12);
-# Motion <- (Behavior$restRelMeanRMSMotion + Behavior$nbackRelMeanRMSMotion + Behavior$idemoRelMeanRMSMotion)/3;
-# Behavior_New$Motion <- as.numeric(Motion);
-# Behavior_New$Sex_factor <- as.factor(Behavior$sex);
-# Behavior_New$F1_Exec_Comp_Res_Accuracy <- as.numeric(Behavior$F1_Exec_Comp_Res_Accuracy);
-# AtlasLoading_Folder <- paste0(ProjectFolder, '/Revision/SingleParcellation/SingleAtlas_Analysis/FinalAtlasLoading');
-# 
-# SubjectsQuantity = 693;
-# FeaturesQuantity = 17734;
-# # Extract Loading
-# Data_Size <- SubjectsQuantity * FeaturesQuantity * 17;
-# Data_All <- matrix(0, 1, Data_Size);
-# dim(Data_All) <- c(SubjectsQuantity, FeaturesQuantity, 17);
-# BBLID <- Behavior_New$BBLID;
-# for (i in c(1:length(BBLID)))
-# {
-#   print(i);
-#   AtlasLoading_File <- paste0(AtlasLoading_Folder, '/', as.character(BBLID[i]), '.mat');
-#   Data <- readMat(AtlasLoading_File);
-#   Data_All[i,,] <- Data$sbj.AtlasLoading.NoMedialWall;
-# }
-# 
-# Gam_Z_Vector_Age_WholeNetworkSum <- matrix(0, 1, 17);
-# Gam_P_Vector_Age_WholeNetworkSum <- matrix(0, 1, 17);
-# Gam_P_Vector_Cognition_WholeNetworkSum <- matrix(0, 1, 17);
[…]

### 2022-08-31 CopiesOfCuiRepScripts/CuiRep_GetVariability.m

@@ -1,98 +1,0 @@
-%
-% For variability of probability atlas:
-% Using MADM=median(|x(i) - median(x)|) to calculate variability
-% For variability of hard label atlas:
-% See: 
-%   https://stats.stackexchange.com/questions/221332/variance-of-a-distribution-of-multi-level-categorical-data
-%
-
-clear
-WorkingFolder = '/data/jux/BBL/projects/pncSingleFuncParcel/Replication/Revision/SingleParcellation/SingleAtlas_Analysis';
-
-SubjectsFolder = '/share/apps/freesurfer/6.0.0/subjects/fsaverage5';
-surfML = '/data/jux/BBL/projects/pncSingleFuncParcel/Replication/data/SNR_Mask/subjects/fsaverage5/lh.Mask_SNR.label';
-mwIndVec_l = read_medial_wall_label(surfML);
-Index_l = setdiff([1:10242], mwIndVec_l); % 10,242 refers to vertices in fsaverage5 
-surfMR = '/data/jux/BBL/projects/pncSingleFuncParcel/Replication/data/SNR_Mask/subjects/fsaverage5/rh.Mask_SNR.label';
-mwIndVec_r = read_medial_wall_label(surfMR);
-Index_r = setdiff([1:10242], mwIndVec_r);
-
-%
-% Variability of probability atlas
-%
-LoadingFolder = [WorkingFolder '/FinalAtlasLoading'];
-DataCell = g_ls([LoadingFolder '/*.mat']);
-for i = 1:length(DataCell)
-  i
-  tmp = load(DataCell{i});
-  for j = 1:17
-    cmd = ['sbj_Loading_lh_Matrix_' num2str(j) '(i, :) = tmp.sbj_AtlasLoading_lh(j, :);'];
-    eval(cmd);
-    cmd = ['sbj_Loading_rh_Matrix_' num2str(j) '(i, :) = tmp.sbj_AtlasLoading_rh(j, :);'];
-    eval(cmd);
-  end
-end
-%
-Variability_Visualize_Folder = [WorkingFolder '/Variability_Visualize'];
-mkdir(Variability_Visualize_Folder);
-Variability_All_lh = zeros(17, 10242);
-Variability_All_rh = zeros(17, 10242);
-for m = 1:17
-  m
-  for n = 1:10242
-    % left hemi
-    cmd = ['tmp_data = sbj_Loading_lh_Matrix_' num2str(m) '(:, n);'];
-    eval(cmd);
[…]

### 2022-08-31 CopiesOfCuiRepScripts/CuiRep_Step_4th_Weight_Visualize_Workbench_EFAccuracy_RandomCV.m

@@ -1,159 +1,0 @@
-
-
-clear all
-
-% Add package to read NPY files into matlab
-addpath('/Users/askeller/Documents/npy-matlab/')
-
-% note: the coefs matrix is 10 rows (folds) x 1010004 (weights at each of 59,412 vertices for each of 17 networks)
-coefs = readNPY('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_Mar2922/all_network/thompson_PC1_coefs.npy');
-
-% Average over 10 folds
-coefs_avg = mean(coefs,1);
-
-
-
-% ReplicationFolder = '/data/jux/BBL/projects/pncSingleFuncParcel/Replication';
-% PredictionFolder = [ReplicationFolder '/Revision/PredictionAnalysis/AtlasLoading/'];
-% Results_Cell = g_ls([PredictionFolder '/2Fold_RandomCV_EFAccuracy/Time_*/Fold_*_Score.mat']);
-% for i = 1:length(Results_Cell)
-% tmp = load(Results_Cell{i});
-% w_Brain_EFAccuracy_AllModels(i, :) = tmp.w_Brain;
-% end
-%w_Brain_EFAccuracy = mean(w_Brain_EFAccuracy_AllModels);
-%VisualizeFolder = [PredictionFolder '/WeightVisualize_EFAccuracy_RandomCV'];
-%mkdir(VisualizeFolder);
-
-% SubjectsFolder = '/share/apps/freesurfer/6.0.0/subjects/fsaverage5';
-% % for surface data
-% surfML = '/data/jux/BBL/projects/pncSingleFuncParcel/Replication/data/SNR_Mask/subjects/fsaverage5/lh.Mask_SNR.label';
-% mwIndVec_l = read_medial_wall_label(surfML);
-% Index_l = setdiff([1:10242], mwIndVec_l);
-% surfMR = '/data/jux/BBL/projects/pncSingleFuncParcel/Replication/data/SNR_Mask/subjects/fsaverage5/rh.Mask_SNR.label';
-% mwIndVec_r = read_medial_wall_label(surfMR);
-% Index_r = setdiff([1:10242], mwIndVec_r);
-
-% load([PredictionFolder '/AtlasLoading_All_RemoveZero.mat']); % NonZeroIndex was here
-
-
-%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%
[…]

### 2022-08-31 CopiesOfCuiRepScripts/Rep_SumWeights_EF.R

@@ -1,177 +1,0 @@
-# This is ASK's replication of Zaixu's script "Step_5th_SumWeights_EF.R" that 
-# will try to recapitulate Figure 7C in his 2020 Neuron paper showing the sum of 
-# the importance of topographic features by network. 
-
-
-library(R.matlab)
-library(ggplot2)
-
-
-#ResultsFolder = '/data/jux/BBL/projects/pncSingleFuncParcel/Replication/Revision';
-#PredictionFolder = paste0(ResultsFolder, '/PredictionAnalysis/AtlasLoading');
-WeightFolder = '/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_7C_SumLoadings/';
-Weight_EFAccuracy_Mat = readMat(paste0(WeightFolder, '/w_Brain_EFAccuracy_Matrix.mat'));
-Weight_EFAccuracy_Matrix = Weight_EFAccuracy_Mat$w.Brain.EFAccuracy.Matrix;
-
-#EFAccuracyEffect_Folder = paste0(ResultsFolder, '/GamAnalysis/AtlasLoading/CognitionEffects');
-# plot contributing weight for age prediction
-data <- data.frame(group = matrix(0, 34, 1));
-data$x <- matrix(0, 34, 1);
-data$y <- matrix(0, 34, 1);
-Pos_Weight <- matrix(0, 1, 17);
-for (i in c(1:17)){
-  EFAccuracyWeight_tmp = Weight_EFAccuracy_Matrix[i,];
-  data$group[i] = 'Below';
-  data$x[i] = i;
-  data$y[i] = sum(EFAccuracyWeight_tmp[which(EFAccuracyWeight_tmp > 0)]);
-  data$group[i + 17] = 'Above';
-  data$x[i + 17] = i;
-  data$y[i + 17] = sum(EFAccuracyWeight_tmp[which(EFAccuracyWeight_tmp < 0)]);
-  Pos_Weight[i] = data$y[i];
-}
-WeightSort <- sort(Pos_Weight, index.return = TRUE);
-Rank <- WeightSort$ix;
-data$x[1:17] <- data$x[1:17][Rank];
-data$y[1:17] <- data$y[1:17][Rank];
-data$x[18:34] <- data$x[18:34][Rank];
-data$y[18:34] <- data$y[18:34][Rank];
-data$x_New <- rbind(as.matrix(c(1:17)),as.matrix(c(1:17)));
-data$x_ <- as.character(data$x_New);
[…]

### 2022-08-31 CopiesOfCuiRepScripts/ViolinPlot_PFNvariability_CuiRep_FromOldLaptop.R

@@ -1,70 +1,0 @@
-# This code is copied and adapted for use with the ABCDFNETS data from Zaixu's script:
-# Step_10th_ViolinPlot_AtlasVariability_Loading.R (on the github pncSingleFuncParcel)
-
-library(R.matlab)
-library(ggplot2);
-
-ResultsFolder = '/Users/askeller/Documents/Kellernet_PrelimAnalysis/';
-AtlasFolder = paste0(ResultsFolder, 'SArank_PFNs/');
-Variability_Mat = readMat(paste0(ResultsFolder,'VariabilityByPFN_Trimmed.mat'));
-
-AtlasLabel_Mat = readMat(paste0(AtlasFolder, '/sbj_AtlasLabel_NoMedialWall_Keller.mat'));
-
-#Variability=as.matrix(Variability_Mat[1])
-
-AllData = data.frame(Variability = matrix(0, 59412, 1));
-AllData$Label = matrix(0, 59412, 1);
-for (i in c(1:59412))
-{
-  AllData$Variability[i] = Variability_Mat$Variability.All[i];
-  AllData$Label[i] = AtlasLabel_Mat$sbj.AtlasLabel.NoMedialWall[i];
-}
-AllData$Variability = as.numeric(AllData$Variability);
-AllData$Label = as.factor(AllData$Label);
-
-
-
-# NOTE: A.S.K ADDING A STEP HERE
-# In Zaixu's original version, this step was not present. I noticed that a lot of the variability values are exactly 0, and this is because a lot of the loading values are dropped to zero. We also are using fslr here which has 59K vertices, whereas Zaixu's version had far fewer. For now, I will eliminate vertices where the variability is exactly 0 (out to like 7 decimal places) since this very likely indicates the loading was zero for all subjects. 
-#AllData = AllData[AllData$Variability!=0.0000000,]
-AllData=AllData[complete.cases(AllData),]
-
-# Order the network by the median value 
-MedianValue = matrix(0, 1, 17);
-for (i in c(1:17)) {
-  ind = which(AllData$Label == i);
-  MedianValue[i] = median(AllData$Variability[ind],na.rm=TRUE);
-}
-tmp = sort(MedianValue, index.return = TRUE);
-
-
-ColorScheme = c("#E76178", "#7499C2", "#F5BA2E", "#7499C2", "#00A131",
[…]

### 2022-08-31 CopiesOfCuiRepScripts/variability_by_pfn3.m

@@ -1,57 +1,0 @@
-% This script will be used to replicate Cui et al. 2020 Neuron Figure 3B
-% (or at least prep the matrices we need to do so).
-
-
-clear all
-
-%file_pattern='/gpfs/fs001/cbica/projects/abcdfnets/results/SingleParcel_1by1/sub-NDARINV*/IndividualParcel_Final_sbj1_comp17_alphaS21_1_alphaL300_vxInfo1_ard0_eta0/final_UV.mat'
-file_pattern='/cbica/projects/abcdfnets/results/SingleParcel_1by1/sub-NDARINV*/IndividualParcel_Final_sbj1_comp17_alphaS21_1_alphaL300_vxInfo1_ard0_eta0/final_UV.mat'
-data_dir=dir(file_pattern);
-data_locations=fullfile({data_dir.folder}, {data_dir.name});
-
-% initialize matrices
-for eachNetwork1 = 1:17
-    eval(['sbj_by_vtx_network' num2str(eachNetwork1) ' = [];'])
-end
-
-
-% Get a separate subject x vertex matrix for each network
-for i = 1:length(data_locations)
-    i
-    UV=load(char(data_locations(i)));
-    V=UV.V; % The V matrix contains the loadings at each vertex by network
-    V=cell2mat(V);
-
-    % ASK is adding this for variability_by_pfn3 to see whether trimming
-    % these small loadings helps:
-
-    % apply ZC code from step 6th - subject AtlasLabel will have parcels for viz
-    V_Max = max(V);
-    trimInd = V ./ max(repmat(V_Max, size(V, 1), 1), eps) < 5e-2;
-    V(trimInd) = 0;
-    %sbj_AtlasLoading_NoMedialWall = V;
-    %[~, sbj_AtlasLabel_NoMedialWall] = max(sbj_AtlasLoading_NoMedialWall, [], 2);
-
-
-    % Loop through each network, get vtx x subj matrix, then transpose
-    for eachNetwork2 = 1:17
-        eval(['sbj_by_vtx_network' num2str(eachNetwork2) '=[sbj_by_vtx_network' num2str(eachNetwork2) ' V(:,eachNetwork2)];'])
-    end
-end
-
-
-% Loop through each network's subject x vertex matrix and calculate
-% the across-subject variability
-Variability_All = zeros(17, size(V,1)); % networks by vertices
-for m = 1:17
-    m
[…]

### 2022-08-31 Step2_RidgeRegression/get_data_for_ridge.R
Step2_RidgeRegression

@@ -1,0 +1,65 @@
+
+# First load in the spatial extent of each PFN (they're in order, 1-17)
+# Then merge with the same datasets as above (NIH toolbox, trauma, etc.)
+pfn_sizes <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/All_PFN_sizes.csv")
+# Change PFN column names so they're sensible
+colnames(pfn_sizes)<-c("subjectkey","PFN1","PFN2","PFN3","PFN4","PFN5","PFN6","PFN7","PFN8","PFN9","PFN10","PFN11","PFN12","PFN13","PFN14","PFN15","PFN16","PFN17")
+
+# Load data
+newdata<-readRDS("/Users/askeller/Documents/Kellernet_PrelimAnalysis/DEAP-data-download_ThompsonScores_ResFamIncome.rds")
+newdata.baseline<-newdata[newdata$event_name=="baseline_year_1_arm_1",]
+colnames(newdata.baseline)[1]<-"subjectkey"
+all.data <- merge(pfn_sizes,newdata.baseline[,c("subjectkey", setdiff(colnames(newdata.baseline),colnames(pfn_sizes)))],by="subjectkey")
+
+
+# Remove subjects based on the following criteria:
+## 1) 8min of retained TRs (600 TRs)
+## 2) ABCD Booleans for rest and T1
+num_TRs <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/num_TRs_by_subj_redo.csv")
+data<-merge(all.data,num_TRs,by="subjectkey")
+data.clean<-data[data$numTRs>=600,]
+
+# Remove participants based on booleans from ABCD
+abcd_imgincl01 <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/abcd_imgincl01.csv")
+abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$eventnam=="baseline_year_1_arm_1",]
+abcd_imgincl01 <- abcd_imgincl01[!abcd_imgincl01$visit=="",] 
+abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_t1w_include==1,] 
+abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_rsfmri_include==1,]
+combined.data <- merge(data.clean,abcd_imgincl01[, c("subjectkey",'imgincl_t1w_include')],by="subjectkey") 
+
+# for simplicity, rename thompson variables
[…]

### 2022-08-31 Step2_RidgeRegression/preprocess.py

@@ -1,0 +1,60 @@
+import glob
+import h5py
+import numpy as np
+import os
+import pandas as pd
+from sklearn import preprocessing
+import sys
+
+"""
+hi. this is going to read these in, you basically just need 
+subjects: path to subjects!
+data_path: path to the actual features
+phenotypes: path to a csv with the to-be-predicted and the noise
+"""
+data_path ='/gpfs/fs001/cbica/projects/abcdfnets/results/SingleParcel_1by1/sub-NDAR{0}/IndividualParcel_Final_sbj1_comp17_alphaS21_1_alphaL300_vxInfo1_ard0_eta0/final_UV.mat'
+control =['sex','meanFD','abcd_site','interview_age']
+try: network = int(sys.argv[1])
+except: network = sys.argv[1]
+outdir = sys.argv[2]
+os.makedirs(outdir,exist_ok=True)
+"""
+load the subject measures 
+"""
+phenotypes = pd.read_csv('/gpfs/fs001/cbica/projects/abcdfnets/data_for_ridge_081822.csv') #load
+#phenotypes['subjectkey'] = np.core.defchararray.strip(phenotypes.subjectkey.values.astype(str),'NDAR_') #strip
+phenotypes = phenotypes.sort_values('subjectkey') #sort 
+phenotypes['meanFD'] = phenotypes['meanFD'].values.astype(np.float16) #saves space
+
+"""
+convert categorical vars to numerical, ie dummy encoding, for sites and sex
+"""
+for c in ['sex','abcd_site']:
+    dumb = pd.get_dummies(phenotypes[c]).astype(np.int8)
+    phenotypes = pd.merge(left=phenotypes,right=dumb,left_index=True,right_index=True)
+    for d in dumb.columns:
+        control.append(d) #we get a lot more columns so we put them in
+    control.remove(c) # remove the original categorical
+
+"""
+load in all the feature weights
+"""
+features = []
+for subject in phenotypes.subjectkey.values:
+    if os.path.exists(data_path.format(subject)) == False:
+        phenotypes = phenotypes.drop(phenotypes.index[phenotypes.subjectkey==subject])
+        continue
+    f = h5py.File(data_path.format(subject), 'r')
+    f = np.array(f[f['V'][0][0]]).astype(np.float16)
+    if type(network) == int:
+        f = f[network]
+    features.append(f)
+features = np.array(features)
[…]

### 2022-08-31 Step2_RidgeRegression/ridge_bootstrapping/keller_proc_predict_boot.py

@@ -1,0 +1,22 @@
+import sys
+import os
+
+homedir = sys.argv[1]
+tmpdir = sys.argv[2]
+network = sys.argv[3]
+phenotype_name = sys.argv[4]
+
+"""
+this makes the features and targets in tmpdir
+"""
+os.system('python /{0}/preprocess.py {1} {2}'.format(homedir,network,tmpdir))
+
+working_dir = homedir + '/results_matchedsamples_boot_081822/{0}_network/'.format(network)
+feature_path = '/{0}/features_{1}.npy'.format(tmpdir,network)
+phenotype_path = '/{0}/phenotypes_target.csv'.format(tmpdir)
+control_path = '/{0}/phenotypes_control.csv'.format(tmpdir)
+
+"""
+this does the actual ridge regression
+"""
+os.system('python /{0}/predict_matchedsamples_bootstrap.py {1} {2} {3} {4} {5} rel_family_id'.format(homedir,working_dir,feature_path,phenotype_path,phenotype_name,control_path))

### 2022-08-31 Step2_RidgeRegression/ridge_bootstrapping/submit_all_boot.py

@@ -1,0 +1,19 @@
+import os
+import sys
+import numpy as np
+"""
+this is the only script you actually should call, it will submit a job
+this job makes the features, and then does the regression. 
+only change the home_dir variable, everything else should run! 
+"""
+
+homedir = '/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller' #sys.argv[1] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/'
+
+tmpdir = '/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles_matchedsamples_boot_081822/' #os.environ['TMPDIR']
+networks = np.array(['all']) 
+network = 'all'
+
+GB = '200G'    
+
+for cog_score in ['thompson_PC1','thompson_PC2','thompson_PC3']:
+        os.system('qsub -l h_vmem={0},s_vmem={0} -N {1} -R y -V -j y -b y -o ~/sge/ -e ~/sge/ python {2}/keller_proc_predict_boot.py {2} {3} {4} {5}'.format(GB,cog_score.split('_')[1],homedir,tmpdir,network,cog_score))

### 2022-08-31 Step2_RidgeRegression/ridge_bootstrapping_null/keller_proc_predict_boot_null.py

@@ -1,0 +1,22 @@
+import sys
+import os
+
+homedir = sys.argv[1]
+tmpdir = sys.argv[2]
+network = sys.argv[3]
+phenotype_name = sys.argv[4]
+
+"""
+this makes the features and targets in tmpdir
+"""
+os.system('python /{0}/preprocess.py {1} {2}'.format(homedir,network,tmpdir))
+
+working_dir = homedir + '/results_matchedsamples_boot_null_081822/{0}_network/'.format(network)
+feature_path = '/{0}/features_{1}.npy'.format(tmpdir,network)
+phenotype_path = '/{0}/phenotypes_target.csv'.format(tmpdir)
+control_path = '/{0}/phenotypes_control.csv'.format(tmpdir)
+
+"""
+this does the actual ridge regression
+"""
+os.system('python /{0}/predict_matchedsamples_bootstrap_null.py {1} {2} {3} {4} {5} rel_family_id'.format(homedir,working_dir,feature_path,phenotype_path,phenotype_name,control_path))

### 2022-08-31 Step2_RidgeRegression/ridge_bootstrapping_null/predict_matchedsamples_bootstrap_null.py

@@ -1,0 +1,102 @@
+import glob
+import h5py
+import numpy as np
+import os
+import pandas as pd
+from sklearn.linear_model import RidgeCV
+from sklearn.model_selection import GroupKFold
+from sklearn.linear_model import LinearRegression
+from sklearn import preprocessing
+import sys
+from scipy.stats import pearsonr
+
+"""
+This script will run ridge regression. To run it, you need:
+
+working_dir: where you want your results saved, does not have to exist, we will make it
+feature_path: path to the actual features, should be a subject x features npy array
+phenotype_path: path to a csv with the to-be-predicted values
+phenotype_name: str of name of column in phenotype_path you want
+control_path: path to csv, regress these features from the features within each fold
+fold_group: in this instance, this is the ABCD train and test split, A for one group, B for the other
+
+"""
+
+folds = 100
+working_dir = sys.argv[1] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/'
+os.makedirs(working_dir,exist_ok=True)
+feature_path = sys.argv[2]  #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles/features_0.npy'
+phenotype_path = sys.argv[3] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles/phenotypes_target.csv'
+phenotype_name = sys.argv[4] #'thompson_PC1'
+control_path = sys.argv[5] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles/phenotypes_control.csv'
+fold_group = 'matched_group' #sys.argv[6] # in this instance, this is the ABCD train and test split, A for one group, B for the other
+
+"""
+load the subject measures you want to control for
+"""
+phenotypes_control = pd.read_csv(control_path)
+"""
+load in all the feature weights
+"""
+features = np.load(feature_path).astype(np.float16)
+"""
+this is adapted from pennlinckit.utils.predict
+"""
+targets = pd.read_csv(phenotype_path)[phenotype_name].values.astype(np.float16)
+fold_group = pd.read_csv(phenotype_path)[fold_group].values.astype(np.float16)
[…]

### 2022-08-31 Step2_RidgeRegression/ridge_bootstrapping_null/submit_all_boot_null.py

@@ -1,0 +1,19 @@
+import os
+import sys
+import numpy as np
+"""
+this is the only script you actually should call, it will submit a job
+this job makes the features, and then does the regression. 
+only change the home_dir variable, everything else should run! 
+"""
+
+homedir = '/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller' #sys.argv[1] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/'
+
+tmpdir = '/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles_matchedsamples_boot_null_081822/' #os.environ['TMPDIR']
+networks = np.array(['all']) 
+network = 'all'
+
+GB = '200G'    
+
+for cog_score in ['thompson_PC1','thompson_PC2','thompson_PC3']:
+        os.system('qsub -l h_vmem={0},s_vmem={0} -N {1} -R y -V -j y -b y -o ~/sge/ -e ~/sge/ python {2}/keller_proc_predict_boot_null.py {2} {3} {4} {5}'.format(GB,cog_score.split('_')[1],homedir,tmpdir,network,cog_score))

### 2022-08-31 Step2_RidgeRegression/ridge_matchedsamples/submit_all.py

@@ -1,0 +1,19 @@
+import os
+import sys
+import numpy as np
+"""
+this is the only script you actually should call, it will submit a job
+this job makes the features, and then does the regression. 
+only change the home_dir variable, everything else should run! 
+"""
+
+homedir = '/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller' #sys.argv[1] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/'
+
+tmpdir = '/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles_matchedsamples_081822/' #os.environ['TMPDIR']
+networks = np.array(['all']) 
+network = 'all'
+
+GB = '200G'    
+
+for cog_score in ['thompson_PC1','thompson_PC2','thompson_PC3']:
+        os.system('qsub -l h_vmem={0},s_vmem={0} -N {1} -R y -V -j y -b y -o ~/sge/ -e ~/sge/ python {2}/keller_proc_predict.py {2} {3} {4} {5}'.format(GB,cog_score.split('_')[1],homedir,tmpdir,network,cog_score))

### 2022-08-31 Step2_RidgeRegression/ridge_matchedsamples_null/predict_matchedsamples_null.py

@@ -1,0 +1,103 @@
+import glob
+import h5py
+import numpy as np
+import os
+import pandas as pd
+from sklearn.linear_model import RidgeCV
+from sklearn.model_selection import GroupKFold
+from sklearn.linear_model import LinearRegression
+from sklearn import preprocessing
+import sys
+from scipy.stats import pearsonr
+
+"""
+This script will run ridge regression. To run it, you need:
+
+working_dir: where you want your results saved, does not have to exist, we will make it
+feature_path: path to the actual features, should be a subject x features npy array
+phenotype_path: path to a csv with the to-be-predicted values
+phenotype_name: str of name of column in phenotype_path you want
+control_path: path to csv, regress these features from the features within each fold
+fold_group: in this instance, this is the ABCD train and test split, A for one group, B for the other
+
+"""
+
+folds = 20
+working_dir = sys.argv[1] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/'
+os.makedirs(working_dir,exist_ok=True)
+feature_path = sys.argv[2]  #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles/features_0.npy'
+phenotype_path = sys.argv[3] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles/phenotypes_target.csv'
+phenotype_name = sys.argv[4] #'thompson_PC1'
+control_path = sys.argv[5] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles/phenotypes_control.csv'
+fold_group = 'matched_group' #sys.argv[6] # in this instance, this is the ABCD train and test split, A for one group, B for the other
+
+"""
+load the subject measures you want to control for
+"""
+phenotypes_control = pd.read_csv(control_path)
+"""
+load in all the feature weights
+"""
+features = np.load(feature_path).astype(np.float16)
+"""
+this is adapted from pennlinckit.utils.predict
+"""
+targets = pd.read_csv(phenotype_path)[phenotype_name].values.astype(np.float16)
+fold_group = pd.read_csv(phenotype_path)[fold_group].values.astype(np.float16)
[…]

### 2022-08-31 Step3_RidgeResultsPlotting/pred_acc_by_PFN.m
Step3_RidgeResultsPlotting

@@ -1,0 +1,238 @@
+%% calculate prediction accuracy within each network.
+
+clear all
+
+% Add package to read NPY files into matlab
+addpath('/Users/askeller/Documents/npy-matlab/')
+
+% fourth column has the matched_group
+data_for_ridge=xlsread('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/data_for_ridge_081822.xls');
+
+% Load in actual cognitive scores
+actual_PC1 = data_for_ridge(:,1);
+actual_PC2 = data_for_ridge(:,2);
+actual_PC3 = data_for_ridge(:,3);
+
+% split data out by matched group
+actual_PC1_samp1 = actual_PC1(data_for_ridge(:,4)==1);
+actual_PC1_samp2 = actual_PC1(data_for_ridge(:,4)==2);
+actual_PC2_samp1 = actual_PC2(data_for_ridge(:,4)==1);
+actual_PC2_samp2 = actual_PC2(data_for_ridge(:,4)==2);
+actual_PC3_samp1 = actual_PC3(data_for_ridge(:,4)==1);
+actual_PC3_samp2 = actual_PC3(data_for_ridge(:,4)==2);
+
+% decision was to combine across the samples, so we will concatenate:
+actual_PC1 = [actual_PC1_samp1; actual_PC1_samp2];
+actual_PC2 = [actual_PC2_samp1; actual_PC2_samp2];
+actual_PC3 = [actual_PC3_samp1; actual_PC3_samp2];
+
+
+% matrix to collect R values by PFN
+Rvals_byPFN = zeros(17,3);
+
+
+% loop through each PFN and calculate the R value
+for eachPFN = 0:16
+
+eval(['folder_name=''/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/' num2str(eachPFN) '_network'';'])
+
+% Load the predicted cognitive scores from the ridge regression
+file_name_pred1_samp1='thompson_PC1_prediction_testA.npy';
+file_name_pred2_samp1='thompson_PC2_prediction_testA.npy';
+file_name_pred3_samp1='thompson_PC3_prediction_testA.npy';
+file_name_pred1_samp2='thompson_PC1_prediction_testB.npy';
[…]

### 2022-08-31 Step4_PredAccSAaxis/SA_rank_by_PFN_spins.Rmd
Step4_PredAccSAaxis

---
title: "R Notebook"
output: html_notebook
---

# This markdown will be used to compare S-A axis rank to prediction accuracy within each PFN
# We'll do this analysis in fsaverage5, since this downsampled version allows us to run spin tests

# Load in the libraries
```{r}
library(gifti)
library(R.matlab)
library(RNifti)
library(ciftiTools)
ciftiTools.setOption('wb_path', '/Users/askeller/Documents/workbench/')
library(ggplot2)
library(randomcoloR)
library(ggforce)
library(mgcv)
```

# Get PFN hard parcel assignment in fsaverage5 space
# Note: range of values is 1-17 for the right hemisphere but 1-16 for the left hemisphere (network 17 is right lateralized)
```{r}
# Load in gifti files with PFN hard parcel assignment
PFNs_gii_L<-read_gifti('/Users/askeller/Documents/Kellernet_PrelimAnalysis/SpinTests/hardparcel_LH.fsaverage5.label.gii')
PFNs_gii_R<-read_gifti('/Users/askeller/Documents/Kellernet_PrelimAnalysis/SpinTests/hardparcel_RH.fsaverage5.label.gii')

# Extract the list of ranks
PFNs_L <- PFNs_gii_L[["data"]][["labels"]]
PFNs_R <- PFNs_gii_R[["data"]][["labels"]]
```

# Get S-A axis rank by PFN in fsaverage5 space
```{r}
# Load in gifti files with S-A axis ranks in fsaverage5 from Val's github repo
SA_axis_gii_L<-read_gifti('/Users/askeller/Documents/Kellernet_PrelimAnalysis/SpinTests/SensorimotorAssociation_Axis_LH.fsaverage5.func.gii')
SA_axis_gii_R<-read_gifti('/Users/askeller/Documents/Kellernet_PrelimAnalysis/SpinTests/SensorimotorAssociation_Axis_RH.fsaverage5.func.gii')

# Extract the list of ranks
SA_L <- SA_axis_gii_L[["data"]][["normal"]]
SA_R <- SA_axis_gii_R[["data"]][["normal"]]

SArank_byPFN <- vector()

for (i in 1:17) {
SArank_byPFN[i] <- mean(c(SA_L[PFNs_L==i],SA_R[PFNs_R==i]))
}
```

# Load in prediction accuracy by PFN
```{r}
predacc <- read.csv('/Users/askeller/Documents/Kellernet_PrelimAnalysis/SpinTests/pred_acc_by_PFN.csv')
predacc_PC1 <- predacc$PC1
predacc_PC2 <- predacc$PC2
predacc_PC3 <- predacc$PC3
```

# Calculate spearman rank correlation for the actual S-A axis rank by PFN
```{r}
cor.test(predacc_PC1,SArank_byPFN,method="spearman")
cor.test(predacc_PC2,SArank_byPFN,method="spearman")
cor.test(predacc_PC3,SArank_byPFN,method="spearman")

result_PC1<-cor.test(predacc_PC1,SArank_byPFN,method="spearman")
result_PC2<-cor.test(predacc_PC2,SArank_byPFN,method="spearman")
result_PC3<-cor.test(predacc_PC3,SArank_byPFN,method="spearman")
```

# Load in the results of the spin testing (from SpinTests_ABCD.m which calls AAB's package)
```{r}
Spin_Results_Mat = readMat('/Users/askeller/Documents/Kellernet_PrelimAnalysis/SpinTests/GroupAtlasLabel_Perm.mat');
```

# Compute null distribution of spearman rank correlations with spin test results 
```{r}
SArank_byPFN_spins <- matrix(0,17,1000)
for (it in 1:1000) {
  for (net in 1:17) {
    if (net == 17) {
      SArank_byPFN_spins[net,it] <- mean(Spin_Results_Mat$bigrotr[it,PFNs_R==net])
    } else {
    SArank_byPFN_spins[net,it] <- mean(c(Spin_Results_Mat$bigrotl[it,PFNs_L==net],Spin_Results_Mat$bigrotr[it,PFNs_R==net]))
    }
  }
}

null_spearman_PC1 <- matrix(0,1,1000)
null_spearman_PC2 <- matrix(0,1,1000)
null_spearman_PC3 <- matrix(0,1,1000)
for (it2 in 1:1000) {
spcorr1<-cor.test(predacc_PC1,SArank_byPFN_spins[,it2],method="spearman")
null_spearman_PC1[1,it2]<-spcorr1$estimate

spcorr2<-cor.test(predacc_PC2,SArank_byPFN_spins[,it2],method="spearman")
null_spearman_PC2[1,it2]<-spcorr2$estimate

spcorr3<-cor.test(predacc_PC3,SArank_byPFN_spins[,it2],method="spearman")
null_spearman_PC3[1,it2]<-spcorr3$estimate
}

# check null distributions
hist(null_spearman_PC1)
hist(null_spearman_PC2)
hist(null_spearman_PC3)
```

# Plot the results
```{r}
png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC1acc_Spins.png",
    width = 2000, 
    height = 2000,
    res=750)
hist(null_spearman_PC1,xlab="Spearman Correlations",border="lightgray",xlim=c(-1,1))
abline(v=result_PC1$estimate,col="goldenrod",lwd=4)
dev.off()

png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC2acc_Spins.png",
    width = 2000, 
    height = 2000,
    res=750)
hist(null_spearman_PC2,xlab="Spearman Correlations",border="lightgray",xlim=c(-1,1))
abline(v=result_PC2$estimate,col="goldenrod",lwd=4)
dev.off()

png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC3acc_Spins.png",
    width = 2000, 
    height = 2000,
    res=750)
hist(null_spearman_PC3,xlab="Spearman Correlations",border="lightgray",xlim=c(-1,1))
abline(v=result_PC3$estimate,col="goldenrod",lwd=4)
dev.off()

df.acc.SA <- cbind.data.frame(predacc_PC1,predacc_PC2,predacc_PC3,SArank_byPFN)

#ggplot(data=df.acc.SA,aes(SArank_byPFN,predacc_PC1)) + geom_bar(stat="identity",fill=SArank_byPFN)

png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC1acc.png",
    width = 4000, 
    height = 4000,
    res=1000)
ggplot(data=df.acc.SA,aes(SArank_byPFN,predacc_PC1,color=SArank_byPFN)) + geom_point(size=3) + geom_smooth(method=lm,color='black') + theme_classic() +
  theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 30000) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy (General Cognition)")
dev.off()

png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC2acc.png",
    width = 4000, 
    height = 4000,
    res=1000)
ggplot(data=df.acc.SA,aes(SArank_byPFN,predacc_PC2,color=SArank_byPFN)) + geom_point(size=3) + geom_smooth(method=lm,color='black') + theme_classic() +
  theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 30000) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy (Executive Function)")
dev.off()

png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC3acc.png",
    width = 4000, 
    height = 4000,
    res=1000)
ggplot(data=df.acc.SA,aes(SArank_byPFN,predacc_PC3,color=SArank_byPFN)) + geom_point(size=3) + geom_smooth(method=lm,color='black') + theme_classic() +
  theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 30000) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy (Learning/Memory)")
dev.off()

```

# wider format figures for poster 
```{r}
png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC1acc_wide.png",
    width = 3000, 
    height = 2800,
    res=1000)
ggplot(data=df.acc.SA,aes(SArank_byPFN,predacc_PC1,color=SArank_byPFN)) + geom_point(size=3) + geom_smooth(method=lm,color='black') + theme_classic() +
  theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 30000) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy")
dev.off()

png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC2acc_wide.png",
    width = 3000, 
    height = 2800,
    res=1000)
ggplot(data=df.acc.SA,aes(SArank_byPFN,predacc_PC2,color=SArank_byPFN)) + geom_point(size=3) + geom_smooth(method=lm,color='black') + theme_classic() +
  theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 30000) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy")
dev.off()

png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC3acc_wide.png",
    width = 3000, 
    height = 2800,
    res=1000)
ggplot(data=df.acc.SA,aes(SArank_byPFN,predacc_PC3,color=SArank_byPFN)) + geom_point(size=3) + geom_smooth(method=lm,color='black') + theme_classic() +
  theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 30000) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy")
dev.off()

png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC1acc_Spins_wide.png",
    width = 1500, 
    height = 1800,
    res=500)
hist(null_spearman_PC1,xlab="Spearman Correlations",border="lightgray",xlim=c(-1,1))
abline(v=result_PC1$estimate,col="goldenrod",lwd=4)
dev.off()

png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC2acc_Spins_wide.png",
    width = 1500, 
    height = 1800,
    res=500)
hist(null_spearman_PC2,xlab="Spearman Correlations",border="lightgray",xlim=c(-1,1))
abline(v=result_PC2$estimate,col="goldenrod",lwd=4)
dev.off()

png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC3acc_Spins_wide.png",
    width = 1500, 
    height = 1800,
    res=500)
hist(null_spearman_PC3,xlab="Spearman Correlations",border="lightgray",xlim=c(-1,1))
abline(v=result_PC3$estimate,col="goldenrod",lwd=4)
dev.off()
```

### 2022-08-31 Step4_PredAccSAaxis/SpinTests_ABCD.m

@@ -1,0 +1,20 @@
+clear
+
+% set up folders
+HomeFolder = '/cbica/projects/abcdfnets/scripts';
+SpinTest_Folder = [HomeFolder '/keller_spins'];
+PermuteData_Folder = [SpinTest_Folder '/PermuteData'];
+mkdir(PermuteData_Folder);
+Configuration_Folder = [SpinTest_Folder '/Configuration'];
+mkdir(Configuration_Folder);
+
+% Spin permutation for group atlas
+AtlasLabel_lh_CSV_Path = [SpinTest_Folder '/SA_AvgRank_LH.csv'];
+AtlasLabel_rh_CSV_Path = [SpinTest_Folder '/SA_AvgRank_RH.csv'];
+AtlasLabel_Perm_File = [PermuteData_Folder '/GroupAtlasLabel_Perm.mat'];
+Configuration_File = [Configuration_Folder '/Configuration_Group.mat'];
+save(Configuration_File, 'AtlasLabel_lh_CSV_Path', 'AtlasLabel_rh_CSV_Path', 'AtlasLabel_Perm_File');
+ScriptPath = [Configuration_Folder '/Script_Group.sh'];
+addpath(genpath('/cbica/projects/abcdfnets/scripts')
+SpinPermuFS(AtlasLabel_lh_CSV_Path, AtlasLabel_rh_CSV_Path, 1000, AtlasLabel_Perm_File)
+

### 2022-08-31 Step4_PredAccSAaxis/convert_SAranks_gii_to_csv.R

@@ -1,0 +1,12 @@
+
+# Load in gifti files with S-A axis ranks in fsaverage5 from Val's github repo
+SA_axis_gii_L<-read_gifti('/Users/askeller/Documents/Kellernet_PrelimAnalysis/SpinTests/SensorimotorAssociation_Axis_LH.fsaverage5.func.gii')
+SA_axis_gii_R<-read_gifti('/Users/askeller/Documents/Kellernet_PrelimAnalysis/SpinTests/SensorimotorAssociation_Axis_RH.fsaverage5.func.gii')
+
+# Extract the list of ranks
+SA_L <- SA_axis_gii_L[["data"]][["normal"]]
+SA_R <- SA_axis_gii_R[["data"]][["normal"]]
+
+# Save them as a csv
+write.csv(SA_L,"/Users/askeller/Documents/Kellernet_PrelimAnalysis/SpinTests/SA_AvgRank_LH.csv")
+write.csv(SA_R,"/Users/askeller/Documents/Kellernet_PrelimAnalysis/SpinTests/SA_AvgRank_RH.csv")

### 2022-08-31 Step5_SumWeights/convert_numpy_arrays_to_mats.py
Step5_SumWeights

@@ -1,0 +1,27 @@
+import numpy as np
+from scipy.io import savemat
+
+PC1_testA=np.load('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/all_network/thompson_PC1_coefs_testA.npy')
+mdic={"PC1_testA": PC1_testA}
+savemat('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/all_network/thompson_PC1_coefs_testA.mat',mdic)
+
+PC2_testA=np.load('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/all_network/thompson_PC2_coefs_testA.npy')
+mdic={"PC2_testA": PC2_testA}
+savemat('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/all_network/thompson_PC2_coefs_testA.mat',mdic)
+
+PC3_testA=np.load('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/all_network/thompson_PC3_coefs_testA.npy')
+mdic={"PC3_testA": PC3_testA}
+savemat('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/all_network/thompson_PC3_coefs_testA.mat',mdic)
+
+
+PC1_testB=np.load('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/all_network/thompson_PC1_coefs_testB.npy')
+mdic={"PC1_testB": PC1_testB}
+savemat('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/all_network/thompson_PC1_coefs_testB.mat',mdic)
+
+PC2_testB=np.load('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/all_network/thompson_PC2_coefs_testB.npy')
+mdic={"PC2_testB": PC2_testB}
+savemat('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/all_network/thompson_PC2_coefs_testB.mat',mdic)
+
[…]

### 2022-08-31 Step5_SumWeights/transform_model_coefficients_to_sum_weights.m

@@ -1,0 +1,166 @@
+%% PC1 - test in subsample A (Discovery)
+
+clear all
+
+% note: the coefs matrix is 1010004 (weights at each of 59,412 vertices for each of 17 networks)
+coefs = load('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/all_network/thompson_PC1_coefs_testA.mat');
+coefs = coefs.PC1_testA;
+
+VertexQuantity = 59412; % 17734;
+
+w_Brain_EFAccuracy_Abs = abs(coefs); %abs(w_Brain_EFAccuracy);
+[~, Sorted_IDs] = sort(w_Brain_EFAccuracy_Abs);
+w_Brain_EFAccuracy_FirstPercent = w_Brain_EFAccuracy_Abs;
+w_Brain_EFAccuracy_FirstPercent(Sorted_IDs(1:round(length(Sorted_IDs) * 0.75))) = 0;
+
+
+% Absolute sum weights
+w_Brain_EFAccuracy_All = zeros(1, VertexQuantity*17);
+w_Brain_EFAccuracy_All(w_Brain_EFAccuracy_FirstPercent>0) = coefs(w_Brain_EFAccuracy_FirstPercent>0);
+
+% Display weight of all regions
+for i = 1:17
+    w_Brain_EFAccuracy_Matrix(i, :) = w_Brain_EFAccuracy_All([(i - 1) * VertexQuantity + 1 : i * VertexQuantity]);
+end
+save(['/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_7C_SumLoadings/w_Brain_PC1_testA.mat'], 'w_Brain_EFAccuracy_Matrix');
+
+
+
+%% PC 2 - test in subsample A (Discovery)
+
+clear all
+
+% note: the coefs matrix is 1010004 (weights at each of 59,412 vertices for each of 17 networks)
+coefs = load('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_081822/all_network/thompson_PC2_coefs_testA.mat');
+coefs = coefs.PC2_testA;
+
+VertexQuantity = 59412; % 17734;
+
+% Display the weight of the first 25% regions with the highest absolute weight
[…]

### 2022-09-12 Step1_TotalCorticalRepresentation/Associations_PFN_Cognition.Rmd
subject ID fix
added line 46 to fix the subject ID names (NDARINV vs. NDAR_INV)

@@
 colnames(pfn_sizes)<-c("subjectkey","PFN1","PFN2","PFN3","PFN4","PFN5","PFN6","PFN7","PFN8","PFN9","PFN10","PFN11","PFN12","PFN13","PFN14","PFN15","PFN16","PFN17")
+pfn_sizes$subjectkey<-gsub('sub-NDARINV','NDAR_INV',pfn_sizes$subjectkey)
 ```

### 2022-09-12 Step4_PredAccSAaxis/SA_rank_by_PFN_spins.Rmd
z-scored S-A axis ranks for viz

@@
 
+## Combine data frame and z-score the S-A axis ranks for visualization
 df.acc.SA <- cbind.data.frame(predacc_PC1,predacc_PC2,predacc_PC3,SArank_byPFN)
-
-#ggplot(data=df.acc.SA,aes(SArank_byPFN,predacc_PC1)) + geom_bar(stat="identity",fill=SArank_byPFN)
+df.acc.SA$SArank_byPFN <- (df.acc.SA$SArank_byPFN - mean(df.acc.SA$SArank_byPFN,na.rm=TRUE))/sd(df.acc.SA$SArank_byPFN,na.rm=TRUE)
 
@@
   theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
-  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 30000) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy (General Cognition)")
+  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 0) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy (General Cognition)")
 dev.off()
@@
   theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
-  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 30000) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy (Executive Function)")
+  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 0) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy (Executive Function)")
 dev.off()
@@
   theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
-  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 30000) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy (Learning/Memory)")
+  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 0) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy (Learning/Memory)")
 dev.off()
@@
   theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
-  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 30000) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy")
+  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 0) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy")
 dev.off()

### 2022-09-13 Step1_TotalCorticalRepresentation/Associations_PFN_Cognition.Rmd
confidence intervals and standardized coefs

@@
 
+# standardize all variables for LMER (separately in Discovery and Replication samples)
+```{r}
+abcd.data.train.harmonized$PFN3<-(abcd.data.train.harmonized$PFN3-mean(abcd.data.train.harmonized$PFN3,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN3,na.rm=TRUE)
+
+abcd.data.train.harmonized$PFN15<-(abcd.data.train.harmonized$PFN15-mean(abcd.data.train.harmonized$PFN15,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN15,na.rm=TRUE)
+
+abcd.data.train.harmonized$PFN17<-(abcd.data.train.harmonized$PFN17-mean(abcd.data.train.harmonized$PFN17,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN17,na.rm=TRUE)
+
+abcd.data.test.harmonized$PFN3<-(abcd.data.test.harmonized$PFN3-mean(abcd.data.test.harmonized$PFN3,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN3,na.rm=TRUE)
+
+abcd.data.test.harmonized$PFN15<-(abcd.data.test.harmonized$PFN15-mean(abcd.data.test.harmonized$PFN15,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN15,na.rm=TRUE)
+
+abcd.data.test.harmonized$PFN17<-(abcd.data.test.harmonized$PFN17-mean(abcd.data.test.harmonized$PFN17,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN17,na.rm=TRUE)
+
+abcd.data.train.harmonized$interview_age<-(abcd.data.train.harmonized$interview_age-mean(abcd.data.train.harmonized$interview_age,na.rm=TRUE))/sd(abcd.data.train.harmonized$interview_age,na.rm=TRUE)
+
+abcd.data.test.harmonized$interview_age<-(abcd.data.test.harmonized$interview_age-mean(abcd.data.test.harmonized$interview_age,na.rm=TRUE))/sd(abcd.data.test.harmonized$interview_age,na.rm=TRUE)
+
+abcd.data.train.harmonized$meanFD<-(abcd.data.train.harmonized$meanFD-mean(abcd.data.train.harmonized$meanFD,na.rm=TRUE))/sd(abcd.data.train.harmonized$meanFD,na.rm=TRUE)
+
+abcd.data.test.harmonized$meanFD<-(abcd.data.test.harmonized$meanFD-mean(abcd.data.test.harmonized$meanFD,na.rm=TRUE))/sd(abcd.data.test.harmonized$meanFD,na.rm=TRUE)
+
+```
+
 # linear mixed effects models associating general cognition with each fronto-parietal PFN
@@
 summary(lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
+```
+
+# get confidence intervals
+```{r}
+confint(lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
+confint(lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
+confint(lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
+
+confint(lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
+confint(lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
+confint(lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
 ```

### 2022-09-16 Step1_TotalCorticalRepresentation/Associations_PFN_Cognition.Rmd
add tables

@@
 summary(lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
+
+mod1<-lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized)
+mod2<-lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized)
+mod3<-lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized)
+mod4<-lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized)
+mod5<-lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized)
+mod6<-lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized)
+
+tab_model(mod1,mod2,mod3,pred.labels = c("Intercept","Age","Sex","Mean FD","General Cognition"),dv.labels=c("PFN 3","PFN 15","PFN 17"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = "/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/Associations_TableX_Discovery.doc")
+
+tab_model(mod4,mod5,mod6,pred.labels = c("Intercept","Age","Sex","Mean FD","General Cognition"),dv.labels=c("PFN 3","PFN 15","PFN 17"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = "/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/Associations_TableX_Replication.doc")
 ```

### 2023-04-12 Step1_TotalCorticalRepresentation/Associations_PFN_Cognition.Rmd
sensitivity analyses

@@
 
-combined.data <- merge(data.clean,abcd_imgincl01[, c("subjectkey",'imgincl_t1w_include')],by="subjectkey") 
+combined.data1 <- merge(data.clean,abcd_imgincl01[, c("subjectkey",'imgincl_t1w_include')],by="subjectkey") 
 ```
@@
 colnames(newdata.baseline)[1]<-"subjectkey"
-all.data <- merge(combined.data,newdata.baseline[,c("subjectkey", setdiff(colnames(newdata.baseline),colnames(combined.data)))],by="subjectkey")
+all.data <- merge(combined.data1,newdata.baseline[,c("subjectkey", setdiff(colnames(newdata.baseline),colnames(combined.data1)))],by="subjectkey")
 
@@
 colnames(all.data)<-gsub("neurocog_pc3.bl","thompson_PC3",colnames(all.data))
+
 ```
@@
 ```{r}
+abcd.data.train.harmonized$PFN1<-(abcd.data.train.harmonized$PFN1-mean(abcd.data.train.harmonized$PFN1,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN1,na.rm=TRUE)
+abcd.data.train.harmonized$PFN2<-(abcd.data.train.harmonized$PFN2-mean(abcd.data.train.harmonized$PFN2,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN2,na.rm=TRUE)
 abcd.data.train.harmonized$PFN3<-(abcd.data.train.harmonized$PFN3-mean(abcd.data.train.harmonized$PFN3,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN3,na.rm=TRUE)
-
+abcd.data.train.harmonized$PFN4<-(abcd.data.train.harmonized$PFN4-mean(abcd.data.train.harmonized$PFN4,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN4,na.rm=TRUE)
+abcd.data.train.harmonized$PFN5<-(abcd.data.train.harmonized$PFN5-mean(abcd.data.train.harmonized$PFN5,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN5,na.rm=TRUE)
+abcd.data.train.harmonized$PFN6<-(abcd.data.train.harmonized$PFN6-mean(abcd.data.train.harmonized$PFN6,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN6,na.rm=TRUE)
+abcd.data.train.harmonized$PFN7<-(abcd.data.train.harmonized$PFN7-mean(abcd.data.train.harmonized$PFN7,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN7,na.rm=TRUE)
+abcd.data.train.harmonized$PFN8<-(abcd.data.train.harmonized$PFN8-mean(abcd.data.train.harmonized$PFN8,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN8,na.rm=TRUE)
+abcd.data.train.harmonized$PFN9<-(abcd.data.train.harmonized$PFN9-mean(abcd.data.train.harmonized$PFN9,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN9,na.rm=TRUE)
+abcd.data.train.harmonized$PFN10<-(abcd.data.train.harmonized$PFN10-mean(abcd.data.train.harmonized$PFN10,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN10,na.rm=TRUE)
+abcd.data.train.harmonized$PFN11<-(abcd.data.train.harmonized$PFN11-mean(abcd.data.train.harmonized$PFN11,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN11,na.rm=TRUE)
+abcd.data.train.harmonized$PFN12<-(abcd.data.train.harmonized$PFN12-mean(abcd.data.train.harmonized$PFN12,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN12,na.rm=TRUE)
+abcd.data.train.harmonized$PFN13<-(abcd.data.train.harmonized$PFN13-mean(abcd.data.train.harmonized$PFN13,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN13,na.rm=TRUE)
+abcd.data.train.harmonized$PFN14<-(abcd.data.train.harmonized$PFN14-mean(abcd.data.train.harmonized$PFN14,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN14,na.rm=TRUE)
 abcd.data.train.harmonized$PFN15<-(abcd.data.train.harmonized$PFN15-mean(abcd.data.train.harmonized$PFN15,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN15,na.rm=TRUE)
-
+abcd.data.train.harmonized$PFN16<-(abcd.data.train.harmonized$PFN16-mean(abcd.data.train.harmonized$PFN16,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN16,na.rm=TRUE)
 abcd.data.train.harmonized$PFN17<-(abcd.data.train.harmonized$PFN17-mean(abcd.data.train.harmonized$PFN17,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN17,na.rm=TRUE)
 
+abcd.data.test.harmonized$PFN1<-(abcd.data.test.harmonized$PFN1-mean(abcd.data.test.harmonized$PFN1,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN1,na.rm=TRUE)
+abcd.data.test.harmonized$PFN2<-(abcd.data.test.harmonized$PFN2-mean(abcd.data.test.harmonized$PFN2,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN2,na.rm=TRUE)
 abcd.data.test.harmonized$PFN3<-(abcd.data.test.harmonized$PFN3-mean(abcd.data.test.harmonized$PFN3,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN3,na.rm=TRUE)
-
+abcd.data.test.harmonized$PFN4<-(abcd.data.test.harmonized$PFN4-mean(abcd.data.test.harmonized$PFN4,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN4,na.rm=TRUE)
+abcd.data.test.harmonized$PFN5<-(abcd.data.test.harmonized$PFN5-mean(abcd.data.test.harmonized$PFN5,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN5,na.rm=TRUE)
+abcd.data.test.harmonized$PFN6<-(abcd.data.test.harmonized$PFN6-mean(abcd.data.test.harmonized$PFN6,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN6,na.rm=TRUE)
+abcd.data.test.harmonized$PFN7<-(abcd.data.test.harmonized$PFN7-mean(abcd.data.test.harmonized$PFN7,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN7,na.rm=TRUE)
+abcd.data.test.harmonized$PFN8<-(abcd.data.test.harmonized$PFN8-mean(abcd.data.test.harmonized$PFN8,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN8,na.rm=TRUE)
+abcd.data.test.harmonized$PFN9<-(abcd.data.test.harmonized$PFN9-mean(abcd.data.test.harmonized$PFN9,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN9,na.rm=TRUE)
+abcd.data.test.harmonized$PFN10<-(abcd.data.test.harmonized$PFN10-mean(abcd.data.test.harmonized$PFN10,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN10,na.rm=TRUE)
+abcd.data.test.harmonized$PFN11<-(abcd.data.test.harmonized$PFN11-mean(abcd.data.test.harmonized$PFN11,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN11,na.rm=TRUE)
+abcd.data.test.harmonized$PFN12<-(abcd.data.test.harmonized$PFN12-mean(abcd.data.test.harmonized$PFN12,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN12,na.rm=TRUE)
+abcd.data.test.harmonized$PFN13<-(abcd.data.test.harmonized$PFN13-mean(abcd.data.test.harmonized$PFN13,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN13,na.rm=TRUE)
+abcd.data.test.harmonized$PFN14<-(abcd.data.test.harmonized$PFN14-mean(abcd.data.test.harmonized$PFN14,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN14,na.rm=TRUE)
 abcd.data.test.harmonized$PFN15<-(abcd.data.test.harmonized$PFN15-mean(abcd.data.test.harmonized$PFN15,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN15,na.rm=TRUE)
-
+abcd.data.test.harmonized$PFN16<-(abcd.data.test.harmonized$PFN16-mean(abcd.data.test.harmonized$PFN16,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN16,na.rm=TRUE)
 abcd.data.test.harmonized$PFN17<-(abcd.data.test.harmonized$PFN17-mean(abcd.data.test.harmonized$PFN17,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN17,na.rm=TRUE)
@@
 abcd.data.train.harmonized$interview_age<-(abcd.data.train.harmonized$interview_age-mean(abcd.data.train.harmonized$interview_age,na.rm=TRUE))/sd(abcd.data.train.harmonized$interview_age,na.rm=TRUE)
-
 abcd.data.test.harmonized$interview_age<-(abcd.data.test.harmonized$interview_age-mean(abcd.data.test.harmonized$interview_age,na.rm=TRUE))/sd(abcd.data.test.harmonized$interview_age,na.rm=TRUE)
@@
 abcd.data.train.harmonized$meanFD<-(abcd.data.train.harmonized$meanFD-mean(abcd.data.train.harmonized$meanFD,na.rm=TRUE))/sd(abcd.data.train.harmonized$meanFD,na.rm=TRUE)
-
 abcd.data.test.harmonized$meanFD<-(abcd.data.test.harmonized$meanFD-mean(abcd.data.test.harmonized$meanFD,na.rm=TRUE))/sd(abcd.data.test.harmonized$meanFD,na.rm=TRUE)
 
+abcd.data.train.harmonized$reshist_addr1_adi_income<-(abcd.data.train.harmonized$reshist_addr1_adi_income-mean(abcd.data.train.harmonized$reshist_addr1_adi_income,na.rm=TRUE))/sd(abcd.data.train.harmonized$reshist_addr1_adi_income,na.rm=TRUE)
+abcd.data.test.harmonized$reshist_addr1_adi_income<-(abcd.data.test.harmonized$reshist_addr1_adi_income-mean(abcd.data.test.harmonized$reshist_addr1_adi_income,na.rm=TRUE))/sd(abcd.data.test.harmonized$reshist_addr1_adi_income,na.rm=TRUE)
 ```
@@
 Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = "/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/Associations_TableX_Replication.doc")
+
+# sensitivity analysis with ADI as an additional covariate:
+mod101<-lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+reshist_addr1_adi_income+thompson_PC1,data=abcd.data.train.harmonized)
+mod102<-lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+reshist_addr1_adi_income+thompson_PC1,data=abcd.data.train.harmonized)
+mod103<-lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+reshist_addr1_adi_income+thompson_PC1,data=abcd.data.train.harmonized)
+mod104<-lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+reshist_addr1_adi_income+thompson_PC1,data=abcd.data.test.harmonized)
+mod105<-lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+reshist_addr1_adi_income+thompson_PC1,data=abcd.data.test.harmonized)
+mod106<-lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+reshist_addr1_adi_income+thompson_PC1,data=abcd.data.test.harmonized)
+
+tab_model(mod101,mod102,mod103,pred.labels = c("Intercept","Age","Sex","Mean FD","ADI","General Cognition"),dv.labels=c("PFN 3","PFN 15","PFN 17"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = "/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/ADI_Sensitivity_TableX_Discovery.doc")
+
+tab_model(mod104,mod105,mod106,pred.labels = c("Intercept","Age","Sex","Mean FD","ADI","General Cognition"),dv.labels=c("PFN 3","PFN 15","PFN 17"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = "/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/ADI_Sensitivity_TableX_Replication.doc")
+
 ```
@@
 
+# Prep/add data for demographics table
+```{r}
+
+# exclude subjects with missing cognitive data
+abcd.data.for.ridge<-abcd.data.traintest[,c("subjectkey","thompson_PC1","thompson_PC2","thompson_PC3","matched_group","interview_age","sex","meanFD","abcd_site","rel_family_id")]
+abcd.data.traintest<-abcd.data.traintest[complete.cases(abcd.data.for.ridge),]
+
+cbcl<-read.table("/Users/askeller/Documents/Kellernet_PrelimAnalysis/aseba/abcd_cbcls01.txt",header=TRUE)
+cbcl_baseline <- cbcl[cbcl$eventname=="baseline_year_1_arm_1",c("subjectkey","cbcl_scr_syn_internal_r","cbcl_scr_syn_external_r","cbcl_scr_syn_totprob_r")]
+cbcl_baseline$cbcl_scr_syn_internal_r <- as.numeric(cbcl_baseline$cbcl_scr_syn_internal_r)
+cbcl_baseline$cbcl_scr_syn_external_r <- as.numeric(cbcl_baseline$cbcl_scr_syn_external_r)
+cbcl_baseline$cbcl_scr_syn_totprob_r <- as.numeric(cbcl_baseline$cbcl_scr_syn_totprob_r)
+
+psychMed<-read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/PsychotropicMeds/ABCD_Psychotropic_Medications.csv")
+psychMed_baseline <- psychMed[psychMed$eventname=="baseline_year_1_arm_1",c("subjectkey","ADHD_meds","Antidepressant_meds","Antipsychotic_meds")]
+psychMed_baseline$ADHD_meds<-as.factor(psychMed_baseline$ADHD_meds)
+psychMed_baseline$Antipsychotic_meds<-as.factor(psychMed_baseline$Antipsychotic_meds)
+psychMed_baseline$Antidepressant_meds<-as.factor(psychMed_baseline$Antidepressant_meds)
+
+abcd.data.traintest<-merge(abcd.data.traintest,cbcl_baseline,by="subjectkey")
+abcd.data.traintest<-merge(abcd.data.traintest,psychMed_baseline,by="subjectkey")
+
+abcd.data.traintest$ADHD_meds<-factor(abcd.data.traintest$ADHD_meds, levels = c("1","0"))
+abcd.data.traintest$Antidepressant_meds<-factor(abcd.data.traintest$Antidepressant_meds, levels = c("1","0"))
+abcd.data.traintest$Antipsychotic_meds<-factor(abcd.data.traintest$Antipsychotic_meds, levels = c("1","0"))
+
+```
+
 # Make a demographics table
 ```{r}
-# exclude subjects with missing cognitive data
-abcd.data.for.ridge<-abcd.data.traintest[,c("subjectkey","thompson_PC1","thompson_PC2","thompson_PC3","matched_group","interview_age","sex","meanFD","abcd_site","rel_family_id")]
-
-abcd.data.traintest<-abcd.data.traintest[complete.cases(abcd.data.for.ridge),]
-
 library(Gmisc)
@@
   set_column_labels(interview_age = "Age (Months)",
-                    sex = "Sex",
+                    sex = "Sex (F)",
                     race.6level = "Race",
                     household.income = "Household Income",
+                    high.educ = "Parent Education",
                     thompson_PC1 = "General Cognition",
@@
                     thompson_PC3 = "Learning/Memory",
-                    high.educ = "Parent Education") %>%
+                    ADHD_meds = "ADHD Medications",
+                    Antidepressant_meds = "Antidepressant Medication",
+                    Antipsychotic_meds = "Antipsychotic Medication",
+                    cbcl_scr_syn_internal_r = "CBCL Int.",
+                    cbcl_scr_syn_external_r = "CBCL Ext.",
+                    cbcl_scr_syn_totprob_r = "CBCL Prob.") %>%
 getDescriptionStatsBy(interview_age,
@@
                         thompson_PC3,
+                        ADHD_meds,
+                        Antidepressant_meds,
+                        Antipsychotic_meds,
+                        cbcl_scr_syn_external_r,
+                        cbcl_scr_syn_internal_r,
+                        cbcl_scr_syn_totprob_r,
                         household.income,
@@
 
+# Look for effects of SES on total cortical representation
+```{r}
+ADI_mod1<-lmer(reshist_addr1_adi_income~interview_age+sex+(1|rel_family_id)+meanFD+PFN1+PFN2+PFN3+PFN4+PFN5+PFN6+PFN7+PFN8+PFN9+PFN10+PFN11+PFN12+PFN13+PFN14+PFN15+PFN16+PFN17,data=abcd.data.train.harmonized)
+ADI_mod2<-lmer(reshist_addr1_adi_income~interview_age+sex+(1|rel_family_id)+meanFD+PFN1+PFN2+PFN3+PFN4+PFN5+PFN6+PFN7+PFN8+PFN9+PFN10+PFN11+PFN12+PFN13+PFN14+PFN15+PFN16+PFN17,data=abcd.data.test.harmonized)
+
+tab_model(ADI_mod1,ADI_mod2,pred.labels = c("Intercept","Age","Sex","Motion","PFN1","PFN2","PFN3","PFN4","PFN5","PFN6","PFN7","PFN8","PFN9","PFN10","PFN11","PFN12","PFN13","PFN14","PFN15","PFN16","PFN17"),dv.labels=c("ADI (Discovery)","ADI (Replication)"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific", file = "/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SES/ADI_by_PFN.doc")
+```
+
 ### Bar plot (Discovery Sample):
@@
 
+net_locs = c()
+for (i in 1:17){
+  net_locs <- c(net_locs,which(z_vec_sorted==i))
+}
+
 # Using 7 colors scheme for bar plot
@@
                  "#4E31A8", "#F5BA2E");
-LineType <- c("dashed", "solid", "solid", "solid", "dashed", "dashed",
-              "dashed", "dashed", "dashed", "dashed", "dashed", "dashed",
-              "dashed", "dashed", "solid", "dashed", "solid");
+LineType <- ifelse(keep_p==1,"solid","dashed");
 Fig <- ggplot(data, aes(EffectRank, CognitionEffects_Z)) +
-  geom_bar(stat = "identity", fill=c("#FFFFFF", "#7499C2", "#F5BA2E",
-                                     "#7499C2", "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF",
-                                     "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF",
-                                     "#FFFFFF", "#F5BA2E", "#FFFFFF", "#F5BA2E"), 
-           colour = BorderColor, linetype = LineType, width = 0.8) + 
+  geom_bar(stat = "identity", fill=ifelse(keep_p==1,BorderColor,"#FFFFFF"), 
+           colour = BorderColor, linetype = LineType, width = 0.8) + ylim(-8.5,5.5) +
   labs(x = "Networks", y = expression(paste("Cognition Association (", italic("Z"), ")"))) + theme_classic() +
-  theme(axis.text.x = ggtext::element_markdown(size= 27, color = BorderColor[c(4,2,11,10,1,9,5,16,14,12,7,8,13,6,3,15,17)]), 
+  theme(axis.text.x = ggtext::element_markdown(size= 27, color = BorderColor[net_locs]), 
         axis.text.y = ggtext::element_markdown(size= 33, color = "black"), 
@@
   theme(axis.text.x = ggtext::element_markdown(angle = 45, hjust = 1)) +
-  scale_x_discrete(labels = c('4','2','11','10','1','9','5','16','14','12','7','8','13','6','3','15','17'),limits = c('5','2','15','1','7','14','11','12','6','4','3','10','13','9','16','8','17')) 
+  scale_x_discrete(labels = as.character(net_locs),limits = as.character(z_vec_sorted)) 
 Fig
-ggsave('/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_032322/NetworkSize_Loading_CogEffects.tiff', width = 19, height = 16, dpi = 600, units = "cm");
+ggsave('/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_032322/NetworkSize_Loading_CogEffects_Disc_Revision.tiff', width = 19, height = 16, dpi = 600, units = "cm");
 
@@
                  "#4E31A8", "#F5BA2E");
-LineType <- c("dashed", "dashed", "solid", "solid", "dashed", "solid",
-              "dashed", "dashed", "dashed", "dashed", "dashed", "dashed",
-              "dashed", "dashed", "solid", "dashed", "solid");
+LineType <- ifelse(keep_p==1,"solid","dashed");
 Fig <- ggplot(data, aes(EffectRank, CognitionEffects_Z)) +
-  geom_bar(stat = "identity", fill=c("#FFFFFF", "#FFFFFF", "#F5BA2E",
-                                     "#7499C2", "#FFFFFF", "#AF33AD", "#FFFFFF", "#FFFFFF",
-                                     "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF",
-                                     "#FFFFFF", "#F5BA2E", "#FFFFFF", "#F5BA2E"), 
-           colour = BorderColor, linetype = LineType, width = 0.8) + 
+  geom_bar(stat = "identity", fill=ifelse(keep_p==1,BorderColor,"#FFFFFF"), 
+           colour = BorderColor, linetype = LineType, width = 0.8) + ylim(-8.5,5.5) + 
   labs(x = "Networks", y = expression(paste("Cognition Association (", italic("Z"), ")"))) + theme_classic() +
-  theme(axis.text.x = ggtext::element_markdown(size= 27, color = BorderColor[c(4,13,9,2,7,12,10,5,16,14,8,1,11,3,15,17,6)]), 
+  theme(axis.text.x = ggtext::element_markdown(size= 27, color = BorderColor[net_locs]), 
         axis.text.y = ggtext::element_markdown(size= 33, color = "black"), 
@@
   theme(axis.text.x = ggtext::element_markdown(angle = 45, hjust = 1)) +
-  scale_x_discrete(labels = c('4','13','9','2','7','12','10','5','16','14','8','1','11','3','15','17','6'),limits = c('12','4','14','1','8','17','5','11','3','7','13','6','2','10','15','9','16')) # + scale_y_continuous(limits = c(-4, 6), breaks = c(-4, -2, 0, 2, 4, 6));
+  scale_x_discrete(labels = as.character(net_locs),limits = as.character(z_vec_sorted)) 
 Fig
-ggsave('/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_032322/NetworkSize_Loading_CogEffects_test.tiff', width = 19, height = 16, dpi = 600, units = "cm");
+ggsave('/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_032322/NetworkSize_Loading_CogEffects_Rep_Revision.tiff', width = 19, height = 16, dpi = 600, units = "cm");
 
 ```
+
+# Test whether results hold with covariates for psychotropic med use:
+```{r}
+abcd.data.train.harmonized.withMeds <- merge(abcd.data.train.harmonized,abcd.data.traintest[,c("subjectkey", setdiff(colnames(abcd.data.traintest),colnames(abcd.data.train.harmonized)))],by="subjectkey")
+abcd.data.test.harmonized.withMeds <- merge(abcd.data.test.harmonized,abcd.data.traintest[,c("subjectkey", setdiff(colnames(abcd.data.traintest),colnames(abcd.data.test.harmonized)))],by="subjectkey")
+
+mod1<-lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+ADHD_meds+Antipsychotic_meds+Antidepressant_meds+thompson_PC1,data=abcd.data.train.harmonized.withMeds)
+mod2<-lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+ADHD_meds+Antipsychotic_meds+Antidepressant_meds+thompson_PC1,data=abcd.data.train.harmonized.withMeds)
+mod3<-lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+ADHD_meds+Antipsychotic_meds+Antidepressant_meds+thompson_PC1,data=abcd.data.train.harmonized.withMeds)
+mod4<-lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+ADHD_meds+Antipsychotic_meds+Antidepressant_meds+thompson_PC1,data=abcd.data.test.harmonized.withMeds)
+mod5<-lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+ADHD_meds+Antipsychotic_meds+Antidepressant_meds+thompson_PC1,data=abcd.data.test.harmonized.withMeds)
+mod6<-lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+ADHD_meds+Antipsychotic_meds+Antidepressant_meds+thompson_PC1,data=abcd.data.test.harmonized.withMeds)
+
+tab_model(mod1,mod2,mod3,pred.labels = c("Intercept","Age","Sex","Mean FD","ADHD Meds","Antipsychotic Meds","Antidepressant Meds","General Cognition"),dv.labels=c("PFN 3","PFN 15","PFN 17"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = "/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/PsychMedUse/Associations_TableX_Disc_PsychMed.doc")
+
+tab_model(mod4,mod5,mod6,pred.labels = c("Intercept","Age","Sex","Mean FD","ADHD Meds","Antipsychotic Meds","Antidepressant Meds","General Cognition"),dv.labels=c("PFN 3","PFN 15","PFN 17"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = "/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/PsychMedUse/Associations_TableX_Rep_PsychMed.doc")
+```

### 2023-04-12 Step3_RidgeResultsPlotting/compare_predicted_actual_matchedsamples.m
sensitivity analyses and hex plots

@@ -49,7 +49,7 @@ actual_PC3_samp2 = actual_PC3(data_for_ridge(:,4)==2);
 %% Load in the results for bootstrapping and null distributions
 
 % ~~~~~ NULL ~~~~~~ %
-folder_name='/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_null_081822/';
+folder_name='/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_matchedsamples_null_081822';
 file_name_acc_PC1_null_samp1='thompson_PC1_acc_null_testA.npy';
 file_name_acc_PC1_null_samp2='thompson_PC1_acc_null_testB.npy';
 file_name_acc_PC2_null_samp1='thompson_PC2_acc_null_testA.npy';
@@ -207,6 +207,82 @@ axis([-0.1 0.1 0 30])
 box off
 
 
+%% Replot the scatterplots as hexplots
+
+figure()
+
+subplot(2,3,1)
+hexscatter(actual_PC1_samp1,pred_PC1_samp1,'res',40)
+hold on
+linearFit = polyfit(actual_PC1_samp1,pred_PC1_samp1,1);
+hline = refline(linearFit);
+hline.Color=color_fill_1;
+hline.LineWidth=3;
+colormap("hot")
+xlabel("Actual Cognitive Performance",'FontSize',12)
+ylabel("Predicted Cognitive Performance",'FontSize',12)
+axis([-4 4 -4 4])
+
+subplot(2,3,4)
+hexscatter(actual_PC1_samp2,pred_PC1_samp2,'res',40)
+hold on
+linearFit = polyfit(actual_PC1_samp2,pred_PC1_samp2,1);
+hline = refline(linearFit);
+hline.Color=color_fill_1;
+hline.LineWidth=3;
+colormap("hot")
+xlabel("Actual Cognitive Performance",'FontSize',12)
+ylabel("Predicted Cognitive Performance",'FontSize',12)
+axis([-4 4 -4 4])
+
+subplot(2,3,2)
+hexscatter(actual_PC2_samp1,pred_PC2_samp1,'res',40)
+hold on
+linearFit = polyfit(actual_PC2_samp1,pred_PC2_samp1,1);
+hline = refline(linearFit);
+hline.Color=color_fill_1;
+hline.LineWidth=3;
[…]

### 2023-04-12 Step1_TotalCorticalRepresentation/Associations_PFN_Cognition.Rmd
sensitivity analyses

@@
 
-# Look for effects of SES on total cortical representation
-```{r}
-ADI_mod1<-lmer(reshist_addr1_adi_income~interview_age+sex+(1|rel_family_id)+meanFD+PFN1+PFN2+PFN3+PFN4+PFN5+PFN6+PFN7+PFN8+PFN9+PFN10+PFN11+PFN12+PFN13+PFN14+PFN15+PFN16+PFN17,data=abcd.data.train.harmonized)
-ADI_mod2<-lmer(reshist_addr1_adi_income~interview_age+sex+(1|rel_family_id)+meanFD+PFN1+PFN2+PFN3+PFN4+PFN5+PFN6+PFN7+PFN8+PFN9+PFN10+PFN11+PFN12+PFN13+PFN14+PFN15+PFN16+PFN17,data=abcd.data.test.harmonized)
-
-tab_model(ADI_mod1,ADI_mod2,pred.labels = c("Intercept","Age","Sex","Motion","PFN1","PFN2","PFN3","PFN4","PFN5","PFN6","PFN7","PFN8","PFN9","PFN10","PFN11","PFN12","PFN13","PFN14","PFN15","PFN16","PFN17"),dv.labels=c("ADI (Discovery)","ADI (Replication)"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
-Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific", file = "/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SES/ADI_by_PFN.doc")
-```
-
 ### Bar plot (Discovery Sample):

### 2023-04-12 Step6_SensitivityAnalyses/IndTask/get_data_for_ridge_IndTask.R
sensitivity analyses

@@ -1,0 +1,104 @@
+
+# First load in the spatial extent of each PFN (they're in order, 1-17)
+# Then merge with the same datasets as above (NIH toolbox, trauma, etc.)
+pfn_sizes <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/All_PFN_sizes.csv")
+# Change PFN column names so they're sensible
+colnames(pfn_sizes)<-c("subjectkey","PFN1","PFN2","PFN3","PFN4","PFN5","PFN6","PFN7","PFN8","PFN9","PFN10","PFN11","PFN12","PFN13","PFN14","PFN15","PFN16","PFN17")
+
+# Load data
+nihtb<-read.table("/Users/askeller/Documents/Kellernet_PrelimAnalysis/NihTB/abcd_tbss01.txt",header=TRUE)
+lmt<-read.table("/Users/askeller/Documents/Kellernet_PrelimAnalysis/Thomp/lmtp201.txt",header=TRUE)
+ravlt<-read.table("/Users/askeller/Documents/Kellernet_PrelimAnalysis/Thomp/abcd_ps01.txt",header=TRUE)
+
+# Convert factors to numeric values
+nihtb$nihtbx_flanker_uncorrected <- as.numeric(nihtb$nihtbx_flanker_uncorrected)
+nihtb$nihtbx_picvocab_uncorrected <- as.numeric(nihtb$nihtbx_picvocab_uncorrected)
+nihtb$nihtbx_pattern_uncorrected <- as.numeric(nihtb$nihtbx_pattern_uncorrected)
+nihtb$nihtbx_picture_uncorrected <- as.numeric(nihtb$nihtbx_picture_uncorrected)
+nihtb$nihtbx_reading_uncorrected <- as.numeric(nihtb$nihtbx_reading_uncorrected)
+nihtb$nihtbx_list_uncorrected <- as.numeric(nihtb$nihtbx_list_uncorrected)
+nihtb$nihtbx_cardsort_uncorrected <- as.numeric(nihtb$nihtbx_cardsort_uncorrected)
+lmt$lmt_scr_perc_correct <- as.numeric(lmt$lmt_scr_perc_correct)
+ravlt$pea_ravlt_sd_trial_i_tc <- as.numeric(ravlt$pea_ravlt_sd_trial_i_tc)
[…]

### 2023-04-12 Step6_SensitivityAnalyses/IndTask/keller_proc_predict_IndTask.py

@@ -1,0 +1,22 @@
+import sys
+import os
+
+homedir = sys.argv[1]
+tmpdir = sys.argv[2]
+network = sys.argv[3]
+phenotype_name = sys.argv[4]
+
+"""
+this makes the features and targets in tmpdir
+"""
+os.system('python /{0}/preprocess_IndTask.py {1} {2}'.format(homedir,network,tmpdir))
+
+working_dir = homedir + '/results_IndTask/{0}_network/'.format(network)
+feature_path = '/{0}/features_{1}.npy'.format(tmpdir,network)
+phenotype_path = '/{0}/phenotypes_target.csv'.format(tmpdir)
+control_path = '/{0}/phenotypes_control.csv'.format(tmpdir)
+
+"""
+this does the actual ridge regression
+"""
+os.system('python /{0}/predict_matchedsamples.py {1} {2} {3} {4} {5} rel_family_id'.format(homedir,working_dir,feature_path,phenotype_path,phenotype_name,control_path))

### 2023-04-12 Step6_SensitivityAnalyses/IndTask/preprocess_IndTask.py

@@ -1,0 +1,60 @@
+import glob
+import h5py
+import numpy as np
+import os
+import pandas as pd
+from sklearn import preprocessing
+import sys
+
+"""
+hi. this is going to read these in, you basically just need 
+subjects: path to subjects!
+data_path: path to the actual features
+phenotypes: path to a csv with the to-be-predicted and the noise
+"""
+data_path ='/gpfs/fs001/cbica/projects/abcdfnets/results/SingleParcel_1by1/sub-NDAR{0}/IndividualParcel_Final_sbj1_comp17_alphaS21_1_alphaL300_vxInfo1_ard0_eta0/final_UV.mat'
+control =['sex','meanFD','abcd_site','interview_age']
+try: network = int(sys.argv[1])
+except: network = sys.argv[1]
+outdir = sys.argv[2]
+os.makedirs(outdir,exist_ok=True)
+"""
+load the subject measures 
+"""
+phenotypes = pd.read_csv('/gpfs/fs001/cbica/projects/abcdfnets/data_for_ridge_IndTask.csv') #load
+#phenotypes['subjectkey'] = np.core.defchararray.strip(phenotypes.subjectkey.values.astype(str),'NDAR_') #strip
+phenotypes = phenotypes.sort_values('subjectkey') #sort 
+phenotypes['meanFD'] = phenotypes['meanFD'].values.astype(np.float16) #saves space
+
+"""
+convert categorical vars to numerical, ie dummy encoding, for sites and sex
+"""
+for c in ['sex','abcd_site']:
+    dumb = pd.get_dummies(phenotypes[c]).astype(np.int8)
+    phenotypes = pd.merge(left=phenotypes,right=dumb,left_index=True,right_index=True)
+    for d in dumb.columns:
+        control.append(d) #we get a lot more columns so we put them in
+    control.remove(c) # remove the original categorical
+
+"""
+load in all the feature weights
+"""
+features = []
+for subject in phenotypes.subjectkey.values:
+    if os.path.exists(data_path.format(subject)) == False:
+        phenotypes = phenotypes.drop(phenotypes.index[phenotypes.subjectkey==subject])
+        continue
+    f = h5py.File(data_path.format(subject), 'r')
+    f = np.array(f[f['V'][0][0]]).astype(np.float16)
+    if type(network) == int:
+        f = f[network]
+    features.append(f)
+features = np.array(features)
[…]

### 2023-04-12 Step6_SensitivityAnalyses/IndTask/submit_all_IndTask.py

@@ -1,0 +1,19 @@
+import os
+import sys
+import numpy as np
+"""
+this is the only script you actually should call, it will submit a job
+this job makes the features, and then does the regression. 
+only change the home_dir variable, everything else should run! 
+"""
+
+homedir = '/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller' #sys.argv[1] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/'
+
+tmpdir = '/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles_IndTask' #os.environ['TMPDIR']
+networks = np.array(['all']) 
+network = 'all'
+
+GB = '200G'    
+
+for cog_score in ['PicVocab','Flanker','Pattern','Reading','Picture','List','CardSort','LMT','RAVLT']:
+        os.system('qsub -l h_vmem={0},s_vmem={0} -N {1} -R y -V -j y -b y -o ~/sge/ -e ~/sge/ python {2}/keller_proc_predict_IndTask.py {2} {3} {4} {5}'.format(GB,cog_score,homedir,tmpdir,network,cog_score))

### 2023-04-12 Step6_SensitivityAnalyses/SES/get_SES_features.R

@@ -1,0 +1,68 @@
+
+# First load in the spatial extent of each PFN (they're in order, 1-17)
+# Then merge with the same datasets as above (NIH toolbox, trauma, etc.)
+pfn_sizes <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/All_PFN_sizes.csv")
+# Change PFN column names so they're sensible
+colnames(pfn_sizes)<-c("subjectkey","PFN1","PFN2","PFN3","PFN4","PFN5","PFN6","PFN7","PFN8","PFN9","PFN10","PFN11","PFN12","PFN13","PFN14","PFN15","PFN16","PFN17")
+
+# Load data
+newdata<-readRDS("/Users/askeller/Documents/Kellernet_PrelimAnalysis/DEAP-data-download_ThompsonScores_ResFamIncome.rds")
+newdata.baseline<-newdata[newdata$event_name=="baseline_year_1_arm_1",]
+colnames(newdata.baseline)[1]<-"subjectkey"
+all.data <- merge(pfn_sizes,newdata.baseline[,c("subjectkey", setdiff(colnames(newdata.baseline),colnames(pfn_sizes)))],by="subjectkey")
+
+
+# Remove subjects based on the following criteria:
+## 1) 8min of retained TRs (600 TRs)
+## 2) ABCD Booleans for rest and T1
+num_TRs <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/num_TRs_by_subj_redo.csv")
+data<-merge(all.data,num_TRs,by="subjectkey")
+data.clean<-data[data$numTRs>=600,]
+
+# Remove participants based on booleans from ABCD
+abcd_imgincl01 <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/abcd_imgincl01.csv")
+abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$eventnam=="baseline_year_1_arm_1",]
+abcd_imgincl01 <- abcd_imgincl01[!abcd_imgincl01$visit=="",] 
+abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_t1w_include==1,] 
+abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_rsfmri_include==1,]
+combined.data <- merge(data.clean,abcd_imgincl01[, c("subjectkey",'imgincl_t1w_include')],by="subjectkey") 
+
+# for simplicity, rename thompson variables
[…]

### 2023-04-12 Step6_SensitivityAnalyses/SES/keller_proc_predict_SES.py

@@ -1,0 +1,22 @@
+import sys
+import os
+
+homedir = sys.argv[1]
+tmpdir = sys.argv[2]
+network = sys.argv[3]
+phenotype_name = sys.argv[4]
+
+"""
+this makes the features and targets in tmpdir
+"""
+os.system('python /{0}/preprocess_SES.py {1} {2}'.format(homedir,network,tmpdir))
+
+working_dir = homedir + '/results_SES/{0}_network/'.format(network)
+feature_path = '/{0}/features_{1}.npy'.format(tmpdir,network)
+phenotype_path = '/{0}/phenotypes_target.csv'.format(tmpdir)
+control_path = '/{0}/phenotypes_control.csv'.format(tmpdir)
+
+"""
+this does the actual ridge regression
+"""
+os.system('python /{0}/predict_matchedsamples_SES.py {1} {2} {3} {4} {5} rel_family_id'.format(homedir,working_dir,feature_path,phenotype_path,phenotype_name,control_path))

### 2023-04-12 Step6_SensitivityAnalyses/SES/keller_proc_predict_SES_PFNs.py

@@ -1,0 +1,22 @@
+import sys
+import os
+
+homedir = sys.argv[1]
+tmpdir = sys.argv[2]
+network = sys.argv[3]
+phenotype_name = sys.argv[4]
+
+"""
+this makes the features and targets in tmpdir
+"""
+os.system('python /{0}/preprocess_SES_PFNs.py {1} {2}'.format(homedir,network,tmpdir))
+
+working_dir = homedir + '/results_SES_PFNs/{0}_network/'.format(network)
+feature_path = '/{0}/features_{1}.npy'.format(tmpdir,network)
+phenotype_path = '/{0}/phenotypes_target.csv'.format(tmpdir)
+control_path = '/{0}/phenotypes_control.csv'.format(tmpdir)
+
+"""
+this does the actual ridge regression
+"""
+os.system('python /{0}/predict_matchedsamples.py {1} {2} {3} {4} {5} rel_family_id'.format(homedir,working_dir,feature_path,phenotype_path,phenotype_name,control_path))

### 2023-04-12 Step6_SensitivityAnalyses/SES/predict_matchedsamples_SES.py

@@ -1,0 +1,108 @@
+import glob
+import h5py
+import numpy as np
+import os
+import pandas as pd
+from sklearn.linear_model import RidgeCV
+from sklearn.model_selection import GroupKFold
+from sklearn.linear_model import LinearRegression
+from sklearn import preprocessing
+import sys
+from scipy.stats import pearsonr
+
+"""
+This script will run ridge regression. To run it, you need:
+
+working_dir: where you want your results saved, does not have to exist, we will make it
+feature_path: path to the actual features, should be a subject x features npy array
+phenotype_path: path to a csv with the to-be-predicted values
+phenotype_name: str of name of column in phenotype_path you want
+control_path: path to csv, regress these features from the features within each fold
+fold_group: in this instance, this is the ABCD train and test split, A for one group, B for the other
+
+"""
+
+working_dir = sys.argv[1] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/'
+os.makedirs(working_dir,exist_ok=True)
+feature_path = sys.argv[2]  #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles/features_0.npy'
+phenotype_path = sys.argv[3] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles/phenotypes_target.csv'
+phenotype_name = sys.argv[4] #'thompson_PC1'
+control_path = sys.argv[5] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles/phenotypes_control.csv'
+fold_group = 'matched_group' #sys.argv[6] # in this instance, this is the ABCD train and test split, A for one group, B for the other
+
+"""
+load the subject measures you want to control for
+"""
+phenotypes_control = pd.read_csv(control_path)
+"""
+load in all the feature weights
+"""
+features = np.load(feature_path)
+"""
+this is adapted from pennlinckit.utils.predict
+"""
+targets = pd.read_csv(phenotype_path)[phenotype_name].values.astype(np.float16)
+fold_group = pd.read_csv(phenotype_path)[fold_group].values.astype(np.float16)
[…]

### 2023-04-12 Step6_SensitivityAnalyses/SES/preprocess_SES.py

@@ -1,0 +1,54 @@
+import glob
+import h5py
+import numpy as np
+import os
+import pandas as pd
+from sklearn import preprocessing
+import sys
+
+"""
+hi. this is going to read these in, you basically just need 
+subjects: path to subjects!
+data_path: path to the actual features
+phenotypes: path to a csv with the to-be-predicted and the noise
+"""
+data_path ='/gpfs/fs001/cbica/projects/abcdfnets/results/SingleParcel_1by1/sub-NDAR{0}/IndividualParcel_Final_sbj1_comp17_alphaS21_1_alphaL300_vxInfo1_ard0_eta0/final_UV.mat'
+control =['sex','meanFD','abcd_site','interview_age']
+try: network = int(sys.argv[1])
+except: network = sys.argv[1]
+outdir = sys.argv[2]
+os.makedirs(outdir,exist_ok=True)
+"""
+load the subject measures 
+"""
+phenotypes = pd.read_csv('/gpfs/fs001/cbica/projects/abcdfnets/data_for_ridge_SES.csv') #load
+#phenotypes['subjectkey'] = np.core.defchararray.strip(phenotypes.subjectkey.values.astype(str),'NDAR_') #strip
+phenotypes = phenotypes.sort_values('subjectkey') #sort 
+phenotypes['meanFD'] = phenotypes['meanFD'].values.astype(np.float16) #saves space
+
+"""
+convert categorical vars to numerical, ie dummy encoding, for sites and sex
+"""
+for c in ['sex','abcd_site']:
+    dumb = pd.get_dummies(phenotypes[c]).astype(np.int8)
+    phenotypes = pd.merge(left=phenotypes,right=dumb,left_index=True,right_index=True)
+    for d in dumb.columns:
+        control.append(d) #we get a lot more columns so we put them in
+    control.remove(c) # remove the original categorical
+
+"""
+load in all the feature weights
+"""
+
+
+features = []
+SESfeatures = pd.read_csv('/gpfs/fs001/cbica/projects/abcdfnets/SES_features.csv') #load
+SESfeaturesOrdered=SESfeatures[SESfeatures.subjectkey==phenotypes.subjectkey.values]['reshist_addr1_adi_income']
+features=np.array(SESfeaturesOrdered)
+features = features.reshape(features.shape[0],-1) #subject by flat array shape to be flat for sklearn
[…]

### 2023-04-12 Step6_SensitivityAnalyses/SES/preprocess_SES_PFNs.py

@@ -1,0 +1,65 @@
+import glob
+import h5py
+import numpy as np
+import os
+import pandas as pd
+from sklearn import preprocessing
+import sys
+
+"""
+hi. this is going to read these in, you basically just need 
+subjects: path to subjects!
+data_path: path to the actual features
+phenotypes: path to a csv with the to-be-predicted and the noise
+"""
+data_path ='/gpfs/fs001/cbica/projects/abcdfnets/results/SingleParcel_1by1/sub-NDAR{0}/IndividualParcel_Final_sbj1_comp17_alphaS21_1_alphaL300_vxInfo1_ard0_eta0/final_UV.mat'
+control =['sex','meanFD','abcd_site','interview_age']
+try: network = int(sys.argv[1])
+except: network = sys.argv[1]
+outdir = sys.argv[2]
+os.makedirs(outdir,exist_ok=True)
+"""
+load the subject measures 
+"""
+phenotypes = pd.read_csv('/gpfs/fs001/cbica/projects/abcdfnets/data_for_ridge_SES.csv') #load
+#phenotypes['subjectkey'] = np.core.defchararray.strip(phenotypes.subjectkey.values.astype(str),'NDAR_') #strip
+phenotypes = phenotypes.sort_values('subjectkey') #sort 
+phenotypes['meanFD'] = phenotypes['meanFD'].values.astype(np.float16) #saves space
+
+"""
+convert categorical vars to numerical, ie dummy encoding, for sites and sex
+"""
+for c in ['sex','abcd_site']:
+    dumb = pd.get_dummies(phenotypes[c]).astype(np.int8)
+    phenotypes = pd.merge(left=phenotypes,right=dumb,left_index=True,right_index=True)
+    for d in dumb.columns:
+        control.append(d) #we get a lot more columns so we put them in
+    control.remove(c) # remove the original categorical
+
+"""
+load in all the feature weights
+"""
+features = []
+for subject in phenotypes.subjectkey.values:
+    if os.path.exists(data_path.format(subject)) == False:
+        phenotypes = phenotypes.drop(phenotypes.index[phenotypes.subjectkey==subject])
+        continue
+    f = h5py.File(data_path.format(subject), 'r')
+    f = np.array(f[f['V'][0][0]]).astype(np.float16)
+    if type(network) == int:
+        f = f[network]
+    features.append(f)
+
[…]

### 2023-04-12 Step6_SensitivityAnalyses/SES/submit_all_SES.py

@@ -1,0 +1,19 @@
+import os
+import sys
+import numpy as np
+"""
+this is the only script you actually should call, it will submit a job
+this job makes the features, and then does the regression. 
+only change the home_dir variable, everything else should run! 
+"""
+
+homedir = '/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller' #sys.argv[1] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/'
+
+tmpdir = '/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles_SES/' #os.environ['TMPDIR']
+networks = np.array(['all']) 
+network = 'all'
+
+GB = '200G'    
+
+for cog_score in ['thompson_PC1','thompson_PC2','thompson_PC3']:
+        os.system('qsub -l h_vmem={0},s_vmem={0} -N {1} -R y -V -j y -b y -o ~/sge/ -e ~/sge/ python {2}/keller_proc_predict_SES.py {2} {3} {4} {5}'.format(GB,cog_score.split('_')[1],homedir,tmpdir,network,cog_score))

### 2023-04-12 Step6_SensitivityAnalyses/SES/submit_all_SES_PFNs.py

@@ -1,0 +1,19 @@
+import os
+import sys
+import numpy as np
+"""
+this is the only script you actually should call, it will submit a job
+this job makes the features, and then does the regression. 
+only change the home_dir variable, everything else should run! 
+"""
+
+homedir = '/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller' #sys.argv[1] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/'
+
+tmpdir = '/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles_SES_PFNs/' #os.environ['TMPDIR']
+networks = np.array(['all']) 
+network = 'all'
+
+GB = '200G'    
+
+for cog_score in ['thompson_PC1','thompson_PC2','thompson_PC3']:
+        os.system('qsub -l h_vmem={0},s_vmem={0} -N {1} -R y -V -j y -b y -o ~/sge/ -e ~/sge/ python {2}/keller_proc_predict_SES_PFNs.py {2} {3} {4} {5}'.format(GB,cog_score.split('_')[1],homedir,tmpdir,network,cog_score))

### 2023-04-12 Step6_SensitivityAnalyses/SeparateSamplesPCA/keller_proc_predict_SepSampPCA.py

@@ -1,0 +1,22 @@
+import sys
+import os
+
+homedir = sys.argv[1]
+tmpdir = sys.argv[2]
+network = sys.argv[3]
+phenotype_name = sys.argv[4]
+
+"""
+this makes the features and targets in tmpdir
+"""
+os.system('python /{0}/preprocess_SepSampPCA.py {1} {2}'.format(homedir,network,tmpdir))
+
+working_dir = homedir + '/results_SepSampPCA/{0}_network/'.format(network)
+feature_path = '/{0}/features_{1}.npy'.format(tmpdir,network)
+phenotype_path = '/{0}/phenotypes_target.csv'.format(tmpdir)
+control_path = '/{0}/phenotypes_control.csv'.format(tmpdir)
+
+"""
+this does the actual ridge regression
+"""
+os.system('python /{0}/predict_matchedsamples.py {1} {2} {3} {4} {5} rel_family_id'.format(homedir,working_dir,feature_path,phenotype_path,phenotype_name,control_path))

### 2023-04-12 Step6_SensitivityAnalyses/SeparateSamplesPCA/keller_proc_predict_SepSampPCA_null.py

@@ -1,0 +1,22 @@
+import sys
+import os
+
+homedir = sys.argv[1]
+tmpdir = sys.argv[2]
+network = sys.argv[3]
+phenotype_name = sys.argv[4]
+
+"""
+this makes the features and targets in tmpdir
+"""
+os.system('python /{0}/preprocess_SepSampPCA.py {1} {2}'.format(homedir,network,tmpdir))
+
+working_dir = homedir + '/results_SepSampPCA_null/{0}_network/'.format(network)
+feature_path = '/{0}/features_{1}.npy'.format(tmpdir,network)
+phenotype_path = '/{0}/phenotypes_target.csv'.format(tmpdir)
+control_path = '/{0}/phenotypes_control.csv'.format(tmpdir)
+
+"""
+this does the actual ridge regression
+"""
+os.system('python /{0}/predict_matchedsamples_null.py {1} {2} {3} {4} {5} rel_family_id'.format(homedir,working_dir,feature_path,phenotype_path,phenotype_name,control_path))

### 2023-04-12 Step6_SensitivityAnalyses/SeparateSamplesPCA/preprocess_SepSampPCA.py

@@ -1,0 +1,60 @@
+import glob
+import h5py
+import numpy as np
+import os
+import pandas as pd
+from sklearn import preprocessing
+import sys
+
+"""
+hi. this is going to read these in, you basically just need 
+subjects: path to subjects!
+data_path: path to the actual features
+phenotypes: path to a csv with the to-be-predicted and the noise
+"""
+data_path ='/gpfs/fs001/cbica/projects/abcdfnets/results/SingleParcel_1by1/sub-NDAR{0}/IndividualParcel_Final_sbj1_comp17_alphaS21_1_alphaL300_vxInfo1_ard0_eta0/final_UV.mat'
+control =['sex','meanFD','abcd_site','interview_age']
+try: network = int(sys.argv[1])
+except: network = sys.argv[1]
+outdir = sys.argv[2]
+os.makedirs(outdir,exist_ok=True)
+"""
+load the subject measures 
+"""
+phenotypes = pd.read_csv('/gpfs/fs001/cbica/projects/abcdfnets/data_for_ridge_SepSampPCA.csv') #load
+#phenotypes['subjectkey'] = np.core.defchararray.strip(phenotypes.subjectkey.values.astype(str),'NDAR_') #strip
+phenotypes = phenotypes.sort_values('subjectkey') #sort 
+phenotypes['meanFD'] = phenotypes['meanFD'].values.astype(np.float16) #saves space
+
+"""
+convert categorical vars to numerical, ie dummy encoding, for sites and sex
+"""
+for c in ['sex','abcd_site']:
+    dumb = pd.get_dummies(phenotypes[c]).astype(np.int8)
+    phenotypes = pd.merge(left=phenotypes,right=dumb,left_index=True,right_index=True)
+    for d in dumb.columns:
+        control.append(d) #we get a lot more columns so we put them in
+    control.remove(c) # remove the original categorical
+
+"""
+load in all the feature weights
+"""
+features = []
+for subject in phenotypes.subjectkey.values:
+    if os.path.exists(data_path.format(subject)) == False:
+        phenotypes = phenotypes.drop(phenotypes.index[phenotypes.subjectkey==subject])
+        continue
+    f = h5py.File(data_path.format(subject), 'r')
+    f = np.array(f[f['V'][0][0]]).astype(np.float16)
+    if type(network) == int:
+        f = f[network]
+    features.append(f)
+features = np.array(features)
[…]

### 2023-04-12 Step6_SensitivityAnalyses/SeparateSamplesPCA/submit_SepSampPCA.py

@@ -1,0 +1,23 @@
+import os
+import sys
+import numpy as np
+"""
+this is the only script you actually should call, it will submit a job
+this job makes the features, and then does the regression. 
+only change the home_dir variable, everything else should run! 
+"""
+
+homedir = '/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller' #sys.argv[1] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/'
+
+tmpdir = '/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles_SepSampPCA/' #os.environ['TMPDIR']
+networks = np.array(['all'])
+networks = np.append(networks,np.arange(0,17))
+
+for network in networks:
+    if network == 'all': 
+        GB = '200G'
+        continue
+    else: GB = '124G'
+    
+    for cog_score in ['SepSampPC1','SepSampPC2','SepSampPC3']:
+        os.system('qsub -l h_vmem={0},s_vmem={0} -N {1} -R y -V -j y -b y -o ~/sge/ -e ~/sge/ python {2}/keller_proc_predict_SepSampPCA.py {2} {3} {4} {5}'.format(GB,cog_score.split('_')[1],homedir,tmpdir,network,cog_score))

### 2023-04-12 Step6_SensitivityAnalyses/SeparateSamplesPCA/submit_all_SepSampPCA.py

@@ -1,0 +1,19 @@
+import os
+import sys
+import numpy as np
+"""
+this is the only script you actually should call, it will submit a job
+this job makes the features, and then does the regression. 
+only change the home_dir variable, everything else should run! 
+"""
+
+homedir = '/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller' #sys.argv[1] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/'
+
+tmpdir = '/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles_SepSampPCA/' #os.environ['TMPDIR']
+networks = np.array(['all']) 
+network = 'all'
+
+GB = '200G'    
+
+for cog_score in ['SepSampPC1','SepSampPC2','SepSampPC3']:
+        os.system('qsub -l h_vmem={0},s_vmem={0} -N {1} -R y -V -j y -b y -o ~/sge/ -e ~/sge/ python {2}/keller_proc_predict_SepSampPCA.py {2} {3} {4} {5}'.format(GB,cog_score,homedir,tmpdir,network,cog_score))

### 2023-04-12 Step6_SensitivityAnalyses/SeparateSamplesPCA/submit_all_SepSampPCA_null.py

@@ -1,0 +1,19 @@
+import os
+import sys
+import numpy as np
+"""
+this is the only script you actually should call, it will submit a job
+this job makes the features, and then does the regression. 
+only change the home_dir variable, everything else should run! 
+"""
+
+homedir = '/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller' #sys.argv[1] #'/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/'
+
+tmpdir = '/cbica/projects/abcdfnets/scripts/keller_ridge/pennlinc-regression/example_keller/tempfiles_SepSampPCA_null/' #os.environ['TMPDIR']
+networks = np.array(['all']) 
+network = 'all'
+
+GB = '200G'    
+
+for cog_score in ['SepSampPC1','SepSampPC2','SepSampPC3']:
+        os.system('qsub -l h_vmem={0},s_vmem={0} -N {1} -R y -V -j y -b y -o ~/sge/ -e ~/sge/ python {2}/keller_proc_predict_SepSampPCA_null.py {2} {3} {4} {5}'.format(GB,cog_score,homedir,tmpdir,network,cog_score))

### 2023-04-12 Step6_SensitivityAnalyses/IndTask/compare_predicted_actual_IndTask.m
sensitivity analyses

@@ -1,0 +1,271 @@
+
+% NOTE: this script is meant to be run with the matlab GUI to make figures
+
+clear all
+
+% Add package to read NPY files into matlab
+addpath('/Users/askeller/Documents/npy-matlab/')
+
+% List the cognitive variables:
+cog_vars = {'PicVocab','Flanker','Pattern','Reading','Picture','List','CardSort','LMT','RAVLT'};
+
+% Specify results folder and data_for_ridge file location
+folder_name='/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/IndTask/results/all_network/';
+data_for_ridge=xlsread('/Users/askeller/Documents/Kellernet_PrelimAnalysis/Keller_PFNsCognition_Codebase_Revision/Step6_SensitivityAnalyses/IndTask/data_for_ridge_IndTask.xls');
+% note: column order is this "PicVocab","Flanker","Pattern","Reading","Picture","LMT","RAVLT","matched_group","interview_age","sex","meanFD","abcd_site","rel_family_id"
+
+% Loop through each outcome variable
+for cog = 1:length(cog_vars)
+
+% Load in prediction results
+eval(['file_name_samp1=''' char(cog_vars(cog)) '_prediction_testA.npy'';'])
+eval(['file_name_samp2=''' char(cog_vars(cog)) '_prediction_testB.npy'';'])
+eval(['pred_' char(cog_vars(cog)) '_samp1 = readNPY([folder_name ''/'' file_name_samp1]);'])
+eval(['pred_' char(cog_vars(cog)) '_samp2 = readNPY([folder_name ''/'' file_name_samp2]);'])
+
+end
+
+
+% Load in actual cognitive scores and split by matched group
+actual_PicVocab_samp1 = data_for_ridge(data_for_ridge(:,10)==1,1);
+actual_Flanker_samp1 = data_for_ridge(data_for_ridge(:,10)==1,2);
+actual_Pattern_samp1 = data_for_ridge(data_for_ridge(:,10)==1,3);
+actual_Reading_samp1 = data_for_ridge(data_for_ridge(:,10)==1,4);
[…]

### 2023-04-12 Step6_SensitivityAnalyses/RestingStateOnly/Associations_PFN_Cognition_Rest.Rmd
sensitivity analyses

--- 2022-09-16 Step1_TotalCorticalRepresentation/Associations_PFN_Cognition.Rmd
@@
 ```{r}
-pfn_sizes <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/All_PFN_sizes.csv") # n=9,132
+pfn_sizes <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/All_PFN_sizes_Rest_082122.csv")
 # Change PFN column names so they're sensible
@@
 tab_model(mod1,mod2,mod3,pred.labels = c("Intercept","Age","Sex","Mean FD","General Cognition"),dv.labels=c("PFN 3","PFN 15","PFN 17"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
-Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = "/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/Associations_TableX_Discovery.doc")
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = "/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/RestSensitivity/Rest_Associations_Table_Discovery.doc")
 
 tab_model(mod4,mod5,mod6,pred.labels = c("Intercept","Age","Sex","Mean FD","General Cognition"),dv.labels=c("PFN 3","PFN 15","PFN 17"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std.
-Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = "/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/Associations_TableX_Replication.doc")
+Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = "/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/RestSensitivity/Rest_Associations_Table_Replication.doc")
 ```
@@
 
-# Make a demographics table
-```{r}
-# exclude subjects with missing cognitive data
-abcd.data.for.ridge<-abcd.data.traintest[,c("subjectkey","thompson_PC1","thompson_PC2","thompson_PC3","matched_group","interview_age","sex","meanFD","abcd_site","rel_family_id")]
-
-abcd.data.traintest<-abcd.data.traintest[complete.cases(abcd.data.for.ridge),]
-
-library(Gmisc)
-demo_table <- abcd.data.traintest %>%
-  mutate(matched_group = factor(matched_group, levels = 1:2, labels = c("Discovery", "Replication"))) %>%
-#subset(matched_group<3) %>%
-  set_column_labels(interview_age = "Age (Months)",
-                    sex = "Sex",
-                    race.6level = "Race",
-                    household.income = "Household Income",
-                    thompson_PC1 = "General Cognition",
-                    thompson_PC2 = "Executive Function",
-                    thompson_PC3 = "Learning/Memory",
-                    high.educ = "Parent Education") %>%
-getDescriptionStatsBy(interview_age, 
-                        sex,
-                        thompson_PC1,
-                        thompson_PC2,
-                        thompson_PC3,
-                        household.income,
-                        race.6level,
-                        high.educ,
-                        add_total_col = TRUE, statistics=TRUE,
-                        by = matched_group)
-
-demo_table
-```
-
 # make figures to replicate Cui et al.
@@
 correlation<-cor.test(abcd.data.train.harmonized$thompson_PC1,abcd.data.train.harmonized$PFN17)
-png("/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_032322/PC1_PFN17_train.png",
+png("/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/RestSensitivity/Rest_PC1_PFN17_train.png",
     width = 3000, 
@@
 correlation<-cor.test(abcd.data.train.harmonized$thompson_PC1,abcd.data.train.harmonized$PFN15)
-png("/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_032322/PC1_PFN15_train.png",
+png("/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/RestSensitivity/Rest_PC1_PFN15_train.png",
     width = 3000, 
@@
 correlation<-cor.test(abcd.data.test.harmonized$thompson_PC1,abcd.data.test.harmonized$PFN17)
-png("/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_032322/PC1_PFN17_test.png",
+png("/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/RestSensitivity/Rest_PC1_PFN17_test.png",
     width = 3000, 
@@
 correlation<-cor.test(abcd.data.test.harmonized$thompson_PC1,abcd.data.test.harmonized$PFN15)
-png("/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_032322/PC1_PFN15_test.png",
+png("/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/RestSensitivity/Rest_PC1_PFN15_test.png",
     width = 3000, 
@@
 correlation<-cor.test(abcd.data.train.harmonized$thompson_PC1,abcd.data.train.harmonized$PFN3)
-png("/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_032322/PC1_PFN3_train.png",
+png("/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/RestSensitivity/Rest_PC1_PFN3_train.png",
     width = 3000, 
@@
 correlation<-cor.test(abcd.data.test.harmonized$thompson_PC1,abcd.data.test.harmonized$PFN3)
-png("/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_032322/PC1_PFN3_test.png",
+png("/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/RestSensitivity/Rest_PC1_PFN3_test.png",
     width = 3000, 
@@
                  "#4E31A8", "#F5BA2E");
-LineType <- c("dashed", "solid", "solid", "solid", "dashed", "dashed",
-              "dashed", "dashed", "dashed", "dashed", "dashed", "dashed",
-              "dashed", "dashed", "solid", "dashed", "solid");
+LineType <- ifelse(keep_p==1,"solid","dashed");
 Fig <- ggplot(data, aes(EffectRank, CognitionEffects_Z)) +
-  geom_bar(stat = "identity", fill=c("#FFFFFF", "#7499C2", "#F5BA2E",
-                                     "#7499C2", "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF",
-                                     "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF",
-                                     "#FFFFFF", "#F5BA2E", "#FFFFFF", "#F5BA2E"), 
+  geom_bar(stat = "identity", fill=ifelse(keep_p==1,BorderColor,"#FFFFFF"), 
            colour = BorderColor, linetype = LineType, width = 0.8) + 
   labs(x = "Networks", y = expression(paste("Cognition Association (", italic("Z"), ")"))) + theme_classic() +
-  theme(axis.text.x = ggtext::element_markdown(size= 27, color = BorderColor[c(4,2,11,10,1,9,5,16,14,12,7,8,13,6,3,15,17)]), 
+  theme(axis.text.x = ggtext::element_markdown(size= 27, color = BorderColor[net_locs]), 
         axis.text.y = ggtext::element_markdown(size= 33, color = "black"), 
@@
   theme(axis.text.x = ggtext::element_markdown(angle = 45, hjust = 1)) +
-  scale_x_discrete(labels = c('4','2','11','10','1','9','5','16','14','12','7','8','13','6','3','15','17'),limits = c('5','2','15','1','7','14','11','12','6','4','3','10','13','9','16','8','17')) 
+  scale_x_discrete(labels = as.character(net_locs),limits = as.character(z_vec_sorted))+scale_y_discrete(limits=c(-4,4)) 
 Fig
-ggsave('/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_032322/NetworkSize_Loading_CogEffects.tiff', width = 19, height = 16, dpi = 600, units = "cm");
+ggsave('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/RestSensitivity/Rest_NetworkSize_Loading_CogEffects_Disc.tiff', width = 19, height = 16, dpi = 600, units = "cm");
 
@@
                  "#4E31A8", "#F5BA2E");
-LineType <- c("dashed", "dashed", "solid", "solid", "dashed", "solid",
-              "dashed", "dashed", "dashed", "dashed", "dashed", "dashed",
-              "dashed", "dashed", "solid", "dashed", "solid");
+LineType <- ifelse(keep_p==1,"solid","dashed");
 Fig <- ggplot(data, aes(EffectRank, CognitionEffects_Z)) +
-  geom_bar(stat = "identity", fill=c("#FFFFFF", "#FFFFFF", "#F5BA2E",
-                                     "#7499C2", "#FFFFFF", "#AF33AD", "#FFFFFF", "#FFFFFF",
-                                     "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF",
-                                     "#FFFFFF", "#F5BA2E", "#FFFFFF", "#F5BA2E"), 
+  geom_bar(stat = "identity", fill=ifelse(keep_p==1,BorderColor,"#FFFFFF"), 
            colour = BorderColor, linetype = LineType, width = 0.8) + 
   labs(x = "Networks", y = expression(paste("Cognition Association (", italic("Z"), ")"))) + theme_classic() +
-  theme(axis.text.x = ggtext::element_markdown(size= 27, color = BorderColor[c(4,13,9,2,7,12,10,5,16,14,8,1,11,3,15,17,6)]), 
+  theme(axis.text.x = ggtext::element_markdown(size= 27, color = BorderColor[net_locs]), 
         axis.text.y = ggtext::element_markdown(size= 33, color = "black"), 
@@
   theme(axis.text.x = ggtext::element_markdown(angle = 45, hjust = 1)) +
-  scale_x_discrete(labels = c('4','13','9','2','7','12','10','5','16','14','8','1','11','3','15','17','6'),limits = c('12','4','14','1','8','17','5','11','3','7','13','6','2','10','15','9','16')) # + scale_y_continuous(limits = c(-4, 6), breaks = c(-4, -2, 0, 2, 4, 6));
+  scale_x_discrete(labels = as.character(net_locs),limits = as.character(z_vec_sorted))+scale_y_discrete(limits=c(-4,4)) 
 Fig
-ggsave('/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_032322/NetworkSize_Loading_CogEffects_test.tiff', width = 19, height = 16, dpi = 600, units = "cm");
+ggsave('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/RestSensitivity/Rest_NetworkSize_Loading_CogEffects_Rep.tiff', width = 19, height = 16, dpi = 600, units = "cm");
 

### 2023-04-12 Step6_SensitivityAnalyses/RestingStateOnly/compare_predicted_actual_rest.m

@@ -1,0 +1,320 @@
+
+clear all
+
+% Add package to read NPY files into matlab
+addpath('/Users/askeller/Documents/npy-matlab/')
+
+folder_name='/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_rest_Aug22';
+file_name_pred1='thompson_PC1_prediction.npy';
+file_name_pred2='thompson_PC2_prediction.npy';
+file_name_pred3='thompson_PC3_prediction.npy';
+
+pred_PC1 = readNPY([folder_name '/' file_name_pred1]);
+pred_PC2 = readNPY([folder_name '/' file_name_pred2]);
+pred_PC3 = readNPY([folder_name '/' file_name_pred3]);
+
+% put predictions on same scale as actual
+pred_PC1 = zscore(pred_PC1);
+pred_PC2 = zscore(pred_PC2);
+pred_PC3 = zscore(pred_PC3);
+
+
+
+actual_PC1=xlsread('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_rest_Aug22/targets_PC1.xls');
+actual_PC2=xlsread('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_rest_Aug22/targets_PC2.xls');
+actual_PC3=xlsread('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RidgeResults/results_rest_Aug22/targets_PC3.xls');
+
+
+% fourth column has the matched_group
+data_for_ridge=xlsread('/Users/askeller/Documents/Kellernet_PrelimAnalysis/data_for_ridge_Rest_081122.xls');
+
+% split data out by matched group to match Fig 7 in Cui 2020
+pred_PC1_samp1 = pred_PC1(data_for_ridge(:,4)==1);
+pred_PC1_samp2 = pred_PC1(data_for_ridge(:,4)==2);
+pred_PC2_samp1 = pred_PC2(data_for_ridge(:,4)==1);
+pred_PC2_samp2 = pred_PC2(data_for_ridge(:,4)==2);
+pred_PC3_samp1 = pred_PC3(data_for_ridge(:,4)==1);
[…]

### 2023-04-12 Step6_SensitivityAnalyses/RestingStateOnly/get_data_for_ridge_restOnlyPFNs.R

@@ -1,0 +1,89 @@
+
+library(tidyr)
+library(dplyr)
+library(readr)
+
+# First load in the spatial extent of each PFN (they're in order, 1-17)
+# Then merge with the same datasets as above (NIH toolbox, trauma, etc.)
+pfn_sizes <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/All_PFN_sizes_Rest_082122.csv")
+# Change PFN column names so they're sensible
+colnames(pfn_sizes)<-c("subjectkey","PFN1","PFN2","PFN3","PFN4","PFN5","PFN6","PFN7","PFN8","PFN9","PFN10","PFN11","PFN12","PFN13","PFN14","PFN15","PFN16","PFN17")
+
+
+# Load data
+newdata<-readRDS("/Users/askeller/Documents/Kellernet_PrelimAnalysis/DEAP-data-download_ThompsonScores_ResFamIncome.rds")
+newdata.baseline<-newdata[newdata$event_name=="baseline_year_1_arm_1",]
+colnames(newdata.baseline)[1]<-"subjectkey"
+all.data <- merge(pfn_sizes,newdata.baseline[,c("subjectkey", setdiff(colnames(newdata.baseline),colnames(pfn_sizes)))],by="subjectkey")
+
+
+
+# Remove subjects based on the following criteria:
+## 1) 8min of retained TRs (600 TRs)
+## 2) ABCD Booleans for rest and T1
+num_TRs <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/num_TRs_by_subj_redo.csv")
+data<-merge(all.data,num_TRs,by="subjectkey")
+data.clean<-data[data$numTRs>=600,] # we go from 7,493 to 7,245 at this step
+
+# Remove participants based on booleans from ABCD
+abcd_imgincl01 <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/abcd_imgincl01.csv")
+abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$eventnam=="baseline_year_1_arm_1",]
+abcd_imgincl01 <- abcd_imgincl01[!abcd_imgincl01$visit=="",] # start here with 11,663
+abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_t1w_include==1,] # down to 11,124
+abcd_imgincl01 <- abcd_imgincl01[abcd_imgincl01$imgincl_rsfmri_include==1,] # down to 9,388
+
[…]

### 2023-04-12 Step6_SensitivityAnalyses/SeparateSamplesPCA/SeparateSamplesCognitionPCA.Rmd
sensitivity analyses

---
title: "SeparateSamplesCognitionPCA"
output: html_document
date: '2023-02-02'
---

# Load in libraries
```{r}
library(mvtnorm)
library(tableone)
library(parallel)
library(rstan)
library(loo)
library(gamm4)
library(Hmisc)
library(FactoMineR)
library(nFactors)
library(reshape2)
library(psych)
library(data.table)
library(mice)
library(abind)
library(cvTools)
library(modEvA)
```

# Load data:
```{r}
nihtb<-read.table("/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SeparateSamplesCognitionPCA/data/abcd_tbss01.txt",header=TRUE)
lmt<-read.table("/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SeparateSamplesCognitionPCA/data/lmtp201.txt",header=TRUE)
ravlt<-read.table("/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SeparateSamplesCognitionPCA/data/abcd_ps01.txt",header=TRUE)
site_info <- readRDS("/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SeparateSamplesCognitionPCA/data/DEAP-siteID.rds")
colnames(site_info)[1]<-"subjectkey"
matched_samples<-read_tsv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SeparateSamplesCognitionPCA/data/participants.tsv")
matched_samples.baseline<-matched_samples[matched_samples$session_id=="ses-baselineYear1Arm1",c("participant_id","matched_group")]
colnames(matched_samples.baseline)[1]<-c("subjectkey")
matched_samples.baseline$subjectkey <- gsub(pattern="sub-NDAR",replacement="NDAR_", matched_samples.baseline$subjectkey)
matched_samples.baseline<-matched_samples.baseline %>% distinct()
matched_samples.baseline<-matched_samples.baseline[!duplicated(matched_samples.baseline$subjectkey),] # remove duplicated subject
data_for_ridge<-read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SeparateSamplesCognitionPCA/data/data_for_ridge_032822_subIDwithNDAR.csv")
data_for_ridge<-data_for_ridge[!duplicated(data_for_ridge$subjectkey),]
subj_to_include<-data.frame(data_for_ridge[,"subjectkey"])
colnames(subj_to_include)[1]<-"subjectkey"
```

# Convert factors to numeric values
```{r}
nihtb$nihtbx_flanker_uncorrected <- as.numeric(nihtb$nihtbx_flanker_uncorrected)
nihtb$nihtbx_picvocab_uncorrected <- as.numeric(nihtb$nihtbx_picvocab_uncorrected)
nihtb$nihtbx_pattern_uncorrected <- as.numeric(nihtb$nihtbx_pattern_uncorrected)
nihtb$nihtbx_picture_uncorrected <- as.numeric(nihtb$nihtbx_picture_uncorrected)
nihtb$nihtbx_reading_uncorrected <- as.numeric(nihtb$nihtbx_reading_uncorrected)
nihtb$nihtbx_list_uncorrected <- as.numeric(nihtb$nihtbx_list_uncorrected)
nihtb$nihtbx_cardsort_uncorrected <- as.numeric(nihtb$nihtbx_cardsort_uncorrected)
lmt$lmt_scr_perc_correct <- as.numeric(lmt$lmt_scr_perc_correct)
ravlt$pea_ravlt_sd_trial_i_tc <- as.numeric(ravlt$pea_ravlt_sd_trial_i_tc)
ravlt$pea_ravlt_sd_trial_ii_tc <- as.numeric(ravlt$pea_ravlt_sd_trial_ii_tc)
ravlt$pea_ravlt_sd_trial_iii_tc <- as.numeric(ravlt$pea_ravlt_sd_trial_iii_tc)
ravlt$pea_ravlt_sd_trial_iv_tc <- as.numeric(ravlt$pea_ravlt_sd_trial_iv_tc)
ravlt$pea_ravlt_sd_trial_v_tc <- as.numeric(ravlt$pea_ravlt_sd_trial_v_tc)
```

# Extract necessary cognition columns for just the baseline data
```{r}
nihtb_keep <- nihtb[nihtb$eventname=="baseline_year_1_arm_1",c("subjectkey","nihtbx_picvocab_uncorrected","nihtbx_flanker_uncorrected","nihtbx_pattern_uncorrected","nihtbx_reading_uncorrected","nihtbx_picture_uncorrected","nihtbx_list_uncorrected","nihtbx_cardsort_uncorrected")]
lmt_keep <- lmt[lmt$eventname=="baseline_year_1_arm_1",c("subjectkey","lmt_scr_perc_correct")]
ravlt_keep <- ravlt[ravlt$eventname=="baseline_year_1_arm_1",c("subjectkey","pea_ravlt_sd_trial_i_tc","pea_ravlt_sd_trial_ii_tc","pea_ravlt_sd_trial_iii_tc","pea_ravlt_sd_trial_iv_tc","pea_ravlt_sd_trial_v_tc")]
```

# for RAVLT we need to generate a summed score (code borrowed from Thompson et al. 2019):
```{r}
ind_pea_ravlt = c(which(names(ravlt_keep)=="pea_ravlt_sd_trial_i_tc"),which(names(ravlt_keep)=="pea_ravlt_sd_trial_ii_tc"),
                  which(names(ravlt_keep)=="pea_ravlt_sd_trial_iii_tc"),which(names(ravlt_keep)=="pea_ravlt_sd_trial_iv_tc"),
                  which(names(ravlt_keep)=="pea_ravlt_sd_trial_v_tc")); names(ravlt_keep)[ind_pea_ravlt]; summary(ravlt_keep[,ind_pea_ravlt])
ravlt_keep$RAVLT <- apply(ravlt_keep[,ind_pea_ravlt],1,sum)
```

# Combine cognitive variables into a dataframe:
```{r}
merged_cognition1<-merge(nihtb_keep,lmt_keep,by="subjectkey")
merged_cognition_final<-merge(merged_cognition1,ravlt_keep,by="subjectkey")
```

# Add in the family, site, and sample info:
```{r}
site_info_keep <- site_info[site_info$event_name=="baseline_year_1_arm_1",c("subjectkey","abcd_site","rel_family_id")]
all_sample_info <- merge(site_info_keep,matched_samples.baseline,by="subjectkey")
data_for_pca <- merge(all_sample_info,merged_cognition_final,by="subjectkey")
```

# Drop unneeded RAVLT columns, and rename all the columns
```{r}
data_for_pca_use <- data_for_pca[,c("subjectkey","abcd_site","rel_family_id","matched_group","nihtbx_picvocab_uncorrected","nihtbx_flanker_uncorrected","nihtbx_pattern_uncorrected","nihtbx_reading_uncorrected","nihtbx_picture_uncorrected","nihtbx_list_uncorrected","nihtbx_cardsort_uncorrected","lmt_scr_perc_correct","RAVLT")]
colnames(data_for_pca_use)<-c("subjectkey","Site","Family","MatchedGroup","PicVocab","Flanker","Pattern","Reading","Picture","List","CardSort","LMT","RAVLT")
data_for_pca_comp<-data_for_pca_use[complete.cases(data_for_pca_use),]
```

### IMPORTANT NOTE HERE: 3 participants who were included in the original n=6,972 do not have complete data and are therefore excluded from this analysis. Final sample will be n=6,969.

# Reduce subject list to match the imaging sample for this paper
```{r}
data_for_pca_final<-merge(data_for_pca_comp,subj_to_include,by="subjectkey")
```

# Split the sample into Discovery and Replication
```{r}
data_for_pca_Disc <- data_for_pca_final[data_for_pca_final$MatchedGroup==1,]
data_for_pca_Rep <- data_for_pca_final[data_for_pca_final$MatchedGroup==2,]
```

# Get indices for the cognitive variables, and check that they're correct
```{r}
ind_cog = c(which(names(data_for_pca_final)=="PicVocab"),which(names(data_for_pca_final)=="Flanker"),
           which(names(data_for_pca_final)=="Pattern"),which(names(data_for_pca_final)=="Picture"),
           which(names(data_for_pca_final)=="Reading"),which(names(data_for_pca_final)=="List"),
           which(names(data_for_pca_final)=="CardSort"),which(names(data_for_pca_final)=="RAVLT"),
           which(names(data_for_pca_final)=="LMT")); names(data_for_pca_final)[ind_cog]
```

# Run a simple PCA on the DISCOVERY dataset and REPLICATION dataset separately
### ASK checked the initial version of this in the full sample on 11/18/22 and verified that the top 3 tasks loading onto the top 3 PC's are the same as for the Thompson et al. 2019 factor scores
```{r}
ind_Y = ind_cog; names(data_for_pca_Disc)[ind_Y]
Y_Disc = as.matrix(scale(data_for_pca_Disc[complete.cases(data_for_pca_Disc[,c(ind_Y)]),ind_Y]))
ev_Disc = eigen(cor(Y_Disc))
ap_Disc = parallel(subject=nrow(Y_Disc),var=ncol(Y_Disc),rep=100,cent=.05)
nS_Disc = nScree(x=ev_Disc$values,aparallel=ap_Disc$eigen$qevpea)
plotnScree(nS_Disc)
ncomp = 3
y.pca.Disc = psych::principal(Y_Disc, rotate="varimax", nfactors=ncomp, scores=TRUE)
y.pca.Disc$loadings

ind_Y = ind_cog; names(data_for_pca_Rep)[ind_Y]
Y_Rep = as.matrix(scale(data_for_pca_Rep[complete.cases(data_for_pca_Rep[,c(ind_Y)]),ind_Y]))
ev_Rep = eigen(cor(Y_Rep))
ap_Rep = parallel(subject=nrow(Y_Rep),var=ncol(Y_Rep),rep=100,cent=.05)
nS_Rep = nScree(x=ev_Rep$values,aparallel=ap_Rep$eigen$qevpea)
plotnScree(nS_Rep)
ncomp = 3
y.pca.Rep = psych::principal(Y_Rep, rotate="varimax", nfactors=ncomp, scores=TRUE)
y.pca.Rep$loadings
```

# Save out the scores for each PC
```{r}
data_for_pca_Disc$SepSampPC1<-y.pca.Disc$scores[,1]
data_for_pca_Disc$SepSampPC2<-y.pca.Disc$scores[,2]
data_for_pca_Disc$SepSampPC3<-y.pca.Disc$scores[,3]

data_for_pca_Rep$SepSampPC1<-y.pca.Rep$scores[,1]
data_for_pca_Rep$SepSampPC2<-y.pca.Rep$scores[,2]
data_for_pca_Rep$SepSampPC3<-y.pca.Rep$scores[,3]

pca_input_and_results <- rbind(data_for_pca_Disc,data_for_pca_Rep)
pca_results <- pca_input_and_results[,c("subjectkey","SepSampPC1","SepSampPC2","SepSampPC3")]
data_for_ridge_6969<-merge(data_for_ridge,pca_results,by="subjectkey")
```

# Check the correlations between the Thompson scores and the separate sample PCA scores
### correlations are 0.970, 0.985 and 0.975 respectively
```{r}
cor.test(data_for_ridge_6969$thompson_PC1,data_for_ridge_6969$SepSampPC1)
cor.test(data_for_ridge_6969$thompson_PC2,data_for_ridge_6969$SepSampPC2)
cor.test(data_for_ridge_6969$thompson_PC3,data_for_ridge_6969$SepSampPC3)
```

# Create a data for ridge file that can be used to run ridge regressions using these new PC scores instead of the Thompson scores as a sensitivity analysis
```{r}
data_for_ridge_SepSampPCA<-data_for_ridge_6969[,c("subjectkey","SepSampPC1","SepSampPC2","SepSampPC3","matched_group","interview_age","sex","meanFD","abcd_site","rel_family_id")]
data_for_ridge_SepSampPCA$subjectkey<-gsub(pattern="NDAR_INV",replacement="INV", data_for_ridge_SepSampPCA$subjectkey)
write.csv(data_for_ridge_SepSampPCA,"/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SeparateSamplesCognitionPCA/data_for_ridge_SepSampPCA.csv")

```

### 2023-04-12 Step6_SensitivityAnalyses/SeparateSamplesPCA/SepSamp_pred_acc_by_PFN.m

@@ -1,0 +1,238 @@
+%% calculate prediction accuracy within each network.
+
+clear all
+
+% Add package to read NPY files into matlab
+addpath('/Users/askeller/Documents/npy-matlab/')
+
+% fourth column has the matched_group
+data_for_ridge=xlsread('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SeparateSamplesCognitionPCA/data_for_ridge_SepSampPCA.xls');
+
+% Load in actual cognitive scores
+actual_PC1 = data_for_ridge(:,1);
+actual_PC2 = data_for_ridge(:,2);
+actual_PC3 = data_for_ridge(:,3);
+
+% split data out by matched group
+actual_PC1_samp1 = actual_PC1(data_for_ridge(:,4)==1);
+actual_PC1_samp2 = actual_PC1(data_for_ridge(:,4)==2);
+actual_PC2_samp1 = actual_PC2(data_for_ridge(:,4)==1);
+actual_PC2_samp2 = actual_PC2(data_for_ridge(:,4)==2);
+actual_PC3_samp1 = actual_PC3(data_for_ridge(:,4)==1);
+actual_PC3_samp2 = actual_PC3(data_for_ridge(:,4)==2);
+
+% decision was to combine across the samples, so we will concatenate:
+actual_PC1 = [actual_PC1_samp1; actual_PC1_samp2];
+actual_PC2 = [actual_PC2_samp1; actual_PC2_samp2];
+actual_PC3 = [actual_PC3_samp1; actual_PC3_samp2];
+
+
+% matrix to collect R values by PFN
+Rvals_byPFN = zeros(17,3);
+
+
+% loop through each PFN and calculate the R value
+for eachPFN = 0:16
+
+eval(['folder_name=''/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SeparateSamplesCognitionPCA/results/' num2str(eachPFN) '_network'';'])
+
+% Load the predicted cognitive scores from the ridge regression
+file_name_pred1_samp1='SepSampPC1_prediction_testA.npy';
+file_name_pred2_samp1='SepSampPC2_prediction_testA.npy';
+file_name_pred3_samp1='SepSampPC3_prediction_testA.npy';
[…]

### 2023-04-12 Step6_SensitivityAnalyses/SeparateSamplesPCA/SepSamp_pred_acc_by_PFN_workbench.R

@@ -1,0 +1,47 @@
+
+
+library(gifti)
+library(R.matlab)
+library(RNifti)
+library(ciftiTools)
+ciftiTools.setOption('wb_path', '/Users/askeller/Documents/workbench/')
+library(ggplot2)
+
+PFNs_hardparcel<-read_cifti('/Users/askeller/Documents/Kellernet_PrelimAnalysis/hardparcel_group.dscalar.nii')
+map_predacc_PC1_lh <- PFNs_hardparcel$data$cortex_left
+map_predacc_PC1_rh <- PFNs_hardparcel$data$cortex_right
+map_predacc_PC2_lh <- PFNs_hardparcel$data$cortex_left
+map_predacc_PC2_rh <- PFNs_hardparcel$data$cortex_right
+map_predacc_PC3_lh <- PFNs_hardparcel$data$cortex_left
+map_predacc_PC3_rh <- PFNs_hardparcel$data$cortex_right
+
+pred_acc <- readMat('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SeparateSamplesCognitionPCA/results/SepSampPCA_pred_acc_by_PFN.mat');
+pred_acc <- pred_acc$Rvals.byPFN
+
+for (PFN in 1:17) {
+    map_predacc_PC1_lh[map_predacc_PC1_lh==PFN,1]=pred_acc[PFN,1]
+    map_predacc_PC2_lh[map_predacc_PC2_lh==PFN,1]=pred_acc[PFN,2]
+    map_predacc_PC3_lh[map_predacc_PC3_lh==PFN,1]=pred_acc[PFN,3]
+    
+    map_predacc_PC1_rh[map_predacc_PC1_rh==PFN,1]=pred_acc[PFN,1]
+    map_predacc_PC2_rh[map_predacc_PC2_rh==PFN,1]=pred_acc[PFN,2]
+    map_predacc_PC3_rh[map_predacc_PC3_rh==PFN,1]=pred_acc[PFN,3]
+}
+
+PFNs_hardparcel_PredAccPC1 <- PFNs_hardparcel
+PFNs_hardparcel_PredAccPC2 <- PFNs_hardparcel
+PFNs_hardparcel_PredAccPC3 <- PFNs_hardparcel
+
+PFNs_hardparcel_PredAccPC1$data$cortex_left <- map_predacc_PC1_lh
[…]

### 2023-04-12 Step6_SensitivityAnalyses/SES/compare_predicted_actual_matchedsamples_SES.m
sensitivity analyses

@@ -1,0 +1,182 @@
+
+% NOTE: this script is meant to be run with the matlab GUI to make figures
+
+clear all
+
+% Add package to read NPY files into matlab
+addpath('/Users/askeller/Documents/npy-matlab/')
+
+
+%% Get predicted scores -- NULL model (ADI only)
+
+% Load in prediction results
+folder_name='/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SES/Results/ADI_Null';
+file_name_pred1_samp1_null='thompson_PC1_prediction_testA.npy';
+file_name_pred2_samp1_null='thompson_PC2_prediction_testA.npy';
+file_name_pred3_samp1_null='thompson_PC3_prediction_testA.npy';
+file_name_pred1_samp2_null='thompson_PC1_prediction_testB.npy';
+file_name_pred2_samp2_null='thompson_PC2_prediction_testB.npy';
+file_name_pred3_samp2_null='thompson_PC3_prediction_testB.npy';
+pred_PC1_samp1_null = readNPY([folder_name '/' file_name_pred1_samp1_null]);
+pred_PC2_samp1_null = readNPY([folder_name '/' file_name_pred2_samp1_null]);
+pred_PC3_samp1_null = readNPY([folder_name '/' file_name_pred3_samp1_null]);
+pred_PC1_samp2_null = readNPY([folder_name '/' file_name_pred1_samp2_null]);
+pred_PC2_samp2_null = readNPY([folder_name '/' file_name_pred2_samp2_null]);
+pred_PC3_samp2_null = readNPY([folder_name '/' file_name_pred3_samp2_null]);
+
+% put predictions on same scale as actual
+pred_PC1_samp1_null = zscore(pred_PC1_samp1_null);
+pred_PC2_samp1_null = zscore(pred_PC2_samp1_null);
+pred_PC3_samp1_null = zscore(pred_PC3_samp1_null);
+pred_PC1_samp2_null = zscore(pred_PC1_samp2_null);
+pred_PC2_samp2_null = zscore(pred_PC2_samp2_null);
+pred_PC3_samp2_null = zscore(pred_PC3_samp2_null);
+
+
[…]

### 2023-04-12 Step6_SensitivityAnalyses/SplitHalfReliability/splithalf_ICCs.Rmd
split half reliability

---
title: "SplitHalf_ICC"
output: html_document
date: '2023-01-25'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(psych)
library(reshape2)
library(gifti)
library(RNifti)
library(ciftiTools)
ciftiTools.setOption('wb_path', '/Users/askeller/Documents/workbench/')
library(ggplot2)

```

# Load in the csvs

```{r}
sub1_Va<-read.csv('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/SingleParcel_1by1_SH/finalV_csvs/sub1_Va.csv',header=FALSE)
sub1_Vb<-read.csv('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/SingleParcel_1by1_SH/finalV_csvs/sub1_Vb.csv',header=FALSE)
sub2_Va<-read.csv('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/SingleParcel_1by1_SH/finalV_csvs/sub2_Va.csv',header=FALSE)
sub2_Vb<-read.csv('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/SingleParcel_1by1_SH/finalV_csvs/sub2_Vb.csv',header=FALSE)
sub3_Va<-read.csv('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/SingleParcel_1by1_SH/finalV_csvs/sub3_Va.csv',header=FALSE)
sub3_Vb<-read.csv('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/SingleParcel_1by1_SH/finalV_csvs/sub3_Vb.csv',header=FALSE)
sub4_Va<-read.csv('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/SingleParcel_1by1_SH/finalV_csvs/sub4_Va.csv',header=FALSE)
sub4_Vb<-read.csv('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/SingleParcel_1by1_SH/finalV_csvs/sub4_Vb.csv',header=FALSE)
sub5_Va<-read.csv('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/SingleParcel_1by1_SH/finalV_csvs/sub5_Va.csv',header=FALSE)
sub5_Vb<-read.csv('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/SingleParcel_1by1_SH/finalV_csvs/sub5_Vb.csv',header=FALSE)
sub6_Va<-read.csv('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/SingleParcel_1by1_SH/finalV_csvs/sub6_Va.csv',header=FALSE)
sub6_Vb<-read.csv('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/SingleParcel_1by1_SH/finalV_csvs/sub6_Vb.csv',header=FALSE)
sub7_Va<-read.csv('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/SingleParcel_1by1_SH/finalV_csvs/sub7_Va.csv',header=FALSE)
sub7_Vb<-read.csv('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/SingleParcel_1by1_SH/finalV_csvs/sub7_Vb.csv',header=FALSE)
sub8_Va<-read.csv('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/SingleParcel_1by1_SH/finalV_csvs/sub8_Va.csv',header=FALSE)
sub8_Vb<-read.csv('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/SingleParcel_1by1_SH/finalV_csvs/sub8_Vb.csv',header=FALSE)
sub9_Va<-read.csv('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/SingleParcel_1by1_SH/finalV_csvs/sub9_Va.csv',header=FALSE)
sub9_Vb<-read.csv('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/SingleParcel_1by1_SH/finalV_csvs/sub9_Vb.csv',header=FALSE)
sub10_Va<-read.csv('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/SingleParcel_1by1_SH/finalV_csvs/sub10_Va.csv',header=FALSE)
sub10_Vb<-read.csv('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/SingleParcel_1by1_SH/finalV_csvs/sub10_Vb.csv',header=FALSE)
```

# Compute ICC
```{r}
ICC_results <- c()

for (sub in 1:10){
  ICCs_sub <- c()

  if (sub == 1){
    Va <- sub1_Va
    Vb <- sub1_Vb
  } else if (sub == 2){
      Va <- sub2_Va
      Vb <- sub2_Vb
  } else if (sub == 3){
      Va <- sub3_Va
      Vb <- sub3_Vb
  } else if (sub == 4){
      Va <- sub4_Va
      Vb <- sub4_Vb 
  } else if (sub == 5){
      Va <- sub5_Va
      Vb <- sub5_Vb 
  } else if (sub == 6){
      Va <- sub6_Va
      Vb <- sub6_Vb 
  } else if (sub == 7){
      Va <- sub7_Va
      Vb <- sub7_Vb 
  } else if (sub == 8){
      Va <- sub8_Va
      Vb <- sub8_Vb 
  } else if (sub == 9){
      Va <- sub9_Va
      Vb <- sub9_Vb 
  } else if (sub == 10){
      Va <- sub10_Va
      Vb <- sub10_Vb 
    }

  for (network in 1:17){
    result<-ICC(data.frame(Va[,network],Vb[,network]))$results$ICC[2]
    ICCs_sub <- c(ICCs_sub,result)
  }
  ICC_results <- rbind(ICC_results,ICCs_sub)
}

# Save results (the above step takes a while to run)
write.csv(ICC_results,'/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/ICCresults_10subj_17PFNs.csv')
```

# Just load it in
```{r}
ICC_results<-read.csv('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/ICCresults_10subj_17PFNs.csv')
```

# Plot results

```{r}
ICC_results_df <- data.frame(ICC_results)
colnames(ICC_results_df)<-c("Default Mode (1)","Somatomotor (2)","Fronto-Parietal (3)","Somatomotor (4)","Dorsal Attention (5)","Visual (6)","Ventral Attention (7)","Default Mode (8)","Ventral Attention (9)","Visual (10)","Somatomotor (11)","Default Mode (12)","Somatomotor (13)","Dorsal Attention (14)","Fronto-Parietal (15)","Auditory (16)","Fronto-Parietal (17)")

ICC_results_melted<-melt(ICC_results_df)
ICC_results_melted$subject<-rep(1:10,17)
colnames(ICC_results_melted)<-c("PFN","ICC","Participant")

ggplot(ICC_results_melted,aes(x=ICC))+geom_histogram()+theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))

ggplot(ICC_results_melted,aes(x=Participant,y=ICC))+geom_point()+scale_x_discrete(limits=c(1:10))+facet_wrap(~PFN)
```
# Make workbench file to create a brainmap of average ICC by network:
```{r}
PFNs_hardparcel<-read_cifti('/Users/askeller/Documents/Kellernet_PrelimAnalysis/hardparcel_group.dscalar.nii')
map_ICC_lh <- PFNs_hardparcel$data$cortex_left
map_ICC_rh <- PFNs_hardparcel$data$cortex_right

for (PFN in 1:17) {
    map_ICC_lh[map_ICC_lh==PFN,1]=mean(ICC_results[,PFN])
    map_ICC_rh[map_ICC_rh==PFN,1]=mean(ICC_results[,PFN])
}

PFNs_hardparcel_ICC <- PFNs_hardparcel
PFNs_hardparcel_ICC$data$cortex_left <- map_ICC_lh
PFNs_hardparcel_ICC$data$cortex_right <- map_ICC_rh

write_cifti(PFNs_hardparcel_ICC,'/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/PFNs_HardParcel_ICC')
```

### 2023-04-12 Step6_SensitivityAnalyses/SplitHalfReliability/splithalf_reliability.m

@@ -1,0 +1,33 @@
+
+% This script will load in the split-half reliability data from Adam on 10
+% subjects from ABCD. Goal is to compute similarity between them.
+
+% Set directory and subject list
+cd('/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/SingleParcel_1by1_SH/')
+subjList = {'sub-NDARINV3MTP07E9','sub-NDARINVG2PGTD44','sub-NDARINVE2GEK6A2','sub-NDARINVU9C9ZMKM','sub-NDARINV581KGKG6','sub-NDARINVK7B15B7Z','sub-NDARINVEBMR55XD','sub-NDARINVZ174YN3F','sub-NDARINV8720DP0M','sub-NDARINVRDJX9GRE'}; 
+%saved_rs = [];
+
+% Loop through each subject and extract UV matrices for part A and part B
+for eachSubj = 1:10
+
+eval(['finalUV_a = load(''/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/SingleParcel_1by1_SH/' char(subjList(eachSubj)) 'a/IndividualParcel_Final_sbj1_comp17_alphaS21_1_alphaL300_vxInfo1_ard0_eta0/final_UV.mat'');'])
+eval(['finalUV_b = load(''/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/SingleParcel_1by1_SH/' char(subjList(eachSubj)) 'b/IndividualParcel_Final_sbj1_comp17_alphaS21_1_alphaL300_vxInfo1_ard0_eta0/final_UV.mat'');'])
+
+V_a = double(cell2mat(finalUV_a.V));
+V_b = double(cell2mat(finalUV_b.V));
+
+
+%[r,p]=corrcoef(V_a,V_b);
+%saved_rs = [saved_rs r(1,2)];
+
+eval(['csvwrite(''/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/SingleParcel_1by1_SH/finalV_csvs/sub' num2str(eachSubj) '_Va.csv'',V_a)'])
[…]

### 2023-04-12 Step6_SensitivityAnalyses/SizeByPredAcc/PFN_Size_By_PredAcc.Rmd
sensitivity analyses

---
title: "PFN_Size_By_PredAcc"
output: html_document
date: '2023-01-31'
---

```{r}
library(gifti)
library(R.matlab)
library(RNifti)
library(ciftiTools)
ciftiTools.setOption('wb_path', '/Users/askeller/Documents/workbench/')
library(ggplot2)
```

# Load in the data
```{r}
PFNs_hardparcel<-read_cifti('/Users/askeller/Documents/Kellernet_PrelimAnalysis/hardparcel_group.dscalar.nii')

pred_acc <- readMat('/Users/askeller/Documents/Kellernet_PrelimAnalysis/pred_acc_by_PFN.mat');
pred_acc <- pred_acc$Rvals.byPFN

```

# Get total size for each PFN from the hard parcellation
```{r}
PFNsize <- c()

for (PFN in 1:17) {
 PFNsize <- c(PFNsize,sum(PFNs_hardparcel$data$cortex_left==PFN)+sum(PFNs_hardparcel$data$cortex_right==PFN))
}

PFNsize_predacc <- data.frame(pred_acc,PFNsize)
colnames(PFNsize_predacc)<-c("PC1","PC2","PC3","Size")
```

# Make a plot of prediction accuracy by PFN size
```{r}
png("/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SizeByPredAcc/Size_By_PredAcc_PC1.png",
    width = 2600, 
    height = 3100,
    res=1200)
ggplot(data=PFNsize_predacc,aes(Size,PC1))+geom_point(size=1,colour=rgb(33/255,80/255,113/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('General Cognition Pred Acc') + xlab('PFN Size')
dev.off()

png("/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SizeByPredAcc/Size_By_PredAcc_PC2.png",
    width = 2600, 
    height = 3100,
    res=1200)
ggplot(data=PFNsize_predacc,aes(Size,PC2))+geom_point(size=1,colour=rgb(33/255,80/255,113/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Executive Function Pred Acc') + xlab('PFN Size')
dev.off()

png("/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SizeByPredAcc/Size_By_PredAcc_PC3.png",
    width = 2600, 
    height = 3100,
    res=1200)
ggplot(data=PFNsize_predacc,aes(Size,PC3))+geom_point(size=1,colour=rgb(33/255,80/255,113/255))+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('Learning/Memory Pred Acc') + xlab('PFN Size')
dev.off() 
```

# Prediction accuracy by PFN size correlations
```{r}
cor.test(PFNsize_predacc$Size,PFNsize_predacc$PC1)
cor.test(PFNsize_predacc$Size,PFNsize_predacc$PC2)
cor.test(PFNsize_predacc$Size,PFNsize_predacc$PC3)
```

# Now test the association between PFN size and S-A axis rank:
```{r}
# Get PFN hard parcel assignment in fsaverage5 space
# Load in gifti files with PFN hard parcel assignment
PFNs_gii_L<-read_gifti('/Users/askeller/Documents/Kellernet_PrelimAnalysis/SpinTests/hardparcel_LH.fsaverage5.label.gii')
PFNs_gii_R<-read_gifti('/Users/askeller/Documents/Kellernet_PrelimAnalysis/SpinTests/hardparcel_RH.fsaverage5.label.gii')
# Note: range of values is 1-17 for the right hemisphere but 1-16 for the left hemisphere (network 17 is right lateralized)

# Extract the list of ranks
PFNs_L <- PFNs_gii_L[["data"]][["labels"]]
PFNs_R <- PFNs_gii_R[["data"]][["labels"]]

# Get S-A axis rank by PFN in fsaverage5 space
# Load in gifti files with S-A axis ranks in fsaverage5 from Val's github repo
SA_axis_gii_L<-read_gifti('/Users/askeller/Documents/Kellernet_PrelimAnalysis/SpinTests/SensorimotorAssociation_Axis_LH.fsaverage5.func.gii')
SA_axis_gii_R<-read_gifti('/Users/askeller/Documents/Kellernet_PrelimAnalysis/SpinTests/SensorimotorAssociation_Axis_RH.fsaverage5.func.gii')

# Extract the list of ranks
SA_L <- SA_axis_gii_L[["data"]][["normal"]]
SA_R <- SA_axis_gii_R[["data"]][["normal"]]

SArank_byPFN <- vector()

for (i in 1:17) {
SArank_byPFN[i] <- mean(c(SA_L[PFNs_L==i],SA_R[PFNs_R==i]))
}
```

# S-A rank by PFN size correlation
```{r}
cor.test(SArank_byPFN,PFNsize_predacc$Size)
PFNsize_predacc$SArank<-SArank_byPFN

# Make a plot of prediction accuracy by PFN size
png("/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SizeByPredAcc/Size_By_SArank2.png",
    width = 3900, 
    height = 3100,
    res=1200)
ggplot(data=PFNsize_predacc,aes(Size,SArank,color=SArank))+geom_point(size=1)+geom_smooth(method=lm,colour='black')+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +ylab('S-A Axis Rank') + xlab('PFN Size') + scale_color_gradient2(low = "goldenrod1", mid = "#f9f7fa", high = "#6f1282", aesthetics = "color", name = NULL,midpoint=26287) 
dev.off() 
```

### 2023-04-20 Step1_TotalCorticalRepresentation/Associations_PFN_Cognition.Rmd
Update Associations_PFN_Cognition.Rmd

@@
 abcd.data.noPFNsCog <- subset(abcd.data.train,select=-c(PFN1,PFN2,PFN3,PFN4,PFN5,PFN6,PFN7,PFN8,PFN9,PFN10,PFN11,PFN12,PFN13,PFN14,PFN15,PFN16,PFN17,thompson_PC1,thompson_PC2,thompson_PC3,meanFD))
-abcd.data.train.harmonized <- cbind(abcd.data.noPFNsCog,dat.harmonized) # Add the harmonized data back into the main dataframe (BE AWARE THAT NOT ALL DATA IS HARMONIZED)
+abcd.data.train.harmonized <- cbind(abcd.data.noPFNsCog,dat.harmonized) # Add the harmonized data back into the main dataframe
 

### 2023-04-20 Step1_TotalCorticalRepresentation/Associations_PFN_Cognition.Rmd
added comments

@@
 
+# load in CBCL data for internalizing, externalizing, and problem behavior symptoms
 cbcl<-read.table("/Users/askeller/Documents/Kellernet_PrelimAnalysis/aseba/abcd_cbcls01.txt",header=TRUE)
@@
 
+# load in psychotropic medication data (assessed by the Medication Inventory from the PhenX instrument and coded according to Shoval et al., 2021)
 psychMed<-read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/PsychotropicMeds/ABCD_Psychotropic_Medications.csv")
@@
 
+# merge dataframes
 abcd.data.traintest<-merge(abcd.data.traintest,cbcl_baseline,by="subjectkey")
@@
 
+# code medication use as a factor
 abcd.data.traintest$ADHD_meds<-factor(abcd.data.traintest$ADHD_meds, levels = c("1","0"))
@@
 ```{r}
+# merge data frames
 abcd.data.train.harmonized.withMeds <- merge(abcd.data.train.harmonized,abcd.data.traintest[,c("subjectkey", setdiff(colnames(abcd.data.traintest),colnames(abcd.data.train.harmonized)))],by="subjectkey")

### 2023-04-20 Step3_RidgeResultsPlotting/compare_predicted_actual_matchedsamples.m
added a comment on polyfit

@@ -86,6 +86,7 @@ acc_PC3_boot_null = readNPY([folder_name '/' file_name_acc_PC3_boot_null]);
 
 
 %% Plotting
+% Note that "polyfit" with the third input variable set to 1 provides a linear fit to the data.
 
 % load colors
 color_fill = gray(10);

### 2023-05-14 Step6_SensitivityAnalyses/SplitHalfReliability/splithalf_ICCs.Rmd
Update splithalf_ICCs.Rmd
added comment on line 96

@@
 write.csv(ICC_results,'/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/ICCresults_10subj_17PFNs.csv') 
+## Note: remove first column of this csv (containing only strings of "ICCs_sub") before loading the results back in below
 ```
